### 2019-03-04 social_closeness_dishonesty.Rmd
PDF document

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Documents/R/github_Said/social_closeness/social_closeness_dishonesty_files/svm-latex-ms.tex
title: "Social Closeness and Dishonesty"
thanks: "Replication files are available on the author's Github account..."
author:
- name: Said E. Jiménez
  affiliation: Universidad Nacional Autónoma de México
- name: Roberto Mercadillo
  affiliation: Universidad Autónoma Metropolitana
- name: Eduardo Garza-Villarreal
  affiliation: Instituto Nacional de Psiquiatría Ramón de la Fuente Muñiz
abstract: "This document provides an introduction to R Markdown, argues for its..."
keywords: "pandoc, r markdown, knitr"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
# spacing: double
bibliography: ~/Dropbox/master.bib
biblio-style: apsr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-03-04 social_closeness_dishonesty.tex
PDF document

\documentclass[12pt,]{article}
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}

  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}

\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center

\renewenvironment{abstract}
 {{%
    \setlength{\leftmargin}{0mm}
    \setlength{\rightmargin}{\leftmargin}%
  }%
  \relax}
 {\endlist}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother

\setcounter{secnumdepth}{0}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

\title{Social Closeness and Dishonesty \thanks{Replication files are available on the author's Github account\ldots{}}  }

\author{\Large Said E. Jiménez\vspace{0.05in} \newline\normalsize\emph{Universidad Nacional Autónoma de México}   \and \Large Roberto Mercadillo\vspace{0.05in} \newline\normalsize\emph{Universidad Autónoma Metropolitana}   \and \Large Eduardo Garza-Villarreal\vspace{0.05in} \newline\normalsize\emph{Instituto Nacional de Psiquiatría Ramón de la Fuente Muñiz}  }

\date{}

\usepackage{titlesec}

\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\itshape}
\titleformat*{\subsubsection}{\normalsize\itshape}
\titleformat*{\paragraph}{\normalsize\itshape}
\titleformat*{\subparagraph}{\normalsize\itshape}

\usepackage{natbib}
\bibliographystyle{apsr}
\usepackage[strings]{underscore} % protect underscores in most circumstances

\newtheorem{hypothesis}{Hypothesis}
\usepackage{setspace}

\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \PassOptionsToPackage{hyphens}{url}\usepackage[unicode=true]{hyperref}
\fi
}

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Said E. Jiménez (Universidad Nacional Autónoma de México) and Roberto Mercadillo (Universidad Autónoma Metropolitana) and Eduardo Garza-Villarreal (Instituto Nacional de Psiquiatría Ramón de la Fuente Muñiz)},
             pdfkeywords = {pandoc, r markdown, knitr},  
            pdftitle={Social Closeness and Dishonesty},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

% add tightlist ----------
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

% \pagenumbering{arabic}% resets `page` counter to 1 
%
% \maketitle

{% \usefont{T1}{pnc}{m}{n}
\setlength{\parindent}{0pt}
\thispagestyle{plain}
{\fontsize{18}{20}\selectfont\raggedright 
\maketitle  % title \par

}

{
   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
\textbf{\authorfont Said E. Jiménez} \hskip 15pt \emph{\small Universidad Nacional Autónoma de México}   \par \textbf{\authorfont Roberto Mercadillo} \hskip 15pt \emph{\small Universidad Autónoma Metropolitana}   \par \textbf{\authorfont Eduardo Garza-Villarreal} \hskip 15pt \emph{\small Instituto Nacional de Psiquiatría Ramón de la Fuente Muñiz}

}

}

\begin{abstract}

    \hbox{\vrule height .2pt width 39.14pc}

    \vskip 8.5pt % \small

\noindent This document provides an introduction to R Markdown, argues for
its\ldots{}

\vskip 8.5pt \noindent \emph{Keywords}: pandoc, r markdown, knitr \par

    \hbox{\vrule height .2pt width 39.14pc}

\end{abstract}

\vskip 6.5pt

\noindent  \subsection{R Markdown}\label{r-markdown}

This is an R Markdown document. Markdown is a simple formatting syntax
for authoring HTML, PDF, and MS Word documents. For more details on
using R Markdown see \url{http://rmarkdown.rstudio.com}.

When you click the \textbf{Knit} button a document will be generated
that includes both content as well as the output of any embedded R code
chunks within the document. You can embed an R code chunk like this:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(cars)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      speed           dist       
##  Min.   : 4.0   Min.   :  2.00  
##  1st Qu.:12.0   1st Qu.: 26.00  
##  Median :15.0   Median : 36.00  
##  Mean   :15.4   Mean   : 42.98  
##  3rd Qu.:19.0   3rd Qu.: 56.00  
##  Max.   :25.0   Max.   :120.00
\end{verbatim}

\subsection{Including Plots}\label{including-plots}

You can also embed plots, for example:

\includegraphics{social_closeness_dishonesty_files/figure-latex/pressure-1.pdf}

Note that the \texttt{echo\ =\ FALSE} parameter was added to the code
chunk to prevent printing of the R code that generated the plot.
\newpage
\singlespacing 
\bibliography{\textasciitilde{}/Dropbox/master.bib}
\end{document}

### 2019-03-04 Manuscript/social_closeness_dishonesty.Rmd
Plots
Adding plots into separate files

--- 2019-03-04 social_closeness_dishonesty.Rmd
@@
     latex_engine: pdflatex
-    template: ~/Documents/R/github_Said/social_closeness/social_closeness_dishonesty_files/svm-latex-ms.tex
+    template: ~/Documents/R/github_Said/social_closeness/Manuscript/social_closeness_dishonesty_files/svm-latex-ms.tex
 title: "Social Closeness and Dishonesty"

### 2019-03-04 figures.R

@@ -1,0 +1,57 @@
+
+# Figures -----------------------------------------------------------------
+
+
+# Packages ----------------------------------------------------------------
+
+
+library(pacman)
+p_load(magrittr, dplyr, forcats, tidyr, modelr, tidybayes,
+       ggstance, ggridges, rstan, brms, tidyverse, bayesplot, rjags)
+
+
+
+# Data --------------------------------------------------------------------
+
+load("social_closeness.RData")
+
+
+# Figure 1 ----------------------------------------------------------------
+ggsave("f1.tiff",
+       path = "~/Documents/R/github_Said/social_closeness/Manuscript/figures/",
+       plot = g1,
+       device = "tiff",
+       width = 9,
+       height = 7,
+       units = "in")
+
+
+# Saving multiple plots into separate files -------------------------------
+
+g <- mget(ls(pattern = "g")) 
+
+invisible(
+  mapply(ggsave, 
+         path = "~/Documents/R/github_Said/social_closeness/Manuscript/figures/",
+         device = "tiff",
+         width = 9.5,
+         height = 7,
+         units = "in",
+         file = paste0(names(g), ".tiff"),
+         plot = g)
+  )
+
+
+# Ploting mixtures --------------------------------------------------------
+
+load("mixture_promise.RData")
+
+ggsave("g16.tiff",
+       path = "~/Documents/R/github_Said/social_closeness/Manuscript/figures/",
+       plot = thetas,
+       device = "tiff",
+       width = 9.5,
+       height = 7,
+       units = "in")
+
+

### 2019-03-04 Manuscript/social_closeness_dishonesty.Rmd
From tiff to jpeg
.

--- 2019-03-04 social_closeness_dishonesty.Rmd
@@
     latex_engine: pdflatex
-    template: ~/Documents/R/github_Said/social_closeness/social_closeness_dishonesty_files/svm-latex-ms.tex
+    template: ~/Documents/R/github_Said/social_closeness/Manuscript/social_closeness_dishonesty_files/svm-latex-ms.tex
 title: "Social Closeness and Dishonesty"
-thanks: "Replication files are available on the author's Github account..."
+thanks: "Replication files are available on the author's Github account https://github.com/saidejp/social_closeness"
 author:
@@
 abstract: "This document provides an introduction to R Markdown, argues for its..."
-keywords: "pandoc, r markdown, knitr"
+keywords: "dishonesty, bayesian hierarchical modeling, mixture modeling"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 fontsize: 12pt
+fig_caption: yes
 # spacing: double
@@
 knitr::opts_chunk$set(echo = TRUE)
+
 ```
 
-## R Markdown
+# Introduction
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+bla bla...
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+# Method
 
-```{r cars}
-summary(cars)
-```
+![Rates](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g1.jpeg)
 
-## Including Plots
+![Rates by partner](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g2.jpeg)
 
-You can also embed plots, for example:
+![Rates by partners and promise condition](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g3.jpeg)
 
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
+![Promises](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g4.jpeg)
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+![Bayesians logistic coefficients](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g5.jpeg)
+
+![Linear population predictor](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g6.jpeg)
+
+![Linear population predictor by subject](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g7.jpeg)
+
+![Population coefficient with uncertainty](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g8.jpeg)
+
+![Model adjusted by subject](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9.jpeg)
+
+![Two latent thetas](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g16.jpeg)
+
+![Subjects from two latent thetas](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g10.jpeg)
+
+![Strategies by group](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g11.jpeg)
+
+![Rates by group](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12.jpeg)
+
+![Rates by group and promise condition](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b.jpeg)
+
+![Reaction times by group](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g13.jpeg)
+
+![Reaction times by partner](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g14.jpeg)
+
+![Difference between groups in reaction time](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g15.jpeg)

### 2019-03-04 Manuscript/social_closeness_dishonesty.tex
From tiff to jpeg
.

--- 2019-03-04 social_closeness_dishonesty.tex
@@
 
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-
 \usepackage{graphicx,grffile}
@@
 
-\title{Social Closeness and Dishonesty \thanks{Replication files are available on the author's Github account\ldots{}}  }
+\title{Social Closeness and Dishonesty \thanks{Replication files are available on the author's Github account
+\url{https://github.com/saidejp/social_closeness}}  }
 
@@
 Jiménez (Universidad Nacional Autónoma de México) and Roberto Mercadillo (Universidad Autónoma Metropolitana) and Eduardo Garza-Villarreal (Instituto Nacional de Psiquiatría Ramón de la Fuente Muñiz)},
-             pdfkeywords = {pandoc, r markdown, knitr},  
+             pdfkeywords = {dishonesty, bayesian hierarchical modeling, mixture modeling},  
             pdftitle={Social Closeness and Dishonesty},
@@
 
-\vskip 8.5pt \noindent \emph{Keywords}: pandoc, r markdown, knitr \par
+\vskip 8.5pt \noindent \emph{Keywords}: dishonesty, bayesian hierarchical modeling, mixture modeling \par
 
@@
 
-\noindent  \subsection{R Markdown}\label{r-markdown}
+\noindent  \section{Introduction}\label{introduction}
 
-This is an R Markdown document. Markdown is a simple formatting syntax
-for authoring HTML, PDF, and MS Word documents. For more details on
-using R Markdown see \url{http://rmarkdown.rstudio.com}.
+bla bla\ldots{}
 
-When you click the \textbf{Knit} button a document will be generated
-that includes both content as well as the output of any embedded R code
-chunks within the document. You can embed an R code chunk like this:
+\section{Method}\label{method}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{summary}\NormalTok{(cars)}
-\end{Highlighting}
-\end{Shaded}
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g1.jpeg}
+\caption{Rates}
+\end{figure}
 
-\begin{verbatim}
-##      speed           dist       
-##  Min.   : 4.0   Min.   :  2.00  
-##  1st Qu.:12.0   1st Qu.: 26.00  
-##  Median :15.0   Median : 36.00  
-##  Mean   :15.4   Mean   : 42.98  
-##  3rd Qu.:19.0   3rd Qu.: 56.00  
-##  Max.   :25.0   Max.   :120.00
-\end{verbatim}
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g2.jpeg}
+\caption{Rates by partner}
+\end{figure}
 
-\subsection{Including Plots}\label{including-plots}
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g3.jpeg}
+\caption{Rates by partners and promise condition}
+\end{figure}
 
-You can also embed plots, for example:
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g4.jpeg}
+\caption{Promises}
+\end{figure}
 
-\includegraphics{social_closeness_dishonesty_files/figure-latex/pressure-1.pdf}
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g5.jpeg}
+\caption{Bayesians logistic coefficients}
+\end{figure}
 
-Note that the \texttt{echo\ =\ FALSE} parameter was added to the code
-chunk to prevent printing of the R code that generated the plot.
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g6.jpeg}
+\caption{Linear population predictor}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g7.jpeg}
+\caption{Linear population predictor by subject}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g8.jpeg}
+\caption{Population coefficient with uncertainty}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9.jpeg}
+\caption{Model adjusted by subject}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g16.jpeg}
+\caption{Two latent thetas}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g10.jpeg}
+\caption{Subjects from two latent thetas}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g11.jpeg}
+\caption{Strategies by group}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12.jpeg}
+\caption{Rates by group}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b.jpeg}
+\caption{Rates by group and promise condition}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g13.jpeg}
+\caption{Reaction times by group}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g14.jpeg}
+\caption{Reaction times by partner}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g15.jpeg}
+\caption{Difference between groups in reaction time}
+\end{figure}
 \newpage

### 2019-03-04 figures.R

@@ -33,11 +33,11 @@ g <- mget(ls(pattern = "g"))
 invisible(
   mapply(ggsave, 
          path = "~/Documents/R/github_Said/social_closeness/Manuscript/figures/",
-         device = "tiff",
-         width = 9.5,
+         device = "jpeg",
+         width = 10,
          height = 7,
          units = "in",
-         file = paste0(names(g), ".tiff"),
+         file = paste0(names(g), ".jpeg"),
          plot = g)
   )
 
@@ -46,11 +46,11 @@ invisible(
 
 load("mixture_promise.RData")
 
-ggsave("g16.tiff",
+ggsave("g16.jpeg",
        path = "~/Documents/R/github_Said/social_closeness/Manuscript/figures/",
        plot = thetas,
-       device = "tiff",
-       width = 9.5,
+       device = "jpeg",
+       width = 10,
        height = 7,
        units = "in")
 

### 2019-03-05 Manuscript/social_closeness_dishonesty.Rmd
.

--- 2019-03-04 social_closeness_dishonesty.Rmd
@@
 ---
+# Template adapted from:http://svmiller.com/blog/2016/02/svm-r-markdown-manuscript/
+
 output: 
@@
 fontsize: 12pt
+# fig_caption: yes
 # spacing: double
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE,
+                      warning = FALSE,
+                      error = FALSE,
+                      message = FALSE,
+                      out.width = '80%',
+                      fig.align = 'center',
+                      dpi = 300)
+
+library(pacman)
+p_load(magrittr, dplyr, forcats, tidyr, modelr, tidybayes,
+       ggstance, ggridges, rstan, brms, tidyverse, bayesplot,
+       rjags)
+
 ```
 
-## R Markdown
+# Introduction
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+bla bla...
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+# Method
 
-```{r cars}
-summary(cars)
+![Difference between groups in reaction time](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g1.jpeg)
+
+```{r g1, fig.cap='Difference between groups in reaction time'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g1.jpeg")
+
 ```
 
-## Including Plots
+```{r g2, fig.cap='Rates by partner'}
 
-You can also embed plots, for example:
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g2.jpeg")
 
-```{r pressure, echo=FALSE}
-plot(pressure)
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r g3, fig.cap='Rates by partners and promise condition'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g3.jpeg")
+
+```
+
+```{r g4, fig.cap='Promises'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g4.jpeg")
+
+```
+
+```{r g5, fig.cap='Bayesians logistic coefficients'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g5.jpeg")
+
+```
+
+```{r g6, fig.cap='Linear population predictor'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g6.jpeg")
+
+```
+
+```{r g7, fig.cap='Linear population predictor by subject'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g7.jpeg")
+
+```
+
+```{r g8, fig.cap='Population coefficient with uncertainty'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g8.jpeg")
+
+```
+
+```{r g9, fig.cap='Model adjusted by subject'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9.jpeg")
+
+```
+
+```{r g16, fig.cap='Two latent thetas'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g16.jpeg")
+
+```
+
+```{r g10, fig.cap='Subjects from two latent thetas'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g10.jpeg")
+
+```
+
+```{r g11, fig.cap='Strategies by group'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g11.jpeg")
+
+```
+
+```{r g12, fig.cap='Rates by group'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12.jpeg")
+
+```
+
+```{r g12_b, fig.cap='Rates by group and promise condition'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b.jpeg")
+
+```
+
+```{r g13, fig.cap='Reaction times by group'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g13.jpeg")
+
+```
+
+```{r g14, fig.cap='Reaction times by partner'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g14.jpeg")
+
+```
+
+```{r g15, fig.cap='Difference between groups in reaction time'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g15.jpeg")
+
+```

### 2019-03-05 Manuscript/social_closeness_dishonesty.tex
.

@@
 \includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g1.jpeg}
-\caption{Rates}
+\caption{Difference between groups in reaction time}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g2.jpeg}
-\caption{Rates by partner}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g1}
+
+}
+
+\caption{Difference between groups in reaction time}\label{fig:g1}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g3.jpeg}
-\caption{Rates by partners and promise condition}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g2}
+
+}
+
+\caption{Rates by partner}\label{fig:g2}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g4.jpeg}
-\caption{Promises}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g3}
+
+}
+
+\caption{Rates by partners and promise condition}\label{fig:g3}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g5.jpeg}
-\caption{Bayesians logistic coefficients}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g4}
+
+}
+
+\caption{Promises}\label{fig:g4}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g6.jpeg}
-\caption{Linear population predictor}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g5}
+
+}
+
+\caption{Bayesians logistic coefficients}\label{fig:g5}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g7.jpeg}
-\caption{Linear population predictor by subject}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g6}
+
+}
+
+\caption{Linear population predictor}\label{fig:g6}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g8.jpeg}
-\caption{Population coefficient with uncertainty}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g7}
+
+}
+
+\caption{Linear population predictor by subject}\label{fig:g7}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9.jpeg}
-\caption{Model adjusted by subject}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g8}
+
+}
+
+\caption{Population coefficient with uncertainty}\label{fig:g8}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g16.jpeg}
-\caption{Two latent thetas}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9}
+
+}
+
+\caption{Model adjusted by subject}\label{fig:g9}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g10.jpeg}
-\caption{Subjects from two latent thetas}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g16}
+
+}
+
+\caption{Two latent thetas}\label{fig:g16}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g11.jpeg}
-\caption{Strategies by group}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g10}
+
+}
+
+\caption{Subjects from two latent thetas}\label{fig:g10}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12.jpeg}
-\caption{Rates by group}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g11}
+
+}
+
+\caption{Strategies by group}\label{fig:g11}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b.jpeg}
-\caption{Rates by group and promise condition}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12}
+
+}
+
+\caption{Rates by group}\label{fig:g12}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g13.jpeg}
-\caption{Reaction times by group}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b}
+
+}
+
+\caption{Rates by group and promise condition}\label{fig:g12_b}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g14.jpeg}
-\caption{Reaction times by partner}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g13}
+
+}
+
+\caption{Reaction times by group}\label{fig:g13}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g15.jpeg}
-\caption{Difference between groups in reaction time}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g14}
+
+}
+
+\caption{Reaction times by partner}\label{fig:g14}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g15}
+
+}
+
+\caption{Difference between groups in reaction time}\label{fig:g15}
 \end{figure}

### 2019-03-07 Manuscript/draft/Untitled.Rmd
Draft in spanish

---
title: "Untitled"
author: "Said E. Jiménez"
date: "6 de marzo de 2019"
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Análisis de datos

Se obtuvieron las proporciones de las decisiones pagar o no pagar la mitad, así como las promesas realizadas, posteriormente se calcularon las variaciones en las proporciones de acuerdo a los compañeros de juego y la condición de presencia o ausencia de promesas.

## Modelamiento Bayesiano

### Modelo Jerárquico

Se utilizó inferencia bayesiana para evaluar el efecto de las condiciones experimentales en la tasa de pago a nivel individual y poblacional. Para tal propósito se realizó un modelo jerárquico que asume que la incertidumbre en el efecto de promesas y parejas sobre la conducta de cada individuo proviene de distribuciones poblacionales comunes para los parámetros del modelo:

$$
\begin{equation}
y_i \sim \mathrm{Bernoulli}(\theta_i) \\
\mathrm{logit(\theta_i)} = \mathbf{X}\beta  +  \mathbf{Z}u
\end{equation}
$$
En el modelo anterior, cada decisión $y_i$ proviene de una distribución Bernoulli con probabilidad de pagar $\theta_i$, el objetivo del modelo jerárquico es predecir cada decisión a través la combinación lineal de los predictores transformados por su función ligadora inversa $\mathrm{logit}$. En el modelo anterior, $\beta$ y $u$ son coeficientes a nivel poblacional y nivel individual respectivamente, mientras que $\mathbf{X}$, $\mathbf{Z}$ son sus correpondientes matrices del diseño.

El modelo estima que la probabilidad $\theta_i$ de que en cada ensayo se decida pagar la mitad está en función del efecto de la presencia de promesas, así como de los compañeros con cercanía social baja (confederado) y alta (amigo) $\beta$. También asume que pueden existir diferencias individuales en el desempeño durante la tarea, las cuales son captadas por los parámetros $u$ y constituyen desviaciones de los coeficientes a nivel poblacional. Cabe remarcar que el modelo evalúa explícitamente la incertidumbre respecto a $u$, lo cual es una ventaja con relación a los modelos que asumen que $u$ es parte del término de error.

El modelo se programó en R por medio del paquete **brms**, que realiza la inferencia mediante el muestreo por Markov chain Monte Carlo a través de **Stan**. Las distribuciones posteriores de todos los parámetros fueron aproximadas con cuatro cadenas de 2000 iteraciones cada una, las primeras 1000 iteraciones de cada cadena fueron descartadas (periodo de calentamiento), para un total de 4000 muestras post-calentamiento. La convergencia del modelo fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que para todos los parámetros fue de 1, lo que se interpreta como convergencia.

### Modelamiento de mezclas latentes

Asume que las decisiones de los individuos podrían provenir de una combinación (o *mezcla*) de procesos psicológicos no observables (*latentes*), el rasgo latente más importante en este experimento es la (des)honestidad. Se modelaron las diferencias en las tasas de pago entre participantes como una combinación de $N$ distribuciones de subpoblaciones. El modelo asumió que las tasas de pago provenían de una, dos o tres mezclas de distribuciones, o grupos latentes.

El modelo de una mezcla, asumía que cada decisión $d_{i,j}$ de cada sujeto provenía de una distribución Bernoulli con probabilidad $\theta_{i,j}$. Asimismo que $\theta_{i,j}$ provenía de una distribución jerárquica Beta con parámetros $\alpha$ y $\beta$. La distribución Beta fue reparametrizada en términos de media $\mu$ y precisión $\lambda$, ya que $\mu = \alpha/(\alpha + \beta)$ y $\lambda = \alpha + \beta$.

$$
\mu \sim \mathrm{Uniform}(0, 1)\\
\lambda \sim \mathrm{Uniform}(40, 800)\\
\theta_{i,j} \sim \mathrm{Beta}(\mu\lambda, (1 - \mu)\lambda)\\
d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j}) 
$$

El modelo de dos mezclas es aproximadamente igual al anterior, sin embargo ahora asume que las decisiones provienen de una *mezcla* de las distribuciones de dos grupos, una distribución Beta con parámetros $\mu_1\lambda_1$ y $(1 - \mu_1) \lambda_1$ y otra con párametros $\mu_2\lambda_2$ y $(1 - \mu_2) \lambda_2$, el parámetro $z_i$ determina la probabilidad de que cada sujeto pertenezca a uno de dos grupos latentes, se distribuye Bernoulli con probabilidad $\phi$, que a su vez sigue una distribución inicial Beta relativamente poco informativa.

$$
\mu_1 \sim \mathrm{Uniform}(0, 1)\\
\mu_2 \sim \mathrm{Uniform}(\mu_1, 1)\\
\lambda_1 \sim \mathrm{Uniform}(40, 800)\\
\lambda_2 \sim \mathrm{Uniform}(4, 100)\\
z_i \sim \mathrm{Bernoulli}(\phi)\\
\theta_{i,j} \sim \Bigg\{
  \begin{array} {lr} 
    \mathrm{Beta}(\mu_1\lambda_1, (1 - \mu_1)\lambda_1) & \mbox{if} & z_i = 0 \\
    \mathrm{Beta}(\mu_2\lambda_2, (1 - \mu_2)\lambda_2) & \mbox{if} & z_i = 1
  \end{array} \\
d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j})\\
\phi \sim \mathrm{Beta}(5, 5)
$$

### 2019-03-07 Manuscript/draft/Untitled.Rmd
.

@@
 Se modelaron las diferencias en las tasas de pago entre participantes como una combinación de $N$ distribuciones de subpoblaciones.
-El modelo asumió que las tasas de pago provenían de una, dos o tres mezclas de distribuciones, o grupos latentes.
+El modelo asumió que las tasas de pago provenían de una o dos mezclas de distribuciones, o grupos latentes.
 
@@
 $$
+
+Los modelos de 1 y 2 mezclas, se programaron en R mediante el paquete **rjags**, que realiza la inferencia mediante el muestreo por Markov chain Monte Carlo a través de **JAGS**.
+Las distribuciones posteriores de todos los parámetros fueron aproximadas con tres cadenas de 13000 iteraciones cada una, se descartaron las primeras 3000 de cada cadena como periodo de calentamiento, para un total de 30000 muestras post-calentamiento.
+La convergencia del modelo fue evaluada a través del cálculo del estadístico $\hat{R}$, que varió de 1 a 1.01 para todos los parámetros lo que indica convergencia, a excepción de $\mu_1$ que obtuvo una estimación de 1.21.

### 2019-03-08 Manuscript/draft/Untitled.Rmd
Draft
Centering model

@@
 $$
-\begin{equation}
-y_i \sim \mathrm{Bernoulli}(\theta_i) \\
-\mathrm{logit(\theta_i)} = \mathbf{X}\beta  +  \mathbf{Z}u
-\end{equation}
+\begin{aligned}
+&y_i \sim \mathrm{Bernoulli}(\theta_i) \\
+&\mathrm{logit(\theta_i)} = \mathbf{X}\beta  +  \mathbf{Z}u
+\end{aligned}
 $$
@@
 El modelo estima que la probabilidad $\theta_i$ de que en cada ensayo se decida pagar la mitad está en función del efecto de la presencia de promesas, así como de los compañeros con cercanía social baja (confederado) y alta (amigo) $\beta$.
-También asume que pueden existir diferencias individuales en el desempeño durante la tarea, las cuales son captadas por los parámetros $u$ y constituyen desviaciones de los coeficientes a nivel poblacional.
+También asume que pueden existir diferencias individuales en el desempeño durante la tarea, las cuales son captadas por los parámetros $u$ y constituyen ajustes a los coeficientes poblacionales.
 Cabe remarcar que el modelo evalúa explícitamente la incertidumbre respecto a $u$, lo cual es una ventaja con relación a los modelos que asumen que $u$ es parte del término de error.
@@
 $$
-\mu \sim \mathrm{Uniform}(0, 1)\\
-\lambda \sim \mathrm{Uniform}(40, 800)\\
-\theta_{i,j} \sim \mathrm{Beta}(\mu\lambda, (1 - \mu)\lambda)\\
-d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j}) 
+\begin{aligned}
+&\mu \sim \mathrm{Uniform}(0, 1)\\
+&\lambda \sim \mathrm{Uniform}(40, 800)\\
+&\theta_{i,j} \sim \mathrm{Beta}(\mu\lambda, (1 - \mu)\lambda)\\
+&d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j}) 
+\end{aligned}
 $$
@@
 
+Se presenta el modelo de 2 mezclas con la notación propuesta por Lee, nodos cuadrados representan variables discretas y nodos circulares variables numéricas.
+Los nodos sombreados representan variables observadas, mientras que los nodos no sombreados son variables latentes.
+Los dos rectángulos representan repeticiones de la relación entre los parámetros del modelo para cada sujeto $i$ y ensayo $j$.
+Se determinó que un individuo pertenecía al grupo de *Deshonestos* si $z_i < 0.5$, dado que la probabilidad de que ese sujeto pagara la mitad en cada ensayo es baja, mientras que se consideró que un individuo pertenecía al grupo de *Honestos* si $z_i > 0.5$, dado que la probabilidad de que el individuo pague la mitad en cada ensayo es alta.
+
 $$
-\mu_1 \sim \mathrm{Uniform}(0, 1)\\
-\mu_2 \sim \mathrm{Uniform}(\mu_1, 1)\\
-\lambda_1 \sim \mathrm{Uniform}(40, 800)\\
-\lambda_2 \sim \mathrm{Uniform}(4, 100)\\
-z_i \sim \mathrm{Bernoulli}(\phi)\\
-\theta_{i,j} \sim \Bigg\{
+\begin{aligned} 
+&\mu_1 \sim \mathrm{Uniform}(0, 1)\\
+&\mu_2 \sim \mathrm{Uniform}(\mu_1, 1)\\
+&\lambda_1 \sim \mathrm{Uniform}(40, 800)\\
+&\lambda_2 \sim \mathrm{Uniform}(4, 100)\\
+&z_i \sim \mathrm{Bernoulli}(\phi)\\
+&\theta_{i,j} \sim \Bigg\{
   \begin{array} {lr} 
@@
   \end{array} \\
-d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j})\\
-\phi \sim \mathrm{Beta}(5, 5)
+&d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j})\\
+&\phi \sim \mathrm{Beta}(5, 5)
+\end{aligned}
 $$
@@
 La convergencia del modelo fue evaluada a través del cálculo del estadístico $\hat{R}$, que varió de 1 a 1.01 para todos los parámetros lo que indica convergencia, a excepción de $\mu_1$ que obtuvo una estimación de 1.21.
+
+### Modelamiento de los tiempos de reacción

### 2019-03-08 Manuscript/draft/Untitled.Rmd
.

@@
 ---
-title: "Untitled"
+title: "Método"
 author: "Said E. Jiménez"
@@
 
-## Análisis de datos
+## Análisis descriptivo de datos
 
@@
 ### Modelamiento de los tiempos de reacción
+
+Un hallazgo constante en la investigación sobre engaño y deshonestidad, es la diferencia en los tiempos de reacción entre quienes toman decisiones *deshonestas* vs.
+decisiones *honestas*, en general, se han encontrado latencias breves en personas *deshonestas* en comparación con las de las personas *honestas*.
+Se estimaron las medias poblacionales del grupo de deshonestos y honestos mediante un modelo bayesiano jerárquico que asumía que el tiempo de reacción proviene de dos distribución normales para cada grupo con parámetros $\mu_{\mathrm{Dishonest}}$ y $\mu_{\mathrm{Honest}}$ y desviación estándar común $\sigma$.
+Asimismo, se modeló la variabilidad intrasujeto en los tiempos de reacción por medio de interceptos variantes por participante.
+El modelo se ajustó en R por medio de **brms** y **Stan** en condiciones iguales a las descritas anteriormente y con resultados adecuados de convergencia para todos los parámetros, $\hat{R} = 1$.
+
+### Contraste de hipótesis
+
+Para los modelos de la tasa de pago y tiempo de reacción se utilizó el factor de Bayes por medio del método de Savage-Dickey, que calcula la razón de la densidad de la distribución posterior sobre la densidad de la distribución inicial de algún parámetro en el punto de interés.
+Específicamente para el modelo de la tasa de pago, se evaluó la hipótesis de si las promesas tendrían un efecto positivo en las tasas de pago ($H_1: \beta^{promise} > 0$), así como si la cercanía social alta (amigo) tendría mayores tasas de pago que la cercanía social baja (confederado) ($H_1: \beta^{friend} - \beta^{confederate} > 0$).
+Para el modelo del tiempo de reacción, la hipótesis fue si los *deshonestos* tendrían tiempos breves en comparación con los *honestos* ($H_1: \mu_{Dishonest} - \mu_{Honest} < 0$).
+
+### Comparación de modelos
+
+EL modelo de una y dos mezclas se compararon por medio del criterio de información DIC (deviance information criteria), en el que los puntajes bajos indican mejores modelos.
+Aunque el puntaje DIC favorece al modelo de una mezcla, dado que la diferencia entre los puntajes DIC de los modelos es mínima y las estrategias conductuales entre los grupos son cualitativamente distintas, consideramos al modelo de dos mezclas como una representación útil e informativa de los datos.

### 2019-03-08 Manuscript/draft/Untitled.Rmd
.

@@
 output:
-  html_document
+  html_document:
+    theme: cerulean
 ---
+
+<style>
+body {
+text-align: justify}
+</style>
 
@@
 Se obtuvieron las proporciones de las decisiones pagar o no pagar la mitad, así como las promesas realizadas, posteriormente se calcularon las variaciones en las proporciones de acuerdo a los compañeros de juego y la condición de presencia o ausencia de promesas.
+
+---
 
@@
 La convergencia del modelo fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que para todos los parámetros fue de 1, lo que se interpreta como convergencia.
+
+---
 
@@
 
+---
+
 ### Modelamiento de los tiempos de reacción
@@
 
+---
+
 ### Contraste de hipótesis
@@
 
+---
+
 ### Comparación de modelos
@@
 EL modelo de una y dos mezclas se compararon por medio del criterio de información DIC (deviance information criteria), en el que los puntajes bajos indican mejores modelos.
-Aunque el puntaje DIC favorece al modelo de una mezcla, dado que la diferencia entre los puntajes DIC de los modelos es mínima y las estrategias conductuales entre los grupos son cualitativamente distintas, consideramos al modelo de dos mezclas como una representación útil e informativa de los datos.
+Aunque el puntaje DIC favorece al modelo de una mezcla, dado que la diferencia entre los puntajes DIC de los modelos es mínima y las estrategias conductuales entre los grupos son cualitativamente distintas, consideramos al modelo de dos mezclas una representación informativa de los datos.

### 2019-03-08 mixture_promises.R
Change precision in mixture model

@@ -67,13 +67,13 @@ m_1 <- jags.model(textConnection(mix_1),
 
 
 # Burning m_1 -------------------------------------------------------------
-update(m_1, 2e3)
+update(m_1, 5e3)
 
 
 # Sampling from posterior m_1 ---------------------------------------------
 post_m_1 <- coda.samples(m_1,
                          variable.names = params,
-                         n.iter = 10e3)
+                         n.iter = 30e3)
 
 
 # Summary m_1 -------------------------------------------------------------
@@ -117,7 +117,7 @@ beta[2] <- (1 - mu2) * lambda2
 
 # Priors for mu1 and mu2
 mu1 ~ dunif(0, 1)
-lambda1 ~ dunif(40, 800)
+lambda1 ~ dunif(4, 100)
 
 mu2 ~ dunif(mu1, 1)
 lambda2 ~ dunif(4, 100)
@@ -129,7 +129,6 @@ lambda2 ~ dunif(4, 100)
 # Parameters m_2 ----------------------------------------------------------
 params2 <- c("z", "mu1", "lambda1", "mu2", "lambda2", "phi")
 
-
 # Compile m_2 -------------------------------------------------------------
 set.seed(1298)
 m_2 <- jags.model(textConnection(mix_2),
@@ -137,13 +136,13 @@ m_2 <- jags.model(textConnection(mix_2),
                   n.chains = 3)
 
 # Burning m_2 -------------------------------------------------------------
-update(m_2, 2e3)
+update(m_2, 5e3)
 
 
 # Sampling from posterior m_2 ---------------------------------------------
 post_m_2 <- coda.samples(m_2,
                          variable.names = params2,
-                         n.iter = 10e3)
+                         n.iter = 20e3)
 
 
 # Summary m_2 -------------------------------------------------------------
@@ -155,86 +154,9 @@ dic_m2 <- dic.samples(m_2, n.iter = 5e3)
 
 
 # Comparing m_1 - m_2 -----------------------------------------------------
+dic_m1
+dic_m2
 dic_m1 - dic_m2
-
-
-# Model 2 with differences on logit scale ---------------------------------
-
-mix_2_logit <- "model {
-
-# Each person belongs to one of two latent groups
-for(i in 1:n_subjects) {
-  z[i] ~ dbern(phi)  # phi is the base rate
-  z1[i] <- z[i] + 1
-}
-
[…]

### 2019-03-08 Manuscript/draft/Untitled.Rmd
Mixture promises data updated

@@
 
-El modelo estima que la probabilidad $\theta_i$ de que en cada ensayo se decida pagar la mitad está en función del efecto de la presencia de promesas, así como de los compañeros con cercanía social baja (confederado) y alta (amigo) $\beta$.
+El modelo estima que la probabilidad $\theta_i$ de que en cada ensayo se decida pagar la mitad está en función del efecto de la presencia de promesas $\beta^{promise}$, así como de los compañeros con cercanía social baja $\beta^{confederate}$ y alta $\beta^{friend}$.
 También asume que pueden existir diferencias individuales en el desempeño durante la tarea, las cuales son captadas por los parámetros $u$ y constituyen ajustes a los coeficientes poblacionales.
@@
 &\mu \sim \mathrm{Uniform}(0, 1)\\
-&\lambda \sim \mathrm{Uniform}(40, 800)\\
+&\lambda \sim \mathrm{Uniform}(4, 100)\\
 &\theta_{i,j} \sim \mathrm{Beta}(\mu\lambda, (1 - \mu)\lambda)\\
@@
 &\mu_2 \sim \mathrm{Uniform}(\mu_1, 1)\\
-&\lambda_1 \sim \mathrm{Uniform}(40, 800)\\
-&\lambda_2 \sim \mathrm{Uniform}(4, 100)\\
+&\lambda_{1:2} \sim \mathrm{Uniform}(4, 100)\\
 &z_i \sim \mathrm{Bernoulli}(\phi)\\
@@
 Los modelos de 1 y 2 mezclas, se programaron en R mediante el paquete **rjags**, que realiza la inferencia mediante el muestreo por Markov chain Monte Carlo a través de **JAGS**.
-Las distribuciones posteriores de todos los parámetros fueron aproximadas con tres cadenas de 13000 iteraciones cada una, se descartaron las primeras 3000 de cada cadena como periodo de calentamiento, para un total de 30000 muestras post-calentamiento.
-La convergencia del modelo fue evaluada a través del cálculo del estadístico $\hat{R}$, que varió de 1 a 1.01 para todos los parámetros lo que indica convergencia, a excepción de $\mu_1$ que obtuvo una estimación de 1.21.
+Las distribuciones posteriores de todos los parámetros fueron aproximadas con tres cadenas de 26000 iteraciones cada una, se descartaron las primeras 6000 de cada cadena como periodo de calentamiento, para un total de 60000 muestras post-calentamiento.
+La convergencia del modelo fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que varió de 1 a 1.05 para todos los parámetros lo que indica convergencia.
 
@@
 
-EL modelo de una y dos mezclas se compararon por medio del criterio de información DIC (deviance information criteria), en el que los puntajes bajos indican mejores modelos.
-Aunque el puntaje DIC favorece al modelo de una mezcla, dado que la diferencia entre los puntajes DIC de los modelos es mínima y las estrategias conductuales entre los grupos son cualitativamente distintas, consideramos al modelo de dos mezclas una representación informativa de los datos.
+El modelo de una y dos mezclas se compararon por medio del criterio de información DIC (deviance information criteria), en el que los puntajes bajos indican mejores modelos.
+La estimación de la diferencia entre el modelo de 1 y 2 mezclas favorece al modelo de dos mezclas ($\mathrm{Difference}= 1.21$, $\mathrm{SE}= 3.49$).

### 2019-03-08 mixture_promises.R

@@ -43,7 +43,7 @@ alpha <- mu * lambda
 beta <- (1 - mu) * lambda
 
 mu ~ dunif(0, 1)
-lambda ~ dunif(40, 800)
+lambda ~ dunif(4, 100)
 
 # likelihood
 
@@ -73,7 +73,7 @@ update(m_1, 5e3)
 # Sampling from posterior m_1 ---------------------------------------------
 post_m_1 <- coda.samples(m_1,
                          variable.names = params,
-                         n.iter = 30e3)
+                         n.iter = 20e3)
 
 
 # Summary m_1 -------------------------------------------------------------

### 2019-03-08 promises_social_closeness.R

@@ -448,7 +448,7 @@ cases_2 <- data %>%
 
 # Prior m_rt --------------------------------------------------------------
 
-prior_rt <- set_prior("normal(0, 5)", class = "b")
+prior_rt <- set_prior("normal(0, 5)", class = "b", lb = 0)
 
 
 # Fitting m_rt ------------------------------------------------------------
@@ -461,7 +461,7 @@ prior_rt <- set_prior("normal(0, 5)", class = "b")
 
 # Hypothesis testing: mu_d = mu_h -----------------------------------------
 
-hypothesis(m_rt, "groupDishonest - groupHonest = 0") 
+hypothesis(m_rt, "groupDishonest - groupHonest = 0")
 hypothesis(m_rt, "groupDishonest - groupHonest < 0") 
 
 

### 2019-03-08 Manuscript/draft/Untitled.Rmd
Results in manuscript

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE,
+                      warning = FALSE,
+                      error = FALSE,
+                      message = FALSE,
+                      out.width = '80%',
+                      fig.align = 'center',
+                      dpi = 300)
 ```
@@
 decisiones *honestas*, en general, se han encontrado latencias breves en personas *deshonestas* en comparación con las de las personas *honestas*.
-Se estimaron las medias poblacionales del grupo de deshonestos y honestos mediante un modelo bayesiano jerárquico que asumía que el tiempo de reacción proviene de dos distribución normales para cada grupo con parámetros $\mu_{\mathrm{Dishonest}}$ y $\mu_{\mathrm{Honest}}$ y desviación estándar común $\sigma$.
+
+Se estimaron las medias poblacionales del grupo de deshonestos y honestos mediante un modelo bayesiano jerárquico que asumía que el tiempo de reacción proviene de una distribución $rt_i \sim \mathrm{Half-Normal}(0, 5)$ (dado que no puede haber tiempos de reacción negativos), con parámetros $\mu_{\mathrm{Dishonest}}$ y $\mu_{\mathrm{Honest}}$ y desviación estándar común $\sigma$.
+
 Asimismo, se modeló la variabilidad intrasujeto en los tiempos de reacción por medio de interceptos variantes por participante.
@@
 
-El modelo de una y dos mezclas se compararon por medio del criterio de información DIC (deviance information criteria), en el que los puntajes bajos indican mejores modelos.
+Los modelos de una y dos mezclas se compararon por medio del criterio de información DIC (deviance information criteria), en el que los puntajes bajos indican mejores modelos.
 La estimación de la diferencia entre el modelo de 1 y 2 mezclas favorece al modelo de dos mezclas ($\mathrm{Difference}= 1.21$, $\mathrm{SE}= 3.49$).
+
+---
+
+## Resultados
+
+Se muestran en las figuras 1, 2, 3 y 4 la frecuencia de veces en que los participantes pagaron la mitad, la proporción de pagos que realizaron a cada pareja, la proporción de pagos por pareja y condición de promesas, así como la frecuencia de promesas que fueron seleccionadas por los participantes, respectivamente.
+
+```{r g1, fig.cap='Fig. 1 Difference between groups in frecuencies of pay back'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g1.jpeg")
+
+```
+
+---
+
+```{r g2, fig.cap='Fig.2 Rates by partner'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g2.jpeg")
+
+```
+
+---
+
+```{r g3, fig.cap='Fig. 3 Rates by partners and promise condition'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g3.jpeg")
+
+```
+
+---
+
+```{r g4, fig.cap='Fig. 4 Frecuencies of promises'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g4.jpeg")
+
+```

### 2019-03-09 Manuscript/draft/Untitled.Rmd
Figure sizes

@@
 
-Se muestran en las figuras 1, 2, 3 y 4 la frecuencia de veces en que los participantes pagaron la mitad, la proporción de pagos que realizaron a cada pareja, la proporción de pagos por pareja y condición de promesas, así como la frecuencia de promesas que fueron seleccionadas por los participantes, respectivamente.
+Se muestra en la figura 1, la frecuencia de veces en que los participantes pagaron la mitad, así como la frecuencia de promesas que fueron seleccionadas.
+En la figura 2, se muestra la proporción de pagos realizados dependiendo de cada pareja y de la condición de promesas.
 
-```{r g1, fig.cap='Fig. 1 Difference between groups in frecuencies of pay back'}
+```{r fig1, fig.cap='Fig. 1 Frecuencies of paying and Promise choice'}
 
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g1.jpeg")
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig1.jpeg")
 
@@
 
-```{r g2, fig.cap='Fig.2 Rates by partner'}
+```{r fig2, fig.cap='Fig. 2 Rates by partners and promise condition'}
 
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g2.jpeg")
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig2.jpeg")
 
 ```
-
----
-
-```{r g3, fig.cap='Fig. 3 Rates by partners and promise condition'}
-
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g3.jpeg")
-
-```
-
----
-
-```{r g4, fig.cap='Fig. 4 Frecuencies of promises'}
-
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g4.jpeg")
-
-```

### 2019-03-09 figures.R

@@ -7,7 +7,8 @@
 
 library(pacman)
 p_load(magrittr, dplyr, forcats, tidyr, modelr, tidybayes,
-       ggstance, ggridges, rstan, brms, tidyverse, bayesplot, rjags)
+       ggstance, ggridges, rstan, brms, tidyverse, bayesplot, rjags, 
+       gridExtra, ggthemes)
 
 
 
@@ -53,5 +54,22 @@ ggsave("g16.jpeg",
        width = 10,
        height = 7,
        units = "in")
+
+
+# Figure 1 ----------------------------------------------------------------
+
+g1 <- g1 + labs(tag = "A", x = "") 
+g4 <- g4 + labs(tag = "B")
+
+g1_g4 <- grid.arrange(g1, g4, ncol = 2)
+
+ggsave("fig1.jpeg",
+       path = "~/Documents/R/github_Said/social_closeness/Manuscript/figures/",
+       plot = g1_g4,
+       device = "jpeg",
+       width = 10,
+       height = 5,
+       units = "in")
+
 
 

### 2019-03-09 Manuscript/draft/Untitled.Rmd
Manuscript update

@@
 
+### Descriptivos
+
 Se muestra en la figura 1, la frecuencia de veces en que los participantes pagaron la mitad, así como la frecuencia de promesas que fueron seleccionadas.
@@
 ```
+
+---
+
+### Resultados: modelo jerárquico
+
+En la tabla 1, se muestran los efectos poblacionales del modelo bayesiano jerárquico para la tasa de pago.
+Se presentan las estimaciones de cada coeficiente del modelo en escala *logit*, su error estándar y los intervalos de credibilidad bayesianos del 95%.
+Los cuales indican los límites inferiores y superiores de las estimaciones entre los que se ubica el 95 % de probabilidad.
+
+<caption>Table 1. Population-Level Effects of Task</caption>
+|Term                |Estimate|  SE|L-95% CI|U-95% CI|
+|:-------------------|-------:|---:|-------:|-------:|
+|$\beta^0$           |   -1.62|0.40|   -2.31|   -1.02|
+|$\beta^{promise}$   |    1.27|0.40|    0.64|    1.92|
+|$\beta^{confederate}$ |    2.01|0.55|    1.20|    2.97|
+|$\beta^{friend}$    |    4.15|0.77|    3.07|    5.49|
+
+---
+
+La figura 3A muestra la incertidumbre con respecto a la estimación de los coeficientes, la linea central indica la mediana de la distribución y el área sombreada el intervalo del 50 % de probabilidad.
+Para visualizar el efecto conjunto de las condiciones experimentales en la probabilidad de pagar la mitad, se realizó su combinación lineal para obtener un sólo predictor ($\mathrm{linpred_i}$), se le aplicó la función ligadora inversa *logit* y se transformó su output en probabilidades por medio de la función logistica $1 / (1 + \exp(-\mathrm{linpred}_i))$.
+
+La figura 3B muestra la probabilidad de pagar la mitad, como función de la combinación lineal de las condiciones experimentales, las lineas delgadas muestran la incertidumbre en la predicción con una muestra aleatoria de tamaño 100 de las distribuciones posteriores de los parámetros poblacionales.
+La linea gruesa representa la media de las distribuciones posteriores de los parámetros poblacionales.
+
+```{r fig3, fig.cap='Fig. 3 Estimates with uncertainty and linear predictor'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig3.jpeg")
+
+```
+
+----
+
+En un procedimiento similar al descrito para la figura 3B, la figura 4 representa el efecto conjunto de las condiciones experimentales en la probabilidad de pagar la mitad para cada sujeto.
+Ya que el modelo jerárquico asume que las diferencias individuales se pueden modelar realizando un ajuste $u$ a los coeficientes poblacionales $\beta$, se obtuvieron 50 muestras aleatorias de las distribuciones posteriores de los parámetros $u$ para cada sujeto, se realizó el ajuste al modelo poblacional y se presenta en lineas delgadas la incertidumbre en la predicción individual.
+
+```{r fig4, fig.cap='Fig. 4 Estimates with uncertainty by subject'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9.jpeg")
+
+```
+
+---
+
+### Resultados: modelo de mezclas latentes
+
+---
+
+### Resultados: tiempo de reacción
+
+---
+
+### Resultados: contraste de hipótesis y comparación de modelos

### 2019-03-09 figures.R

@@ -73,3 +73,20 @@ ggsave("fig1.jpeg",
 
 
 
+# Figure 3 ----------------------------------------------------------------
+
+g5 <- g5 + labs(tag = "A", x = "Estimate", y = "") +
+  theme(axis.text.y = element_text(size = 8))
+          
+
+g8 <- g8 + labs(tag = "B")
+
+fig3 <- grid.arrange(g5, g8, ncol = 2)
+
+ggsave("fig3.jpeg",
+       path = "~/Documents/R/github_Said/social_closeness/Manuscript/figures/",
+       plot = fig3,
+       device = "jpeg",
+       width = 10,
+       height = 5,
+       units = "in")

### 2019-03-09 tables.R

@@ -1,0 +1,21 @@
+# Tables
+library(pacman)
+p_load(magrittr, dplyr, forcats, tidyr, modelr, tidybayes,
+       ggstance, ggridges, rstan, brms, tidyverse, bayesplot)
+
+
+# Loading data ------------------------------------------------------------
+
+load("social_closeness.RData")
+
+
+# Tidying model 1 output --------------------------------------------------
+m_tidy <- broom::tidy(m) %>% 
+  slice(1:4)
+
+knitr::kable(m_tidy, 
+             format = "markdown", 
+             padding = 0, 
+             digits = 2,
+             col.names = c("Term", "Estimate", "SE", "L-95% CI", "U-95% CI"))
+

### 2019-03-10 Manuscript/draft/Untitled.Rmd
Creating figure 5

@@
 
-Se estimaron las medias poblacionales del grupo de deshonestos y honestos mediante un modelo bayesiano jerárquico que asumía que el tiempo de reacción proviene de una distribución $rt_i \sim \mathrm{Half-Normal}(0, 5)$ (dado que no puede haber tiempos de reacción negativos), con parámetros $\mu_{\mathrm{Dishonest}}$ y $\mu_{\mathrm{Honest}}$ y desviación estándar común $\sigma$.
+Se estimaron las medias poblacionales del grupo de deshonestos y honestos mediante un modelo bayesiano jerárquico que asumía que el tiempo de reacción proviene de una distribución $rt_i \sim \mathrm{Half-Normal}(0, 5)$ (dado que no puede haber tiempos de reacción negativos), con parámetros $\mu_{Dishonest}$ y $\mu_{Honest}$ y desviación estándar común $\sigma$.
 

### 2019-03-10 figures.R

@@ -90,3 +90,38 @@ ggsave("fig3.jpeg",
        width = 10,
        height = 5,
        units = "in")
+
+
+
+# Figure 5 ----------------------------------------------------------------
+
+bayesplot_theme_set(theme_bw(base_size = 15) +
+                    theme(panel.grid.major = element_line(linetype = "blank"), 
+                          panel.grid.minor = element_line(linetype = "blank")))
+
+f_partner <- pp_check(m, 
+                      type = "bars_grouped", 
+                      nsamples = 50, 
+                      group = "partner") +
+  scale_x_continuous(breaks = c(0, 1), 
+                     labels = c("No", "Yes"),
+                     name = "Pay back") 
+
+
+f_promise <- pp_check(m, 
+                      type = "bars_grouped", 
+                      nsamples = 50, 
+                      group = "promise") + 
+  scale_x_continuous(breaks = c(0, 1), 
+                     labels = c("No", "Yes"),
+                     name = "Pay back")
+
+
+ggsave("fig5.jpeg",
+       path = "~/Documents/R/github_Said/social_closeness/Manuscript/figures/",
+       plot = f_partner,
+       device = "jpeg",
+       width = 10,
+       height = 5,
+       units = "in")
+

### 2019-03-10 Manuscript/draft/Untitled.Rmd
Updating tables and figures

@@
 |Term                  |Estimate|  SE|L-95% CI|U-95% CI|
-|:-------------------|-------:|---:|-------:|-------:|
+|:---------------------|-------:|---:|-------:|-------:|
 |$\beta^0$             |   -1.62|0.40|   -2.31|   -1.02|
@@
 
+La **distribución posterior predictiva** consiste en simular el tipo de observaciones que podrían surgir con el modelo original, pero una vez que los parámetros de éste han sido actualizados con los datos observados.
+En este caso, cuando el modelo ha aprendido de las decisiones de los sujetos, tiene la capacidad de generar una _"replica"_ de los datos observados, por cada combinación de los parámetros obtenidos en la distribución posterior.
+
+En la figura 5, se obtuvieron 50 muestras aleatorias de la distribución posterior de los parámetros poblacionales $\beta$ y se simularon 50 datasets con las decisiones que se esperarían con esos parámetros.
+Se presentan en barras las decisiones realizadas por nuestros participantes $y$, mientras que el punto con dispersión muestra la distribución de los valores esperados en las 50 _replicas_ $y_{rep}$.
+
+```{r fig5, fig.cap='Fig. 5 Posterior predictive distribution of choices by partner'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig5.jpeg")
+
+```
+
+---
+
 ### Resultados: modelo de mezclas latentes
+
+El modelo de 2-mezclas latentes identificó dos subpoblaciones de tamaño 10; en la tabla 2 se muestran los resúmenes de las distribuciones posteriores de los parámetros de ambas subpoblaciones y el parámetro de la mezcla $\phi$.
+Una de las subpoblaciones tiene alta probabilidad de pagar $\mu_1$, la que denominamos __honestos__ y la otra subpoblación tiene una probabilidad de pagar menor por lo que fue denominada __deshonestos__ $\mu_2$.
+En la figura 6A se muestran las distribuciones posteriores de las dos $\mu$'s, correspondientes a la probabilidad de pagar de los dos grupos latentes.
+Y en la figura 6B se presentan las decisiones de dos sujetos extraídos de las dos subpoblaciones, el sujeto 5 de la subpoblación de __deshonestos__ y el 17 de la subpoblación de __honestos__.
+En la figura 7 se muestra la frecuencia de las decisiones de los dos grupos latentes, dependiendo de si estaban en la condición con o sin promesa.
+
+<caption>Table 2. Parameters of 2-Mixture Model</caption>
+|Parameter    | Mean|   SD|L-95% CI|U-95% CI|
+|:------------|----:|----:|-------:|-------:|
+|$\mu_{1}$    | 0.56| 0.05|    0.44|    0.65|
+|$\mu_{2}$    | 0.70| 0.05|    0.61|    0.82|
+|$\lambda_{1}$|48.99|28.57|    5.50|   97.49|
+|$\lambda_{2}$|54.79|26.24|    7.80|   97.61|
+|$\phi$       | 0.49| 0.15|    0.21|    0.77|
+
+---
+
+```{r fig6, fig.cap='Fig. 6 Posteriors from two latent groups and two cases'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig6.jpeg")
+
+```
+
+---
+
+```{r fig7, fig.cap='Fig. 7 Payment frecuency by latent group and promise condition'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b.jpeg")
+
+```
 

### 2019-03-10 figures.R

@@ -125,3 +125,19 @@ ggsave("fig5.jpeg",
        height = 5,
        units = "in")
 
+
+# Figure 6 ----------------------------------------------------------------
+
+thetas <- thetas + labs(tag = "A")
+g10 <- g10 + labs(tag = "B")
+
+fig6 <- gridExtra::grid.arrange(thetas, g10, ncol = 2)
+
+
+ggsave("fig6.jpeg",
+       path = "~/Documents/R/github_Said/social_closeness/Manuscript/figures/",
+       plot = fig6,
+       device = "jpeg",
+       width = 10,
+       height = 5,
+       units = "in")

### 2019-03-10 mixture_promises.R

@@ -186,11 +186,11 @@ x_intercepts <- chains_m_2 %>%
              size = 1) +
   scale_color_manual(values = c("#053778", "#A4CAE3")) +
   scale_fill_manual(values = c("#053778", "#A4CAE3")) +
-  labs(x = c("Estimate" = expression(theta)), 
+  labs(x = expression(mu), 
        y = "Count",
        col = NULL,
        fill = NULL) +
-  theme_bw(base_size = 15) +
+  theme_bw(base_size = 12) +
   theme(panel.grid = element_line(linetype = "blank"),
         legend.position = "bottom"))
 

### 2019-03-10 tables.R

@@ -19,3 +19,23 @@ knitr::kable(m_tidy,
              digits = 2,
              col.names = c("Term", "Estimate", "SE", "L-95% CI", "U-95% CI"))
 
+
+
+# Tidying mixture model output --------------------------------------------
+
+load("mixture_promises.RData")
+
+m_2_tidy <- ggmcmc::ggs(post_m_2) %>% 
+  filter(Parameter %in% c("lambda1", "lambda2", "mu1", "mu2", "phi"))
+
+
+m_2_tidy %>% 
+  group_by(Parameter) %>% 
+  summarise(mean = mean(value),
+            sd = sd(value),
+            l_95 = quantile(value, .025),
+            u_95 = quantile(value, .975)) %>% 
+  knitr::kable("markdown",
+               padding = 0, 
+               digits = 2,
+               col.names = c("Parameter", "Mean", "SD", "L-95% CI", "U-95% CI")) 

### 2019-03-10 Manuscript/draft/Untitled.Rmd
Results in manuscript

@@
 
-```{r fig2, fig.cap='Fig. 2 Rates by partners and promise condition'}
+```{r fig2, fig.cap='Fig. 2 Rates by partners and promise condition', fig.height=10, fig.width=5}
 
@@
 
-```{r fig7, fig.cap='Fig. 7 Payment frecuency by latent group and promise condition'}
+```{r fig7, fig.cap='Fig. 7 Payment frecuency by latent group and promise condition', fig.height=10, fig.width=5}
 
@@
 
+En la tabla 3 se presentan las estimaciones poblacionales del modelo bayesiano de los tiempos de reacción, se resumen las distribuciones posteriores de cada parámetro, incluyendo la estimación de su media, su error estándar y los intervalos de credibilidad bayesianos del 95%.
+En la figura 8A se muestran con puntos los tiempos de reacción en segundos para cada decisión realizada de acuerdo con cada subgrupo, se agregó a cada grupo un kernel de densidad simétrico para representar la cantidad de casos acumulados a lo largo de los diferentes valores del tiempo de reacción.
+
+En la figura 8B se presenta la diferencia de las estimaciones posteriores, el punto con dispersión representa el estimador puntual de la diferencia entre las subpoblaciones y el intervalo de credibilidad bayesiano del 95%.
+El histograma representa la distribución posterior de la diferencia entre los parámetros de las subpoblaciones.
+
+<caption>Table 3. Parameters estimates of reaction time model</caption>
+|Term              | Estimate|   SE| L-95% CI| U-95% CI|
+|:-----------------|--------:|----:|--------:|--------:|
+|$\mu_{Dishonest}$ |     2.93| 0.23|     2.55|     3.31|
+|$\mu_{Honest}$    |     3.06| 0.22|     2.69|     3.42|
+|$\mu_{difference}$|    -0.13| 0.32|    -0.77|     0.52|  
+|$\sigma$          |     1.23| 0.05|     1.15|     1.31|
+|$\sigma_{subject}$|     0.65| 0.14|     0.45|     0.89|
+
+---
+
+```{r fig8, fig.cap='Fig. 8 Differences in reaction time by latent group'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig8.jpeg")
+
+```
+
 ---
@@
 ### Resultados: contraste de hipótesis y comparación de modelos
+
+En la tabla 4 se muestran las hipótesis contrastadas, las estimaciones, los errores estándar y el factor de Bayes (BF) para cada una.
+Se interpretan los BF's como evidencia en favor de la hipótesis alterna $BF_{10}$ de acuerdo a la clasificación de Jeffreys (1961).
+La hipótesis uno de si la condición de promesas tiene un efecto superior a 0, se interpreta como "evidencia extrema" a su favor, la hipótesis de si el efecto en la tasa de pago es superior para el amigo que para el confederado también se interpreta como "evidencia superior" a su favor, la hipótesis sobre si la diferencia entre los tiempos de reacción entre honestos y deshonestos es menor a cero, se interpreta como "evidencia anecdótica" a su favor.
+
+Dado que el intervalo de credibilidad bayesiano para la estimación de la diferencia entre los tiempos de reacción de las subpoblaciones incluye el cero, se decidió evaluar la hipótesis de si la diferencia es igual a 0, el BF correspondiente se interpreta como "evidencia fuerte" en favor a la diferencia igual a 0.
+Finalmente, se comparó el DIC para los modelos de una ($DIC_{1}$) y dos ($DIC_{2}$) mezclas, cuya diferencia apoya al modelo de dos mezclas latentes.
+
+<caption>Table 4. Hypothesis testing and model comparison</caption>
+|Hypothesis                                    | Estimate|   SE|$BF_{10}$| 
+|:---------------------------------------------|--------:|----:|--------:|
+|$\beta^{promise} > 0$                         |     1.27| 0.40|      499|    
+|$\beta^{friend} - \beta^{confederate} > 0$    |     2.14| 0.77|   665.67|    
+|$\mu_{Dishonest} - \mu_{Honest} < 0$          |    -0.13| 0.32|     1.96|   
+|$\mu_{Dishonest} - \mu_{Honest} = 0$          |    -0.13| 0.32|    20.36|  
+|$DIC_{1} - DIC_{2}$                           |    1.21 | 3.49|      -  |

### 2019-03-10 figures.R

@@ -141,3 +141,21 @@ ggsave("fig6.jpeg",
        width = 10,
        height = 5,
        units = "in")
+
+
+
+# Figure 8 ----------------------------------------------------------------
+
+g13 <- g13 + labs(tag = "A")
+g15 <- g15 + labs(tag = "B")
+
+
+fig8 <- gridExtra::grid.arrange(g13, g15, ncol = 2)
+
+ggsave("fig8.jpeg",
+       path = "~/Documents/R/github_Said/social_closeness/Manuscript/figures/",
+       plot = fig8,
+       device = "jpeg",
+       width = 10,
+       height = 5,
+       units = "in")

### 2019-03-10 promises_social_closeness.R

@@ -108,7 +108,7 @@ prior <- c(set_prior("normal(0, 5)", class = "b"),
 
 # Hypothesis testing ------------------------------------------------------
 
-hypothesis(m, "promisePromise > 0", class = "b")
+hypothesis(m, "promisePromise > 0", class = "b") 
 hypothesis(m, "partnerFriend - partnerConfederate > 0", class = "b") 
 
 

### 2019-03-10 tables.R

@@ -39,3 +39,13 @@ m_2_tidy %>%
                padding = 0, 
                digits = 2,
                col.names = c("Parameter", "Mean", "SD", "L-95% CI", "U-95% CI")) 
+
+
+# Tidying reaction time model output --------------------------------------
+
+m_rt_tidy <- broom::tidy(m_rt) %>%  slice(1:4)
+
+knitr::kable(m_rt_tidy,
+             format = "markdown",
+             digits = 2,
+             col.names = c("Term", "Estimate", "SE", "L-95% CI", "U-95% CI"))

### 2019-03-11 Manuscript/draft/Untitled.Rmd
.

@@
 <caption>Table 4. Hypothesis testing and model comparison</caption>
-|Hypothesis                                    | Estimate|   SE|$BF_{10}$| 
+|Hypothesis                                    | Estimate|   SE|BF$_{10}$| 
 |:---------------------------------------------|--------:|----:|--------:|
@@
 |$\mu_{Dishonest} - \mu_{Honest} = 0$          |    -0.13| 0.32|    20.36|  
-|$DIC_{1} - DIC_{2}$                           |    1.21 | 3.49|      -  |
+|$DIC_{1} - DIC_{2}$                           |     1.21| 3.49|      -  |

### 2019-03-11 Manuscript/draft/Untitled.Rmd
Participant's description

@@
 ```
+
+## Participantes
+
+Se incluyeron 20 personas voluntarias (18 mujeres), en un rango de edad de ..., su nivel educativo mínimo fue licenciatura, se trató de estudiantes de estado civil soltero.
+Todos los participantes reportaron no tener historial médico de tipo neurológico ni psiquiátrico al momento del experimento.
+Los participantes acudieron con un amigo considerado _cercano_ por ellos mismos, quien cumplía las siguientes características: era una persona del mismo sexo que el participante, no tenía un vínculo familiar y no se trataba de una persona con una relación de tipo sentimental y/o sexual.
+
+---
+
+## Materiales y Procedimiento
+
+---
 
@@
 |$DIC_{1} - DIC_{2}$                           |     1.21| 3.49|      -  |
+
+---

### 2019-03-11 Manuscript/draft/Untitled.Rmd
.

@@
 ## Materiales y Procedimiento
+
+Se trata de una adaptación de la tarea de confianza y promesas presentada por Baumgartner (2009), que consiste en 24 ensayos entre dos jugadores A y B, el jugador A tiene originalmente 0 pesos mexicanos y el jugador B tiene 2 pesos, al jugador B se le presenta la oportunidad de invertir su dinero al jugador A o conservarlo, si invierte su dinero se multiplica por 5 pesos, de modo que el jugador A recibe 10 pesos.
+Finalmente, el jugador A toma la decisión de pagar la mitad al jugador B o quedarse los 10 pesos.
+La estructura descrita se repite en 24 ensayos, sin embargo, en 4 de los ensayos el jugador A puede enviar una promesa a B, las promesas son que siempre, casi siempre, algunas veces o nunca, pagar la mitad
 

### 2019-03-12 Manuscript/draft/Untitled.Rmd
Update of procedure section

--- 2019-03-11 Manuscript/draft/Untitled.Rmd
@@
 ## Materiales y Procedimiento
+
+Se trata de una adaptación de la tarea de confianza y promesas presentada por Baumgartner (2009), que consiste en 24 ensayos entre dos jugadores **A** y **B**, el jugador **A** tiene originalmente 0 pesos mexicanos y el jugador **B** tiene 2 pesos, al jugador **B** se le presenta la oportunidad de invertir su dinero al jugador **A** o conservarlo, si invierte su dinero se multiplica por 5 pesos, de modo que el jugador **A** recibe 10 pesos.
+Finalmente, el jugador **A** toma la decisión de pagar la mitad al jugador **B** o quedarse los 10 pesos.
+La estructura descrita se repite en 24 ensayos, sin embargo, en 4 de los ensayos el jugador **A** puede enviar una promesa a **B**, las promesas son que _siempre_, _casi siempre_, _algunas veces_ o _nunca_ pagaran la mitad.
+Cada promesa es válida por tres ensayos, de modo que 12 de los ensayos tienen el efecto de la promesa y los otros 12 no lo tienen.
+
+La variación respecto a la tarea original es que en nuestro experimento se presentan tres compañeros de juego con tres niveles de cercanía social **computadora** (cercanía nula), **confederado** (cercanía baja) y **amigo** (cercanía alta) en el papel del jugador **B**, mientras que el sujeto siempre realiza el papel de jugador **A**.
+Cada compañero de juego realizó el rol de **B** en 8 de los 24 ensayos totales, sin embargo, tanto la condición de promesas como la de cercanía social fueron presentadas al sujeto **A** en orden pseudoaleatorio (ya que se mantuvo el mismo orden en la tarea para todos los sujetos).
+
+Con el fin de simplificar la tarea y homogeneizar la experiencia de todos nuestros participantes, se programaron _a priori_ las decisiones de los compañeros **B** sobre si invertían o no su monto inicial, se programó que los tres compañeros decidieran invertir en 6 ensayos y no invertir en 2, los cuales también se presentaron al sujeto **A** en orden pseudoaleatorio.
+La historia encubierta para todos nuestros sujetos en el papel de **A** fue que estarían jugando en tiempo real con su amigo, el confederado (que se le dijo que sería otra persona desconocida de su mismo sexo) y la computadora.
 

### 2019-03-12 Manuscript/draft/Untitled.Rmd
Update participant and methods section

@@
 
-Se incluyeron 20 personas voluntarias (18 mujeres), en un rango de edad de ..., su nivel educativo mínimo fue licenciatura, se trató de estudiantes de estado civil soltero.
+Se incluyeron 20 personas voluntarias (18 mujeres), en un rango de edad de 19-33 años, su nivel educativo mínimo fue licenciatura, se trató principalmente de estudiantes de estado civil soltero.
 Todos los participantes reportaron no tener historial médico de tipo neurológico ni psiquiátrico al momento del experimento.
-Los participantes acudieron con un amigo considerado _cercano_ por ellos mismos, quien cumplía las siguientes características: era una persona del mismo sexo que el participante, no tenía un vínculo familiar y no se trataba de una persona con una relación de tipo sentimental y/o sexual.
+Los participantes acudieron al estudio con un amigo considerado _cercano_ por ellos mismos, quien cumplía las siguientes características: era una persona del mismo sexo que el participante, no tenía un vínculo familiar y no se trataba de una persona con una relación de tipo sentimental y/o sexual.
 
@@
 La variación respecto a la tarea original es que en nuestro experimento se presentan tres compañeros de juego con tres niveles de cercanía social **computadora** (cercanía nula), **confederado** (cercanía baja) y **amigo** (cercanía alta) en el papel del jugador **B**, mientras que el sujeto siempre realiza el papel de jugador **A**.
-Cada compañero de juego realizó el rol de **B** en 8 de los 24 ensayos totales, sin embargo, tanto la condición de promesas como la de cercanía social fueron presentadas al sujeto **A** en orden pseudoaleatorio (ya que se mantuvo el mismo orden en la tarea para todos los sujetos).
-
+Cada compañero de juego realizó el rol de **B** en 8 de los 24 ensayos totales, sin embargo, tanto la condición de promesas como la de cercanía social fueron presentadas al sujeto **A** en orden pseudoaleatorio, lo que significa que se realizó la aleatorización de los ensayos una vez y se mantuvo el mismo orden para todos los sujetos.
 Con el fin de simplificar la tarea y homogeneizar la experiencia de todos nuestros participantes, se programaron _a priori_ las decisiones de los compañeros **B** sobre si invertían o no su monto inicial, se programó que los tres compañeros decidieran invertir en 6 ensayos y no invertir en 2, los cuales también se presentaron al sujeto **A** en orden pseudoaleatorio.
 La historia encubierta para todos nuestros sujetos en el papel de **A** fue que estarían jugando en tiempo real con su amigo, el confederado (que se le dijo que sería otra persona desconocida de su mismo sexo) y la computadora.
+
+En la figura A se muestra un diagrama de la cronología de la tarea experimental, cada caja representa una pantalla que se le mostró a los sujetos de manera secuencial de izquierda a derecha, se incluyen las duraciones de cada pantalla en segundos.
+La parte A$_{1}$ corresponde a un ejemplo de los ensayos sin promesas y la A$_{2}$ de los ensayos con promesas.
+La fase de fijación sólo consistía en un período en el que el sujeto tenía que prestar atención sin realizar ninguna conducta en particular, la **fase de promesas** en la parte A$_{1}$ le indicaba al sujeto que los siguientes tres ensayos se podían decidir sin el efecto de la promesa, mientras que en A$_{2}$ se le pedía al sujeto que decidiera entre _siempre_, _casi siempre_, _algunas veces_ o _nunca_ pagaría la mitad.
+A lo anterior le seguía otro período de fijación, posteriormente los ensayos tanto en A$_{1}$ como en A$_{2}$ continuaban aproximadamente de la misma forma, en la **fase de anticipación/asignación** se le asignaba un compañero de juego (computadora, confederado o amigo) y se le daba el mensaje de que su compañero estaba tomando su decisión, posteriormente en la **fase de decisión** se le indicaba al participante cuál había sido la decisión de su compañero (si invirtió sus 2 pesos o no), se le recordaba su nivel de promesas (si se trataba de ensayos con promesas) y, en el caso de que su compañero hubiera invertido, se le pedía que decidiera si pagaba de regreso o no.
+Finalmente, en la **fase de feedback** se mostraban los pagos para ese ensayo y se repetía la secuencia.
+La tarea se programó en PsychoPy2 versión 1.84.2, que registraba las respuestas de los sujetos y los tiempos de reacción en segundos.
+
+```{r figA, fig.cap='Fig. A. Task of promises and social closeness'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/task.png")
+
+```
 

### 2019-03-12 Manuscript/draft/Untitled.Rmd
update manuscript

@@
 
-Se incluyeron 20 personas voluntarias (18 mujeres), en un rango de edad de 19-33 años, su nivel educativo mínimo fue licenciatura, se trató principalmente de estudiantes de estado civil soltero.
+Se incluyeron 20 personas voluntarias (18 mujeres), en un rango de edad de 19-33 años, su nivel educativo mínimo fue licenciatura, su ocupación principal fue estudiantes y eran solteros.
 Todos los participantes reportaron no tener historial médico de tipo neurológico ni psiquiátrico al momento del experimento.
@@
 
-Se trata de una adaptación de la tarea de confianza y promesas presentada por Baumgartner (2009), que consiste en 24 ensayos entre dos jugadores **A** y **B**, el jugador **A** tiene originalmente 0 pesos mexicanos y el jugador **B** tiene 2 pesos, al jugador **B** se le presenta la oportunidad de invertir su dinero al jugador **A** o conservarlo, si invierte su dinero se multiplica por 5 pesos, de modo que el jugador **A** recibe 10 pesos.
+Todos los participantes realizaron una adaptación de la tarea de confianza y promesas presentada por Baumgartner (2009), que consiste en 24 ensayos entre dos jugadores **A** y **B**, el jugador **A** tiene originalmente 0 pesos mexicanos y el jugador **B** tiene 2 pesos, al jugador **B** se le presenta la oportunidad de invertir su dinero al jugador **A** o conservarlo, si invierte su dinero se multiplica por 5 pesos, de modo que el jugador **A** recibe 10 pesos.
 Finalmente, el jugador **A** toma la decisión de pagar la mitad al jugador **B** o quedarse los 10 pesos.
@@
 
-La variación respecto a la tarea original es que en nuestro experimento se presentan tres compañeros de juego con tres niveles de cercanía social **computadora** (cercanía nula), **confederado** (cercanía baja) y **amigo** (cercanía alta) en el papel del jugador **B**, mientras que el sujeto siempre realiza el papel de jugador **A**.
+La variación respecto a la tarea original es que en nuestro experimento se presentaron tres compañeros de juego con tres niveles de cercanía social en el papel del jugador **B**: **computadora** (cercanía nula), **confederado** (cercanía baja) y **amigo** (cercanía alta), mientras que el participante principal siempre fungió el papel del jugador **A**.
 Cada compañero de juego realizó el rol de **B** en 8 de los 24 ensayos totales, sin embargo, tanto la condición de promesas como la de cercanía social fueron presentadas al sujeto **A** en orden pseudoaleatorio, lo que significa que se realizó la aleatorización de los ensayos una vez y se mantuvo el mismo orden para todos los sujetos.
@@
 
-En la figura A se muestra un diagrama de la cronología de la tarea experimental, cada caja representa una pantalla que se le mostró a los sujetos de manera secuencial de izquierda a derecha, se incluyen las duraciones de cada pantalla en segundos.
+En la figura A se muestra un diagrama de la cronología de la tarea experimental con las duraciones de cada fase en segundos, cada caja de izquierda a derecha representa una pantalla que se le mostró a los sujetos de manera secuencial.
 La parte A$_{1}$ corresponde a un ejemplo de los ensayos sin promesas y la A$_{2}$ de los ensayos con promesas.
-La fase de fijación sólo consistía en un período en el que el sujeto tenía que prestar atención sin realizar ninguna conducta en particular, la **fase de promesas** en la parte A$_{1}$ le indicaba al sujeto que los siguientes tres ensayos se podían decidir sin el efecto de la promesa, mientras que en A$_{2}$ se le pedía al sujeto que decidiera entre _siempre_, _casi siempre_, _algunas veces_ o _nunca_ pagaría la mitad.
-A lo anterior le seguía otro período de fijación, posteriormente los ensayos tanto en A$_{1}$ como en A$_{2}$ continuaban aproximadamente de la misma forma, en la **fase de anticipación/asignación** se le asignaba un compañero de juego (computadora, confederado o amigo) y se le daba el mensaje de que su compañero estaba tomando su decisión, posteriormente en la **fase de decisión** se le indicaba al participante cuál había sido la decisión de su compañero (si invirtió sus 2 pesos o no), se le recordaba su nivel de promesas (si se trataba de ensayos con promesas) y, en el caso de que su compañero hubiera invertido, se le pedía que decidiera si pagaba de regreso o no.
+La fase de fijación sólo consistió en un período en el que el sujeto prestaba atención sin realizar ninguna conducta en particular, la **fase de promesas** en la parte A$_{1}$ le indicó al sujeto que los siguientes tres ensayos se podían decidir sin el efecto de la promesa, mientras que en A$_{2}$ se le pidió al sujeto que decidiera entre _siempre_, _casi siempre_, _algunas veces_ o _nunca_ pagar la mitad.
+A lo anterior, le siguió otro período de fijación, posteriormente los ensayos tanto en A$_{1}$ como en A$_{2}$ continuaron aproximadamente de la misma forma, en la **fase de anticipación/asignación** se le indicó a los sujetos quién era su compañero de juego para ese ensayo (computadora, confederado o amigo) y se le dió el mensaje de que su compañero estaba tomando su decisión, posteriormente en la **fase de decisión** se le dió al participante la información sobre cuál había sido la decisión de su compañero (si invirtió sus 2 pesos o no), se le recordaba su nivel de promesas (si se trataba de ensayos con promesas) y, en el caso de que su compañero hubiera invertido, se le pedía que decidiera si pagaba de regreso o no.
 Finalmente, en la **fase de feedback** se mostraban los pagos para ese ensayo y se repetía la secuencia.
@@
 
-El modelo de dos mezclas es aproximadamente igual al anterior, sin embargo ahora asume que las decisiones provienen de una *mezcla* de las distribuciones de dos grupos, una distribución Beta con parámetros $\mu_1\lambda_1$ y $(1 - \mu_1) \lambda_1$ y otra con párametros $\mu_2\lambda_2$ y $(1 - \mu_2) \lambda_2$, el parámetro $z_i$ determina la probabilidad de que cada sujeto pertenezca a uno de dos grupos latentes, se distribuye Bernoulli con probabilidad $\phi$, que a su vez sigue una distribución inicial Beta relativamente poco informativa.
+El modelo de dos mezclas es aproximadamente igual al anterior, sin embargo ahora asume que las decisiones provienen de una *mezcla* de las distribuciones de dos subpoblaciones, una distribución Beta con parámetros $\mu_1\lambda_1$ y $(1 - \mu_1) \lambda_1$ y otra con párametros $\mu_2\lambda_2$ y $(1 - \mu_2) \lambda_2$, el parámetro $z_i$ determina la probabilidad de que cada sujeto pertenezca a uno de dos grupos latentes, se distribuye Bernoulli con probabilidad $\phi$, que a su vez sigue una distribución inicial Beta relativamente poco informativa.
 
@@
 Asimismo, se modeló la variabilidad intrasujeto en los tiempos de reacción por medio de interceptos variantes por participante.
-El modelo se ajustó en R por medio de **brms** y **Stan** en condiciones iguales a las descritas anteriormente y con resultados adecuados de convergencia para todos los parámetros, $\hat{R} = 1$.
+El modelo se ajustó en R por medio de **brms** y **Stan** en condiciones iguales a las descritas anteriormente para el modelo jerárquico y obtuvo resultados adecuados de convergencia para todos los parámetros, $\hat{R} = 1$.
 
@@
 La figura 3A muestra la incertidumbre con respecto a la estimación de los coeficientes, la linea central indica la mediana de la distribución y el área sombreada el intervalo del 50 % de probabilidad.
+Se puede observar que la condición de promesas y cercanía social alta (amigo) obtuvieron estimaciones mayores que el intercepto, que para este caso podría considerarse la estimación del efecto de la ausencia de promesas y cercanía social.
+
 Para visualizar el efecto conjunto de las condiciones experimentales en la probabilidad de pagar la mitad, se realizó su combinación lineal para obtener un sólo predictor ($\mathrm{linpred_i}$), se le aplicó la función ligadora inversa *logit* y se transformó su output en probabilidades por medio de la función logistica $1 / (1 + \exp(-\mathrm{linpred}_i))$.
-
 La figura 3B muestra la probabilidad de pagar la mitad, como función de la combinación lineal de las condiciones experimentales, las lineas delgadas muestran la incertidumbre en la predicción con una muestra aleatoria de tamaño 100 de las distribuciones posteriores de los parámetros poblacionales.
 La linea gruesa representa la media de las distribuciones posteriores de los parámetros poblacionales.
+Se puede observar, que a medida que se incrementa el valor del predictor lineal, se incrementa rápidamente la probabilidad de pago.
+Cabe destacar que el el valor del predictor lineal aumenta con la presencia de las condiciones experimentales de cercanía social y promesas.
 
@@
 
+Se puede observar en algunos sujetos (e.g sujeto 2 ó 17) que a medida que incrementa el predictor lineal, aumenta rápidamente la probabilidad de pago, sin embargo, para otros (e.g.
+sujeto 1 ó 5), existe incertidumbre respecto al efecto del predictor lineal, lo que sugiere que aún en la condición de promesas y en presencia de compañeros con cercanía social, el participante podría no pagar.
+La incertidumbre en la predicción de las respuestas de algunos jugadores, sugiere que podrían existir por lo menos dos procesos cognitivos que podrían dar lugar las decisiones observadas, lo que se explora con mayor detenimiento con el modelo de mezclas latentes.
+
 ```{r fig4, fig.cap='Fig. 4 Estimates with uncertainty by subject'}
@@
 La **distribución posterior predictiva** consiste en simular el tipo de observaciones que podrían surgir con el modelo original, pero una vez que los parámetros de éste han sido actualizados con los datos observados.
-En este caso, cuando el modelo ha aprendido de las decisiones de los sujetos, tiene la capacidad de generar una _"replica"_ de los datos observados, por cada combinación de los parámetros obtenidos en la distribución posterior.
+En este caso, cuando el modelo ha aprendido de las decisiones de los sujetos, tiene la capacidad de generar una _"réplica"_ de los datos observados, para cada combinación de los parámetros obtenidos en la distribución posterior.
 
-En la figura 5, se obtuvieron 50 muestras aleatorias de la distribución posterior de los parámetros poblacionales $\beta$ y se simularon 50 datasets con las decisiones que se esperarían con esos parámetros.
+En la figura 5, se obtuvieron 50 muestras aleatorias de la distribución posterior de los parámetros poblacionales $\beta$ y se simularon 50 datasets con las decisiones que se esperarían dado el valor de esos parámetros.
 Se presentan en barras las decisiones realizadas por nuestros participantes $y$, mientras que el punto con dispersión muestra la distribución de los valores esperados en las 50 _replicas_ $y_{rep}$.
+Se puede observar que el modelo reproduce con bastante precisión los datos observados, lo cual es un indicador del adecuado ajuste del modelo.
 
@@
 Una de las subpoblaciones tiene alta probabilidad de pagar $\mu_1$, la que denominamos __honestos__ y la otra subpoblación tiene una probabilidad de pagar menor por lo que fue denominada __deshonestos__ $\mu_2$.
-En la figura 6A se muestran las distribuciones posteriores de las dos $\mu$'s, correspondientes a la probabilidad de pagar de los dos grupos latentes.
+En la figura 6A se muestran las distribuciones posteriores de las dos $\mu$'s, correspondientes a la probabilidad de pagar de las dos subpoblaciones latentes.
 Y en la figura 6B se presentan las decisiones de dos sujetos extraídos de las dos subpoblaciones, el sujeto 5 de la subpoblación de __deshonestos__ y el 17 de la subpoblación de __honestos__.
-En la figura 7 se muestra la frecuencia de las decisiones de los dos grupos latentes, dependiendo de si estaban en la condición con o sin promesa.
+Se puede observar que el sujeto 5 decide no pagar en la mayoría de los ensayos, independientemente de la condición de promesas y cercanía social, mientras que el sujeto 17 sólo decidió no pagar en tres ocasiones cuando su compañero fue la computadora.
 
@@
 ---
+
+En la figura 7 se muestra la frecuencia de las decisiones de los dos grupos latentes, dependiendo de si estaban en la condición con o sin promesa.
 

### 2019-03-16 Manuscript/draft/Untitled.tex
.

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Método},
            pdfauthor={Said E. Jiménez},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{Método}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Said E. Jiménez}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{6 de marzo de 2019}

\begin{document}
\maketitle

\subsection{Participantes}\label{participantes}

Se incluyeron 20 personas voluntarias (18 mujeres), en un rango de edad
de 19-33 años, su nivel educativo mínimo fue licenciatura, su ocupación
principal fue estudiantes y eran solteros. Todos los participantes
reportaron no tener historial médico de tipo neurológico ni psiquiátrico
al momento del experimento. Los participantes acudieron al estudio con
un amigo considerado \emph{cercano} por ellos mismos, quien cumplía las
siguientes características: era una persona del mismo sexo que el
participante, no tenía un vínculo familiar y no se trataba de una
persona con una relación de tipo sentimental y/o sexual.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsection{Materiales y
Procedimiento}\label{materiales-y-procedimiento}

Todos los participantes realizaron una adaptación de la tarea de
confianza y promesas presentada por Baumgartner (2009), que consiste en
24 ensayos entre dos jugadores \textbf{A} y \textbf{B}, el jugador
\textbf{A} tiene originalmente 0 pesos mexicanos y el jugador \textbf{B}
tiene 2 pesos, al jugador \textbf{B} se le presenta la oportunidad de
invertir su dinero al jugador \textbf{A} o conservarlo, si invierte su
dinero se multiplica por 5 pesos, de modo que el jugador \textbf{A}
recibe 10 pesos. Finalmente, el jugador \textbf{A} toma la decisión de
pagar la mitad al jugador \textbf{B} o quedarse los 10 pesos. La
estructura descrita se repite en 24 ensayos, sin embargo, en 4 de los
ensayos el jugador \textbf{A} puede enviar una promesa a \textbf{B}, las
promesas son que \emph{siempre}, \emph{casi siempre}, \emph{algunas
veces} o \emph{nunca} pagaran la mitad. Cada promesa es válida por tres
ensayos, de modo que 12 de los ensayos tienen el efecto de la promesa y
los otros 12 no lo tienen.

La variación respecto a la tarea original es que en nuestro experimento
se presentaron tres compañeros de juego con tres niveles de cercanía
social en el papel del jugador \textbf{B}: \textbf{computadora}
(cercanía nula), \textbf{confederado} (cercanía baja) y \textbf{amigo}
(cercanía alta), mientras que el participante principal siempre fungió
el papel del jugador \textbf{A}. Cada compañero de juego realizó el rol
de \textbf{B} en 8 de los 24 ensayos totales, sin embargo, tanto la
condición de promesas como la de cercanía social fueron presentadas al
sujeto \textbf{A} en orden pseudoaleatorio, lo que significa que se
realizó la aleatorización de los ensayos una vez y se mantuvo el mismo
orden para todos los sujetos. Con el fin de simplificar la tarea y
homogeneizar la experiencia de todos nuestros participantes, se
programaron \emph{a priori} las decisiones de los compañeros \textbf{B}
sobre si invertían o no su monto inicial, se programó que los tres
compañeros decidieran invertir en 6 ensayos y no invertir en 2, los
cuales también se presentaron al sujeto \textbf{A} en orden
pseudoaleatorio. La historia encubierta para todos nuestros sujetos en
el papel de \textbf{A} fue que estarían jugando en tiempo real con su
amigo, el confederado (que se le dijo que sería otra persona desconocida
de su mismo sexo) y la computadora.

En la figura A se muestra un diagrama de la cronología de la tarea
experimental con las duraciones de cada fase en segundos, cada caja de
izquierda a derecha representa una pantalla que se le mostró a los
sujetos de manera secuencial. La parte A\(_{1}\) corresponde a un
ejemplo de los ensayos sin promesas y la A\(_{2}\) de los ensayos con
promesas. La fase de fijación sólo consistió en un período en el que el
sujeto prestaba atención sin realizar ninguna conducta en particular, la
\textbf{fase de promesas} en la parte A\(_{1}\) le indicó al sujeto que
los siguientes tres ensayos se podían decidir sin el efecto de la
promesa, mientras que en A\(_{2}\) se le pidió al sujeto que decidiera
entre \emph{siempre}, \emph{casi siempre}, \emph{algunas veces} o
\emph{nunca} pagar la mitad. A lo anterior, le siguió otro período de
fijación, posteriormente los ensayos tanto en A\(_{1}\) como en
A\(_{2}\) continuaron aproximadamente de la misma forma, en la
\textbf{fase de anticipación/asignación} se le indicó a los sujetos
quién era su compañero de juego para ese ensayo (computadora,
confederado o amigo) y se le dió el mensaje de que su compañero estaba
tomando su decisión, posteriormente en la \textbf{fase de decisión} se
le dió al participante la información sobre cuál había sido la decisión
de su compañero (si invirtió sus 2 pesos o no), se le recordaba su nivel
de promesas (si se trataba de ensayos con promesas) y, en el caso de que
su compañero hubiera invertido, se le pedía que decidiera si pagaba de
regreso o no. Finalmente, en la \textbf{fase de feedback} se mostraban
los pagos para ese ensayo y se repetía la secuencia. La tarea se
programó en PsychoPy2 versión 1.84.2, que registraba las respuestas de
los sujetos y los tiempos de reacción en segundos.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/task}

}

\caption{Fig. A. Task of promises and social closeness}\label{fig:figA}
\end{figure}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsection{Análisis descriptivo de
datos}\label{analisis-descriptivo-de-datos}

Se obtuvieron las proporciones de las decisiones pagar o no pagar la
mitad, así como las promesas realizadas, posteriormente se calcularon
las variaciones en las proporciones de acuerdo a los compañeros de juego
y la condición de presencia o ausencia de promesas.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsection{Modelamiento Bayesiano}\label{modelamiento-bayesiano}

\subsubsection{Modelo Jerárquico}\label{modelo-jerarquico}

Se utilizó inferencia bayesiana para evaluar el efecto de las
condiciones experimentales en la tasa de pago a nivel individual y
poblacional. Para tal propósito se realizó un modelo jerárquico que
asume que la incertidumbre en el efecto de promesas y parejas sobre la
conducta de cada individuo proviene de distribuciones poblacionales
comunes para los parámetros del modelo:

\[
\begin{aligned}
&y_i \sim \mathrm{Bernoulli}(\theta_i) \\
&\mathrm{logit(\theta_i)} = \mathbf{X}\beta  +  \mathbf{Z}u
\end{aligned}
\] En el modelo anterior, cada decisión \(y_i\) proviene de una
distribución Bernoulli con probabilidad de pagar \(\theta_i\), el
objetivo del modelo jerárquico es predecir cada decisión a través la
combinación lineal de los predictores transformados por su función
ligadora inversa \(\mathrm{logit}\). En el modelo anterior, \(\beta\) y
\(u\) son coeficientes a nivel poblacional y nivel individual
respectivamente, mientras que \(\mathbf{X}\), \(\mathbf{Z}\) son sus
correpondientes matrices del diseño.

El modelo estima que la probabilidad \(\theta_i\) de que en cada ensayo
se decida pagar la mitad está en función del efecto de la presencia de
promesas \(\beta^{promise}\), así como de los compañeros con cercanía
social baja \(\beta^{confederate}\) y alta \(\beta^{friend}\). También
asume que pueden existir diferencias individuales en el desempeño
durante la tarea, las cuales son captadas por los parámetros \(u\) y
constituyen ajustes a los coeficientes poblacionales. Cabe remarcar que
el modelo evalúa explícitamente la incertidumbre respecto a \(u\), lo
cual es una ventaja con relación a los modelos que asumen que \(u\) es
parte del término de error.

El modelo se programó en R por medio del paquete \textbf{brms}, que
realiza la inferencia mediante el muestreo por Markov chain Monte Carlo
a través de \textbf{Stan}. Las distribuciones posteriores de todos los
parámetros fueron aproximadas con cuatro cadenas de 2000 iteraciones
cada una, las primeras 1000 iteraciones de cada cadena fueron
descartadas (periodo de calentamiento), para un total de 4000 muestras
post-calentamiento. La convergencia del modelo fue evaluada a través de
la inspección visual de las cadenas y el cálculo del estadístico
\(\hat{R}\), que para todos los parámetros fue de 1, lo que se
interpreta como convergencia.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsubsection{Modelamiento de mezclas
latentes}\label{modelamiento-de-mezclas-latentes}

Asume que las decisiones de los individuos podrían provenir de una
combinación (o \emph{mezcla}) de procesos psicológicos no observables
(\emph{latentes}), el rasgo latente más importante en este experimento
es la (des)honestidad. Se modelaron las diferencias en las tasas de pago
entre participantes como una combinación de \(N\) distribuciones de
subpoblaciones. El modelo asumió que las tasas de pago provenían de una
o dos mezclas de distribuciones, o grupos latentes.

El modelo de una mezcla, asumía que cada decisión \(d_{i,j}\) de cada
sujeto provenía de una distribución Bernoulli con probabilidad
\(\theta_{i,j}\). Asimismo que \(\theta_{i,j}\) provenía de una
distribución jerárquica Beta con parámetros \(\alpha\) y \(\beta\). La
distribución Beta fue reparametrizada en términos de media \(\mu\) y
precisión \(\lambda\), ya que \(\mu = \alpha/(\alpha + \beta)\) y
\(\lambda = \alpha + \beta\).

\[
\begin{aligned}
&\mu \sim \mathrm{Uniform}(0, 1)\\
&\lambda \sim \mathrm{Uniform}(4, 100)\\
&\theta_{i,j} \sim \mathrm{Beta}(\mu\lambda, (1 - \mu)\lambda)\\
&d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j}) 
\end{aligned}
\]

El modelo de dos mezclas es aproximadamente igual al anterior, sin
embargo ahora asume que las decisiones provienen de una \emph{mezcla} de
las distribuciones de dos subpoblaciones, una distribución Beta con
parámetros \(\mu_1\lambda_1\) y \((1 - \mu_1) \lambda_1\) y otra con
párametros \(\mu_2\lambda_2\) y \((1 - \mu_2) \lambda_2\), el parámetro
\(z_i\) determina la probabilidad de que cada sujeto pertenezca a uno de
dos grupos latentes, se distribuye Bernoulli con probabilidad \(\phi\),
que a su vez sigue una distribución inicial Beta relativamente poco
informativa.

Se presenta el modelo de 2 mezclas con la notación propuesta por Lee,
nodos cuadrados representan variables discretas y nodos circulares
variables numéricas. Los nodos sombreados representan variables
observadas, mientras que los nodos no sombreados son variables latentes.
Los dos rectángulos representan repeticiones de la relación entre los
parámetros del modelo para cada sujeto \(i\) y ensayo \(j\). Se
determinó que un individuo pertenecía al grupo de \emph{Deshonestos} si
\(z_i < 0.5\), dado que la probabilidad de que ese sujeto pagara la
mitad en cada ensayo es baja, mientras que se consideró que un individuo
pertenecía al grupo de \emph{Honestos} si \(z_i > 0.5\), dado que la
probabilidad de que el individuo pague la mitad en cada ensayo es alta.

\[
\begin{aligned} 
&\mu_1 \sim \mathrm{Uniform}(0, 1)\\
&\mu_2 \sim \mathrm{Uniform}(\mu_1, 1)\\
&\lambda_{1:2} \sim \mathrm{Uniform}(4, 100)\\
&z_i \sim \mathrm{Bernoulli}(\phi)\\
&\theta_{i,j} \sim \Bigg\{
  \begin{array} {lr} 
    \mathrm{Beta}(\mu_1\lambda_1, (1 - \mu_1)\lambda_1) & \mbox{if} & z_i = 0 \\
    \mathrm{Beta}(\mu_2\lambda_2, (1 - \mu_2)\lambda_2) & \mbox{if} & z_i = 1
  \end{array} \\
&d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j})\\
&\phi \sim \mathrm{Beta}(5, 5)
\end{aligned}
\]

Los modelos de 1 y 2 mezclas, se programaron en R mediante el paquete
\textbf{rjags}, que realiza la inferencia mediante el muestreo por
Markov chain Monte Carlo a través de \textbf{JAGS}. Las distribuciones
posteriores de todos los parámetros fueron aproximadas con tres cadenas
de 26000 iteraciones cada una, se descartaron las primeras 6000 de cada
cadena como periodo de calentamiento, para un total de 60000 muestras
post-calentamiento. La convergencia del modelo fue evaluada a través de
la inspección visual de las cadenas y el cálculo del estadístico
\(\hat{R}\), que varió de 1 a 1.05 para todos los parámetros lo que
indica convergencia.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsubsection{Modelamiento de los tiempos de
reacción}\label{modelamiento-de-los-tiempos-de-reaccion}

Un hallazgo constante en la investigación sobre engaño y deshonestidad,
es la diferencia en los tiempos de reacción entre quienes toman
decisiones \emph{deshonestas} vs.~decisiones \emph{honestas}, en
general, se han encontrado latencias breves en personas
\emph{deshonestas} en comparación con las de las personas
\emph{honestas}.

Se estimaron las medias poblacionales del grupo de deshonestos y
honestos mediante un modelo bayesiano jerárquico que asumía que el
tiempo de reacción proviene de una distribución
\(rt_i \sim \mathrm{Half-Normal}(0, 5)\) (dado que no puede haber
tiempos de reacción negativos), con parámetros \(\mu_{Dishonest}\) y
\(\mu_{Honest}\) y desviación estándar común \(\sigma\).

Asimismo, se modeló la variabilidad intrasujeto en los tiempos de
reacción por medio de interceptos variantes por participante. El modelo
se ajustó en R por medio de \textbf{brms} y \textbf{Stan} en condiciones
iguales a las descritas anteriormente para el modelo jerárquico y obtuvo
resultados adecuados de convergencia para todos los parámetros,
\(\hat{R} = 1\).

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsubsection{Contraste de hipótesis}\label{contraste-de-hipotesis}

Para los modelos de la tasa de pago y tiempo de reacción se utilizó el
factor de Bayes por medio del método de Savage-Dickey, que calcula la
razón de la densidad de la distribución posterior sobre la densidad de
la distribución inicial de algún parámetro en el punto de interés.
Específicamente para el modelo de la tasa de pago, se evaluó la
hipótesis de si las promesas tendrían un efecto positivo en las tasas de
pago (\(H_1: \beta^{promise} > 0\)), así como si la cercanía social alta
(amigo) tendría mayores tasas de pago que la cercanía social baja
(confederado) (\(H_1: \beta^{friend} - \beta^{confederate} > 0\)). Para
el modelo del tiempo de reacción, la hipótesis fue si los
\emph{deshonestos} tendrían tiempos breves en comparación con los
\emph{honestos} (\(H_1: \mu_{Dishonest} - \mu_{Honest} < 0\)).

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsubsection{Comparación de modelos}\label{comparacion-de-modelos}

Los modelos de una y dos mezclas se compararon por medio del criterio de
información DIC (deviance information criteria), en el que los puntajes
bajos indican mejores modelos. La estimación de la diferencia entre el
modelo de 1 y 2 mezclas favorece al modelo de dos mezclas
(\(\mathrm{Difference}= 1.21\), \(\mathrm{SE}= 3.49\)).

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsection{Resultados}\label{resultados}

\subsubsection{Descriptivos}\label{descriptivos}

Se muestra en la figura 1, la frecuencia de veces en que los
participantes pagaron la mitad, así como la frecuencia de promesas que
fueron seleccionadas. En la figura 2, se muestra la proporción de pagos
realizados dependiendo de cada pareja y de la condición de promesas.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig1}

}

\caption{Fig. 1 Frecuencies of paying and Promise choice}\label{fig:fig1}
\end{figure}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig2}

}

\caption{Fig. 2 Rates by partners and promise condition}\label{fig:fig2}
\end{figure}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsubsection{Resultados: modelo
jerárquico}\label{resultados-modelo-jerarquico}

En la tabla 1, se muestran los efectos poblacionales del modelo
bayesiano jerárquico para la tasa de pago. Se presentan las estimaciones
de cada coeficiente del modelo en escala \emph{logit}, su error estándar
y los intervalos de credibilidad bayesianos del 95\%. Los cuales indican
los límites inferiores y superiores de las estimaciones entre los que se
ubica el 95 \% de probabilidad.

Table 1. Population-Level Effects of Task

\begin{longtable}[]{@{}lrrrr@{}}
\toprule
Term & Estimate & SE & L-95\% CI & U-95\% CI\tabularnewline
\midrule
\endhead
\(\beta^0\) & -1.62 & 0.40 & -2.31 & -1.02\tabularnewline
\(\beta^{promise}\) & 1.27 & 0.40 & 0.64 & 1.92\tabularnewline
\(\beta^{confederate}\) & 2.01 & 0.55 & 1.20 & 2.97\tabularnewline
\(\beta^{friend}\) & 4.15 & 0.77 & 3.07 & 5.49\tabularnewline
\bottomrule
\end{longtable}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

La figura 3A muestra la incertidumbre con respecto a la estimación de
los coeficientes, la linea central indica la mediana de la distribución
y el área sombreada el intervalo del 50 \% de probabilidad. Se puede
observar que la condición de promesas y cercanía social alta (amigo)
obtuvieron estimaciones mayores que el intercepto, que para este caso
podría considerarse la estimación del efecto de la ausencia de promesas
y cercanía social.

Para visualizar el efecto conjunto de las condiciones experimentales en
la probabilidad de pagar la mitad, se realizó su combinación lineal para
obtener un sólo predictor (\(\mathrm{linpred_i}\)), se le aplicó la
función ligadora inversa \emph{logit} y se transformó su output en
probabilidades por medio de la función logistica
\(1 / (1 + \exp(-\mathrm{linpred}_i))\). La figura 3B muestra la
probabilidad de pagar la mitad, como función de la combinación lineal de
las condiciones experimentales, las lineas delgadas muestran la
incertidumbre en la predicción con una muestra aleatoria de tamaño 100
de las distribuciones posteriores de los parámetros poblacionales. La
linea gruesa representa la media de las distribuciones posteriores de
los parámetros poblacionales. Se puede observar, que a medida que se
incrementa el valor del predictor lineal, se incrementa rápidamente la
probabilidad de pago. Cabe destacar que el el valor del predictor lineal
aumenta con la presencia de las condiciones experimentales de cercanía
social y promesas.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig3}

}

\caption{Fig. 3 Estimates with uncertainty and linear predictor}\label{fig:fig3}
\end{figure}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

En un procedimiento similar al descrito para la figura 3B, la figura 4
representa el efecto conjunto de las condiciones experimentales en la
probabilidad de pagar la mitad para cada sujeto. Ya que el modelo
jerárquico asume que las diferencias individuales se pueden modelar
realizando un ajuste \(u\) a los coeficientes poblacionales \(\beta\),
se obtuvieron 50 muestras aleatorias de las distribuciones posteriores
de los parámetros \(u\) para cada sujeto, se realizó el ajuste al modelo
poblacional y se presenta en lineas delgadas la incertidumbre en la
predicción individual.

Se puede observar en algunos sujetos (e.g sujeto 2 ó 17) que a medida
que incrementa el predictor lineal, aumenta rápidamente la probabilidad
de pago, sin embargo, para otros (e.g.~sujeto 1 ó 5), existe
incertidumbre respecto al efecto del predictor lineal, lo que sugiere
que aún en la condición de promesas y en presencia de compañeros con
cercanía social, el participante podría no pagar. La incertidumbre en la
predicción de las respuestas de algunos jugadores, sugiere que podrían
existir por lo menos dos procesos cognitivos que podrían dar lugar las
decisiones observadas, lo que se explora con mayor detenimiento con el
modelo de mezclas latentes.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9}

}

\caption{Fig. 4 Estimates with uncertainty by subject}\label{fig:fig4}
\end{figure}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

La \textbf{distribución posterior predictiva} consiste en simular el
tipo de observaciones que podrían surgir con el modelo original, pero
una vez que los parámetros de éste han sido actualizados con los datos
observados. En este caso, cuando el modelo ha aprendido de las
decisiones de los sujetos, tiene la capacidad de generar una
\emph{``réplica''} de los datos observados, para cada combinación de los
parámetros obtenidos en la distribución posterior.

En la figura 5, se obtuvieron 50 muestras aleatorias de la distribución
posterior de los parámetros poblacionales \(\beta\) y se simularon 50
datasets con las decisiones que se esperarían dado el valor de esos
parámetros. Se presentan en barras las decisiones realizadas por
nuestros participantes \(y\), mientras que el punto con dispersión
muestra la distribución de los valores esperados en las 50
\emph{replicas} \(y_{rep}\). Se puede observar que el modelo reproduce
con bastante precisión los datos observados, lo cual es un indicador del
adecuado ajuste del modelo.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig5}

}

\caption{Fig. 5 Posterior predictive distribution of choices by partner}\label{fig:fig5}
\end{figure}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsubsection{Resultados: modelo de mezclas
latentes}\label{resultados-modelo-de-mezclas-latentes}

El modelo de 2-mezclas latentes identificó dos subpoblaciones de tamaño
10; en la tabla 2 se muestran los resúmenes de las distribuciones
posteriores de los parámetros de ambas subpoblaciones y el parámetro de
la mezcla \(\phi\). Una de las subpoblaciones tiene alta probabilidad de
pagar \(\mu_1\), la que denominamos \textbf{honestos} y la otra
subpoblación tiene una probabilidad de pagar menor por lo que fue
denominada \textbf{deshonestos} \(\mu_2\). En la figura 6A se muestran
las distribuciones posteriores de las dos \(\mu\)'s, correspondientes a
la probabilidad de pagar de las dos subpoblaciones latentes. Y en la
figura 6B se presentan las decisiones de dos sujetos extraídos de las
dos subpoblaciones, el sujeto 5 de la subpoblación de
\textbf{deshonestos} y el 17 de la subpoblación de \textbf{honestos}. Se
puede observar que el sujeto 5 decide no pagar en la mayoría de los
ensayos, independientemente de la condición de promesas y cercanía
social, mientras que el sujeto 17 sólo decidió no pagar en tres
ocasiones cuando su compañero fue la computadora.

Table 2. Parameters of 2-Mixture Model

\begin{longtable}[]{@{}lrrrr@{}}
\toprule
Parameter & Mean & SD & L-95\% CI & U-95\% CI\tabularnewline
\midrule
\endhead
\(\mu_{1}\) & 0.56 & 0.05 & 0.44 & 0.65\tabularnewline
\(\mu_{2}\) & 0.70 & 0.05 & 0.61 & 0.82\tabularnewline
\(\lambda_{1}\) & 48.99 & 28.57 & 5.50 & 97.49\tabularnewline
\(\lambda_{2}\) & 54.79 & 26.24 & 7.80 & 97.61\tabularnewline
\(\phi\) & 0.49 & 0.15 & 0.21 & 0.77\tabularnewline
\bottomrule
\end{longtable}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig6}

}

\caption{Fig. 6 Posteriors from two latent groups and two cases}\label{fig:fig6}
\end{figure}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

En la figura 7 se muestra la frecuencia de las decisiones de los dos
grupos latentes, dependiendo de si estaban en la condición con o sin
promesa.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b}

}

\caption{Fig. 7 Payment frecuency by latent group and promise condition}\label{fig:fig7}
\end{figure}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsubsection{Resultados: tiempo de
reacción}\label{resultados-tiempo-de-reaccion}

En la tabla 3 se presentan las estimaciones poblacionales del modelo
bayesiano de los tiempos de reacción, se resumen las distribuciones
posteriores de cada parámetro, incluyendo la estimación de su media, su
error estándar y los intervalos de credibilidad bayesianos del 95\%. En
la figura 8A se muestran con puntos los tiempos de reacción en segundos
para cada decisión realizada de acuerdo con cada subgrupo, se agregó a
cada grupo un kernel de densidad simétrico para representar la cantidad
de casos acumulados a lo largo de los diferentes valores del tiempo de
reacción.

En la figura 8B se presenta la diferencia de las estimaciones
posteriores, el punto con dispersión representa el estimador puntual de
la diferencia entre las subpoblaciones y el intervalo de credibilidad
bayesiano del 95\%. El histograma representa la distribución posterior
de la diferencia entre los parámetros de las subpoblaciones.

Table 3. Parameters estimates of reaction time model

\begin{longtable}[]{@{}lrrrr@{}}
\toprule
Term & Estimate & SE & L-95\% CI & U-95\% CI\tabularnewline
\midrule
\endhead
\(\mu_{Dishonest}\) & 2.93 & 0.23 & 2.55 & 3.31\tabularnewline
\(\mu_{Honest}\) & 3.06 & 0.22 & 2.69 & 3.42\tabularnewline
\(\mu_{difference}\) & -0.13 & 0.32 & -0.77 & 0.52\tabularnewline
\(\sigma\) & 1.23 & 0.05 & 1.15 & 1.31\tabularnewline
\(\sigma_{subject}\) & 0.65 & 0.14 & 0.45 & 0.89\tabularnewline
\bottomrule
\end{longtable}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig8}

}

\caption{Fig. 8 Differences in reaction time by latent group}\label{fig:fig8}
\end{figure}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\subsubsection{Resultados: contraste de hipótesis y comparación de
modelos}\label{resultados-contraste-de-hipotesis-y-comparacion-de-modelos}

En la tabla 4 se muestran las hipótesis contrastadas, las estimaciones,
los errores estándar y el factor de Bayes (BF) para cada una. Se
interpretan los BF's como evidencia en favor de la hipótesis alterna
\(BF_{10}\) de acuerdo a la clasificación de Jeffreys (1961). La
hipótesis uno de si la condición de promesas tiene un efecto superior a
0, se interpreta como ``evidencia extrema'' a su favor, la hipótesis de
si el efecto en la tasa de pago es superior para el amigo que para el
confederado también se interpreta como ``evidencia superior'' a su
favor, la hipótesis sobre si la diferencia entre los tiempos de reacción
entre honestos y deshonestos es menor a cero, se interpreta como
``evidencia anecdótica'' a su favor.

Dado que el intervalo de credibilidad bayesiano para la estimación de la
diferencia entre los tiempos de reacción de las subpoblaciones incluye
el cero, se decidió evaluar la hipótesis de si la diferencia es igual a
0, el BF correspondiente se interpreta como ``evidencia fuerte'' en
favor a la diferencia igual a 0. Finalmente, se comparó el DIC para los
modelos de una (\(DIC_{1}\)) y dos (\(DIC_{2}\)) mezclas, cuya
diferencia apoya al modelo de dos mezclas latentes.

Table 4. Hypothesis testing and model comparison

\begin{longtable}[]{@{}lrrr@{}}
\toprule
Hypothesis & Estimate & SE & BF\(_{10}\)\tabularnewline
\midrule
\endhead
\(\beta^{promise} > 0\) & 1.27 & 0.40 & 499\tabularnewline
\(\beta^{friend} - \beta^{confederate} > 0\) & 2.14 & 0.77 &
665.67\tabularnewline
\(\mu_{Dishonest} - \mu_{Honest} < 0\) & -0.13 & 0.32 &
1.96\tabularnewline
\(\mu_{Dishonest} - \mu_{Honest} = 0\) & -0.13 & 0.32 &
20.36\tabularnewline
\(DIC_{1} - DIC_{2}\) & 1.21 & 3.49 & -\tabularnewline
\bottomrule
\end{longtable}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\end{document}

### 2019-03-16 Manuscript/pdf/pdf_manuscript_social_closeness.Rmd
.

--- 2019-03-12 Manuscript/draft/Untitled.Rmd
@@
 output: 
-  html_document:
-    theme: cerulean
+  pdf_document:
+    toc: true
+    toc_depth: 3
+    keep_tex: true
 ---
-
-<style>
-body {
-text-align: justify}
-</style>
 
@@
                       dpi = 300)
+
+library(kableExtra)
+
 ```
@@
 Los participantes acudieron al estudio con un amigo considerado _cercano_ por ellos mismos, quien cumplía las siguientes características: era una persona del mismo sexo que el participante, no tenía un vínculo familiar y no se trataba de una persona con una relación de tipo sentimental y/o sexual.
-
----
 
@@
 
-En la figura A se muestra un diagrama de la cronología de la tarea experimental con las duraciones de cada fase en segundos, cada caja de izquierda a derecha representa una pantalla que se le mostró a los sujetos de manera secuencial.
+En la figura 1 se muestra un diagrama de la cronología de la tarea experimental con las duraciones de cada fase en segundos, cada caja de izquierda a derecha representa una pantalla que se le mostró a los sujetos de manera secuencial.
 La parte A$_{1}$ corresponde a un ejemplo de los ensayos sin promesas y la A$_{2}$ de los ensayos con promesas.
@@
 
-```{r figA, fig.cap='Fig. A. Task of promises and social closeness'}
+```{r figA, fig.cap='Task of promises and social closeness'}
 
@@
 
----
+## Modelamiento Bayesiano
 
-## Análisis descriptivo de datos
+### Análisis descriptivo
 
 Se obtuvieron las proporciones de las decisiones pagar o no pagar la mitad, así como las promesas realizadas, posteriormente se calcularon las variaciones en las proporciones de acuerdo a los compañeros de juego y la condición de presencia o ausencia de promesas.
-
----
-
-## Modelamiento Bayesiano
 
@@
 La convergencia del modelo fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que para todos los parámetros fue de 1, lo que se interpreta como convergencia.
-
----
 
@@
   \begin{array} {lr} 
-    \mathrm{Beta}(\mu_1\lambda_1, (1 - \mu_1)\lambda_1) & \mbox{if} & z_i = 0 \\
-    \mathrm{Beta}(\mu_2\lambda_2, (1 - \mu_2)\lambda_2) & \mbox{if} & z_i = 1
+    \mathrm{Beta}(\mu_1\lambda_1, (1 - \mu_1)\lambda_1) \quad \mbox{if} \quad z_i = 0 \\
+    \mathrm{Beta}(\mu_2\lambda_2, (1 - \mu_2)\lambda_2) \quad \mbox{if} \quad z_i = 1
   \end{array} \\
@@
 La convergencia del modelo fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que varió de 1 a 1.05 para todos los parámetros lo que indica convergencia.
-
----
 
@@
 
----
-
 ### Contraste de hipótesis
@@
 
----
-
 ### Comparación de modelos
@@
 
----
-
 ## Resultados
@@
 
-Se muestra en la figura 1, la frecuencia de veces en que los participantes pagaron la mitad, así como la frecuencia de promesas que fueron seleccionadas.
-En la figura 2, se muestra la proporción de pagos realizados dependiendo de cada pareja y de la condición de promesas.
+Se muestra en la figura 2, la frecuencia de veces en que los participantes pagaron la mitad, así como la frecuencia de promesas que fueron seleccionadas.
+En la figura 3, se muestra la proporción de pagos realizados dependiendo de cada pareja y de la condición de promesas.
 
-```{r fig1, fig.cap='Fig. 1 Frecuencies of paying and Promise choice'}
+```{r fig2, fig.cap='Frecuencies of paying and Promise choice'}
 
@@
 
----
-
-```{r fig2, fig.cap='Fig. 2 Rates by partners and promise condition', fig.height=10, fig.width=5}
+```{r fig3, fig.cap='Rates by partners and promise condition', fig.height=10, fig.width=5}
 
@@
 ```
-
----
 
@@
 
----
-
-La figura 3A muestra la incertidumbre con respecto a la estimación de los coeficientes, la linea central indica la mediana de la distribución y el área sombreada el intervalo del 50 % de probabilidad.
+La figura 4A muestra la incertidumbre con respecto a la estimación de los coeficientes, la linea central indica la mediana de la distribución y el área sombreada el intervalo del 50 % de probabilidad.
 Se puede observar que la condición de promesas y cercanía social alta (amigo) obtuvieron estimaciones mayores que el intercepto, que para este caso podría considerarse la estimación del efecto de la ausencia de promesas y cercanía social.
@@
 Para visualizar el efecto conjunto de las condiciones experimentales en la probabilidad de pagar la mitad, se realizó su combinación lineal para obtener un sólo predictor ($\mathrm{linpred_i}$), se le aplicó la función ligadora inversa *logit* y se transformó su output en probabilidades por medio de la función logistica $1 / (1 + \exp(-\mathrm{linpred}_i))$.
-La figura 3B muestra la probabilidad de pagar la mitad, como función de la combinación lineal de las condiciones experimentales, las lineas delgadas muestran la incertidumbre en la predicción con una muestra aleatoria de tamaño 100 de las distribuciones posteriores de los parámetros poblacionales.
+La figura 4B muestra la probabilidad de pagar la mitad, como función de la combinación lineal de las condiciones experimentales, las lineas delgadas muestran la incertidumbre en la predicción con una muestra aleatoria de tamaño 100 de las distribuciones posteriores de los parámetros poblacionales.
 La linea gruesa representa la media de las distribuciones posteriores de los parámetros poblacionales.
@@
 
-```{r fig3, fig.cap='Fig. 3 Estimates with uncertainty and linear predictor'}
+```{r fig4, fig.cap='Estimates with uncertainty and linear predictor'}
 
@@
 
-----
-
-En un procedimiento similar al descrito para la figura 3B, la figura 4 representa el efecto conjunto de las condiciones experimentales en la probabilidad de pagar la mitad para cada sujeto.
+En un procedimiento similar al descrito para la figura 4B, la figura 5 representa el efecto conjunto de las condiciones experimentales en la probabilidad de pagar la mitad para cada sujeto.
 Ya que el modelo jerárquico asume que las diferencias individuales se pueden modelar realizando un ajuste $u$ a los coeficientes poblacionales $\beta$, se obtuvieron 50 muestras aleatorias de las distribuciones posteriores de los parámetros $u$ para cada sujeto, se realizó el ajuste al modelo poblacional y se presenta en lineas delgadas la incertidumbre en la predicción individual.
@@
 
-```{r fig4, fig.cap='Fig. 4 Estimates with uncertainty by subject'}
+```{r fig5, fig.cap='Estimates with uncertainty by subject'}
 
@@
 
----
-
 La **distribución posterior predictiva** consiste en simular el tipo de observaciones que podrían surgir con el modelo original, pero una vez que los parámetros de éste han sido actualizados con los datos observados.
@@
 
-En la figura 5, se obtuvieron 50 muestras aleatorias de la distribución posterior de los parámetros poblacionales $\beta$ y se simularon 50 datasets con las decisiones que se esperarían dado el valor de esos parámetros.
+En la figura 6, se obtuvieron 50 muestras aleatorias de la distribución posterior de los parámetros poblacionales $\beta$ y se simularon 50 datasets con las decisiones que se esperarían dado el valor de esos parámetros.
 Se presentan en barras las decisiones realizadas por nuestros participantes $y$, mientras que el punto con dispersión muestra la distribución de los valores esperados en las 50 _replicas_ $y_{rep}$.
@@
 
-```{r fig5, fig.cap='Fig. 5 Posterior predictive distribution of choices by partner'}
+```{r fig6, fig.cap='Posterior predictive distribution of choices by partner'}
 
@@
 
----
-
 ### Resultados: modelo de mezclas latentes
@@
 Una de las subpoblaciones tiene alta probabilidad de pagar $\mu_1$, la que denominamos __honestos__ y la otra subpoblación tiene una probabilidad de pagar menor por lo que fue denominada __deshonestos__ $\mu_2$.
-En la figura 6A se muestran las distribuciones posteriores de las dos $\mu$'s, correspondientes a la probabilidad de pagar de las dos subpoblaciones latentes.
-Y en la figura 6B se presentan las decisiones de dos sujetos extraídos de las dos subpoblaciones, el sujeto 5 de la subpoblación de __deshonestos__ y el 17 de la subpoblación de __honestos__.
+En la figura 7A se muestran las distribuciones posteriores de las dos $\mu$'s, correspondientes a la probabilidad de pagar de las dos subpoblaciones latentes.
+Y en la figura 7B se presentan las decisiones de dos sujetos extraídos de las dos subpoblaciones, el sujeto 5 de la subpoblación de __deshonestos__ y el 17 de la subpoblación de __honestos__.
 Se puede observar que el sujeto 5 decide no pagar en la mayoría de los ensayos, independientemente de la condición de promesas y cercanía social, mientras que el sujeto 17 sólo decidió no pagar en tres ocasiones cuando su compañero fue la computadora.
@@
 
----
-
-```{r fig6, fig.cap='Fig. 6 Posteriors from two latent groups and two cases'}
+```{r fig7, fig.cap='Posteriors from two latent groups and two cases'}
 
@@
 
----
+En la figura 8 se muestra la frecuencia de las decisiones de los dos grupos latentes, dependiendo de si estaban en la condición con o sin promesa.
 
-En la figura 7 se muestra la frecuencia de las decisiones de los dos grupos latentes, dependiendo de si estaban en la condición con o sin promesa.
-
-```{r fig7, fig.cap='Fig. 7 Payment frecuency by latent group and promise condition', fig.height=10, fig.width=5}
+```{r fig8, fig.cap='Payment frecuency by latent group and promise condition', fig.height=10, fig.width=5}
 
@@
 
----
-
 ### Resultados: tiempo de reacción
@@
 En la tabla 3 se presentan las estimaciones poblacionales del modelo bayesiano de los tiempos de reacción, se resumen las distribuciones posteriores de cada parámetro, incluyendo la estimación de su media, su error estándar y los intervalos de credibilidad bayesianos del 95%.
-En la figura 8A se muestran con puntos los tiempos de reacción en segundos para cada decisión realizada de acuerdo con cada subgrupo, se agregó a cada grupo un kernel de densidad simétrico para representar la cantidad de casos acumulados a lo largo de los diferentes valores del tiempo de reacción.
+En la figura 9A se muestran con puntos los tiempos de reacción en segundos para cada decisión realizada de acuerdo con cada subgrupo, se agregó a cada grupo un kernel de densidad simétrico para representar la cantidad de casos acumulados a lo largo de los diferentes valores del tiempo de reacción.
 
-En la figura 8B se presenta la diferencia de las estimaciones posteriores, el punto con dispersión representa el estimador puntual de la diferencia entre las subpoblaciones y el intervalo de credibilidad bayesiano del 95%.
+En la figura 9B se presenta la diferencia de las estimaciones posteriores, el punto con dispersión representa el estimador puntual de la diferencia entre las subpoblaciones y el intervalo de credibilidad bayesiano del 95%.
 El histograma representa la distribución posterior de la diferencia entre los parámetros de las subpoblaciones.
@@
 
----
-
-```{r fig8, fig.cap='Fig. 8 Differences in reaction time by latent group'}
+```{r fig9, fig.cap='Differences in reaction time by latent group'}
 
@@
 |$DIC_{1} - DIC_{2}$                           |     1.21| 3.49|      -  |
-
----

### 2019-03-16 Manuscript/pdf/pdf_manuscript_social_closeness.tex
.

--- 2019-03-16 Manuscript/draft/Untitled.tex
@@
 
+{
+\setcounter{tocdepth}{3}
+\tableofcontents
+}
 \subsection{Participantes}\label{participantes}
@@
 persona con una relación de tipo sentimental y/o sexual.
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 
-En la figura A se muestra un diagrama de la cronología de la tarea
+En la figura 1 se muestra un diagrama de la cronología de la tarea
 experimental con las duraciones de cada fase en segundos, cada caja de
@@
 
-\caption{Fig. A. Task of promises and social closeness}\label{fig:figA}
+\caption{Task of promises and social closeness}\label{fig:figA}
 \end{figure}
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+\subsection{Modelamiento Bayesiano}\label{modelamiento-bayesiano}
 
-\subsection{Análisis descriptivo de
-datos}\label{analisis-descriptivo-de-datos}
+\subsubsection{Análisis descriptivo}\label{analisis-descriptivo}
 
@@
 y la condición de presencia o ausencia de promesas.
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
-\subsection{Modelamiento Bayesiano}\label{modelamiento-bayesiano}
 
@@
 interpreta como convergencia.
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 indica convergencia.
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
 \subsubsection{Contraste de hipótesis}\label{contraste-de-hipotesis}
@@
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
 \subsubsection{Comparación de modelos}\label{comparacion-de-modelos}
@@
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
 \subsection{Resultados}\label{resultados}
@@
 
-Se muestra en la figura 1, la frecuencia de veces en que los
+Se muestra en la figura 2, la frecuencia de veces en que los
 participantes pagaron la mitad, así como la frecuencia de promesas que
-fueron seleccionadas. En la figura 2, se muestra la proporción de pagos
+fueron seleccionadas. En la figura 3, se muestra la proporción de pagos
 realizados dependiendo de cada pareja y de la condición de promesas.
@@
 
-\caption{Fig. 1 Frecuencies of paying and Promise choice}\label{fig:fig1}
+\caption{Frecuencies of paying and Promise choice}\label{fig:fig2}
 \end{figure}
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 
-\caption{Fig. 2 Rates by partners and promise condition}\label{fig:fig2}
+\caption{Rates by partners and promise condition}\label{fig:fig3}
 \end{figure}
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
-La figura 3A muestra la incertidumbre con respecto a la estimación de
+La figura 4A muestra la incertidumbre con respecto a la estimación de
 los coeficientes, la linea central indica la mediana de la distribución
@@
 probabilidades por medio de la función logistica
-\(1 / (1 + \exp(-\mathrm{linpred}_i))\). La figura 3B muestra la
+\(1 / (1 + \exp(-\mathrm{linpred}_i))\). La figura 4B muestra la
 probabilidad de pagar la mitad, como función de la combinación lineal de
@@
 
-\caption{Fig. 3 Estimates with uncertainty and linear predictor}\label{fig:fig3}
+\caption{Estimates with uncertainty and linear predictor}\label{fig:fig4}
 \end{figure}
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
-En un procedimiento similar al descrito para la figura 3B, la figura 4
+En un procedimiento similar al descrito para la figura 4B, la figura 5
 representa el efecto conjunto de las condiciones experimentales en la
@@
 
-\caption{Fig. 4 Estimates with uncertainty by subject}\label{fig:fig4}
+\caption{Estimates with uncertainty by subject}\label{fig:fig5}
 \end{figure}
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 
-En la figura 5, se obtuvieron 50 muestras aleatorias de la distribución
+En la figura 6, se obtuvieron 50 muestras aleatorias de la distribución
 posterior de los parámetros poblacionales \(\beta\) y se simularon 50
@@
 
-\caption{Fig. 5 Posterior predictive distribution of choices by partner}\label{fig:fig5}
+\caption{Posterior predictive distribution of choices by partner}\label{fig:fig6}
 \end{figure}
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 subpoblación tiene una probabilidad de pagar menor por lo que fue
-denominada \textbf{deshonestos} \(\mu_2\). En la figura 6A se muestran
+denominada \textbf{deshonestos} \(\mu_2\). En la figura 7A se muestran
 las distribuciones posteriores de las dos \(\mu\)'s, correspondientes a
 la probabilidad de pagar de las dos subpoblaciones latentes. Y en la
-figura 6B se presentan las decisiones de dos sujetos extraídos de las
+figura 7B se presentan las decisiones de dos sujetos extraídos de las
 dos subpoblaciones, el sujeto 5 de la subpoblación de
@@
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
 \begin{figure}
@@
 
-\caption{Fig. 6 Posteriors from two latent groups and two cases}\label{fig:fig6}
+\caption{Posteriors from two latent groups and two cases}\label{fig:fig7}
 \end{figure}
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
-En la figura 7 se muestra la frecuencia de las decisiones de los dos
+En la figura 8 se muestra la frecuencia de las decisiones de los dos
 grupos latentes, dependiendo de si estaban en la condición con o sin
@@
 
-\caption{Fig. 7 Payment frecuency by latent group and promise condition}\label{fig:fig7}
+\caption{Payment frecuency by latent group and promise condition}\label{fig:fig8}
 \end{figure}
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 error estándar y los intervalos de credibilidad bayesianos del 95\%. En
-la figura 8A se muestran con puntos los tiempos de reacción en segundos
+la figura 9A se muestran con puntos los tiempos de reacción en segundos
 para cada decisión realizada de acuerdo con cada subgrupo, se agregó a
@@
 
-En la figura 8B se presenta la diferencia de las estimaciones
+En la figura 9B se presenta la diferencia de las estimaciones
 posteriores, el punto con dispersión representa el estimador puntual de
@@
 
-\caption{Fig. 8 Differences in reaction time by latent group}\label{fig:fig8}
+\caption{Differences in reaction time by latent group}\label{fig:fig9}
 \end{figure}
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
 \end{document}

### 2019-03-16 Manuscript/social_closeness_dishonesty.Rmd
Draft in spanish
.

--- 2019-03-04 Manuscript/social_closeness_dishonesty.Rmd
@@
 title: "Social Closeness and Dishonesty"
-thanks: "Replication files are available on the author's Github account..."
+thanks: "Replication files are available on the author's Github account https://github.com/saidejp/social_closeness"
 author:
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE,
+                      warning = FALSE,
+                      error = FALSE,
+                      message = FALSE,
+                      out.width = '80%',
+                      fig.align = 'center',
+                      dpi = 300)
 ```
 
-## R Markdown
+## Participantes
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+Se incluyeron 20 personas voluntarias (18 mujeres), en un rango de edad de 19-33 años, su nivel educativo mínimo fue licenciatura, su ocupación principal fue estudiantes y eran solteros.
+Todos los participantes reportaron no tener historial médico de tipo neurológico ni psiquiátrico al momento del experimento.
+Los participantes acudieron al estudio con un amigo considerado _cercano_ por ellos mismos, quien cumplía las siguientes características: era una persona del mismo sexo que el participante, no tenía un vínculo familiar y no se trataba de una persona con una relación de tipo sentimental y/o sexual.
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+---
 
-```{r cars}
-summary(cars)
+## Materiales y Procedimiento
+
+Todos los participantes realizaron una adaptación de la tarea de confianza y promesas presentada por Baumgartner (2009), que consiste en 24 ensayos entre dos jugadores **A** y **B**, el jugador **A** tiene originalmente 0 pesos mexicanos y el jugador **B** tiene 2 pesos, al jugador **B** se le presenta la oportunidad de invertir su dinero al jugador **A** o conservarlo, si invierte su dinero se multiplica por 5 pesos, de modo que el jugador **A** recibe 10 pesos.
+Finalmente, el jugador **A** toma la decisión de pagar la mitad al jugador **B** o quedarse los 10 pesos.
+La estructura descrita se repite en 24 ensayos, sin embargo, en 4 de los ensayos el jugador **A** puede enviar una promesa a **B**, las promesas son que _siempre_, _casi siempre_, _algunas veces_ o _nunca_ pagaran la mitad.
+Cada promesa es válida por tres ensayos, de modo que 12 de los ensayos tienen el efecto de la promesa y los otros 12 no lo tienen.
+
+La variación respecto a la tarea original es que en nuestro experimento se presentaron tres compañeros de juego con tres niveles de cercanía social en el papel del jugador **B**: **computadora** (cercanía nula), **confederado** (cercanía baja) y **amigo** (cercanía alta), mientras que el participante principal siempre fungió el papel del jugador **A**.
+Cada compañero de juego realizó el rol de **B** en 8 de los 24 ensayos totales, sin embargo, tanto la condición de promesas como la de cercanía social fueron presentadas al sujeto **A** en orden pseudoaleatorio, lo que significa que se realizó la aleatorización de los ensayos una vez y se mantuvo el mismo orden para todos los sujetos.
+Con el fin de simplificar la tarea y homogeneizar la experiencia de todos nuestros participantes, se programaron _a priori_ las decisiones de los compañeros **B** sobre si invertían o no su monto inicial, se programó que los tres compañeros decidieran invertir en 6 ensayos y no invertir en 2, los cuales también se presentaron al sujeto **A** en orden pseudoaleatorio.
+La historia encubierta para todos nuestros sujetos en el papel de **A** fue que estarían jugando en tiempo real con su amigo, el confederado (que se le dijo que sería otra persona desconocida de su mismo sexo) y la computadora.
+
+En la figura A se muestra un diagrama de la cronología de la tarea experimental con las duraciones de cada fase en segundos, cada caja de izquierda a derecha representa una pantalla que se le mostró a los sujetos de manera secuencial.
+La parte A$_{1}$ corresponde a un ejemplo de los ensayos sin promesas y la A$_{2}$ de los ensayos con promesas.
+La fase de fijación sólo consistió en un período en el que el sujeto prestaba atención sin realizar ninguna conducta en particular, la **fase de promesas** en la parte A$_{1}$ le indicó al sujeto que los siguientes tres ensayos se podían decidir sin el efecto de la promesa, mientras que en A$_{2}$ se le pidió al sujeto que decidiera entre _siempre_, _casi siempre_, _algunas veces_ o _nunca_ pagar la mitad.
+A lo anterior, le siguió otro período de fijación, posteriormente los ensayos tanto en A$_{1}$ como en A$_{2}$ continuaron aproximadamente de la misma forma, en la **fase de anticipación/asignación** se le indicó a los sujetos quién era su compañero de juego para ese ensayo (computadora, confederado o amigo) y se le dió el mensaje de que su compañero estaba tomando su decisión, posteriormente en la **fase de decisión** se le dió al participante la información sobre cuál había sido la decisión de su compañero (si invirtió sus 2 pesos o no), se le recordaba su nivel de promesas (si se trataba de ensayos con promesas) y, en el caso de que su compañero hubiera invertido, se le pedía que decidiera si pagaba de regreso o no.
+Finalmente, en la **fase de feedback** se mostraban los pagos para ese ensayo y se repetía la secuencia.
+La tarea se programó en PsychoPy2 versión 1.84.2, que registraba las respuestas de los sujetos y los tiempos de reacción en segundos.
+
+```{r figA, fig.cap='Fig. A. Task of promises and social closeness'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/task.png")
+
 ```
 
-## Including Plots
+---
 
-You can also embed plots, for example:
+## Análisis descriptivo de datos
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+Se obtuvieron las proporciones de las decisiones pagar o no pagar la mitad, así como las promesas realizadas, posteriormente se calcularon las variaciones en las proporciones de acuerdo a los compañeros de juego y la condición de presencia o ausencia de promesas.
+
+---
+
+## Modelamiento Bayesiano
+
+### Modelo Jerárquico
+
+Se utilizó inferencia bayesiana para evaluar el efecto de las condiciones experimentales en la tasa de pago a nivel individual y poblacional.
+Para tal propósito se realizó un modelo jerárquico que asume que la incertidumbre en el efecto de promesas y parejas sobre la conducta de cada individuo proviene de distribuciones poblacionales comunes para los parámetros del modelo:
+
+$$
+\begin{aligned}
+&y_i \sim \mathrm{Bernoulli}(\theta_i) \\
+&\mathrm{logit(\theta_i)} = \mathbf{X}\beta  +  \mathbf{Z}u
+\end{aligned}
+$$
+En el modelo anterior, cada decisión $y_i$ proviene de una distribución Bernoulli con probabilidad de pagar $\theta_i$, el objetivo del modelo jerárquico es predecir cada decisión a través la combinación lineal de los predictores transformados por su función ligadora inversa $\mathrm{logit}$.
+En el modelo anterior, $\beta$ y $u$ son coeficientes a nivel poblacional y nivel individual respectivamente, mientras que $\mathbf{X}$, $\mathbf{Z}$ son sus correpondientes matrices del diseño.
+
+El modelo estima que la probabilidad $\theta_i$ de que en cada ensayo se decida pagar la mitad está en función del efecto de la presencia de promesas $\beta^{promise}$, así como de los compañeros con cercanía social baja $\beta^{confederate}$ y alta $\beta^{friend}$.
+También asume que pueden existir diferencias individuales en el desempeño durante la tarea, las cuales son captadas por los parámetros $u$ y constituyen ajustes a los coeficientes poblacionales.
+Cabe remarcar que el modelo evalúa explícitamente la incertidumbre respecto a $u$, lo cual es una ventaja con relación a los modelos que asumen que $u$ es parte del término de error.
+
+El modelo se programó en R por medio del paquete **brms**, que realiza la inferencia mediante el muestreo por Markov chain Monte Carlo a través de **Stan**.
+Las distribuciones posteriores de todos los parámetros fueron aproximadas con cuatro cadenas de 2000 iteraciones cada una, las primeras 1000 iteraciones de cada cadena fueron descartadas (periodo de calentamiento), para un total de 4000 muestras post-calentamiento.
+La convergencia del modelo fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que para todos los parámetros fue de 1, lo que se interpreta como convergencia.
+
+---
+
+### Modelamiento de mezclas latentes
+
+Asume que las decisiones de los individuos podrían provenir de una combinación (o *mezcla*) de procesos psicológicos no observables (*latentes*), el rasgo latente más importante en este experimento es la (des)honestidad.
+Se modelaron las diferencias en las tasas de pago entre participantes como una combinación de $N$ distribuciones de subpoblaciones.
+El modelo asumió que las tasas de pago provenían de una o dos mezclas de distribuciones, o grupos latentes.
+
+El modelo de una mezcla, asumía que cada decisión $d_{i,j}$ de cada sujeto provenía de una distribución Bernoulli con probabilidad $\theta_{i,j}$.
+Asimismo que $\theta_{i,j}$ provenía de una distribución jerárquica Beta con parámetros $\alpha$ y $\beta$.
+La distribución Beta fue reparametrizada en términos de media $\mu$ y precisión $\lambda$, ya que $\mu = \alpha/(\alpha + \beta)$ y $\lambda = \alpha + \beta$.
+
+$$
+\begin{aligned}
+&\mu \sim \mathrm{Uniform}(0, 1)\\
+&\lambda \sim \mathrm{Uniform}(4, 100)\\
+&\theta_{i,j} \sim \mathrm{Beta}(\mu\lambda, (1 - \mu)\lambda)\\
+&d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j}) 
+\end{aligned}
+$$
+
+El modelo de dos mezclas es aproximadamente igual al anterior, sin embargo ahora asume que las decisiones provienen de una *mezcla* de las distribuciones de dos subpoblaciones, una distribución Beta con parámetros $\mu_1\lambda_1$ y $(1 - \mu_1) \lambda_1$ y otra con párametros $\mu_2\lambda_2$ y $(1 - \mu_2) \lambda_2$, el parámetro $z_i$ determina la probabilidad de que cada sujeto pertenezca a uno de dos grupos latentes, se distribuye Bernoulli con probabilidad $\phi$, que a su vez sigue una distribución inicial Beta relativamente poco informativa.
+
+Se presenta el modelo de 2 mezclas con la notación propuesta por Lee, nodos cuadrados representan variables discretas y nodos circulares variables numéricas.
+Los nodos sombreados representan variables observadas, mientras que los nodos no sombreados son variables latentes.
+Los dos rectángulos representan repeticiones de la relación entre los parámetros del modelo para cada sujeto $i$ y ensayo $j$.
+Se determinó que un individuo pertenecía al grupo de *Deshonestos* si $z_i < 0.5$, dado que la probabilidad de que ese sujeto pagara la mitad en cada ensayo es baja, mientras que se consideró que un individuo pertenecía al grupo de *Honestos* si $z_i > 0.5$, dado que la probabilidad de que el individuo pague la mitad en cada ensayo es alta.
+
+$$
+\begin{aligned} 
+&\mu_1 \sim \mathrm{Uniform}(0, 1)\\
+&\mu_2 \sim \mathrm{Uniform}(\mu_1, 1)\\
+&\lambda_{1:2} \sim \mathrm{Uniform}(4, 100)\\
+&z_i \sim \mathrm{Bernoulli}(\phi)\\
+&\theta_{i,j} \sim \Bigg\{
+  \begin{array} {lr} 
+    \mathrm{Beta}(\mu_1\lambda_1, (1 - \mu_1)\lambda_1) \quad \mbox{if} \quad z_i = 0 \\
+    \mathrm{Beta}(\mu_2\lambda_2, (1 - \mu_2)\lambda_2) \quad \mbox{if} \quad z_i = 1
+  \end{array} \\
+&d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j})\\
+&\phi \sim \mathrm{Beta}(5, 5)
+\end{aligned}
+$$
+
+Los modelos de 1 y 2 mezclas, se programaron en R mediante el paquete **rjags**, que realiza la inferencia mediante el muestreo por Markov chain Monte Carlo a través de **JAGS**.
+Las distribuciones posteriores de todos los parámetros fueron aproximadas con tres cadenas de 26000 iteraciones cada una, se descartaron las primeras 6000 de cada cadena como periodo de calentamiento, para un total de 60000 muestras post-calentamiento.
+La convergencia del modelo fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que varió de 1 a 1.05 para todos los parámetros lo que indica convergencia.
+
+---
+
+### Modelamiento de los tiempos de reacción
+
+Un hallazgo constante en la investigación sobre engaño y deshonestidad, es la diferencia en los tiempos de reacción entre quienes toman decisiones *deshonestas* vs.
+decisiones *honestas*, en general, se han encontrado latencias breves en personas *deshonestas* en comparación con las de las personas *honestas*.
+
+Se estimaron las medias poblacionales del grupo de deshonestos y honestos mediante un modelo bayesiano jerárquico que asumía que el tiempo de reacción proviene de una distribución $rt_i \sim \mathrm{Half-Normal}(0, 5)$ (dado que no puede haber tiempos de reacción negativos), con parámetros $\mu_{Dishonest}$ y $\mu_{Honest}$ y desviación estándar común $\sigma$.
+
+Asimismo, se modeló la variabilidad intrasujeto en los tiempos de reacción por medio de interceptos variantes por participante.
+El modelo se ajustó en R por medio de **brms** y **Stan** en condiciones iguales a las descritas anteriormente para el modelo jerárquico y obtuvo resultados adecuados de convergencia para todos los parámetros, $\hat{R} = 1$.
+
+---
+
+### Contraste de hipótesis
+
+Para los modelos de la tasa de pago y tiempo de reacción se utilizó el factor de Bayes por medio del método de Savage-Dickey, que calcula la razón de la densidad de la distribución posterior sobre la densidad de la distribución inicial de algún parámetro en el punto de interés.
+Específicamente para el modelo de la tasa de pago, se evaluó la hipótesis de si las promesas tendrían un efecto positivo en las tasas de pago ($H_1: \beta^{promise} > 0$), así como si la cercanía social alta (amigo) tendría mayores tasas de pago que la cercanía social baja (confederado) ($H_1: \beta^{friend} - \beta^{confederate} > 0$).
+Para el modelo del tiempo de reacción, la hipótesis fue si los *deshonestos* tendrían tiempos breves en comparación con los *honestos* ($H_1: \mu_{Dishonest} - \mu_{Honest} < 0$).
+
+---
+
+### Comparación de modelos
+
+Los modelos de una y dos mezclas se compararon por medio del criterio de información DIC (deviance information criteria), en el que los puntajes bajos indican mejores modelos.
+La estimación de la diferencia entre el modelo de 1 y 2 mezclas favorece al modelo de dos mezclas ($\mathrm{Difference}= 1.21$, $\mathrm{SE}= 3.49$).
+
+---
+
+## Resultados
+
+### Descriptivos
+
+Se muestra en la figura 1, la frecuencia de veces en que los participantes pagaron la mitad, así como la frecuencia de promesas que fueron seleccionadas.
+En la figura 2, se muestra la proporción de pagos realizados dependiendo de cada pareja y de la condición de promesas.
+
+```{r fig1, fig.cap='Fig. 1 Frecuencies of paying and Promise choice'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig1.jpeg")
+
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+---
+
+```{r fig2, fig.cap='Fig. 2 Rates by partners and promise condition', fig.height=10, fig.width=5}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig2.jpeg")
+
+```
+
+---
+
+### Resultados: modelo jerárquico
+
+En la tabla 1, se muestran los efectos poblacionales del modelo bayesiano jerárquico para la tasa de pago.
+Se presentan las estimaciones de cada coeficiente del modelo en escala *logit*, su error estándar y los intervalos de credibilidad bayesianos del 95%.
+Los cuales indican los límites inferiores y superiores de las estimaciones entre los que se ubica el 95 % de probabilidad.
+
+<caption>Table 1. Population-Level Effects of Task</caption>
+|Term                  |Estimate|  SE|L-95% CI|U-95% CI|
+|:---------------------|-------:|---:|-------:|-------:|
+|$\beta^0$             |   -1.62|0.40|   -2.31|   -1.02|
+|$\beta^{promise}$     |    1.27|0.40|    0.64|    1.92|
+|$\beta^{confederate}$ |    2.01|0.55|    1.20|    2.97|
+|$\beta^{friend}$      |    4.15|0.77|    3.07|    5.49|
+
+---
+
+La figura 3A muestra la incertidumbre con respecto a la estimación de los coeficientes, la linea central indica la mediana de la distribución y el área sombreada el intervalo del 50 % de probabilidad.
+Se puede observar que la condición de promesas y cercanía social alta (amigo) obtuvieron estimaciones mayores que el intercepto, que para este caso podría considerarse la estimación del efecto de la ausencia de promesas y cercanía social.
+
+Para visualizar el efecto conjunto de las condiciones experimentales en la probabilidad de pagar la mitad, se realizó su combinación lineal para obtener un sólo predictor ($\mathrm{linpred_i}$), se le aplicó la función ligadora inversa *logit* y se transformó su output en probabilidades por medio de la función logistica $1 / (1 + \exp(-\mathrm{linpred}_i))$.
+La figura 3B muestra la probabilidad de pagar la mitad, como función de la combinación lineal de las condiciones experimentales, las lineas delgadas muestran la incertidumbre en la predicción con una muestra aleatoria de tamaño 100 de las distribuciones posteriores de los parámetros poblacionales.
+La linea gruesa representa la media de las distribuciones posteriores de los parámetros poblacionales.
+Se puede observar, que a medida que se incrementa el valor del predictor lineal, se incrementa rápidamente la probabilidad de pago.
+Cabe destacar que el el valor del predictor lineal aumenta con la presencia de las condiciones experimentales de cercanía social y promesas.
+
+```{r fig3, fig.cap='Fig. 3 Estimates with uncertainty and linear predictor'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig3.jpeg")
+
+```
+
+----
+
+En un procedimiento similar al descrito para la figura 3B, la figura 4 representa el efecto conjunto de las condiciones experimentales en la probabilidad de pagar la mitad para cada sujeto.
+Ya que el modelo jerárquico asume que las diferencias individuales se pueden modelar realizando un ajuste $u$ a los coeficientes poblacionales $\beta$, se obtuvieron 50 muestras aleatorias de las distribuciones posteriores de los parámetros $u$ para cada sujeto, se realizó el ajuste al modelo poblacional y se presenta en lineas delgadas la incertidumbre en la predicción individual.
+
+Se puede observar en algunos sujetos (e.g sujeto 2 ó 17) que a medida que incrementa el predictor lineal, aumenta rápidamente la probabilidad de pago, sin embargo, para otros (e.g.
+sujeto 1 ó 5), existe incertidumbre respecto al efecto del predictor lineal, lo que sugiere que aún en la condición de promesas y en presencia de compañeros con cercanía social, el participante podría no pagar.
+La incertidumbre en la predicción de las respuestas de algunos jugadores, sugiere que podrían existir por lo menos dos procesos cognitivos que podrían dar lugar las decisiones observadas, lo que se explora con mayor detenimiento con el modelo de mezclas latentes.
+
+```{r fig4, fig.cap='Fig. 4 Estimates with uncertainty by subject'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9.jpeg")
+
+```
+
+---
+
+La **distribución posterior predictiva** consiste en simular el tipo de observaciones que podrían surgir con el modelo original, pero una vez que los parámetros de éste han sido actualizados con los datos observados.
+En este caso, cuando el modelo ha aprendido de las decisiones de los sujetos, tiene la capacidad de generar una _"réplica"_ de los datos observados, para cada combinación de los parámetros obtenidos en la distribución posterior.
+
+En la figura 5, se obtuvieron 50 muestras aleatorias de la distribución posterior de los parámetros poblacionales $\beta$ y se simularon 50 datasets con las decisiones que se esperarían dado el valor de esos parámetros.
+Se presentan en barras las decisiones realizadas por nuestros participantes $y$, mientras que el punto con dispersión muestra la distribución de los valores esperados en las 50 _replicas_ $y_{rep}$.
+Se puede observar que el modelo reproduce con bastante precisión los datos observados, lo cual es un indicador del adecuado ajuste del modelo.
+
+```{r fig5, fig.cap='Fig. 5 Posterior predictive distribution of choices by partner'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig5.jpeg")
+
+```
+
+---
+
+### Resultados: modelo de mezclas latentes
+
+El modelo de 2-mezclas latentes identificó dos subpoblaciones de tamaño 10; en la tabla 2 se muestran los resúmenes de las distribuciones posteriores de los parámetros de ambas subpoblaciones y el parámetro de la mezcla $\phi$.
+Una de las subpoblaciones tiene alta probabilidad de pagar $\mu_1$, la que denominamos __honestos__ y la otra subpoblación tiene una probabilidad de pagar menor por lo que fue denominada __deshonestos__ $\mu_2$.
+En la figura 6A se muestran las distribuciones posteriores de las dos $\mu$'s, correspondientes a la probabilidad de pagar de las dos subpoblaciones latentes.
+Y en la figura 6B se presentan las decisiones de dos sujetos extraídos de las dos subpoblaciones, el sujeto 5 de la subpoblación de __deshonestos__ y el 17 de la subpoblación de __honestos__.
+Se puede observar que el sujeto 5 decide no pagar en la mayoría de los ensayos, independientemente de la condición de promesas y cercanía social, mientras que el sujeto 17 sólo decidió no pagar en tres ocasiones cuando su compañero fue la computadora.
+
+<caption>Table 2. Parameters of 2-Mixture Model</caption>
+|Parameter    | Mean|   SD|L-95% CI|U-95% CI|
+|:------------|----:|----:|-------:|-------:|
+|$\mu_{1}$    | 0.56| 0.05|    0.44|    0.65|
+|$\mu_{2}$    | 0.70| 0.05|    0.61|    0.82|
+|$\lambda_{1}$|48.99|28.57|    5.50|   97.49|
+|$\lambda_{2}$|54.79|26.24|    7.80|   97.61|
+|$\phi$       | 0.49| 0.15|    0.21|    0.77|
+
+---
+
+```{r fig6, fig.cap='Fig. 6 Posteriors from two latent groups and two cases'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig6.jpeg")
+
+```
+
+---
+
+En la figura 7 se muestra la frecuencia de las decisiones de los dos grupos latentes, dependiendo de si estaban en la condición con o sin promesa.
+
+```{r fig7, fig.cap='Fig. 7 Payment frecuency by latent group and promise condition', fig.height=10, fig.width=5}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b.jpeg")
+
+```
+
+---
+
+### Resultados: tiempo de reacción
+
+En la tabla 3 se presentan las estimaciones poblacionales del modelo bayesiano de los tiempos de reacción, se resumen las distribuciones posteriores de cada parámetro, incluyendo la estimación de su media, su error estándar y los intervalos de credibilidad bayesianos del 95%.
+En la figura 8A se muestran con puntos los tiempos de reacción en segundos para cada decisión realizada de acuerdo con cada subgrupo, se agregó a cada grupo un kernel de densidad simétrico para representar la cantidad de casos acumulados a lo largo de los diferentes valores del tiempo de reacción.
+
+En la figura 8B se presenta la diferencia de las estimaciones posteriores, el punto con dispersión representa el estimador puntual de la diferencia entre las subpoblaciones y el intervalo de credibilidad bayesiano del 95%.
+El histograma representa la distribución posterior de la diferencia entre los parámetros de las subpoblaciones.
+
+<caption>Table 3. Parameters estimates of reaction time model</caption>
+|Term              | Estimate|   SE| L-95% CI| U-95% CI|
+|:-----------------|--------:|----:|--------:|--------:|
+|$\mu_{Dishonest}$ |     2.93| 0.23|     2.55|     3.31|
+|$\mu_{Honest}$    |     3.06| 0.22|     2.69|     3.42|
+|$\mu_{difference}$|    -0.13| 0.32|    -0.77|     0.52|  
+|$\sigma$          |     1.23| 0.05|     1.15|     1.31|
+|$\sigma_{subject}$|     0.65| 0.14|     0.45|     0.89|
+
+---
+
+```{r fig8, fig.cap='Fig. 8 Differences in reaction time by latent group'}
+
+knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig8.jpeg")
+
+```
+
+---
+
+### Resultados: contraste de hipótesis y comparación de modelos
+
+En la tabla 4 se muestran las hipótesis contrastadas, las estimaciones, los errores estándar y el factor de Bayes (BF) para cada una.
+Se interpretan los BF's como evidencia en favor de la hipótesis alterna $BF_{10}$ de acuerdo a la clasificación de Jeffreys (1961).
+La hipótesis uno de si la condición de promesas tiene un efecto superior a 0, se interpreta como "evidencia extrema" a su favor, la hipótesis de si el efecto en la tasa de pago es superior para el amigo que para el confederado también se interpreta como "evidencia superior" a su favor, la hipótesis sobre si la diferencia entre los tiempos de reacción entre honestos y deshonestos es menor a cero, se interpreta como "evidencia anecdótica" a su favor.
+
+Dado que el intervalo de credibilidad bayesiano para la estimación de la diferencia entre los tiempos de reacción de las subpoblaciones incluye el cero, se decidió evaluar la hipótesis de si la diferencia es igual a 0, el BF correspondiente se interpreta como "evidencia fuerte" en favor a la diferencia igual a 0.
+Finalmente, se comparó el DIC para los modelos de una ($DIC_{1}$) y dos ($DIC_{2}$) mezclas, cuya diferencia apoya al modelo de dos mezclas latentes.
+
+<caption>Table 4. Hypothesis testing and model comparison</caption>
+|Hypothesis                                    | Estimate|   SE|BF$_{10}$| 
+|:---------------------------------------------|--------:|----:|--------:|
+|$\beta^{promise} > 0$                         |     1.27| 0.40|      499|    
+|$\beta^{friend} - \beta^{confederate} > 0$    |     2.14| 0.77|   665.67|    
+|$\mu_{Dishonest} - \mu_{Honest} < 0$          |    -0.13| 0.32|     1.96|   
+|$\mu_{Dishonest} - \mu_{Honest} = 0$          |    -0.13| 0.32|    20.36|  
+|$DIC_{1} - DIC_{2}$                           |     1.21| 3.49|      -  |
+
+---

### 2019-03-16 Manuscript/social_closeness_dishonesty.tex
.

--- 2019-03-04 Manuscript/social_closeness_dishonesty.tex
@@
 
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\usepackage{longtable,booktabs}
 
@@
 
-\noindent  \section{Introduction}\label{introduction}
+\noindent  \subsection{Participantes}\label{participantes}
 
-bla bla\ldots{}
+Se incluyeron 20 personas voluntarias (18 mujeres), en un rango de edad
+de 19-33 años, su nivel educativo mínimo fue licenciatura, su ocupación
+principal fue estudiantes y eran solteros. Todos los participantes
+reportaron no tener historial médico de tipo neurológico ni psiquiátrico
+al momento del experimento. Los participantes acudieron al estudio con
+un amigo considerado \emph{cercano} por ellos mismos, quien cumplía las
+siguientes características: era una persona del mismo sexo que el
+participante, no tenía un vínculo familiar y no se trataba de una
+persona con una relación de tipo sentimental y/o sexual.
 
-\section{Method}\label{method}
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\subsection{Materiales y
+Procedimiento}\label{materiales-y-procedimiento}
+
+Todos los participantes realizaron una adaptación de la tarea de
+confianza y promesas presentada por Baumgartner (2009), que consiste en
+24 ensayos entre dos jugadores \textbf{A} y \textbf{B}, el jugador
+\textbf{A} tiene originalmente 0 pesos mexicanos y el jugador \textbf{B}
+tiene 2 pesos, al jugador \textbf{B} se le presenta la oportunidad de
+invertir su dinero al jugador \textbf{A} o conservarlo, si invierte su
+dinero se multiplica por 5 pesos, de modo que el jugador \textbf{A}
+recibe 10 pesos. Finalmente, el jugador \textbf{A} toma la decisión de
+pagar la mitad al jugador \textbf{B} o quedarse los 10 pesos. La
+estructura descrita se repite en 24 ensayos, sin embargo, en 4 de los
+ensayos el jugador \textbf{A} puede enviar una promesa a \textbf{B}, las
+promesas son que \emph{siempre}, \emph{casi siempre}, \emph{algunas
+veces} o \emph{nunca} pagaran la mitad. Cada promesa es válida por tres
+ensayos, de modo que 12 de los ensayos tienen el efecto de la promesa y
+los otros 12 no lo tienen.
+
+La variación respecto a la tarea original es que en nuestro experimento
+se presentaron tres compañeros de juego con tres niveles de cercanía
+social en el papel del jugador \textbf{B}: \textbf{computadora}
+(cercanía nula), \textbf{confederado} (cercanía baja) y \textbf{amigo}
+(cercanía alta), mientras que el participante principal siempre fungió
+el papel del jugador \textbf{A}. Cada compañero de juego realizó el rol
+de \textbf{B} en 8 de los 24 ensayos totales, sin embargo, tanto la
+condición de promesas como la de cercanía social fueron presentadas al
+sujeto \textbf{A} en orden pseudoaleatorio, lo que significa que se
+realizó la aleatorización de los ensayos una vez y se mantuvo el mismo
+orden para todos los sujetos. Con el fin de simplificar la tarea y
+homogeneizar la experiencia de todos nuestros participantes, se
+programaron \emph{a priori} las decisiones de los compañeros \textbf{B}
+sobre si invertían o no su monto inicial, se programó que los tres
+compañeros decidieran invertir en 6 ensayos y no invertir en 2, los
+cuales también se presentaron al sujeto \textbf{A} en orden
+pseudoaleatorio. La historia encubierta para todos nuestros sujetos en
+el papel de \textbf{A} fue que estarían jugando en tiempo real con su
+amigo, el confederado (que se le dijo que sería otra persona desconocida
+de su mismo sexo) y la computadora.
+
+En la figura A se muestra un diagrama de la cronología de la tarea
+experimental con las duraciones de cada fase en segundos, cada caja de
+izquierda a derecha representa una pantalla que se le mostró a los
+sujetos de manera secuencial. La parte A\(_{1}\) corresponde a un
+ejemplo de los ensayos sin promesas y la A\(_{2}\) de los ensayos con
+promesas. La fase de fijación sólo consistió en un período en el que el
+sujeto prestaba atención sin realizar ninguna conducta en particular, la
+\textbf{fase de promesas} en la parte A\(_{1}\) le indicó al sujeto que
+los siguientes tres ensayos se podían decidir sin el efecto de la
+promesa, mientras que en A\(_{2}\) se le pidió al sujeto que decidiera
+entre \emph{siempre}, \emph{casi siempre}, \emph{algunas veces} o
+\emph{nunca} pagar la mitad. A lo anterior, le siguió otro período de
+fijación, posteriormente los ensayos tanto en A\(_{1}\) como en
+A\(_{2}\) continuaron aproximadamente de la misma forma, en la
+\textbf{fase de anticipación/asignación} se le indicó a los sujetos
+quién era su compañero de juego para ese ensayo (computadora,
+confederado o amigo) y se le dió el mensaje de que su compañero estaba
+tomando su decisión, posteriormente en la \textbf{fase de decisión} se
+le dió al participante la información sobre cuál había sido la decisión
+de su compañero (si invirtió sus 2 pesos o no), se le recordaba su nivel
+de promesas (si se trataba de ensayos con promesas) y, en el caso de que
+su compañero hubiera invertido, se le pedía que decidiera si pagaba de
+regreso o no. Finalmente, en la \textbf{fase de feedback} se mostraban
+los pagos para ese ensayo y se repetía la secuencia. La tarea se
+programó en PsychoPy2 versión 1.84.2, que registraba las respuestas de
+los sujetos y los tiempos de reacción en segundos.
 
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g1.jpeg}
-\caption{Rates}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/task}
+
+}
+
+\caption{Fig. A. Task of promises and social closeness}\label{fig:figA}
 \end{figure}
 
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\subsection{Análisis descriptivo de
+datos}\label{analisis-descriptivo-de-datos}
+
+Se obtuvieron las proporciones de las decisiones pagar o no pagar la
+mitad, así como las promesas realizadas, posteriormente se calcularon
+las variaciones en las proporciones de acuerdo a los compañeros de juego
+y la condición de presencia o ausencia de promesas.
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\subsection{Modelamiento Bayesiano}\label{modelamiento-bayesiano}
+
+\subsubsection{Modelo Jerárquico}\label{modelo-jerarquico}
+
+Se utilizó inferencia bayesiana para evaluar el efecto de las
+condiciones experimentales en la tasa de pago a nivel individual y
+poblacional. Para tal propósito se realizó un modelo jerárquico que
+asume que la incertidumbre en el efecto de promesas y parejas sobre la
+conducta de cada individuo proviene de distribuciones poblacionales
+comunes para los parámetros del modelo:
+
+\[
+\begin{aligned}
+&y_i \sim \mathrm{Bernoulli}(\theta_i) \\
+&\mathrm{logit(\theta_i)} = \mathbf{X}\beta  +  \mathbf{Z}u
+\end{aligned}
+\] En el modelo anterior, cada decisión \(y_i\) proviene de una
+distribución Bernoulli con probabilidad de pagar \(\theta_i\), el
+objetivo del modelo jerárquico es predecir cada decisión a través la
+combinación lineal de los predictores transformados por su función
+ligadora inversa \(\mathrm{logit}\). En el modelo anterior, \(\beta\) y
+\(u\) son coeficientes a nivel poblacional y nivel individual
+respectivamente, mientras que \(\mathbf{X}\), \(\mathbf{Z}\) son sus
+correpondientes matrices del diseño.
+
+El modelo estima que la probabilidad \(\theta_i\) de que en cada ensayo
+se decida pagar la mitad está en función del efecto de la presencia de
+promesas \(\beta^{promise}\), así como de los compañeros con cercanía
+social baja \(\beta^{confederate}\) y alta \(\beta^{friend}\). También
+asume que pueden existir diferencias individuales en el desempeño
+durante la tarea, las cuales son captadas por los parámetros \(u\) y
+constituyen ajustes a los coeficientes poblacionales. Cabe remarcar que
+el modelo evalúa explícitamente la incertidumbre respecto a \(u\), lo
+cual es una ventaja con relación a los modelos que asumen que \(u\) es
+parte del término de error.
+
+El modelo se programó en R por medio del paquete \textbf{brms}, que
+realiza la inferencia mediante el muestreo por Markov chain Monte Carlo
+a través de \textbf{Stan}. Las distribuciones posteriores de todos los
+parámetros fueron aproximadas con cuatro cadenas de 2000 iteraciones
+cada una, las primeras 1000 iteraciones de cada cadena fueron
+descartadas (periodo de calentamiento), para un total de 4000 muestras
+post-calentamiento. La convergencia del modelo fue evaluada a través de
+la inspección visual de las cadenas y el cálculo del estadístico
+\(\hat{R}\), que para todos los parámetros fue de 1, lo que se
+interpreta como convergencia.
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\subsubsection{Modelamiento de mezclas
+latentes}\label{modelamiento-de-mezclas-latentes}
+
+Asume que las decisiones de los individuos podrían provenir de una
+combinación (o \emph{mezcla}) de procesos psicológicos no observables
+(\emph{latentes}), el rasgo latente más importante en este experimento
+es la (des)honestidad. Se modelaron las diferencias en las tasas de pago
+entre participantes como una combinación de \(N\) distribuciones de
+subpoblaciones. El modelo asumió que las tasas de pago provenían de una
+o dos mezclas de distribuciones, o grupos latentes.
+
+El modelo de una mezcla, asumía que cada decisión \(d_{i,j}\) de cada
+sujeto provenía de una distribución Bernoulli con probabilidad
+\(\theta_{i,j}\). Asimismo que \(\theta_{i,j}\) provenía de una
+distribución jerárquica Beta con parámetros \(\alpha\) y \(\beta\). La
+distribución Beta fue reparametrizada en términos de media \(\mu\) y
+precisión \(\lambda\), ya que \(\mu = \alpha/(\alpha + \beta)\) y
+\(\lambda = \alpha + \beta\).
+
+\[
+\begin{aligned}
+&\mu \sim \mathrm{Uniform}(0, 1)\\
+&\lambda \sim \mathrm{Uniform}(4, 100)\\
+&\theta_{i,j} \sim \mathrm{Beta}(\mu\lambda, (1 - \mu)\lambda)\\
+&d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j}) 
+\end{aligned}
+\]
+
+El modelo de dos mezclas es aproximadamente igual al anterior, sin
+embargo ahora asume que las decisiones provienen de una \emph{mezcla} de
+las distribuciones de dos subpoblaciones, una distribución Beta con
+parámetros \(\mu_1\lambda_1\) y \((1 - \mu_1) \lambda_1\) y otra con
+párametros \(\mu_2\lambda_2\) y \((1 - \mu_2) \lambda_2\), el parámetro
+\(z_i\) determina la probabilidad de que cada sujeto pertenezca a uno de
+dos grupos latentes, se distribuye Bernoulli con probabilidad \(\phi\),
+que a su vez sigue una distribución inicial Beta relativamente poco
+informativa.
+
+Se presenta el modelo de 2 mezclas con la notación propuesta por Lee,
+nodos cuadrados representan variables discretas y nodos circulares
+variables numéricas. Los nodos sombreados representan variables
+observadas, mientras que los nodos no sombreados son variables latentes.
+Los dos rectángulos representan repeticiones de la relación entre los
+parámetros del modelo para cada sujeto \(i\) y ensayo \(j\). Se
+determinó que un individuo pertenecía al grupo de \emph{Deshonestos} si
+\(z_i < 0.5\), dado que la probabilidad de que ese sujeto pagara la
+mitad en cada ensayo es baja, mientras que se consideró que un individuo
+pertenecía al grupo de \emph{Honestos} si \(z_i > 0.5\), dado que la
+probabilidad de que el individuo pague la mitad en cada ensayo es alta.
+
+\[
+\begin{aligned} 
+&\mu_1 \sim \mathrm{Uniform}(0, 1)\\
+&\mu_2 \sim \mathrm{Uniform}(\mu_1, 1)\\
+&\lambda_{1:2} \sim \mathrm{Uniform}(4, 100)\\
+&z_i \sim \mathrm{Bernoulli}(\phi)\\
+&\theta_{i,j} \sim \Bigg\{
+  \begin{array} {lr} 
+    \mathrm{Beta}(\mu_1\lambda_1, (1 - \mu_1)\lambda_1) \quad \mbox{if} \quad z_i = 0 \\
+    \mathrm{Beta}(\mu_2\lambda_2, (1 - \mu_2)\lambda_2) \quad \mbox{if} \quad z_i = 1
+  \end{array} \\
+&d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j})\\
+&\phi \sim \mathrm{Beta}(5, 5)
+\end{aligned}
+\]
+
+Los modelos de 1 y 2 mezclas, se programaron en R mediante el paquete
+\textbf{rjags}, que realiza la inferencia mediante el muestreo por
+Markov chain Monte Carlo a través de \textbf{JAGS}. Las distribuciones
+posteriores de todos los parámetros fueron aproximadas con tres cadenas
+de 26000 iteraciones cada una, se descartaron las primeras 6000 de cada
+cadena como periodo de calentamiento, para un total de 60000 muestras
+post-calentamiento. La convergencia del modelo fue evaluada a través de
+la inspección visual de las cadenas y el cálculo del estadístico
+\(\hat{R}\), que varió de 1 a 1.05 para todos los parámetros lo que
+indica convergencia.
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\subsubsection{Modelamiento de los tiempos de
+reacción}\label{modelamiento-de-los-tiempos-de-reaccion}
+
+Un hallazgo constante en la investigación sobre engaño y deshonestidad,
+es la diferencia en los tiempos de reacción entre quienes toman
+decisiones \emph{deshonestas} vs.~decisiones \emph{honestas}, en
+general, se han encontrado latencias breves en personas
+\emph{deshonestas} en comparación con las de las personas
+\emph{honestas}.
+
+Se estimaron las medias poblacionales del grupo de deshonestos y
+honestos mediante un modelo bayesiano jerárquico que asumía que el
+tiempo de reacción proviene de una distribución
+\(rt_i \sim \mathrm{Half-Normal}(0, 5)\) (dado que no puede haber
+tiempos de reacción negativos), con parámetros \(\mu_{Dishonest}\) y
+\(\mu_{Honest}\) y desviación estándar común \(\sigma\).
+
+Asimismo, se modeló la variabilidad intrasujeto en los tiempos de
+reacción por medio de interceptos variantes por participante. El modelo
+se ajustó en R por medio de \textbf{brms} y \textbf{Stan} en condiciones
+iguales a las descritas anteriormente para el modelo jerárquico y obtuvo
+resultados adecuados de convergencia para todos los parámetros,
+\(\hat{R} = 1\).
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\subsubsection{Contraste de hipótesis}\label{contraste-de-hipotesis}
+
+Para los modelos de la tasa de pago y tiempo de reacción se utilizó el
+factor de Bayes por medio del método de Savage-Dickey, que calcula la
+razón de la densidad de la distribución posterior sobre la densidad de
+la distribución inicial de algún parámetro en el punto de interés.
+Específicamente para el modelo de la tasa de pago, se evaluó la
+hipótesis de si las promesas tendrían un efecto positivo en las tasas de
+pago (\(H_1: \beta^{promise} > 0\)), así como si la cercanía social alta
+(amigo) tendría mayores tasas de pago que la cercanía social baja
+(confederado) (\(H_1: \beta^{friend} - \beta^{confederate} > 0\)). Para
+el modelo del tiempo de reacción, la hipótesis fue si los
+\emph{deshonestos} tendrían tiempos breves en comparación con los
+\emph{honestos} (\(H_1: \mu_{Dishonest} - \mu_{Honest} < 0\)).
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\subsubsection{Comparación de modelos}\label{comparacion-de-modelos}
+
+Los modelos de una y dos mezclas se compararon por medio del criterio de
+información DIC (deviance information criteria), en el que los puntajes
+bajos indican mejores modelos. La estimación de la diferencia entre el
+modelo de 1 y 2 mezclas favorece al modelo de dos mezclas
+(\(\mathrm{Difference}= 1.21\), \(\mathrm{SE}= 3.49\)).
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\subsection{Resultados}\label{resultados}
+
+\subsubsection{Descriptivos}\label{descriptivos}
+
+Se muestra en la figura 1, la frecuencia de veces en que los
+participantes pagaron la mitad, así como la frecuencia de promesas que
+fueron seleccionadas. En la figura 2, se muestra la proporción de pagos
+realizados dependiendo de cada pareja y de la condición de promesas.
+
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g2.jpeg}
-\caption{Rates by partner}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig1}
+
+}
+
+\caption{Fig. 1 Frecuencies of paying and Promise choice}\label{fig:fig1}
 \end{figure}
 
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g3.jpeg}
-\caption{Rates by partners and promise condition}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig2}
+
+}
+
+\caption{Fig. 2 Rates by partners and promise condition}\label{fig:fig2}
 \end{figure}
 
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\subsubsection{Resultados: modelo
+jerárquico}\label{resultados-modelo-jerarquico}
+
+En la tabla 1, se muestran los efectos poblacionales del modelo
+bayesiano jerárquico para la tasa de pago. Se presentan las estimaciones
+de cada coeficiente del modelo en escala \emph{logit}, su error estándar
+y los intervalos de credibilidad bayesianos del 95\%. Los cuales indican
+los límites inferiores y superiores de las estimaciones entre los que se
+ubica el 95 \% de probabilidad.
+
+Table 1. Population-Level Effects of Task
+
+\begin{longtable}[]{@{}lrrrr@{}}
+\toprule
+Term & Estimate & SE & L-95\% CI & U-95\% CI\tabularnewline
+\midrule
+\endhead
+\(\beta^0\) & -1.62 & 0.40 & -2.31 & -1.02\tabularnewline
+\(\beta^{promise}\) & 1.27 & 0.40 & 0.64 & 1.92\tabularnewline
+\(\beta^{confederate}\) & 2.01 & 0.55 & 1.20 & 2.97\tabularnewline
+\(\beta^{friend}\) & 4.15 & 0.77 & 3.07 & 5.49\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+La figura 3A muestra la incertidumbre con respecto a la estimación de
+los coeficientes, la linea central indica la mediana de la distribución
+y el área sombreada el intervalo del 50 \% de probabilidad. Se puede
+observar que la condición de promesas y cercanía social alta (amigo)
+obtuvieron estimaciones mayores que el intercepto, que para este caso
+podría considerarse la estimación del efecto de la ausencia de promesas
+y cercanía social.
+
+Para visualizar el efecto conjunto de las condiciones experimentales en
+la probabilidad de pagar la mitad, se realizó su combinación lineal para
+obtener un sólo predictor (\(\mathrm{linpred_i}\)), se le aplicó la
+función ligadora inversa \emph{logit} y se transformó su output en
+probabilidades por medio de la función logistica
+\(1 / (1 + \exp(-\mathrm{linpred}_i))\). La figura 3B muestra la
+probabilidad de pagar la mitad, como función de la combinación lineal de
+las condiciones experimentales, las lineas delgadas muestran la
+incertidumbre en la predicción con una muestra aleatoria de tamaño 100
+de las distribuciones posteriores de los parámetros poblacionales. La
+linea gruesa representa la media de las distribuciones posteriores de
+los parámetros poblacionales. Se puede observar, que a medida que se
+incrementa el valor del predictor lineal, se incrementa rápidamente la
+probabilidad de pago. Cabe destacar que el el valor del predictor lineal
+aumenta con la presencia de las condiciones experimentales de cercanía
+social y promesas.
+
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g4.jpeg}
-\caption{Promises}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig3}
+
+}
+
+\caption{Fig. 3 Estimates with uncertainty and linear predictor}\label{fig:fig3}
 \end{figure}
 
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+En un procedimiento similar al descrito para la figura 3B, la figura 4
+representa el efecto conjunto de las condiciones experimentales en la
+probabilidad de pagar la mitad para cada sujeto. Ya que el modelo
+jerárquico asume que las diferencias individuales se pueden modelar
+realizando un ajuste \(u\) a los coeficientes poblacionales \(\beta\),
+se obtuvieron 50 muestras aleatorias de las distribuciones posteriores
+de los parámetros \(u\) para cada sujeto, se realizó el ajuste al modelo
+poblacional y se presenta en lineas delgadas la incertidumbre en la
+predicción individual.
+
+Se puede observar en algunos sujetos (e.g sujeto 2 ó 17) que a medida
+que incrementa el predictor lineal, aumenta rápidamente la probabilidad
+de pago, sin embargo, para otros (e.g.~sujeto 1 ó 5), existe
+incertidumbre respecto al efecto del predictor lineal, lo que sugiere
+que aún en la condición de promesas y en presencia de compañeros con
+cercanía social, el participante podría no pagar. La incertidumbre en la
+predicción de las respuestas de algunos jugadores, sugiere que podrían
+existir por lo menos dos procesos cognitivos que podrían dar lugar las
+decisiones observadas, lo que se explora con mayor detenimiento con el
+modelo de mezclas latentes.
+
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g5.jpeg}
-\caption{Bayesians logistic coefficients}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9}
+
+}
+
+\caption{Fig. 4 Estimates with uncertainty by subject}\label{fig:fig4}
 \end{figure}
 
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+La \textbf{distribución posterior predictiva} consiste en simular el
+tipo de observaciones que podrían surgir con el modelo original, pero
+una vez que los parámetros de éste han sido actualizados con los datos
+observados. En este caso, cuando el modelo ha aprendido de las
+decisiones de los sujetos, tiene la capacidad de generar una
+\emph{``réplica''} de los datos observados, para cada combinación de los
+parámetros obtenidos en la distribución posterior.
+
+En la figura 5, se obtuvieron 50 muestras aleatorias de la distribución
+posterior de los parámetros poblacionales \(\beta\) y se simularon 50
+datasets con las decisiones que se esperarían dado el valor de esos
+parámetros. Se presentan en barras las decisiones realizadas por
+nuestros participantes \(y\), mientras que el punto con dispersión
+muestra la distribución de los valores esperados en las 50
+\emph{replicas} \(y_{rep}\). Se puede observar que el modelo reproduce
+con bastante precisión los datos observados, lo cual es un indicador del
+adecuado ajuste del modelo.
+
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g6.jpeg}
-\caption{Linear population predictor}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig5}
+
+}
+
+\caption{Fig. 5 Posterior predictive distribution of choices by partner}\label{fig:fig5}
 \end{figure}
 
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\subsubsection{Resultados: modelo de mezclas
+latentes}\label{resultados-modelo-de-mezclas-latentes}
+
+El modelo de 2-mezclas latentes identificó dos subpoblaciones de tamaño
+10; en la tabla 2 se muestran los resúmenes de las distribuciones
+posteriores de los parámetros de ambas subpoblaciones y el parámetro de
+la mezcla \(\phi\). Una de las subpoblaciones tiene alta probabilidad de
+pagar \(\mu_1\), la que denominamos \textbf{honestos} y la otra
+subpoblación tiene una probabilidad de pagar menor por lo que fue
+denominada \textbf{deshonestos} \(\mu_2\). En la figura 6A se muestran
+las distribuciones posteriores de las dos \(\mu\)'s, correspondientes a
+la probabilidad de pagar de las dos subpoblaciones latentes. Y en la
+figura 6B se presentan las decisiones de dos sujetos extraídos de las
+dos subpoblaciones, el sujeto 5 de la subpoblación de
+\textbf{deshonestos} y el 17 de la subpoblación de \textbf{honestos}. Se
+puede observar que el sujeto 5 decide no pagar en la mayoría de los
+ensayos, independientemente de la condición de promesas y cercanía
+social, mientras que el sujeto 17 sólo decidió no pagar en tres
+ocasiones cuando su compañero fue la computadora.
+
+Table 2. Parameters of 2-Mixture Model
+
+\begin{longtable}[]{@{}lrrrr@{}}
+\toprule
+Parameter & Mean & SD & L-95\% CI & U-95\% CI\tabularnewline
+\midrule
+\endhead
+\(\mu_{1}\) & 0.56 & 0.05 & 0.44 & 0.65\tabularnewline
+\(\mu_{2}\) & 0.70 & 0.05 & 0.61 & 0.82\tabularnewline
+\(\lambda_{1}\) & 48.99 & 28.57 & 5.50 & 97.49\tabularnewline
+\(\lambda_{2}\) & 54.79 & 26.24 & 7.80 & 97.61\tabularnewline
+\(\phi\) & 0.49 & 0.15 & 0.21 & 0.77\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g7.jpeg}
-\caption{Linear population predictor by subject}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig6}
+
+}
+
+\caption{Fig. 6 Posteriors from two latent groups and two cases}\label{fig:fig6}
 \end{figure}
 
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+En la figura 7 se muestra la frecuencia de las decisiones de los dos
+grupos latentes, dependiendo de si estaban en la condición con o sin
+promesa.
+
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g8.jpeg}
-\caption{Population coefficient with uncertainty}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b}
+
+}
+
+\caption{Fig. 7 Payment frecuency by latent group and promise condition}\label{fig:fig7}
 \end{figure}
 
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\subsubsection{Resultados: tiempo de
+reacción}\label{resultados-tiempo-de-reaccion}
+
+En la tabla 3 se presentan las estimaciones poblacionales del modelo
+bayesiano de los tiempos de reacción, se resumen las distribuciones
+posteriores de cada parámetro, incluyendo la estimación de su media, su
+error estándar y los intervalos de credibilidad bayesianos del 95\%. En
+la figura 8A se muestran con puntos los tiempos de reacción en segundos
+para cada decisión realizada de acuerdo con cada subgrupo, se agregó a
+cada grupo un kernel de densidad simétrico para representar la cantidad
+de casos acumulados a lo largo de los diferentes valores del tiempo de
+reacción.
+
+En la figura 8B se presenta la diferencia de las estimaciones
+posteriores, el punto con dispersión representa el estimador puntual de
+la diferencia entre las subpoblaciones y el intervalo de credibilidad
+bayesiano del 95\%. El histograma representa la distribución posterior
+de la diferencia entre los parámetros de las subpoblaciones.
+
+Table 3. Parameters estimates of reaction time model
+
+\begin{longtable}[]{@{}lrrrr@{}}
+\toprule
+Term & Estimate & SE & L-95\% CI & U-95\% CI\tabularnewline
+\midrule
+\endhead
+\(\mu_{Dishonest}\) & 2.93 & 0.23 & 2.55 & 3.31\tabularnewline
+\(\mu_{Honest}\) & 3.06 & 0.22 & 2.69 & 3.42\tabularnewline
+\(\mu_{difference}\) & -0.13 & 0.32 & -0.77 & 0.52\tabularnewline
+\(\sigma\) & 1.23 & 0.05 & 1.15 & 1.31\tabularnewline
+\(\sigma_{subject}\) & 0.65 & 0.14 & 0.45 & 0.89\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
 \begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9.jpeg}
-\caption{Model adjusted by subject}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig8}
+
+}
+
+\caption{Fig. 8 Differences in reaction time by latent group}\label{fig:fig8}
 \end{figure}
 
-\begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g16.jpeg}
-\caption{Two latent thetas}
-\end{figure}
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
-\begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g10.jpeg}
-\caption{Subjects from two latent thetas}
-\end{figure}
+\subsubsection{Resultados: contraste de hipótesis y comparación de
+modelos}\label{resultados-contraste-de-hipotesis-y-comparacion-de-modelos}
 
-\begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g11.jpeg}
-\caption{Strategies by group}
-\end{figure}
+En la tabla 4 se muestran las hipótesis contrastadas, las estimaciones,
+los errores estándar y el factor de Bayes (BF) para cada una. Se
+interpretan los BF's como evidencia en favor de la hipótesis alterna
+\(BF_{10}\) de acuerdo a la clasificación de Jeffreys (1961). La
+hipótesis uno de si la condición de promesas tiene un efecto superior a
+0, se interpreta como ``evidencia extrema'' a su favor, la hipótesis de
+si el efecto en la tasa de pago es superior para el amigo que para el
+confederado también se interpreta como ``evidencia superior'' a su
+favor, la hipótesis sobre si la diferencia entre los tiempos de reacción
+entre honestos y deshonestos es menor a cero, se interpreta como
+``evidencia anecdótica'' a su favor.
 
-\begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12.jpeg}
-\caption{Rates by group}
-\end{figure}
+Dado que el intervalo de credibilidad bayesiano para la estimación de la
+diferencia entre los tiempos de reacción de las subpoblaciones incluye
+el cero, se decidió evaluar la hipótesis de si la diferencia es igual a
+0, el BF correspondiente se interpreta como ``evidencia fuerte'' en
+favor a la diferencia igual a 0. Finalmente, se comparó el DIC para los
+modelos de una (\(DIC_{1}\)) y dos (\(DIC_{2}\)) mezclas, cuya
+diferencia apoya al modelo de dos mezclas latentes.
 
-\begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b.jpeg}
-\caption{Rates by group and promise condition}
-\end{figure}
+Table 4. Hypothesis testing and model comparison
 
-\begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g13.jpeg}
-\caption{Reaction times by group}
-\end{figure}
+\begin{longtable}[]{@{}lrrr@{}}
+\toprule
+Hypothesis & Estimate & SE & BF\(_{10}\)\tabularnewline
+\midrule
+\endhead
+\(\beta^{promise} > 0\) & 1.27 & 0.40 & 499\tabularnewline
+\(\beta^{friend} - \beta^{confederate} > 0\) & 2.14 & 0.77 &
+665.67\tabularnewline
+\(\mu_{Dishonest} - \mu_{Honest} < 0\) & -0.13 & 0.32 &
+1.96\tabularnewline
+\(\mu_{Dishonest} - \mu_{Honest} = 0\) & -0.13 & 0.32 &
+20.36\tabularnewline
+\(DIC_{1} - DIC_{2}\) & 1.21 & 3.49 & -\tabularnewline
+\bottomrule
+\end{longtable}
 
-\begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g14.jpeg}
-\caption{Reaction times by partner}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g15.jpeg}
-\caption{Difference between groups in reaction time}
-\end{figure}
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 \newpage

### 2019-03-16 tables.R

@@ -14,8 +14,9 @@ m_tidy <- broom::tidy(m) %>%
   slice(1:4)
 
 knitr::kable(m_tidy, 
-             format = "markdown", 
-             padding = 0, 
+             format = "latex",
+             longtable = TRUE,
+             #padding = 0, 
              digits = 2,
              col.names = c("Term", "Estimate", "SE", "L-95% CI", "U-95% CI"))
 
@@ -48,4 +49,7 @@ m_rt_tidy <- broom::tidy(m_rt) %>%  slice(1:4)
 knitr::kable(m_rt_tidy,
              format = "markdown",
              digits = 2,
+             longtble = TRUE,
              col.names = c("Term", "Estimate", "SE", "L-95% CI", "U-95% CI"))
+
+

### 2019-03-16 Manuscript/pdf/template.tex
.

\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{ifpdf,amsmath,amsthm,amssymb,amsfonts,newtxtext,newtxmath} 
\usepackage{array,graphicx,dcolumn,multirow,hevea,abstract,hanging}
\usepackage[labelfont=sc,textfont=sf]{caption}
\usepackage[hyperfootnotes=false,breaklinks=true]{hyperref} % was dvipdfmx
\urlstyle{rm}
\usepackage[hyphenbreaks]{breakurl}
%\usepackage{natbib} % must come afer hyperfootnotes
%\setlength{\bibsep}{0pt}
\usepackage{booktabs} % \toprule \midrule \bottomrule \cmidrule(lr){a-b}
% define centered and ragged columns:
\newcolumntype{L}[1]{>{\raggedright\arraybackslash }p{#1}} % can use m{}
\newcolumntype{C}[1]{>{\centering\arraybackslash }p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash }p{#1}}
\newcolumntype{d}[1]{D{.}{.}{#1}} % d{3.2} for 3 places on l, 2 on r
\newcommand{\mc}{\multicolumn}
\topmargin=-.3in \oddsidemargin=-.1in \evensidemargin=-.1in \textheight=9in \textwidth=6.8in
\setlength\tabcolsep{1mm}
\setlength\columnsep{5mm}
\setlength\abovecaptionskip{1ex}
\setlength\belowcaptionskip{.5ex}
\setlength\belowbottomsep{.3ex}
\setlength\lightrulewidth{.04em}
\renewcommand\arraystretch{1.2}
\renewcommand{\topfraction}{1}
\renewcommand{\textfraction}{0}
\renewcommand{\floatpagefraction}{.9}
% \renewcommand{\baselinestretch}{1.00} \large\normalsize % for fixing spaces
\widowpenalty=1000
\clubpenalty=1000
\setlength{\parskip}{0ex}
\let\tempone\itemize
\let\temptwo\enditemize
\let\tempthree\enumerate
\let\tempfour\endenumerate
\renewenvironment{itemize}{\tempone\setlength{\itemsep}{0pt}}{\temptwo}
\renewenvironment{enumerate}{\tempthree\setlength{\itemsep}{0pt}}{\tempfour}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{page}{1} % start with first page

\title{How to use this template (and other stuff)}

\author{
Jonathan Baron\thanks{Department of Psychology, University of
  Pennsylvania. Email: baron@upenn.edu.}\;\,\thanks{Some other address.}
\and 
  Some O. Person\thanks{Yet another place.} 
\and
  Y. Another Author\footnotemark[2] % indicates same as 2nd thanks
}

\date{} % leave empty
\begin{document} % goes here

% fill in short title
\newcommand{\jref}{http://journal.sjdm.org/volxx.x.html}
\newcommand{\jhead}{Judgment and Decision Making, Vol.~xx, No.~x}
\newcommand{\jdate}{xxxxxxx 20xx}
\pagestyle{myheadings} \markright{\protect\small \href{\jref}{\jhead}, \jdate \hfill SHORT TITLE \qquad}
\begin{htmlonly}
\href{\jref}{\jhead}, \jdate, pp.\
\end{htmlonly}
%\begin{latexonly}
\twocolumn[
\vspace{-.3in}
{\small \href{\jref}{\jhead}, \jdate, pp.\ XX--XX}
%\end{latexonly}

\maketitle

%\begin{latexonly}
\vspace{-3mm}
\begin{onecolabstract}
%\end{latexonly}
The abstract is a brief (usually one paragraph) summary
of the whole paper, including the problem, the method for solving
it (when not obvious), the results, and the conclusions suggested
or drawn.  Do not write the abstract as a hasty
afterthought. Look at it as a real exercise in cramming the most
information in one paragraph.  The reader should not have to read
any of the rest of the paper in order to understand the abstract
fully.  Many readers will read only the abstract.  Other readers
will use it to decide what to look for in the paper, or to decide
whether to read the whole thing.  Remember 
\href{http://en.wikipedia.org/wiki/The_Elements_of_Style}{Strunk \&
  White's} admonition, ``Omit needless words.''

\smallskip
\noindent
Keywords: journal, template, latex
%\begin{latexonly}
\end{onecolabstract}\bigskip
]
%\end{latexonly}

{\renewcommand{\thefootnote}{}
\footnotetext{ % note blank lines above and below acknowledgment

  Portions of this template are shamelessly stolen from other
  documents lying around on the author's computer. He is grateful to
  Lenovo, Inc.

Copyright: \copyright\ 2019.
The authors license this article under the terms of the
\href{http://creativecommons.org/licenses/by/3.0/}{Creative Commons
  Attribution 3.0 License.}
}}

\saythanks

\setlength{\baselineskip}{12pt plus.2pt}

\section{Introduction}

To use this file, click ``Open as template''. Here is some meaningless
text as an example. Delete all the text that is not part of your paper.

Einstein said that $E = MC^2$.

Many authors (Jones, 2016; Smith, 2017) have trouble replicating this
result.

Our hypothesis is that $E = MC^3$.

\section{Method} % example of a heading

Here is an example of a one-column table using new column definitions.

%Table 1
\begin{table}[t]
\caption{Experiment 3: Mean (SD) willingness to contribute to identified
and unidentified victims, for self and for the average student.}
\begin{tabular}{L{.7in}C{.7in}C{.7in}C{.7in}}\toprule
 & Self & Average student & Total\\\midrule
Identified victim & 68.28 (55.77) & 45.30 (66.17) & 56.79 (61.89)\\
Unidentified victim & 54.06 (61.89) & 38.63 (67.20) & 46.35 (60.63)\\\midrule
Total & 61.17 (58.81) & 41.97 (66.51) & \\\bottomrule
\mc{4}{p{2.8in}}{Here is a meaningless note about this table.}\\
\end{tabular}
\end{table}

Here is another example of a table (hspace not needed but can be
used). Use ``table*'' with the asterisk when the table needs 2
columns.  A table will generally go at the top of the first page that
refers to it, or as soon after that pages as possible. Do not assume
that tables will appear at the place they are put in the text. In the
tex file, they generally have to go before they are mentioned, in
order to appear in the best place.\footnote{Footnotes at the end of
  sentences should go after the period.}

%Table 2
\begin{table*}[t]\centering
\caption{This table is a very fancy table with a lot of small
  corrections in it, like the tildes in brackets. You don't need to do
this sort of stuff with your own tables. But it may be useful to look
at how notes are done, and how extra space is inserted between columns.}
\begin{tabular}{llrc@{\quad}rc@{\quad}rc@{\quad}rc}\toprule
 &  & \mc{2}{C{1in}}{Accuracy of first response (\%) {\ }} &
\mc{2}{C{1in}}{Accuracy of final response (\%) {\ }} &
\mc{2}{C{1in}}{Change of mind (\%) {\ }} & \mc{2}{C{1in}}{Response time (ms) {\ }}\\
\cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}\cmidrule(lr){9-10}
 &  & { ~ } \itshape M & \itshape SD & { ~ }  \itshape M & \itshape SD & { ~ }  \itshape M &
\itshape SD & { ~ ~ }  \itshape M {\ } & \itshape SD\\\midrule
Experiment 1 & Congruent & 73 & 44 & 85 & 36 & 20 & 40 & 1479 & 495\\
 & Incongruent & 45 & 50 & 84 & 37 & 45 & 50 & 1625 & 498\\
Experiment 2 & Congruent & 69 & 46 & 85 & 36 & 26 & 44 & 1567 & 477\\
 & Incongruent & 43 & 50 & 85 & 35 & 49 & 50 & 1695 & 469\\\bottomrule
\mc{10}{p{6in}}{Note. Means and standard deviations are calculated based on the
trial level values (ignoring participants).}
\end{tabular}
\end{table*}

\section{Results}

Use subsections and subsubsections etc. freely.

The following is an example of a one-column figure. The caption can be
long, and fully describe the figure, even if it is redundant with the text.

\begin{figure}[t!]
\includegraphics[width=\columnwidth]{dut11.eps}
\caption{The caption goes under the figure like this. Note that
  columnwidth is the width of a column. But you can use any units,
  e.g., ``3in'' or ``50mm''.}
\end{figure}

Here is a two-column figure. A figure will generally go at the top of
the first page that refers to it, or as soon after that pages as
possible. Do not assume that figures will appear at the place they are
put in the text. In the tex file, they generally have to go before
they are mentioned, in order to appear in the best place.

\begin{figure*}[t!]\centering
\includegraphics[width=5in]{dut11.eps}
\caption{The caption like this.}
\end{figure*}

\section{Discussion}

It turns out that $E = MC^2$.  Specifically,
\begin{equation}
E = \frac { \sum_{i=1}^n ( M_i C )^2 }{ \alpha + \beta }
\end{equation}
Equation 1 is true.

\subsection{How to write Mathematics}

\LaTeX{} is great at typesetting mathematics. Let $X_1, X_2, \ldots,
X_n$ be a sequence of independent and identically distributed random
variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 <
\infty$, and let
\[S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i\]
denote their mean. Then as $n$ approaches infinity, the random
variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal
$\mathcal{N}(0, \sigma^2)$.

\subsection{How to add Lists}

You can make lists with automatic numbering \dots

\begin{enumerate}
\item Like this,
\item and like this.
\end{enumerate}
\dots or bullet points \dots
\begin{itemize}
\item Like this,
\item and like this.
\end{itemize}

References should be in APA style. Examples are below.

\section*{References}

\begin{hangparas}{1em}{1}

  Aarts, H., \& Dijksterhuis, A. (1999).  How often did I do it?
  Experienced ease of retrieval and frequency estimates of past
  behavior.  \textit{Acta Psychologica, 103}(3), 77--89. \url{http://someurl.html}.

  Barberis, N. \& Thaler, R. (2003). A survey of behavioral finance.
  In G. M. Constantinides, M. Harris \& R. Stultz (Eds.),
  \textit{Handbook of the Economics of Finance,} pp.\ 1053--1123.
  Elsevier Science, North Holland, Amsterdam

\vfill % use this for column breaks
\break

Grice, H. P. (1975).  Logic and conversation. In P. Cole \& J.
L. Morgan, (Eds.), \textit{Speech Acts}, pp.\ 41--58. London: Academic
Press. \url{http://dx.doi.org/3.14159--1x}.
\end{hangparas}

\bigskip
\section*{Appendix}

The asterisk means that these divisions are not numbered.

\subsection*{How to write Mathematics}

This section is completely redundant with the text. Do not do
that. This is just an example.

\LaTeX{} is great at typesetting mathematics. Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
\[S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i\]
denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.

\subsection*{How to create Sections and Subsections}

Use section and subsections to organize your document. Simply use the section and subsection buttons in the toolbar to create them, and we'll handle all the formatting and numbering automatically.

\end{document}

### 2019-03-19 Manuscript/draft/Untitled.Rmd
.
Include .bib file

@@
     theme: cerulean
+bibliography: judgement.bib
+csl: apa.csl
 ---
@@
 ```
+
+## Introducción
+
+Desde la infidelidad afectiva hasta los fraudes financieros, la deshonestidad es ubicua en la interacciones humanas.
+Para el estudio de este fenómeno, se han utilizado frecuentemente: cuestionarios de autorreporte [@Halevy2014], encuestas [@Serota2010] o narraciones autobiográficas sobre mentiras que los participantes hayan dicho (o bien, de las que hayan sido victimas) [@DePaulo2004].
+Sin embargo, existe la preocupación de que los resultados derivados de estos estudios incluyan sesgos por deseabilidad social, o que tengan poco poder predictivo [@Baumgartner2013].
+De manera paralela,
+múltiples estudios han abordado la deshonestidad en el laboratorio, en donde ésta puede surgir de manera genuina y generar consecuencias específicas para el participante o para otros [@Gneezy2005; @Gneezy2013; @Fischbacher2013a].
 
@@
 ---
+
+## Referencias

### 2019-03-24 Manuscript/draft/Untitled.Rmd
Updating manuscript and references

@@
 ---
-title: "Método"
+title: "Modelamiento Bayesiano Jerárquico de la (Des)honestidad: el Efecto de la Cercanía Social"
 author: "Said E. Jiménez"
@@
 
-## Introducción
+# Introducción
 
@@
 Sin embargo, existe la preocupación de que los resultados derivados de estos estudios incluyan sesgos por deseabilidad social, o que tengan poco poder predictivo [@Baumgartner2013].
-De manera paralela,
-múltiples estudios han abordado la deshonestidad en el laboratorio, en donde ésta puede surgir de manera genuina y generar consecuencias específicas para el participante o para otros [@Gneezy2005; @Gneezy2013; @Fischbacher2013a].
+Para contrarrestar dichas críticas, múltiples estudios han abordado la deshonestidad en el laboratorio, en donde ésta puede surgir de manera genuina y generar consecuencias específicas para el participante o para otros [@Gneezy2005; @Gneezy2013; @Fischbacher2013a].
+
+Un ejemplo de los experimentos sobre deshonestidad son los estudios en los que los participantes realizan promesas sobre su comportamiento (e.g.
+si inviertes tu dinero en mí te retribuiré después); y posteriormente tienen la posibilidad de cumplir o romper sus promesas [@Vanberg2008; @Baumgartner2013; @Baumgartner2009; @Charness2006].
+En general, se sabe que las personas tienen preferencia por mantener sus promesas _per se_, en este sentido son honestas.
+Sin embargo, nosotros creemos que el efecto de las promesas puede variar en función de la cercanía hacia la persona a la que se le promete algo, por ejemplo, la cantidad de dinero a la que una persona está dispuesta a renunciar para compartirla con otra, decrece de forma hiperbólica dependiendo de la distancia social percibida [@Rachlin2006; @Vekaria2017].
+Asimismo, se sabe que la experiencia subjetiva de compartir tiene mayor valor cuando se trata de alguien cercano que alguien lejano (e.g.
+un amigo vs.
+un desconocido) [@Fareri2012].
+Así, es justificable pensar que a mayor cercanía social habrá un mayor efecto de las promesas, de modo que la gente será más honesta.
+Y, aumentará la deshonestidad conforme la cercanía social disminuya.
+
+---
+
+# Método
 

### 2019-03-24 Manuscript/draft/Untitled.Rmd
Update manuscript

@@
 ---
-title: "Modelamiento Bayesiano Jerárquico de la (Des)honestidad: el Efecto de la Cercanía Social"
+title: "Modelamiento Bayesiano de la (Des)honestidad: el Efecto de la Cercanía Social"
 author: "Said E. Jiménez"
@@
 un desconocido) [@Fareri2012].
-Así, es justificable pensar que a mayor cercanía social habrá un mayor efecto de las promesas, de modo que la gente será más honesta.
-Y, aumentará la deshonestidad conforme la cercanía social disminuya.
+Así, es posible pensar que a mayor cercanía social habrá un mayor efecto de las promesas -la gente será más honesta-, y aumentará la deshonestidad conforme la cercanía social disminuya.
 

### 2019-03-25 Manuscript/draft/Untitled.Rmd
.

@@
 En general, se sabe que las personas tienen preferencia por mantener sus promesas _per se_, en este sentido son honestas.
-Sin embargo, nosotros creemos que el efecto de las promesas puede variar en función de la cercanía hacia la persona a la que se le promete algo, por ejemplo, la cantidad de dinero a la que una persona está dispuesta a renunciar para compartirla con otra, decrece de forma hiperbólica dependiendo de la distancia social percibida [@Rachlin2006; @Vekaria2017].
+Sin embargo, nosotros creemos que el efecto de las promesas puede variar en función de la cercanía percibida hacia la persona a la que se le promete algo, por ejemplo, la cantidad de dinero a la que una persona está dispuesta a renunciar para compartirla con otra, decrece de forma hiperbólica dependiendo de la distancia social percibida [@Rachlin2006; @Vekaria2017].
 Asimismo, se sabe que la experiencia subjetiva de compartir tiene mayor valor cuando se trata de alguien cercano que alguien lejano (e.g.
@@
 Así, es posible pensar que a mayor cercanía social habrá un mayor efecto de las promesas -la gente será más honesta-, y aumentará la deshonestidad conforme la cercanía social disminuya.
+
+El presente trabajo evalúa los efectos de la cercanía social en la deshonestidad, utilizando métodos de inferencia Bayesiana y modelamiento cognitivo [@Lee2014; @Lee2018].
+A la fecha, los estudios que evalúan el efecto de las promesas en la cooperación o la deshonestidad se han basado en modelos que promedian los resultados entre todos los sujetos experimentales, lo que ignora la posibilidad de diferencias individuales entre la conducta de los sujetos [@Lee2005].
+Para modelar las diferencias individuales, al mismo tiempo que estimamos parámetros poblacionales, usamos un Modelo Bayesiano Jerárquico que estima dichas diferencias explícitamente y asume que provienen de una distribución poblacional común [@Gelman2006; @Burkner2017].
+
+En dos de los estudios que utilizan tareas experimentales con promesas [@Baumgartner2013; @Baumgartner2009], se ha realizado la clasificación de los individuos de acuerdo con su comportamiento durante la tarea, aquellos sujetos que tienen altas tasas de pago se han denominado _Deshonestos_, mientras que aquellos que tienen bajas tasas les han llamado _Honestos_.
+Nuestro estudio, propone modelar las diferencias en las tasas de pago por medio de un modelo de mezclas latentes, lo que asume que la conducta de nuestros sujetos durante el experimento podría provenir de dos procesos cognitivos no observables: _honestidad_ y _deshonestidad_.
+El modelamiento de mezclas latentes asume que cada individuo es honesto o no lo es, y que el mismo individuo utiliza el mismo proceso cognitivo durante toda la tarea, lo que permite distribuir a los individuos en conjuntos con diferentes comportamientos [@Lee2018].
 

### 2019-03-25 Manuscript/draft/Untitled.Rmd
.

@@
 
-En dos de los estudios que utilizan tareas experimentales con promesas [@Baumgartner2013; @Baumgartner2009], se ha realizado la clasificación de los individuos de acuerdo con su comportamiento durante la tarea, aquellos sujetos que tienen altas tasas de pago se han denominado _Deshonestos_, mientras que aquellos que tienen bajas tasas les han llamado _Honestos_.
-Nuestro estudio, propone modelar las diferencias en las tasas de pago por medio de un modelo de mezclas latentes, lo que asume que la conducta de nuestros sujetos durante el experimento podría provenir de dos procesos cognitivos no observables: _honestidad_ y _deshonestidad_.
-El modelamiento de mezclas latentes asume que cada individuo es honesto o no lo es, y que el mismo individuo utiliza el mismo proceso cognitivo durante toda la tarea, lo que permite distribuir a los individuos en conjuntos con diferentes comportamientos [@Lee2018].
+Por otra parte, en dos de los estudios que utilizan tareas experimentales con promesas [@Baumgartner2013; @Baumgartner2009], se ha realizado la clasificación de los individuos de acuerdo con su comportamiento durante la tarea, aquellos sujetos que tienen altas tasas de pago se han denominado _Honestos_, mientras que aquellos que tienen bajas tasas les han llamado _Deshonestos_.
+Nuestro estudio, propone modelar las diferencias en las tasas de pago por medio de un modelo de mezclas latentes, que asume que la conducta de nuestros sujetos durante el experimento podría provenir de dos procesos cognitivos no observables: _honestidad_ y _deshonestidad_.
+El modelamiento de mezclas latentes asume que cada individuo es honesto o no lo es, y que el mismo individuo utiliza el mismo proceso cognitivo durante toda la tarea, lo que permite distribuir a los sujetos en conjuntos con diferentes comportamientos [@Lee2018].
+
+Finalmente, algunos estudios han encontrado diferencias en los tiempos de reacción entre _honestos_ y _deshonestos_ [@Ben-Shakhar2017], con los subgrupos detectados por medio del modelo de mezclas latentes, modelamos los tiempos de reacción de las subpoblaciones y evaluamos por medio del factor de Bayes la evidencia en favor del hallazgo descrito en la literatura.
 

### 2019-03-26 monotonic.R
Analyzing task using monotonic predictors.

@@ -1,0 +1,120 @@
+
+# Monotonic predictors ----------------------------------------------------
+
+# Packages ----------------------------------------------------------------
+
+library(pacman)
+p_load(magrittr, dplyr, forcats, tidyr, modelr, tidybayes,
+       ggstance, ggridges, rstan, brms, tidyverse, bayesplot)
+
+
+# Reading data ------------------------------------------------------------
+
+data <- read.csv("data.csv") %>% as_tibble()
+
+
+
+# Creating ordinal predictors ---------------------------------------------
+
+d_ord <- data %>% 
+  mutate(
+    prom_ord = case_when(
+      prom_keys == "No response" ~ 0,
+      prom_keys == "Never" ~ 1,
+      prom_keys == "Sometimes" ~ 2,
+      prom_keys == "Mostly" ~ 3,
+      prom_keys == "Always" ~ 4,
+      is.na(prom_keys) & promise == "No promise" ~ 0
+    ),
+    part_ord = case_when(
+      partner == "Computer" ~ 0,
+      partner == "Confederate" ~ 1,
+      partner == "Friend" ~ 2
+    )
+  ) %>% 
+  fill(prom_ord) %>% 
+  filter(dec_partner == "Trust") %>% 
+  mutate(not_pay = if_else(response == 1, 0, 1)) %>% 
+  select(id, part_ord, prom_ord, not_pay)
+
+
+
+# Modeling ----------------------------------------------------------------
+
+
+
+# M0 varying intercepts ---------------------------------------------------
+
+m0 <- brm(not_pay ~ 1 + (1 | id),
+          data = d_ord,
+          sample_prior = "yes",
+          family = bernoulli("logit"),
+          control = list(adapt_delta = 0.95))
+
+m0 <- add_criterion(m0, "kfold", K = 10)
+
+
+# M1 ordinal predictor prom -----------------------------------------------
+
+prior1 <- prior(normal(0, 10), class = "b") +
+  prior(dirichlet(1, 1, 1, 1), class = "simo", coef = "moprom_ord1")
+
+m1 <- brm(not_pay ~ mo(prom_ord) + (mo(prom_ord) | id),
+          data = d_ord,
+          prior = prior1,
+          sample_prior = "yes",
+          family = bernoulli("logit"),
+          control = list(adapt_delta = 0.95))
+
+m1 <- add_criterion(m1, "kfold", K = 10)
+
+
[…]

### 2019-06-25 varying_effects_promises.R
Analysis of varying effects by promise level

@@ -1,0 +1,107 @@
+# Varying effects by promises ----
+
+
+# Data --------------------------------------------------------------------
+
+load("~/Documents/R/github_Said/website/said/public/candidatura/candidatura.RData")
+
+
+# Packages ----------------------------------------------------------------
+
+pacman::p_load(tidyverse, brms)
+
+
+# Pay by promise level and partner ----------------------------------------
+
+d_ord %>% 
+  mutate(pay_back = ifelse(response == 1, "Pay back", "Not to pay back")) %>% 
+  ggplot(aes(x = prom_ord, fill = pay_back)) +
+  geom_bar(position = "fill") + 
+  labs(fill = NULL,
+       y = "Percent",
+       x = NULL) +
+  facet_wrap(~part_ord) +
+  scale_fill_manual(values = c("#A4CAE3", "#053778")) +
+  my_theme +
+  coord_flip() +
+  theme(legend.position = "bottom", 
+        axis.text.x = element_text(size = 10)) 
+
+
+# Model: varying effects by promise level ---------------------------------
+
+data3 <- d_ord %>% 
+  filter(dec_partner == "Trust") %>% 
+  mutate(prom_ord = factor(prom_ord, ordered = F),
+         part_ord = factor(part_ord, ordered = F),
+         response = as.integer(response))
+
+prior2 <- c(set_prior("normal(0, 2)", class = "b"), 
+           set_prior("cauchy(0, 2)", class = "sd"),
+           set_prior("lkj(2)", class = "cor"))
+
+fit <- brm(response ~ part_ord + (part_ord | prom_ord),
+           data = data3,
+           family = bernoulli("logit"),
+           prior = prior2,
+           sample_prior = "yes",
+           chains = 4,
+           cores = 4,
+           control = list(adapt_delta = 0.99))
+
+
+# Hypothesis --------------------------------------------------------------
+
+hypothesis(fit, "part_ordFriend - part_ordConfederate > 0")
+hypothesis(fit, "part_ordConfederate > 0")
+
+
+
+# Posterior Predictive ----------------------------------------------------
+
+pp_check(fit, type = "bars_grouped", group = "prom_ord", nsamples = 30)
+
+
+pp_2 <- posterior_predict(fit, nsamples = 100) %>% 
+  as_tibble()
+
[…]

### 2019-06-25 varying_effects_promises.R
Hierarchical clustering

@@ -103,5 +103,24 @@ pp_cases_2 <- data3 %>%
   theme(legend.position = "top", 
         axis.text.x = element_text(size = 10)))
 
-  
+
+# Clustering --------------------------------------------------------------
+
+perc <- cases %>% 
+  group_by(id) %>% 
+  summarise(perc = mean(response)) 
+
+x <- cases %>% 
+  group_by(id) %>% 
+  summarise(perc = mean(response)) %>% 
+  pull(perc)
+
+id <- cases %>% 
+  group_by(id) %>% 
+  summarise(perc = mean(response)) %>% 
+  pull(id)
+
+clust <- hclust(dist(x), method = "ward.D", members = id)
+p_clust <- plot(clust)
+
 

### 2019-06-26 varying_effects_promises.R
Analysis of broken promises

@@ -15,6 +15,7 @@ pacman::p_load(tidyverse, brms)
 
 d_ord %>% 
   mutate(pay_back = ifelse(response == 1, "Pay back", "Not to pay back")) %>% 
+  filter(dec_partner == "Trust") %>% 
   ggplot(aes(x = prom_ord, fill = pay_back)) +
   geom_bar(position = "fill") + 
   labs(fill = NULL,
@@ -121,6 +122,82 @@ id <- cases %>%
   pull(id)
 
 clust <- hclust(dist(x), method = "ward.D", members = id)
-p_clust <- plot(clust)
+plot(clust)
+
+
+
+high <- c(32, 15, 6, 13, 38, 36, 20, 19, 7, 14, 23, 28, 37, 42, 31, 3, 9, 10, 40)
+low <- c(33, 16, 29, 12, 25, 30, 39, 27, 24, 22, 17, 11, 2, 5, 35, 26, 21, 1, 8, 
+         41, 34, 4, 18)
+
+data3 <- data3 %>% 
+  mutate(group = ifelse(id %in% high, "Unselfish", "Selfish") %>% 
+           factor(levels = c("Unselfish", "Selfish")))
+
+data3 %>% 
+  group_by(group) %>% 
+  summarise(mean = mean(response),
+            sd = sd(response),
+            sum = sum(response),
+            n = n())
+
+prop.test(c(286, 240), n = c(342, 414))
+
+
+
+
+# Analyzing broken promises -----------------------------------------------
+
+broken <- d_ord %>% 
+  filter(prom_ord == "Always", dec_partner == "Trust") %>% 
+  mutate(broken = if_else(response == 1, 0, 1) %>% 
+           as.integer(),
+         part_ord = factor(part_ord, ordered = F))
+
+  
+broken %>% 
+  group_by(part_ord) %>% 
+  summarise(mean = mean(response),
+            sd = sd(response),
+            sum = sum(response),
+            n = n(),
+            broken = n - sum)
+
+
+# Modeling Broken Promises ------------------------------------------------
+
+fit2 <- brm(broken ~ -1 + part_ord + (-1 + part_ord | id),
+            data = broken,
+            family = bernoulli("logit"),
+            prior = prior2,
+            sample_prior = "yes",
+            chains = 4,
+            cores = 4,
+            control = list(adapt_delta = 0.95))
+
+
+
[…]

### 2019-06-28 article_spanish.Rmd
New data in varying effects by promise

--- 2019-03-24 Manuscript/draft/Untitled.Rmd
@@
 ---
-title: "Modelamiento Bayesiano de la (Des)honestidad: el Efecto de la Cercanía Social"
+title: "Social closeness in the face of deception"
 author: "Said E. Jiménez"
-date: "6 de marzo de 2019"
+date: "6/27/2019"
 output: 
-  html_document: 
-    theme: cerulean
-bibliography: judgement.bib
-csl: apa.csl
+  pdf_document:
+    toc: true
+    number_sections: true
+fontsize: 12pt
 ---
 
-<style>
-body {
-text-align: justify}
-</style>
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, fig.align='center', dev = "png", dpi = 400)
+load("~/Documents/R/github_Said/website/said/public/candidatura/candidatura.RData")
+pacman::p_load(tidyverse)
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE,
-                      warning = FALSE,
-                      error = FALSE,
-                      message = FALSE,
-                      out.width = '80%',
-                      fig.align = 'center',
-                      dpi = 300)
 ```
@@
 
-Desde la infidelidad afectiva hasta los fraudes financieros, la deshonestidad es ubicua en la interacciones humanas.
-Para el estudio de este fenómeno, se han utilizado frecuentemente: cuestionarios de autorreporte [@Halevy2014], encuestas [@Serota2010] o narraciones autobiográficas sobre mentiras que los participantes hayan dicho (o bien, de las que hayan sido victimas) [@DePaulo2004].
-Sin embargo, existe la preocupación de que los resultados derivados de estos estudios incluyan sesgos por deseabilidad social, o que tengan poco poder predictivo [@Baumgartner2013].
-Para contrarrestar dichas críticas, múltiples estudios han abordado la deshonestidad en el laboratorio, en donde ésta puede surgir de manera genuina y generar consecuencias específicas para el participante o para otros [@Gneezy2005; @Gneezy2013; @Fischbacher2013a].
+# Métodos
 
-Un ejemplo de los experimentos sobre deshonestidad son los estudios en los que los participantes realizan promesas sobre su comportamiento (e.g.
-si inviertes tu dinero en mí te retribuiré después); y posteriormente tienen la posibilidad de cumplir o romper sus promesas [@Vanberg2008; @Baumgartner2013; @Baumgartner2009; @Charness2006].
-En general, se sabe que las personas tienen preferencia por mantener sus promesas _per se_, en este sentido son honestas.
-Sin embargo, nosotros creemos que el efecto de las promesas puede variar en función de la cercanía hacia la persona a la que se le promete algo, por ejemplo, la cantidad de dinero a la que una persona está dispuesta a renunciar para compartirla con otra, decrece de forma hiperbólica dependiendo de la distancia social percibida [@Rachlin2006; @Vekaria2017].
-Asimismo, se sabe que la experiencia subjetiva de compartir tiene mayor valor cuando se trata de alguien cercano que alguien lejano (e.g.
-un amigo vs.
-un desconocido) [@Fareri2012].
-Así, es posible pensar que a mayor cercanía social habrá un mayor efecto de las promesas -la gente será más honesta-, y aumentará la deshonestidad conforme la cercanía social disminuya.
+## Sujetos
 
----
-
-# Método
-
-## Participantes
-
-Se incluyeron 20 personas voluntarias (18 mujeres), en un rango de edad de 19-33 años, su nivel educativo mínimo fue licenciatura, su ocupación principal fue estudiantes y eran solteros.
-Todos los participantes reportaron no tener historial médico de tipo neurológico ni psiquiátrico al momento del experimento.
+Se incluyeron 45 sujetos (15 hombres), reclutados en la Universidad Nacional Autónoma de México, en un rango de edad de 19 a 33 años y su nivel educativo mínimo fue licenciatura.
 Los participantes acudieron al estudio con un amigo considerado _cercano_ por ellos mismos, quien cumplía las siguientes características: era una persona del mismo sexo que el participante, no tenía un vínculo familiar y no se trataba de una persona con una relación de tipo sentimental y/o sexual.
 
----
-
-## Materiales y Procedimiento
+## Tarea y procedimiento
 
@@
 
-En la figura A se muestra un diagrama de la cronología de la tarea experimental con las duraciones de cada fase en segundos, cada caja de izquierda a derecha representa una pantalla que se le mostró a los sujetos de manera secuencial.
+En la Figura 1 se muestra un diagrama de la cronología de la tarea experimental con las duraciones de cada fase en segundos, cada caja de izquierda a derecha representa una pantalla que se le mostró a los sujetos de manera secuencial.
 La parte A$_{1}$ corresponde a un ejemplo de los ensayos sin promesas y la A$_{2}$ de los ensayos con promesas.
@@
 
-```{r figA, fig.cap='Fig. A. Task of promises and social closeness'}
+```{r figA, fig.cap='Task of promises and social closeness', out.width='80%'}
 
@@
 
----
+# Resultados
 
-## Análisis descriptivo de datos
+## Descriptivos
 
-Se obtuvieron las proporciones de las decisiones pagar o no pagar la mitad, así como las promesas realizadas, posteriormente se calcularon las variaciones en las proporciones de acuerdo a los compañeros de juego y la condición de presencia o ausencia de promesas.
+Se analizaron 756 decisiones sobre pagar o no la mitad (18 por sujeto), así cómo 168 
+promesas (4 por sujeto), 69.6% de las decisiones fueron pagar la mitad, mientras que la proporción de las promesas seleccionadas fueron 4.17%, 14.9% 41.1%, 37.5%, respectivamente para las promesas, nunca, algunas veces, casi siempre y siempre.
+En la Figura 2 se muestra la proporción de pagos dependiendo de los niveles de promesas y los compañeros de juego.
+Romper promesas, es decir, que el sujeto haya prometido siempre y posteriormente decida no pagar la mitad ocurrió solamente el 11.1% de los ensayos, de los cuales, 7.63% fueron ensayos con la computadora, 3.47% con el desconocido y 0% con el amigo.
 
----
+```{r fig2, fig.cap='Pay back rate by partners and promises levels'}
 
-## Modelamiento Bayesiano
-
-### Modelo Jerárquico
-
-Se utilizó inferencia bayesiana para evaluar el efecto de las condiciones experimentales en la tasa de pago a nivel individual y poblacional.
-Para tal propósito se realizó un modelo jerárquico que asume que la incertidumbre en el efecto de promesas y parejas sobre la conducta de cada individuo proviene de distribuciones poblacionales comunes para los parámetros del modelo:
-
-$$
-\begin{aligned}
-&y_i \sim \mathrm{Bernoulli}(\theta_i) \\
-&\mathrm{logit(\theta_i)} = \mathbf{X}\beta  +  \mathbf{Z}u
-\end{aligned}
-$$
-En el modelo anterior, cada decisión $y_i$ proviene de una distribución Bernoulli con probabilidad de pagar $\theta_i$, el objetivo del modelo jerárquico es predecir cada decisión a través la combinación lineal de los predictores transformados por su función ligadora inversa $\mathrm{logit}$.
-En el modelo anterior, $\beta$ y $u$ son coeficientes a nivel poblacional y nivel individual respectivamente, mientras que $\mathbf{X}$, $\mathbf{Z}$ son sus correpondientes matrices del diseño.
-
-El modelo estima que la probabilidad $\theta_i$ de que en cada ensayo se decida pagar la mitad está en función del efecto de la presencia de promesas $\beta^{promise}$, así como de los compañeros con cercanía social baja $\beta^{confederate}$ y alta $\beta^{friend}$.
-También asume que pueden existir diferencias individuales en el desempeño durante la tarea, las cuales son captadas por los parámetros $u$ y constituyen ajustes a los coeficientes poblacionales.
-Cabe remarcar que el modelo evalúa explícitamente la incertidumbre respecto a $u$, lo cual es una ventaja con relación a los modelos que asumen que $u$ es parte del término de error.
-
-El modelo se programó en R por medio del paquete **brms**, que realiza la inferencia mediante el muestreo por Markov chain Monte Carlo a través de **Stan**.
-Las distribuciones posteriores de todos los parámetros fueron aproximadas con cuatro cadenas de 2000 iteraciones cada una, las primeras 1000 iteraciones de cada cadena fueron descartadas (periodo de calentamiento), para un total de 4000 muestras post-calentamiento.
-La convergencia del modelo fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que para todos los parámetros fue de 1, lo que se interpreta como convergencia.
-
----
-
-### Modelamiento de mezclas latentes
-
-Asume que las decisiones de los individuos podrían provenir de una combinación (o *mezcla*) de procesos psicológicos no observables (*latentes*), el rasgo latente más importante en este experimento es la (des)honestidad.
-Se modelaron las diferencias en las tasas de pago entre participantes como una combinación de $N$ distribuciones de subpoblaciones.
-El modelo asumió que las tasas de pago provenían de una o dos mezclas de distribuciones, o grupos latentes.
-
-El modelo de una mezcla, asumía que cada decisión $d_{i,j}$ de cada sujeto provenía de una distribución Bernoulli con probabilidad $\theta_{i,j}$.
-Asimismo que $\theta_{i,j}$ provenía de una distribución jerárquica Beta con parámetros $\alpha$ y $\beta$.
-La distribución Beta fue reparametrizada en términos de media $\mu$ y precisión $\lambda$, ya que $\mu = \alpha/(\alpha + \beta)$ y $\lambda = \alpha + \beta$.
-
-$$
-\begin{aligned}
-&\mu \sim \mathrm{Uniform}(0, 1)\\
-&\lambda \sim \mathrm{Uniform}(4, 100)\\
-&\theta_{i,j} \sim \mathrm{Beta}(\mu\lambda, (1 - \mu)\lambda)\\
-&d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j}) 
-\end{aligned}
-$$
-
-El modelo de dos mezclas es aproximadamente igual al anterior, sin embargo ahora asume que las decisiones provienen de una *mezcla* de las distribuciones de dos subpoblaciones, una distribución Beta con parámetros $\mu_1\lambda_1$ y $(1 - \mu_1) \lambda_1$ y otra con párametros $\mu_2\lambda_2$ y $(1 - \mu_2) \lambda_2$, el parámetro $z_i$ determina la probabilidad de que cada sujeto pertenezca a uno de dos grupos latentes, se distribuye Bernoulli con probabilidad $\phi$, que a su vez sigue una distribución inicial Beta relativamente poco informativa.
-
-Se presenta el modelo de 2 mezclas con la notación propuesta por Lee, nodos cuadrados representan variables discretas y nodos circulares variables numéricas.
-Los nodos sombreados representan variables observadas, mientras que los nodos no sombreados son variables latentes.
-Los dos rectángulos representan repeticiones de la relación entre los parámetros del modelo para cada sujeto $i$ y ensayo $j$.
-Se determinó que un individuo pertenecía al grupo de *Deshonestos* si $z_i < 0.5$, dado que la probabilidad de que ese sujeto pagara la mitad en cada ensayo es baja, mientras que se consideró que un individuo pertenecía al grupo de *Honestos* si $z_i > 0.5$, dado que la probabilidad de que el individuo pague la mitad en cada ensayo es alta.
-
-$$
-\begin{aligned} 
-&\mu_1 \sim \mathrm{Uniform}(0, 1)\\
-&\mu_2 \sim \mathrm{Uniform}(\mu_1, 1)\\
-&\lambda_{1:2} \sim \mathrm{Uniform}(4, 100)\\
-&z_i \sim \mathrm{Bernoulli}(\phi)\\
-&\theta_{i,j} \sim \Bigg\{
-  \begin{array} {lr} 
-    \mathrm{Beta}(\mu_1\lambda_1, (1 - \mu_1)\lambda_1) \quad \mbox{if} \quad z_i = 0 \\
-    \mathrm{Beta}(\mu_2\lambda_2, (1 - \mu_2)\lambda_2) \quad \mbox{if} \quad z_i = 1
-  \end{array} \\
-&d_{i,j} \sim \mathrm{Bernoulli}(\theta_{i,j})\\
-&\phi \sim \mathrm{Beta}(5, 5)
-\end{aligned}
-$$
-
-Los modelos de 1 y 2 mezclas, se programaron en R mediante el paquete **rjags**, que realiza la inferencia mediante el muestreo por Markov chain Monte Carlo a través de **JAGS**.
-Las distribuciones posteriores de todos los parámetros fueron aproximadas con tres cadenas de 26000 iteraciones cada una, se descartaron las primeras 6000 de cada cadena como periodo de calentamiento, para un total de 60000 muestras post-calentamiento.
-La convergencia del modelo fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que varió de 1 a 1.05 para todos los parámetros lo que indica convergencia.
-
----
-
-### Modelamiento de los tiempos de reacción
-
-Un hallazgo constante en la investigación sobre engaño y deshonestidad, es la diferencia en los tiempos de reacción entre quienes toman decisiones *deshonestas* vs.
-decisiones *honestas*, en general, se han encontrado latencias breves en personas *deshonestas* en comparación con las de las personas *honestas*.
-
-Se estimaron las medias poblacionales del grupo de deshonestos y honestos mediante un modelo bayesiano jerárquico que asumía que el tiempo de reacción proviene de una distribución $rt_i \sim \mathrm{Half-Normal}(0, 5)$ (dado que no puede haber tiempos de reacción negativos), con parámetros $\mu_{Dishonest}$ y $\mu_{Honest}$ y desviación estándar común $\sigma$.
-
-Asimismo, se modeló la variabilidad intrasujeto en los tiempos de reacción por medio de interceptos variantes por participante.
-El modelo se ajustó en R por medio de **brms** y **Stan** en condiciones iguales a las descritas anteriormente para el modelo jerárquico y obtuvo resultados adecuados de convergencia para todos los parámetros, $\hat{R} = 1$.
-
----
-
-### Contraste de hipótesis
-
-Para los modelos de la tasa de pago y tiempo de reacción se utilizó el factor de Bayes por medio del método de Savage-Dickey, que calcula la razón de la densidad de la distribución posterior sobre la densidad de la distribución inicial de algún parámetro en el punto de interés.
-Específicamente para el modelo de la tasa de pago, se evaluó la hipótesis de si las promesas tendrían un efecto positivo en las tasas de pago ($H_1: \beta^{promise} > 0$), así como si la cercanía social alta (amigo) tendría mayores tasas de pago que la cercanía social baja (confederado) ($H_1: \beta^{friend} - \beta^{confederate} > 0$).
-Para el modelo del tiempo de reacción, la hipótesis fue si los *deshonestos* tendrían tiempos breves en comparación con los *honestos* ($H_1: \mu_{Dishonest} - \mu_{Honest} < 0$).
-
----
-
-### Comparación de modelos
-
-Los modelos de una y dos mezclas se compararon por medio del criterio de información DIC (deviance information criteria), en el que los puntajes bajos indican mejores modelos.
-La estimación de la diferencia entre el modelo de 1 y 2 mezclas favorece al modelo de dos mezclas ($\mathrm{Difference}= 1.21$, $\mathrm{SE}= 3.49$).
-
----
-
-## Resultados
-
-### Descriptivos
-
-Se muestra en la figura 1, la frecuencia de veces en que los participantes pagaron la mitad, así como la frecuencia de promesas que fueron seleccionadas.
-En la figura 2, se muestra la proporción de pagos realizados dependiendo de cada pareja y de la condición de promesas.
-
-```{r fig1, fig.cap='Fig. 1 Frecuencies of paying and Promise choice'}
-
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig1.jpeg")
+g14 + theme(text = element_text(size = 10),
+            axis.text.x = element_text(size = 8))
 
@@
 
----
+## Modelamiento Bayesiano Jerárquico
 
-```{r fig2, fig.cap='Fig. 2 Rates by partners and promise condition', fig.height=10, fig.width=5}
+### Efectos variantes por sujeto
 
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig2.jpeg")
+### Efectos variantes por promesas
 
-```
+### Análisis de cluster jerárquico
 
----
+# Discusión
 
-### Resultados: modelo jerárquico
-
-En la tabla 1, se muestran los efectos poblacionales del modelo bayesiano jerárquico para la tasa de pago.
-Se presentan las estimaciones de cada coeficiente del modelo en escala *logit*, su error estándar y los intervalos de credibilidad bayesianos del 95%.
-Los cuales indican los límites inferiores y superiores de las estimaciones entre los que se ubica el 95 % de probabilidad.
-
-<caption>Table 1. Population-Level Effects of Task</caption>
-|Term                  |Estimate|  SE|L-95% CI|U-95% CI|
-|:---------------------|-------:|---:|-------:|-------:|
-|$\beta^0$             |   -1.62|0.40|   -2.31|   -1.02|
-|$\beta^{promise}$     |    1.27|0.40|    0.64|    1.92|
-|$\beta^{confederate}$ |    2.01|0.55|    1.20|    2.97|
-|$\beta^{friend}$      |    4.15|0.77|    3.07|    5.49|
-
----
-
-La figura 3A muestra la incertidumbre con respecto a la estimación de los coeficientes, la linea central indica la mediana de la distribución y el área sombreada el intervalo del 50 % de probabilidad.
-Se puede observar que la condición de promesas y cercanía social alta (amigo) obtuvieron estimaciones mayores que el intercepto, que para este caso podría considerarse la estimación del efecto de la ausencia de promesas y cercanía social.
-
-Para visualizar el efecto conjunto de las condiciones experimentales en la probabilidad de pagar la mitad, se realizó su combinación lineal para obtener un sólo predictor ($\mathrm{linpred_i}$), se le aplicó la función ligadora inversa *logit* y se transformó su output en probabilidades por medio de la función logistica $1 / (1 + \exp(-\mathrm{linpred}_i))$.
-La figura 3B muestra la probabilidad de pagar la mitad, como función de la combinación lineal de las condiciones experimentales, las lineas delgadas muestran la incertidumbre en la predicción con una muestra aleatoria de tamaño 100 de las distribuciones posteriores de los parámetros poblacionales.
-La linea gruesa representa la media de las distribuciones posteriores de los parámetros poblacionales.
-Se puede observar, que a medida que se incrementa el valor del predictor lineal, se incrementa rápidamente la probabilidad de pago.
-Cabe destacar que el el valor del predictor lineal aumenta con la presencia de las condiciones experimentales de cercanía social y promesas.
-
-```{r fig3, fig.cap='Fig. 3 Estimates with uncertainty and linear predictor'}
-
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig3.jpeg")
-
-```
-
-----
-
-En un procedimiento similar al descrito para la figura 3B, la figura 4 representa el efecto conjunto de las condiciones experimentales en la probabilidad de pagar la mitad para cada sujeto.
-Ya que el modelo jerárquico asume que las diferencias individuales se pueden modelar realizando un ajuste $u$ a los coeficientes poblacionales $\beta$, se obtuvieron 50 muestras aleatorias de las distribuciones posteriores de los parámetros $u$ para cada sujeto, se realizó el ajuste al modelo poblacional y se presenta en lineas delgadas la incertidumbre en la predicción individual.
-
-Se puede observar en algunos sujetos (e.g sujeto 2 ó 17) que a medida que incrementa el predictor lineal, aumenta rápidamente la probabilidad de pago, sin embargo, para otros (e.g.
-sujeto 1 ó 5), existe incertidumbre respecto al efecto del predictor lineal, lo que sugiere que aún en la condición de promesas y en presencia de compañeros con cercanía social, el participante podría no pagar.
-La incertidumbre en la predicción de las respuestas de algunos jugadores, sugiere que podrían existir por lo menos dos procesos cognitivos que podrían dar lugar las decisiones observadas, lo que se explora con mayor detenimiento con el modelo de mezclas latentes.
-
-```{r fig4, fig.cap='Fig. 4 Estimates with uncertainty by subject'}
-
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9.jpeg")
-
-```
-
----
-
-La **distribución posterior predictiva** consiste en simular el tipo de observaciones que podrían surgir con el modelo original, pero una vez que los parámetros de éste han sido actualizados con los datos observados.
-En este caso, cuando el modelo ha aprendido de las decisiones de los sujetos, tiene la capacidad de generar una _"réplica"_ de los datos observados, para cada combinación de los parámetros obtenidos en la distribución posterior.
-
-En la figura 5, se obtuvieron 50 muestras aleatorias de la distribución posterior de los parámetros poblacionales $\beta$ y se simularon 50 datasets con las decisiones que se esperarían dado el valor de esos parámetros.
-Se presentan en barras las decisiones realizadas por nuestros participantes $y$, mientras que el punto con dispersión muestra la distribución de los valores esperados en las 50 _replicas_ $y_{rep}$.
-Se puede observar que el modelo reproduce con bastante precisión los datos observados, lo cual es un indicador del adecuado ajuste del modelo.
-
-```{r fig5, fig.cap='Fig. 5 Posterior predictive distribution of choices by partner'}
-
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig5.jpeg")
-
-```
-
----
-
-### Resultados: modelo de mezclas latentes
-
-El modelo de 2-mezclas latentes identificó dos subpoblaciones de tamaño 10; en la tabla 2 se muestran los resúmenes de las distribuciones posteriores de los parámetros de ambas subpoblaciones y el parámetro de la mezcla $\phi$.
-Una de las subpoblaciones tiene alta probabilidad de pagar $\mu_1$, la que denominamos __honestos__ y la otra subpoblación tiene una probabilidad de pagar menor por lo que fue denominada __deshonestos__ $\mu_2$.
-En la figura 6A se muestran las distribuciones posteriores de las dos $\mu$'s, correspondientes a la probabilidad de pagar de las dos subpoblaciones latentes.
-Y en la figura 6B se presentan las decisiones de dos sujetos extraídos de las dos subpoblaciones, el sujeto 5 de la subpoblación de __deshonestos__ y el 17 de la subpoblación de __honestos__.
-Se puede observar que el sujeto 5 decide no pagar en la mayoría de los ensayos, independientemente de la condición de promesas y cercanía social, mientras que el sujeto 17 sólo decidió no pagar en tres ocasiones cuando su compañero fue la computadora.
-
-<caption>Table 2. Parameters of 2-Mixture Model</caption>
-|Parameter    | Mean|   SD|L-95% CI|U-95% CI|
-|:------------|----:|----:|-------:|-------:|
-|$\mu_{1}$    | 0.56| 0.05|    0.44|    0.65|
-|$\mu_{2}$    | 0.70| 0.05|    0.61|    0.82|
-|$\lambda_{1}$|48.99|28.57|    5.50|   97.49|
-|$\lambda_{2}$|54.79|26.24|    7.80|   97.61|
-|$\phi$       | 0.49| 0.15|    0.21|    0.77|
-
----
-
-```{r fig6, fig.cap='Fig. 6 Posteriors from two latent groups and two cases'}
-
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig6.jpeg")
-
-```
-
----
-
-En la figura 7 se muestra la frecuencia de las decisiones de los dos grupos latentes, dependiendo de si estaban en la condición con o sin promesa.
-
-```{r fig7, fig.cap='Fig. 7 Payment frecuency by latent group and promise condition', fig.height=10, fig.width=5}
-
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b.jpeg")
-
-```
-
----
-
-### Resultados: tiempo de reacción
-
-En la tabla 3 se presentan las estimaciones poblacionales del modelo bayesiano de los tiempos de reacción, se resumen las distribuciones posteriores de cada parámetro, incluyendo la estimación de su media, su error estándar y los intervalos de credibilidad bayesianos del 95%.
-En la figura 8A se muestran con puntos los tiempos de reacción en segundos para cada decisión realizada de acuerdo con cada subgrupo, se agregó a cada grupo un kernel de densidad simétrico para representar la cantidad de casos acumulados a lo largo de los diferentes valores del tiempo de reacción.
-
-En la figura 8B se presenta la diferencia de las estimaciones posteriores, el punto con dispersión representa el estimador puntual de la diferencia entre las subpoblaciones y el intervalo de credibilidad bayesiano del 95%.
-El histograma representa la distribución posterior de la diferencia entre los parámetros de las subpoblaciones.
-
-<caption>Table 3. Parameters estimates of reaction time model</caption>
-|Term              | Estimate|   SE| L-95% CI| U-95% CI|
-|:-----------------|--------:|----:|--------:|--------:|
-|$\mu_{Dishonest}$ |     2.93| 0.23|     2.55|     3.31|
-|$\mu_{Honest}$    |     3.06| 0.22|     2.69|     3.42|
-|$\mu_{difference}$|    -0.13| 0.32|    -0.77|     0.52|  
-|$\sigma$          |     1.23| 0.05|     1.15|     1.31|
-|$\sigma_{subject}$|     0.65| 0.14|     0.45|     0.89|
-
----
-
-```{r fig8, fig.cap='Fig. 8 Differences in reaction time by latent group'}
-
-knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/fig8.jpeg")
-
-```
-
----
-
-### Resultados: contraste de hipótesis y comparación de modelos
-
-En la tabla 4 se muestran las hipótesis contrastadas, las estimaciones, los errores estándar y el factor de Bayes (BF) para cada una.
-Se interpretan los BF's como evidencia en favor de la hipótesis alterna $BF_{10}$ de acuerdo a la clasificación de Jeffreys (1961).
-La hipótesis uno de si la condición de promesas tiene un efecto superior a 0, se interpreta como "evidencia extrema" a su favor, la hipótesis de si el efecto en la tasa de pago es superior para el amigo que para el confederado también se interpreta como "evidencia superior" a su favor, la hipótesis sobre si la diferencia entre los tiempos de reacción entre honestos y deshonestos es menor a cero, se interpreta como "evidencia anecdótica" a su favor.
-
-Dado que el intervalo de credibilidad bayesiano para la estimación de la diferencia entre los tiempos de reacción de las subpoblaciones incluye el cero, se decidió evaluar la hipótesis de si la diferencia es igual a 0, el BF correspondiente se interpreta como "evidencia fuerte" en favor a la diferencia igual a 0.
-Finalmente, se comparó el DIC para los modelos de una ($DIC_{1}$) y dos ($DIC_{2}$) mezclas, cuya diferencia apoya al modelo de dos mezclas latentes.
-
-<caption>Table 4. Hypothesis testing and model comparison</caption>
-|Hypothesis                                    | Estimate|   SE|BF$_{10}$| 
-|:---------------------------------------------|--------:|----:|--------:|
-|$\beta^{promise} > 0$                         |     1.27| 0.40|      499|    
-|$\beta^{friend} - \beta^{confederate} > 0$    |     2.14| 0.77|   665.67|    
-|$\mu_{Dishonest} - \mu_{Honest} < 0$          |    -0.13| 0.32|     1.96|   
-|$\mu_{Dishonest} - \mu_{Honest} = 0$          |    -0.13| 0.32|    20.36|  
-|$DIC_{1} - DIC_{2}$                           |     1.21| 3.49|      -  |
-
----
-
-## Referencias
+# Referencias

### 2019-06-28 varying_effects_promises.R

@@ -13,7 +13,7 @@ pacman::p_load(tidyverse, brms)
 
 # Pay by promise level and partner ----------------------------------------
 
-d_ord %>% 
+(g14 <- d_ord %>% 
   mutate(pay_back = ifelse(response == 1, "Pay back", "Not to pay back")) %>% 
   filter(dec_partner == "Trust") %>% 
   ggplot(aes(x = prom_ord, fill = pay_back)) +
@@ -25,8 +25,8 @@ d_ord %>%
   scale_fill_manual(values = c("#A4CAE3", "#053778")) +
   my_theme +
   coord_flip() +
-  theme(legend.position = "bottom", 
-        axis.text.x = element_text(size = 10)) 
+  theme(legend.position = "top", 
+        axis.text.x = element_text(size = 10)))
 
 
 # Model: varying effects by promise level ---------------------------------
@@ -105,44 +105,19 @@ pp_cases_2 <- data3 %>%
         axis.text.x = element_text(size = 10)))
 
 
-# Clustering --------------------------------------------------------------
 
-perc <- cases %>% 
-  group_by(id) %>% 
-  summarise(perc = mean(response)) 
-
-x <- cases %>% 
-  group_by(id) %>% 
-  summarise(perc = mean(response)) %>% 
-  pull(perc)
-
-id <- cases %>% 
-  group_by(id) %>% 
-  summarise(perc = mean(response)) %>% 
-  pull(id)
-
-clust <- hclust(dist(x), method = "ward.D", members = id)
-plot(clust)
-
-
-
-high <- c(32, 15, 6, 13, 38, 36, 20, 19, 7, 14, 23, 28, 37, 42, 31, 3, 9, 10, 40)
-low <- c(33, 16, 29, 12, 25, 30, 39, 27, 24, 22, 17, 11, 2, 5, 35, 26, 21, 1, 8, 
-         41, 34, 4, 18)
-
-data3 <- data3 %>% 
-  mutate(group = ifelse(id %in% high, "Unselfish", "Selfish") %>% 
-           factor(levels = c("Unselfish", "Selfish")))
-
-data3 %>% 
-  group_by(group) %>% 
-  summarise(mean = mean(response),
-            sd = sd(response),
-            sum = sum(response),
-            n = n())
-
-prop.test(c(286, 240), n = c(342, 414))
-
+(g13b <- ggplot(d_g13, aes(x = part_ord, y = rate, col = case))  +
[…]

### 2019-07-04 article_spanish.Rmd
.

@@
 fontsize: 12pt
+bibliography: judgement.bib
+csl: apa.csl
+header-includes: \usepackage{float}
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.align='center', dev = "png", dpi = 400)
+knitr::opts_chunk$set(echo=FALSE, fig.align='center', dev='png', dpi=400, out.width='80%')
 load("~/Documents/R/github_Said/website/said/public/candidatura/candidatura.RData")
-pacman::p_load(tidyverse)
+pacman::p_load(tidyverse, kableExtra)
 
@@
 
-### Efectos variantes por sujeto
+### Efecto de la cercanía social en el engaño
 
-### Efectos variantes por promesas
+Para evaluar la hipótesis de que la cercanía social reduciría el engaño, se filtraron todos los ensayos en los que los sujetos promieteron que _siempre_ pagarían y después decidieron no pagar.
+Posteriormente, se utilizó inferencia bayesiana para evaluar el efecto de los compañeros de juego en la decisión de romper la promesa a nivel individual y poblacional.
+Para tal propósito, se realizó un modelo bayesiano jerárquico que asume que la incertidumbre en la estimación del efecto de los compañeros sobre la decisión de romper la promesa varía dependiendo de cada individuo, sin embargo, también asume que dichas variaciones pertenecen a distribuciones poblacionales comunes para el efecto de cada compañero sobre la decisión.
+
+$$
+\begin{aligned}
+&y_i \sim \mathrm{Bernoulli}(\theta_i) \\
+&\mathrm{logit(\theta_i)} = \mathbf{X}\beta  +  \mathbf{Z}u
+\end{aligned}
+$$
+
+En el modelo anterior, la decisión de romper la promesa $y_i$ proviene de una distribución Bernoulli con probabilidad de pagar $\theta_i$, el objetivo del modelo jerárquico es predecir cada decisión a través la combinación lineal de los efectos de cada compañero de juego, transformados por su función ligadora inversa $\mathrm{logit}$.
+En este modelo, $\beta$ y $u$ son coeficientes a nivel poblacional y nivel individual respectivamente, mientras que $\mathbf{X}$, $\mathbf{Z}$ son sus correpondientes matrices del diseño.
+El modelo estima que la probabilidad $\theta_i$ de que en cada ensayo se decida romper la promesa está en función del efecto de la presencia de los compañeros con cercanía nula $\beta^{computer}$, baja $\beta^{confederate}$ y alta $\beta^{friend}$.
+
+El modelo se programó en R por medio del paquete **brms**, que realiza la inferencia mediante el muestreo por Markov chain Monte Carlo a través de **Stan**.
+Las distribuciones posteriores de todos los parámetros fueron aproximadas con cuatro cadenas de 2000 iteraciones cada una, las primeras 1000 iteraciones de cada cadena fueron descartadas (periodo de calentamiento), para un total de 4000 muestras post-calentamiento.
+La convergencia del modelo fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que para todos los parámetros fue de 1, lo que se interpreta como convergencia.
+
+En la Figura 3, se muestra la probabilidad posterior de romper la promesa dependiendo del compañero de juego, los circulos corresponden con las medianas de las distribuciones de las estimaciones posteriores de los efectos, la barra gruesa y la barra delgada corresponden con el intervalo del 50% y 97% de probabilidad posterior.
+
+```{r fig3, fig.cap='Posterior probability of Breaking the Promise'}
+bayesplot::mcmc_intervals(
+  samples_fit2,
+  prob_outer = 0.97
+  ) +
+  labs(x = "Posterior Probability") +
+  geom_vline(xintercept = 0, lty = 2, col = "gray") +
+  my_theme
+
+```
+
+### Efectos de las promesas y la cercanía social en la decisión
+
+Para evaluar el efecto las condiciones experimentales en la decisión de pagar la mitad, se utilizaron todos los ensayos en los que los compañeros decidieron invertir.
+Nuevamente, se realizó un modelo bayesiano jerárquico, que asume que las promesas y los compañeros de juego tienen un efecto que varía para cada individuo, sin embargo, también asume que dichas variaciones pertenecen a distribuciones poblacionales comunes.
+El modelo estima que la probabilidad $\theta_i$ de que en cada ensayo se decida pagar la mitad está en función del efecto de la presencia de promesas $\beta^{promise}$, así como de los compañeros con cercanía social baja $\beta^{confederate}$ y alta $\beta^{friend}$.
+
+El modelo se programó en R por medio del paquete **brms**, que realiza la inferencia mediante el muestreo por Markov chain Monte Carlo a través de **Stan**.
+Las distribuciones posteriores de todos los parámetros fueron aproximadas con cuatro cadenas de 2000 iteraciones cada una, las primeras 1000 iteraciones de cada cadena fueron descartadas (periodo de calentamiento), para un total de 4000 muestras post-calentamiento.
+La convergencia del modelo fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que para todos los parámetros fue de 1, lo que se interpreta como convergencia.
+
+En la Figura 4 se presentan las distribuciones posteriores de los coeficientes $\beta$ en escala logit, la linea central representa la mediana de la distribución y el área sombreada coresponde con el intervalo de 50% de probabilidad posterior.
+
+```{r fig4, fig.cap='Posterior estimates in logit scale'}
+
+g5
+
+```
+
+Asimismo, la Figura 5 presenta la distribución posterior predictiva en contraste con la proporción de las decisiones de los primeros doce sujetos en la fase de promesas.
+La distribución posterior predictiva simula observaciones del modelo y las compara con los datos reales, nos sirve para identificar si el modelo es suficientemente cercano al proceso que ha generado los datos.
+
+```{r fig5, fig.cap='Posterior predictive over pay back rate', out.width='100%'}
+
+g9 + 
+  labs(x = NULL, y = "Rate") +
+  theme(axis.text.y = element_text(size = 8),
+           strip.text.x = element_text(size = 8))
+
+```
+
+### Efectos de la cercanía social variantes por promesas
+
+En este modelo se asume que la cercanía social tiene un efecto que varía para cada nivel de promesa, lo que implica que hay niveles de promesas que son más sensibles al efecto de los compañeros de juego.
+Nuevamente, se realizó un modelo bayesiano jerárquico para estimar el efecto de los compañeros de juego a nivel poblacional y la variabilidad dependiendo de los niveles de promesa.
+En la Figura 6 se muestra la distribución posterior predictiva, comparada con las tasas de pago de todos los individuos a los diferentes compañeros y su variación por el nivel de promesa.
+
+```{r fig6, fig.cap='Posterior predictive over pay back rate, Social Closeness Varying effects by Promise levels'}
+
+g13b + 
+  theme(axis.text.x = element_text(size = 7))
+
+```
+
+```{r tabla}
+
+tabla1 <- broom::tidy(fit) %>% 
+  slice(1:3)
+
+tabla1[, 1] <- c("Intercept", "Confederate", "Friend")
+
+kable(tabla1, 
+      digits = 3, 
+      booktabs = T,
+      col.names = c("Term", "Estimate", "Est.Error", "Lower", "Upper"),
+      caption = c("Posterior coefficients estimates")) %>%
+  add_header_above(c(" ", " " = 2, "95 % CI" = 2)) %>% 
+  kable_styling(latex_options = "hold_position")
+
+```
 
 ### Análisis de cluster jerárquico
+
+En el estudio orginal de promesas [@Baumgartner2009], los autores optaron por dividir su muestra en dos de acuerdo a la técnica de agrupamiento jerárquico con el método de Ward.
+De esta manera obtuvieron dos conjuntos de participantes que eran diferentes en sus tasas de pago, a pesar de que ambos hacían promesas muy altas, por tal motivo los autores denominaron al grupo que pagaba poco _deshonestos_ y al grupo que pagaba mucho _honestos_.
+En un ejercicio similar, en el presente estudio realizamos la técnica de agrupamiento jerárquico para obtener una solución de 2 grupos y encontramos dos conjuntos similares en $n$ (Grupo 1 = 23, Grupo 2 = 19), con proporciones de pago bastante diferentes (Grupo 1 = 58%, Grupo 2 = 84%), con una diferencia en un intervalo de confianza del 95% de 19% a 32% en favor del Grupo 2.
 

### 2019-07-04 varying_effects_promises.R

@@ -8,7 +8,7 @@ load("~/Documents/R/github_Said/website/said/public/candidatura/candidatura.RDat
 
 # Packages ----------------------------------------------------------------
 
-pacman::p_load(tidyverse, brms)
+pacman::p_load(tidyverse, brms, tidybayes)
 
 
 # Pay by promise level and partner ----------------------------------------
@@ -233,5 +233,21 @@ marginal_effects(fit3, categorical = T)
 
 hypothesis(fit3, "groupLow < 0")
 
+diff_data <- posterior_samples(fit3) %>% 
+  select(low = b_groupLow)
 
-
+ggplot(diff_data, aes(x = low)) +
+  geom_histogram(fill = "#A4CAE3",
+                 col = "#A4CAE3",
+                 alpha = 0.4) +
+  geom_vline(xintercept = 0,
+             lty = 2,
+             col = "#787878",
+             size = .6) +
+  stat_pointintervalh(aes(y = 0),
+                      .width = .95,
+                      size = 10,
+                      col = "#053778") +
+  labs(x = "Low",
+       y = "Count") +
+  my_theme

### 2019-07-06 article_spanish.Rmd
.

--- 2019-06-28 article_spanish.Rmd
@@
 
-```{r figA, fig.cap='Task of promises and social closeness', out.width='80%'}
+```{r figA, fig.cap='Task of promises and social closeness'}
 
@@
 
-Se analizaron 756 decisiones sobre pagar o no la mitad (18 por sujeto), así cómo 168 
+Se analizaron 756 decisiones sobre pagar o no la mitad (18 por sujeto), así como 168 
 promesas (4 por sujeto), 69.6% de las decisiones fueron pagar la mitad, mientras que la proporción de las promesas seleccionadas fueron 4.17%, 14.9% 41.1%, 37.5%, respectivamente para las promesas, nunca, algunas veces, casi siempre y siempre.
@@
 
-### Efectos variantes por sujeto
+Todos los modelos presentados a continuación se programaron en R por medio del paquete **brms** [@Burkner2017; @R2019], que realiza la inferencia mediante el muestreo por Markov chain Monte Carlo a través de **Stan** [@Rstan2018].
+Para cada modelo, las distribuciones posteriores de todos los parámetros fueron aproximadas con cuatro cadenas de 2000 iteraciones cada una, las primeras 1000 iteraciones de cada cadena fueron descartadas (periodo de calentamiento), para un total de 4000 muestras post-calentamiento.
+La convergencia de los modelos fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que para todos los parámetros fue de 1, lo que se interpreta como convergencia.
 
-### Efectos variantes por promesas
+### Efecto de la cercanía social en el engaño
 
-### Análisis de cluster jerárquico
+Para evaluar la hipótesis de que la cercanía social reduciría el engaño, se filtraron todos los ensayos en los que los sujetos promieteron que _siempre_ pagarían y después decidieron no pagar.
+Posteriormente, se utilizó inferencia bayesiana para evaluar el efecto de los compañeros de juego en la decisión de romper la promesa a nivel individual y poblacional.
+Para tal propósito, se realizó un modelo bayesiano jerárquico que asume que la incertidumbre en la estimación del efecto de los compañeros sobre la decisión de romper la promesa varía dependiendo de cada individuo, sin embargo, también asume que dichas variaciones pertenecen a distribuciones poblacionales comunes para el efecto de cada compañero sobre la decisión [@Gelman2006].
+
+$$
+\begin{aligned}
+&y_i \sim \mathrm{Bernoulli}(\theta_i) \\
+&\mathrm{logit(\theta_i)} = \mathbf{X}\beta  +  \mathbf{Z}u
+\end{aligned}
+$$
+
+En el modelo anterior, la decisión de romper la promesa $y_i$ proviene de una distribución Bernoulli con probabilidad de pagar $\theta_i$, el objetivo del modelo jerárquico es predecir cada decisión a través de la combinación lineal de los efectos de cada compañero de juego, transformados por su función ligadora inversa $\mathrm{logit}$ [@Burkner2017].
+En este modelo, $\beta$ y $u$ son coeficientes a nivel poblacional y nivel individual respectivamente, mientras que $\mathbf{X}$, $\mathbf{Z}$ son sus correpondientes matrices del diseño.
+En este caso, los coeficientes poblacionales corresponden con la presencia de los compañeros con cercanía social nula $\beta^{computer}$, baja $\beta^{confederate}$ y alta $\beta^{friend}$.
+
+En la Figura 3, se muestra la probabilidad posterior de romper la promesa dependiendo del compañero de juego, los circulos corresponden con las medianas de las distribuciones de las estimaciones posteriores de los efectos, la barra gruesa y la barra delgada corresponden con el intervalo del 50% y 95% de probabilidad posterior.
+Es claro que la probabilidad de romper la promesa va disminuyendo conforme va aumentando la cercanía social, sin embargo, calculamos las razones de evidencia para las siguientes hipótesis:
+
+1. Hay mayor probabilidad de que se rompa la promesa a un compañero con cercanía nula (computadora) en comparación con los compañeros con cercanía social (desconocido y amigo).
+
+2. Hay mayor probabilidad de que se rompa la promesa a un compañero con cercanía social baja (desconocido) en comparación con el compañero de cercanía social alta (amigo).
+
+La razón entre la probabilidad posterior de las hipótesis mencionadas y sus correspondientes hipótesis alternativas fue de 10.33 y 5.58 respectivamente para las hipótesis 1 y 2.
+Cabe mencionar que la hipótesis de que la cercanía social reduciría el engaño fue expresada _a priori_ como parte de un proyecto de investigación más amplio y se puede consultar aquí: https://osf.io/re7kp/.
+
+```{r fig3, fig.cap='Posterior probability of Breaking the Promise'}
+bayesplot::mcmc_intervals(
+  samples_fit2,
+  prob_outer = 0.95
+  ) +
+  labs(x = "Posterior Probability") +
+  geom_vline(xintercept = 0, lty = 2, col = "gray") +
+  my_theme
+
+```
+
+### Efectos de las promesas y la cercanía social en la decisión
+
+Para evaluar el efecto de las condiciones experimentales en la decisión de pagar la mitad, se utilizaron todos los ensayos en los que los compañeros decidieron invertir.
+Nuevamente, se realizó un modelo bayesiano jerárquico, que asume que las promesas y los compañeros de juego tienen un efecto que varía para cada individuo, sin embargo, también asume que dichas variaciones pertenecen a distribuciones poblacionales comunes.
+El modelo estima que la probabilidad $\theta_i$ de que en cada ensayo se decida pagar la mitad está en función del efecto de la presencia de promesas $\beta^{promise}$, así como de los compañeros con cercanía social baja $\beta^{confederate}$ y alta $\beta^{friend}$.
+
+En la Figura 4 se presentan las distribuciones posteriores de los coeficientes $\beta$ en escala logit, la linea central representa la mediana de la distribución y el área sombreada corresponde con el intervalo de 50% de probabilidad posterior.
+Como se puede observar, más del 95% de la densidad posterior de los coeficientes poblacionales está superior al 0, lo que indica fuerte evidencia del efecto de las condiciones experimentales en la decisión de pagar, de modo que la presencia de promesas y del confederado aumentan claramente la probabilidad de pagar, pero la presencia del amigo es la condición que más efecto tiene en esta conducta.
+
+Asimismo, la Figura 5 presenta la distribución posterior predictiva en contraste con la proporción de las decisiones a cada compañero, cada panel corresponde con uno de los primeros doce sujetos en la fase de promesas.
+Las respuestas sobre la linea punteada indicarían que el sujeto pago la mitad de los ensayos en que ese compañero estuvo presente.
+La distribución posterior predictiva simula observaciones del modelo y las compara con los datos reales, nos sirve para identificar si el modelo es suficientemente cercano al proceso que ha generado los datos [@Schad2019; @Lee2014].
+Se puede observar que existe gran correspondencia entre la respuesta de los sujetos y las predicciones del modelo, aún en los casos en los que el modelo se "equivoca" (por ejemplo el sujeto 1) la respuesta observada se sitúa en el margen de error de la predicción, lo que da credibilidad a las estimaciones.
+
+```{r fig4, fig.cap='Posterior estimates in logit scale'}
+
+g5
+
+```
+
+```{r fig5, fig.cap='Posterior predictive over pay back rate', out.width='100%', out.height='100%'}
+
+d_g9 %>% 
+    ggplot(aes(x = treatment, y = rate, col = case)) +
+    geom_hline(yintercept = 0.5, lty = 2, col = "gray") +
+    geom_line(aes(group = case), show.legend = F) +
+    geom_pointrange(aes(ymax = rate + pred_sd, ymin = rate - pred_sd),
+                    shape = 21, fill = "white", size = 0.4) +
+    scale_color_manual(values = c("#053778", "#A4CAE3")) +
+    facet_wrap(~id) +
+    my_theme +
+    scale_y_continuous(breaks = c(0, 0.5, 1.0)) +  
+    theme(axis.text.x = element_text(angle = 75, hjust = 1), 
+          legend.position = "top",
+          text = element_text(size = 10)) +
+    labs(x = NULL, y = "Rate", col = NULL)
+
+```
+
+### Efectos de la cercanía social variantes por promesas
+
+En este modelo se asume que la cercanía social tiene un efecto que varía para cada nivel de promesa, lo que implica que hay niveles de promesa que son más sensibles que otros al efecto de los compañeros de juego sobre la decisión de pagar la mitad.
+Nuevamente se realizó un modelo bayesiano jerárquico para estimar el efecto de los compañeros de juego a nivel poblacional y las variaciones dependiendo de los niveles de promesa.
+La Tabla 1 resume las distribuciones posteriores de los coeficientes del modelo en escala logit, incluye los estimadores puntuales, sus errores estándar y los intervalos de credibilidad bayesianos del 95%.
+Se puede observar una estimación similar a los modelos anteriores, con evidencia fuerte del efecto de la cercanía social sobre la decisión de pagar la mitad.
+Por otra parte, en la Figura 6 se muestra la distribución posterior predictiva, comparada con las tasas de pago de todos los individuos a los diferentes compañeros y su variación por el nivel de promesa.
+A excepción de con la promesa _never_, se observa un efecto positivo monotónico de los compañeros de juego en todos los niveles de promesa, sin embargo se puede observar cómo el efecto de la cercanía social varía dependiendo de la fuerza de la promesa.
+
+```{r fig6, fig.cap='Posterior predictive over pay back rate, Social Closeness Varying effects by Promise levels'}
+
+g13b + 
+  scale_y_continuous(breaks = c(0, 0.5, 1.0)) +  
+  theme(axis.text.x = element_text(size = 7))
+
+```
+
+```{r tabla}
+
+tabla1 <- broom::tidy(fit) %>% 
+  slice(1:3)
+
+tabla1[, 1] <- c("Intercept", "Confederate", "Friend")
+
+kable(tabla1, 
+      digits = 3, 
+      booktabs = T,
+      col.names = c("Term", "Estimate", "Est.Error", "Lower", "Upper"),
+      caption = c("Posterior coefficients estimates")) %>%
+  add_header_above(c(" ", " " = 2, "95 % CI" = 2)) %>% 
+  kable_styling(latex_options = "hold_position")
+
+```
+
+### Compromiso expresado en las promesas
+
+En el estudio orginal de promesas [@Baumgartner2009], los autores optaron por dividir su muestra en dos de acuerdo a la técnica de agrupamiento jerárquico con el método de Ward.
+De esta manera obtuvieron dos conjuntos de participantes que eran diferentes en sus tasas de pago, a pesar de que ambos hacían promesas muy altas, por tal motivo los autores denominaron al grupo que pagaba poco _deshonestos_ y al grupo que pagaba mucho _honestos_.
+En un ejercicio similar, en el presente estudio realizamos la técnica de agrupamiento jerárquico para obtener una solución de 2 grupos y encontramos dos conjuntos similares en $n$ que denominamos grupo "Low" y "High" (Low = 23, High = 19), con proporciones de pago bastante diferentes (Low = 58%, High = 84%), con una diferencia en un intervalo de confianza del 95% de 19% a 32% en favor del grupo High.
+
+Aunque pareciera un resultado similar al reportado en el trabajo de Baumgartner (2009), exploramos el patrón de promesas de ambos grupos para determinar si era posible clasificar a nuestros sujetos como honestos y deshonestos.
+Si hipotetizamos que el compromiso de pagar seria reflejado en el nivel de promesas seleccionado, un grupo de deshonestos podría generar en sus compañeros la creencia de que pagará al seleccionar un nivel alto de promesas (siempre o casi siempre) y, posteriormente, traicionar esa confianza al decidir no pagar la mitad.
+
+Con el objetivo de explorar si los grupos representan a poblaciones que no difieren en el nivel de compromiso expresado en las promesas, utilizamos un modelo bayesiano acumulativo, que asume que los niveles de promesas son una varable ordinal observada $Y$ que se origina de la categorización de una variable latente continua $\tilde{Y}$, para este caso, _el compromiso expresado de pagar la mitad_ [@Burkner2019].
+El grado en que los sujetos del grupo High difieren del grupo Low, en desviaciones estándar normales ($z$-values), en la escala latente de $\tilde{Y}$, tiene un estimador puntual de 0.95, lo que implica que el grupo de High tiene 0.95 $z$-values mayor compromiso de pagar la mitad que el grupo Low.
+
+El intervalo de credibilidad bayesiano del 95% indica que el grupo High está entre 0.35 a 1.58 $z$-values de diferencia con respecto a Low.
+Por lo que podemos concluir con al menos 95% de probabilidad posterior que las personas que pertenecen al grupo High expresaron en sus promesas mayor compromiso de pagar la mitad de lo que hicieron los sujetos del grupo Low.
+Si observamos la Figura 7, la probabilidad de seleccionar los diferentes niveles de promesas varía dependiendo del grupo, el que tuvo mayor porcentaje de decisiones de pagar la mitad tiene más probabilidad de seleccionar _Always_ (grupo High), mientras que el grupo que tuvo menor porcentaje de decisiones de pagar la mitad tiene más probabilidad de seleccionar _Mostly_ (grupo Low).
+
+Según nuestros datos, no podríamos justificar la clasificación de nuestros grupos de acuerdo con su honestidad o deshonestidad, al menos no con la técnica empleada en Baumgartner (2009).
+Ya que las personas fueron bastante consistentes con cumplir lo que prometían pagar.
+
+```{r fig7, fig.cap='Promise choices by group'}
+
+# Cumulative model
+plt$`group:cats__` +
+  labs(x = "Group",
+       col = "Promise",
+       fill = "Promise") +
+  scale_fill_manual(values = RColorBrewer::brewer.pal(9, "Blues")[c(3, 5, 7, 9)], 
+                    aesthetics = "col") +
+  my_theme
+
+```
 

### 2019-07-06 varying_effects_promises.R

@@ -251,3 +251,43 @@ ggplot(diff_data, aes(x = low)) +
   labs(x = "Low",
        y = "Count") +
   my_theme
+
+
+
+data5 <- data4 %>% 
+  filter(prom_ord != "No response") %>% 
+  mutate(prom_ord = fct_drop(prom_ord),
+         group = factor(group, levels = c("Low", "High")))
+  
+fit4 <- brm(prom_ord ~ group + (1 | id + trial), 
+            data = data5,
+            family = cumulative("probit"),
+            sample_prior = "yes",
+            chains = 4,
+            cores = 4,
+            control = list(adapt_delta = 0.99, 
+                           max_treedepth = 15))
+
+plt <-  plot(marginal_effects(fit4, categorical = T))
+
+
+plt$`group:cats__` +
+  labs(x = NULL,
+       col = "Promise",
+       fill = "Promise") +
+  scale_fill_manual(values = RColorBrewer::brewer.pal(9, "Blues")[c(3,5,7,9)], 
+                    aesthetics = "col") +
+  my_theme 
+
+
+data %>% 
+  mutate(ahead = lead(decision)) %>% 
+  select(partner, dec_partner, decision, ahead) %>% 
+  count(partner, dec_partner, ahead)
+
+
+d_ord %>% 
+  mutate(ahead = lead(prom_ord, n = 2L)) %>% 
+  filter(ahead != "No response") %>% 
+  select(dec_partner, ahead) %>% 
+  count(dec_partner, ahead)

### 2019-07-10 article_spanish.Rmd
Introduction

@@
 fontsize: 12pt
-bibliography: judgement.bib
+bibliography: promises.bib
 csl: apa.csl
@@
 # Introducción
+
+A la fecha, la inmensa mayoría de los estudios sobre engaño en economía, psicología y neurociencias, se han realizado en personas que NO se conocen entre sí [por indicar algunos, @Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
+En psicología social existen estudios que abordan el engaño en las relaciones interpersonales cercanas, sin embargo utilizan metodologías de autorreporte [@DePaulo1998; @DePaulo2004] o bien exploran las habilidades de detección del engaño en amigos del mismo sexo [@Anderson2002].
 

### 2019-07-10 article_spanish.Rmd
introduction

--- 2019-07-06 article_spanish.Rmd
@@
 # Introducción
+
+Los seres humanos somos animales sociales y obtenemos ventajas de serlo.
+Historicamente, pertenecer a un grupo social ha brindado protección y garantizado el acceso a recursos como el alimento, actualmente se ha mostrado evidencia de que pertencer a un circulo social tiene un efecto positivo en la longevidad, la salud física y mental [@Tough2017; @Holt-Lunstad2018].
+La interrelación entre la cercanía social y la cooperación es clave para la conformación de grandes grupos de individuos sin una relación genética, dichos grupos conforman la base de comunidades, sociedades y naciones, así como probablemente constituyen una de las condiciones más importantes para la supervivencia humana [@Fehr2003; @Fehr2018].
+
+Un requisito importante para que haya cooperación entre individuos es la comunicación, un metaanálisis que evaluó el efecto de la comunicación verbal o escrita en la cooperación en dilemas sociales, con base en 45 tamaños de efecto reportó un efecto positivo grande ($d = 1.01$) independientemente de la vía de comunicación [@Balliet2010].
+
+Si las relaciones sociales son tan importantes, se podría pensar que una buena cantidad de las interacciones en que ocurre el engaño involucran personas de nuestro circulo social, de hecho la literatura ha mostrado que la gente frecuentemente miente a personas de las que se depende para obtener recursos [@VonHippel2011; @DePaulo1998; @Steinel2004].
+
+A la fecha, la inmensa mayoría de los estudios sobre toma de decisiones que involucran engaño en economía, psicología y neurociencias, se han realizado en personas que NO se conocen entre sí [por mencionar algunos, @Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
+En psicología social existen estudios que abordan el engaño en las relaciones interpersonales cercanas, sin embargo utilizan metodologías de autorreporte [@DePaulo1998; @DePaulo2004] o más bien exploran el desarrollo de habilidades de detección del engaño en amigos del mismo sexo [@Anderson2002].
+
+Economia cooperación
+
+IDT dice qué
 

### 2019-07-11 article_spanish.Rmd
.

@@
 author: "Said E. Jiménez"
-date: "6/27/2019"
+date: "July 2019"
 output: 
   pdf_document:
-    toc: true
     number_sections: true
@@
 Historicamente, pertenecer a un grupo social ha brindado protección y garantizado el acceso a recursos como el alimento, actualmente se ha mostrado evidencia de que pertencer a un circulo social tiene un efecto positivo en la longevidad, la salud física y mental [@Tough2017; @Holt-Lunstad2018].
-La interrelación entre la cercanía social y la cooperación es clave para la conformación de grandes grupos de individuos sin una relación genética, dichos grupos conforman la base de comunidades, sociedades y naciones, así como probablemente constituyen una de las condiciones más importantes para la supervivencia humana [@Fehr2003; @Fehr2018].
+La interrelación entre la cercanía social y la cooperación es clave para la conformación de grandes grupos de individuos sin una relación genética, dichos grupos conforman la base de comunidades, sociedades y naciones, así como probablemente constituyen una de las condiciones más fundamentales para la supervivencia humana [@Fehr2003; @Fehr2018].
 
-Un requisito importante para que haya cooperación entre individuos es la comunicación, un metaanálisis que evaluó el efecto de la comunicación verbal o escrita en la cooperación en dilemas sociales, con base en 45 tamaños de efecto reportó un efecto positivo grande ($d = 1.01$) independientemente de la vía de comunicación [@Balliet2010].
+Un requisito importante para que haya cooperación entre individuos es la comunicación, un metaanálisis  de 45 estudios reportó un efecto positivo grande ($d = 1.01$) de la comunicación en la cooperación independientemente del medio comunicativo [@Balliet2010].
+De manera paralela, se sabe que posteriormente a sesiones de comunicación entre individuos completamente desconocidos hay un incremento de la cercanía social subjetiva [@Aron1997].
+Una de las formas de comunicación que ha recibido mayor atención en la teoría de juegos psicológica son las promesas, en una interacción entre quien la envía y la recibe, se cree que las promesas influyen en las creencias del receptor generando confianza y cooperación [@Charness2006; @Vanberg2008; @Baumgartner2009].
+
+Sin embargo, existen situaciones donde se traiciona la confianza y se rompen las promesas,
+
+tasas de divorcio, engaños politicos,
 

### 2019-07-11 article_spanish.Rmd
intro

@@
 csl: apa.csl
-header-includes: \usepackage{float}
 ---
@@
 De manera paralela, se sabe que posteriormente a sesiones de comunicación entre individuos completamente desconocidos hay un incremento de la cercanía social subjetiva [@Aron1997].
+Sugiriendo una relación positiva entre la comunicación, la cooperación y la cercanía social.
+
 Una de las formas de comunicación que ha recibido mayor atención en la teoría de juegos psicológica son las promesas, en una interacción entre quien la envía y la recibe, se cree que las promesas influyen en las creencias del receptor generando confianza y cooperación [@Charness2006; @Vanberg2008; @Baumgartner2009].
-
-Sin embargo, existen situaciones donde se traiciona la confianza y se rompen las promesas,
-
-tasas de divorcio, engaños politicos,
+Sin embargo, existen situaciones en que se traiciona la confianza, se rompen las promesas o se engaña, por ejemplo, aproximadamente el 11% de las personas encuestadas por la General Social Survey (GSS) en 2018 respondieron que sí han tenido sexo con alguien diferente a su pareja mientras están casados [@GSS2018].
+Otro ejemplo, de acuerdo con el Washington Post el presidente Trump ha dicho 10,796 afirmaciones falsas o engañosas en 869 días en el cargo [@Kessler2019].
 
@@
 En psicología social existen estudios que abordan el engaño en las relaciones interpersonales cercanas, sin embargo utilizan metodologías de autorreporte [@DePaulo1998; @DePaulo2004] o más bien exploran el desarrollo de habilidades de detección del engaño en amigos del mismo sexo [@Anderson2002].
-
-Economia cooperación
-
-IDT dice qué
 

### 2019-07-11 article_spanish.Rmd
New title.

@@
 ---
-title: "Social closeness in the face of deception"
+title: "Good guys or potential cooperators: an experimental and Bayesian account for two explanations"
 author: "Said E. Jiménez"
@@
 
-Una de las formas de comunicación que ha recibido mayor atención en la teoría de juegos psicológica son las promesas, en una interacción entre quien la envía y la recibe, se cree que las promesas influyen en las creencias del receptor generando confianza y cooperación [@Charness2006; @Vanberg2008; @Baumgartner2009].
+Una de las formas de comunicación que ha recibido mayor atención en la teoría de juegos psicológica son las promesas, en una interacción entre quien la envía y la recibe, se cree que las promesas influyen en las creencias del receptor generando confianza y cooperación [@Charness2006; @Vanberg2008].
 Sin embargo, existen situaciones en que se traiciona la confianza, se rompen las promesas o se engaña, por ejemplo, aproximadamente el 11% de las personas encuestadas por la General Social Survey (GSS) en 2018 respondieron que sí han tenido sexo con alguien diferente a su pareja mientras están casados [@GSS2018].
@@
 
-Si las relaciones sociales son tan importantes, se podría pensar que una buena cantidad de las interacciones en que ocurre el engaño involucran personas de nuestro circulo social, de hecho la literatura ha mostrado que la gente frecuentemente miente a personas de las que se depende para obtener recursos [@VonHippel2011; @DePaulo1998; @Steinel2004].
-
-A la fecha, la inmensa mayoría de los estudios sobre toma de decisiones que involucran engaño en economía, psicología y neurociencias, se han realizado en personas que NO se conocen entre sí [por mencionar algunos, @Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
+En el laboratorio se han estudiado explícitamente estas transgresiones a la confianza en experimentos donde las personas tienen incentivos para mentir o no cumplir sus promesas.
+Sin embargo, la inmensa mayoría de estos estudios en economía, psicología y neurociencias, se han realizado en personas que NO se conocen entre sí [por mencionar algunos, @Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
 En psicología social existen estudios que abordan el engaño en las relaciones interpersonales cercanas, sin embargo utilizan metodologías de autorreporte [@DePaulo1998; @DePaulo2004] o más bien exploran el desarrollo de habilidades de detección del engaño en amigos del mismo sexo [@Anderson2002].

### 2019-07-12 article_spanish.Rmd
intro

@@
 ---
-title: "Good guys or potential cooperators: an experimental and Bayesian account for two explanations"
+title: "Nice guys or potential cooperators: an experimental and Bayesian account for two explanations"
 author: "Said E. Jiménez"
@@
 De manera paralela, se sabe que posteriormente a sesiones de comunicación entre individuos completamente desconocidos hay un incremento de la cercanía social subjetiva [@Aron1997].
-Sugiriendo una relación positiva entre la comunicación, la cooperación y la cercanía social.
+Así, los hallazgos sugirien una relación positiva entre la comunicación, la cooperación y la cercanía social.
 
@@
 Sin embargo, la inmensa mayoría de estos estudios en economía, psicología y neurociencias, se han realizado en personas que NO se conocen entre sí [por mencionar algunos, @Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
-En psicología social existen estudios que abordan el engaño en las relaciones interpersonales cercanas, sin embargo utilizan metodologías de autorreporte [@DePaulo1998; @DePaulo2004] o más bien exploran el desarrollo de habilidades de detección del engaño en amigos del mismo sexo [@Anderson2002].
+En psicología social existen estudios que abordan el engaño en las relaciones interpersonales cercanas, sin embargo utilizan mediciones de autorreporte [@DePaulo1998; @DePaulo2004] o más bien exploran el desarrollo de habilidades de detección del engaño en amigos del mismo sexo [@Anderson2002].
+Pese a la presencia generalizada de las interacciones entre seres humanos que pertenecen al mismo grupo, no se conoce cómo la cercanía social entre sujetos puede tener un efecto en el cumplimiento o rompimiento de las promesas.
+
+En el presente manuscrito, se exploran los efectos de tres compañeros con diferentes niveles de cercanía social en el cumplimiento y rompimiento de promesas, así como en la cooperación en un juego de confianza.
+Lo anterior, lo analizamos a la luz de las dos motivaciones principales que se han señalado en la literatura respecto a cumplir promesas:
+
+1. La _instrumental_, sugiere que se cumplen las promesas para hacer más fácil la cooperación en el futuro.
+
+2. La _intrinseca_, menciona que se cumplen las promesas por el propósito de hacer lo moralmente correcto.
 

### 2019-07-12 article_spanish.Rmd
Hypothesis

@@
 
-En el laboratorio se han estudiado explícitamente estas transgresiones a la confianza en experimentos donde las personas tienen incentivos para mentir o no cumplir sus promesas.
+En el laboratorio se han estudiado explícitamente estas transgresiones a la confianza en experimentos donde los sujetos tienen incentivos para mentir o no cumplir sus promesas.
 Sin embargo, la inmensa mayoría de estos estudios en economía, psicología y neurociencias, se han realizado en personas que NO se conocen entre sí [por mencionar algunos, @Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
@@
 En el presente manuscrito, se exploran los efectos de tres compañeros con diferentes niveles de cercanía social en el cumplimiento y rompimiento de promesas, así como en la cooperación en un juego de confianza.
-Lo anterior, lo analizamos a la luz de las dos motivaciones principales que se han señalado en la literatura respecto a cumplir promesas:
+Lo anterior, lo analizamos a la luz de las dos motivaciones principales que se han señalado en la literatura respecto a cumplir promesas [@Baumgartner2009]:
 
@@
 2. La _intrinseca_, menciona que se cumplen las promesas por el propósito de hacer lo moralmente correcto.
+
+En nuestro estudio, los sujetos realizan un juego de cooperación estándar en parejas con tres fases: _primero_, el fideicomisario realiza una promesa sobre pagar la mitad de sus ganancias independientemente de quién sea su inversor; _segundo_, el inversor recibe la promesa y decide si invierte su presupuesto inicial; _tercero_, en caso de que el inversor haya dado el presupuesto, el fideicomisario se enfrenta a la decisión de pagar o no la mitad de sus ganancias.
+Con el propósito de evaluar el efecto de la cercanía social, nuestros sujetos participan en el papel de fideicomisario frente a tres compañeros con diferentes niveles de cercanía social (nula, baja y alta) en el rol del inversor: una _computadora_, un _extraño_ y un _amigo_.
+
+Las manipulaciones mencionadas nos permiten evaluar varias hipótesis, la primera fue propuesta _a priori_ y es derivada de un proyecto de investigación más grande (se puede consultar el preregistro de la hipótesis aquí: https://osf.io/u97fd), mientras que las siguientes son de carácter exploratorio:
+
+1.
+La cercanía social reducirá la conducta de romper la promesa.
+De acuerdo con la motivación _instrumental_, esperamos que los sujetos mantengan sus promesas con los amigos por el propósito de facilitar la cooperación en el futuro, la cual se puede extender inclusive más allá de los ensayos en el experimento.
+También esperamos, aunque en menor grado, que los sujetos cumplan las promesas a los extraños, con el propósito de facilitar la cooperación por lo menos durante los ensayos que dure el experimento.
+Finalmente, anticipamos que los participantes rompan las promesas a la computadora, por tratarse de un compañero sin cercanía social y del que no podrían asegurar cooperación en futuros ensayos.
+Cabe destacar que si los participantes cumplen las promesas a la computadora, se daría evidencia en favor de la motivación _intrínseca_.
 

### 2019-07-13 article_spanish.Rmd
Hypothesis

@@
 Cabe destacar que si los participantes cumplen las promesas a la computadora, se daría evidencia en favor de la motivación _intrínseca_.
+
+2.
+Habrá un efecto de la cercanía social en la cooperación, independientemente de las promesas.
+Esperamos que haya más probabilidad de pagarle al _amigo_ que al _extraño_ y más probabilidad de pagarle al extraño que la _computadora_.
+De acuerdo con la motivación _instrumental_, la cooperación será mayor para compañeros con los que el sujeto anticipe mayor cooperación en el futuro (amigo > extraño > computadora).
+
+3.
+Las promesas incrementarán la cooperación mediadas por la cercanía social.
+Exploramos la posibilidad de que el _mecanismo_ que explica el efecto de la comunicación en la cooperación sea el incremento en la cercanía social.
+
+4.
+Finalmente, obtendremos dos submuestras de acuerdo con la tasa de cooperación de los sujetos como se realizó en otro estudio [@Baumgartner2009].
+Sin embargo, lo que en el estudio mencionado se clasificó como grupo de _honestos_ y _deshonestos_, mostraremos que en nuestra muestra no se sostiene porque si los grupos difieren es su tasa de pago será por la diferencia en su nivel de compromiso expresado en las promesas.
 

### 2019-07-15 article_spanish.Rmd
Updating data

@@
 knitr::opts_chunk$set(echo=FALSE, fig.align='center', dev='png', dpi=400, out.width='80%')
-load("~/Documents/R/github_Said/website/said/public/candidatura/candidatura.RData")
+load("~/Google Drive/PromesaConducta_8to2/data/promesas_analisis/Analisis-Comportamiento/promesas_analisis/data.RData")
 pacman::p_load(tidyverse, kableExtra)
@@
 3.
-Las promesas incrementarán la cooperación mediadas por la cercanía social.
-Exploramos la posibilidad de que el _mecanismo_ que explica el efecto de la comunicación en la cooperación sea el incremento en la cercanía social.
-
-4.
 Finalmente, obtendremos dos submuestras de acuerdo con la tasa de cooperación de los sujetos como se realizó en otro estudio [@Baumgartner2009].
@@
 
-g14 + theme(text = element_text(size = 10),
+p2 + theme(text = element_text(size = 10),
             axis.text.x = element_text(size = 8))
@@
 ```{r fig3, fig.cap='Posterior probability of Breaking the Promise'}
-bayesplot::mcmc_intervals(
-  samples_fit2,
-  prob_outer = 0.95
-  ) +
-  labs(x = "Posterior Probability") +
-  geom_vline(xintercept = 0, lty = 2, col = "gray") +
-  my_theme
+p3
 
@@
 
-g5
+p4
 
@@
 
-g13b + 
+p6 + 
   scale_y_continuous(breaks = c(0, 0.5, 1.0)) +  
@@
 
-tabla1[, 1] <- c("Intercept", "Confederate", "Friend")
+tabla1[, 1] <- c("Intercept", "Stranger", "Friend")
 
@@
 # Cumulative model
-plt$`group:cats__` +
-  labs(x = "Group",
-       col = "Promise",
-       fill = "Promise") +
-  scale_fill_manual(values = RColorBrewer::brewer.pal(9, "Blues")[c(3, 5, 7, 9)], 
-                    aesthetics = "col") +
-  my_theme
+p7
 

### 2019-07-16 article_spanish.Rmd
Updating task description

@@
 Finalmente, obtendremos dos submuestras de acuerdo con la tasa de cooperación de los sujetos como se realizó en otro estudio [@Baumgartner2009].
-Sin embargo, lo que en el estudio mencionado se clasificó como grupo de _honestos_ y _deshonestos_, mostraremos que en nuestra muestra no se sostiene porque si los grupos difieren es su tasa de pago será por la diferencia en su nivel de compromiso expresado en las promesas.
+Sin embargo, lo que en el estudio mencionado se clasificó como grupo de _honestos_ y _deshonestos_, mostraremos que en nuestra muestra no se sostiene porque si los grupos difieren en su tasa de pago será por la diferencia en su nivel de compromiso expresado en las promesas.
 
@@
 
-Todos los participantes realizaron una adaptación de la tarea de confianza y promesas presentada por Baumgartner (2009), que consiste en 24 ensayos entre dos jugadores **A** y **B**, el jugador **A** tiene originalmente 0 pesos mexicanos y el jugador **B** tiene 2 pesos, al jugador **B** se le presenta la oportunidad de invertir su dinero al jugador **A** o conservarlo, si invierte su dinero se multiplica por 5 pesos, de modo que el jugador **A** recibe 10 pesos.
-Finalmente, el jugador **A** toma la decisión de pagar la mitad al jugador **B** o quedarse los 10 pesos.
-La estructura descrita se repite en 24 ensayos, sin embargo, en 4 de los ensayos el jugador **A** puede enviar una promesa a **B**, las promesas son que _siempre_, _casi siempre_, _algunas veces_ o _nunca_ pagaran la mitad.
+Todos los participantes realizaron una adaptación de la tarea de confianza y promesas presentada por Baumgartner (2009), que consiste en 24 ensayos entre dos jugadores: fideicomisario e inversor.
+El fideicomisario tiene originalmente 0 pesos mexicanos y el inversor tiene 2 pesos, al inversor se le presenta la oportunidad de dar su dinero al fideicomisario o conservarlo, si invierte su dinero se multiplica por 5 pesos, de modo que el fideicomisario tenga 10 pesos.
+Finalmente, el fideicomisario toma la decisión de pagar la mitad al inversor o quedarse los 10 pesos.
+
+La estructura descrita se repite en 24 ensayos, sin embargo, en 4 de los ensayos el fideicomisario puede enviar una promesa al inversor, las promesas son que _siempre_, _casi siempre_, _algunas veces_ o _nunca_ pagaran la mitad.
 Cada promesa es válida por tres ensayos, de modo que 12 de los ensayos tienen el efecto de la promesa y los otros 12 no lo tienen.
 
-La variación respecto a la tarea original es que en nuestro experimento se presentaron tres compañeros de juego con tres niveles de cercanía social en el papel del jugador **B**: **computadora** (cercanía nula), **confederado** (cercanía baja) y **amigo** (cercanía alta), mientras que el participante principal siempre fungió el papel del jugador **A**.
-Cada compañero de juego realizó el rol de **B** en 8 de los 24 ensayos totales, sin embargo, tanto la condición de promesas como la de cercanía social fueron presentadas al sujeto **A** en orden pseudoaleatorio, lo que significa que se realizó la aleatorización de los ensayos una vez y se mantuvo el mismo orden para todos los sujetos.
-Con el fin de simplificar la tarea y homogeneizar la experiencia de todos nuestros participantes, se programaron _a priori_ las decisiones de los compañeros **B** sobre si invertían o no su monto inicial, se programó que los tres compañeros decidieran invertir en 6 ensayos y no invertir en 2, los cuales también se presentaron al sujeto **A** en orden pseudoaleatorio.
-La historia encubierta para todos nuestros sujetos en el papel de **A** fue que estarían jugando en tiempo real con su amigo, el confederado (que se le dijo que sería otra persona desconocida de su mismo sexo) y la computadora.
+La variación respecto a la tarea original es que en nuestro experimento se presentaron tres compañeros de juego con tres niveles de cercanía social en el papel del inversor: *computadora* (cercanía nula), *extraño* (cercanía baja) y *amigo* (cercanía alta), mientras que el sujeto funge el papel de fideicomisario.
+Cada compañero de juego realiza el rol de inversor en 8 de los 24 ensayos totales, sin embargo, tanto la condición de promesas como la de cercanía social fueron presentadas al fideicomisario en orden pseudoaleatorio.
+
+Dado que nuestro interés principal fue la conducta del fideicomisario, se programaron _a priori_ las decisiones de los inversores para que dieran su monto en 6 ensayos y en 2 no lo hicieran.
+La historia encubierta para todos nuestros sujetos fue que estarían jugando en tiempo real con su amigo, el extraño (que se le dijo que sería otra persona desconocida de su mismo sexo) y la computadora.
 

### 2019-07-17 article_spanish.Rmd
Updating manuscript

@@
 Se incluyeron 45 sujetos (15 hombres), reclutados en la Universidad Nacional Autónoma de México, en un rango de edad de 19 a 33 años y su nivel educativo mínimo fue licenciatura.
-Los participantes acudieron al estudio con un amigo considerado _cercano_ por ellos mismos, quien cumplía las siguientes características: era una persona del mismo sexo que el participante, no tenía un vínculo familiar y no se trataba de una persona con una relación de tipo sentimental y/o sexual.
+Los participantes acudieron al estudio con un amigo considerado _cercano_ por ellos mismos, quien cumplía las siguientes características: era una persona del mismo sexo que el sujeto, no tenía un vínculo familiar y no se trataba de una persona con una relación de tipo sentimental y/o sexual.
+30 de los sujetos (15 hombres) realizaron la tarea dentro de un equipo de Imagen por Resonancia Magnética (MRI), sin embargo, sus datos de imagen no son analizados en el presente trabajo.
 
-## Tarea y procedimiento
+## Tarea
 
-Todos los participantes realizaron una adaptación de la tarea de confianza y promesas presentada por Baumgartner (2009), que consiste en 24 ensayos entre dos jugadores: fideicomisario e inversor.
+Todos los sujetos realizaron una adaptación de la tarea de confianza y promesas presentada por Baumgartner (2009).
+La tarea se programó en PsychoPy2 versión 1.84.2 [@Peirce2019; @Peirce2008] y consiste en 24 ensayos entre dos jugadores: fideicomisario e inversor.
 El fideicomisario tiene originalmente 0 pesos mexicanos y el inversor tiene 2 pesos, al inversor se le presenta la oportunidad de dar su dinero al fideicomisario o conservarlo, si invierte su dinero se multiplica por 5 pesos, de modo que el fideicomisario tenga 10 pesos.
@@
 Cada promesa es válida por tres ensayos, de modo que 12 de los ensayos tienen el efecto de la promesa y los otros 12 no lo tienen.
+Cabe mencionar, que las promesas no se realizan hacia algún compañero en particular, si no que el sujeto expresa su nivel de compromiso de pagar la mitad independientemente de quiénes sean sus compañeros en los tres siguientes ensayos en que la promesa es valida.
 
@@
 La fase de fijación sólo consistió en un período en el que el sujeto prestaba atención sin realizar ninguna conducta en particular, la **fase de promesas** en la parte A$_{1}$ le indicó al sujeto que los siguientes tres ensayos se podían decidir sin el efecto de la promesa, mientras que en A$_{2}$ se le pidió al sujeto que decidiera entre _siempre_, _casi siempre_, _algunas veces_ o _nunca_ pagar la mitad.
-A lo anterior, le siguió otro período de fijación, posteriormente los ensayos tanto en A$_{1}$ como en A$_{2}$ continuaron aproximadamente de la misma forma, en la **fase de anticipación/asignación** se le indicó a los sujetos quién era su compañero de juego para ese ensayo (computadora, confederado o amigo) y se le dió el mensaje de que su compañero estaba tomando su decisión, posteriormente en la **fase de decisión** se le dió al participante la información sobre cuál había sido la decisión de su compañero (si invirtió sus 2 pesos o no), se le recordaba su nivel de promesas (si se trataba de ensayos con promesas) y, en el caso de que su compañero hubiera invertido, se le pedía que decidiera si pagaba de regreso o no.
+A lo anterior, le siguió otro período de fijación, posteriormente los ensayos tanto en A$_{1}$ como en A$_{2}$ continúan de la misma forma.
+
+En la **fase de anticipación/asignación** se le indicó a los sujetos quién era su compañero de juego para ese ensayo (computadora, confederado o amigo) y se le dió el mensaje de que su compañero estaba tomando su decisión, posteriormente en la **fase de decisión** se le dió al participante la información sobre cuál había sido la decisión de su compañero (si invirtió sus 2 pesos o no), se le recordaba su nivel de promesas (si se trataba de ensayos con promesas) y, en el caso de que su compañero hubiera invertido, se le pedía que decidiera si pagaba de regreso o no.
 Finalmente, en la **fase de feedback** se mostraban los pagos para ese ensayo y se repetía la secuencia.
-La tarea se programó en PsychoPy2 versión 1.84.2, que registraba las respuestas de los sujetos y los tiempos de reacción en segundos.
 
@@
 
+## Procedimiento
+
+Cada sujeto acudió con un amigo de su mismo sexo considerado cercano por él o ella, se les enfatizó que no tuvieran una relación romántica y/o familiar, para tratar de excluir el efecto en la cooperación por la relación consanguínea o por atracción sexual.
+En el laboratorio los sujetos y sus acompañantes firmaron un documento en el que consentían su participación, después eran entrenados en la tarea por dos de los investigadores, primero se les explicó verbalmente el juego, y posteriormente se les presentó la interfaz computarizada en un equipo portátil.
+
+Se les indicó que tomarían sus decisiones con cuatro botones del teclado de la computadora, los cuales correspondían con los niveles de promesas y con sólo dos de estos para tomar su decisión de pagar o no la mitad.
+Los amigos escucharon la explicación, se les indicó que ellos tomarían sus decisiones en una habitación aparte en otra computadora.
+Los sujetos realizaban entre 3 y 6 ensayos de práctica junto con el investigador los cuales ejemplificaban el curso del juego cuando el inversor daba su presupuesto.
+En los ensayos de práctica se mostraban todas las fases señaladas en la Figura 1, sin embargo, la identidad de los inversores estaba reemplazada por signos de interrogación.
+
+Cuando los sujetos no reportaban dudas procedíamos a llevarlos sin sus acompañantes a otra sala dónde tomarían sus decisiones en una computadora portátil, o bien, con el sistema de respuestas Lumina cedrus en el caso de que fuera un sujeto al que también realizamos MRI.
+Los sujetos iniciaban la tarea creyendo que jugarían realmente con los tres compañeros de diferente cercanía social.
+En la otra habitación o sala, otro de los investigadores realizaba el _debriefing_ al acompañante, se les comentaba que el propósito de la investigación era saber si su presencia tenía un efecto en las decisiones del sujeto, pero que para simplificar el análisis sus respuestas fueron programadas _a priori_ por lo que su participación concluía ahí.
+
+Cuando el sujeto concluía la tarea también se realizaba el _debriefing_, se le comentaba que las decisiones de sus compañeros habían sido programadas.
+Aunque ningún participante ejerció su derecho, se les indicó tanto a los sujetos como sus acompañantes que podrían retirar su participación y consentimiento informado si consideraban estar en desacuerdo por el _engaño_ cometido por el investigador.
+
 # Resultados
@@
 
-Se analizaron 756 decisiones sobre pagar o no la mitad (18 por sujeto), así como 168 
-promesas (4 por sujeto), 69.6% de las decisiones fueron pagar la mitad, mientras que la proporción de las promesas seleccionadas fueron 4.17%, 14.9% 41.1%, 37.5%, respectivamente para las promesas, nunca, algunas veces, casi siempre y siempre.
+Se analizaron 810 decisiones sobre pagar o no la mitad (18 por sujeto), así como 180 
+promesas (4 por sujeto), 69% de las decisiones fueron pagar la mitad, mientras que la proporción de las promesas seleccionadas fueron 5.4%, 16.2% 43.8%, 40.2%, respectivamente para las promesas _nunca_, _algunas veces_, _casi siempre_ y _siempre_.
 En la Figura 2 se muestra la proporción de pagos dependiendo de los niveles de promesas y los compañeros de juego.
-Romper promesas, es decir, que el sujeto haya prometido siempre y posteriormente decida no pagar la mitad ocurrió solamente el 11.1% de los ensayos, de los cuales, 7.63% fueron ensayos con la computadora, 3.47% con el desconocido y 0% con el amigo.
+Romper promesas, es decir, que el sujeto haya prometido siempre y posteriormente decida no pagar la mitad ocurrió solamente el 12.4% (19/153) de los ensayos, de los cuales, 8.50% (13/153) fueron ensayos con la computadora, 3.92%  (6/153) con el extraño y 0% (0/153) con el amigo.
 
@@
 La convergencia de los modelos fue evaluada a través de la inspección visual de las cadenas y el cálculo del estadístico $\hat{R}$, que para todos los parámetros fue de 1, lo que se interpreta como convergencia.
+Se utilizaron distribuciones iniciales vagamente informativas para los parámetros de interés en los modelos, lo que permite que los datos dominen la inferencia, asimismo asume lo menos posible respecto a la naturaleza del fenómeno, lo que podría ser adecuado para el estado de evidencia actual en el problema que estamos estudiando [@McElreath2018].
 
-### Efecto de la cercanía social en el engaño
+### Efecto de la cercanía social sobre romper las promesas
 
-Para evaluar la hipótesis de que la cercanía social reduciría el engaño, se filtraron todos los ensayos en los que los sujetos promieteron que _siempre_ pagarían y después decidieron no pagar.
-Posteriormente, se utilizó inferencia bayesiana para evaluar el efecto de los compañeros de juego en la decisión de romper la promesa a nivel individual y poblacional.
-Para tal propósito, se realizó un modelo bayesiano jerárquico que asume que la incertidumbre en la estimación del efecto de los compañeros sobre la decisión de romper la promesa varía dependiendo de cada individuo, sin embargo, también asume que dichas variaciones pertenecen a distribuciones poblacionales comunes para el efecto de cada compañero sobre la decisión [@Gelman2006].
+Para evaluar la hipótesis de que la cercanía social reduciría la conducta de romper la promesa, se filtraron todos los ensayos en los que los sujetos promieteron que _siempre_ pagarían y después decidieron no pagar.
+Posteriormente, se utilizó inferencia Bayesiana para evaluar el efecto de los compañeros de juego en la decisión de romper la promesa a nivel individual y poblacional.
+Para tal propósito, se realizó un modelo Bayesiano jerárquico que asume que la incertidumbre en la estimación del efecto de los compañeros sobre la decisión de romper la promesa varía dependiendo de cada individuo, sin embargo, también asume que dichas variaciones pertenecen a distribuciones poblacionales comunes de el efecto de cada compañero sobre la decisión [@Gelman2006].
 
@@
 En este modelo, $\beta$ y $u$ son coeficientes a nivel poblacional y nivel individual respectivamente, mientras que $\mathbf{X}$, $\mathbf{Z}$ son sus correpondientes matrices del diseño.
-En este caso, los coeficientes poblacionales corresponden con la presencia de los compañeros con cercanía social nula $\beta^{computer}$, baja $\beta^{confederate}$ y alta $\beta^{friend}$.
+En este caso, los coeficientes poblacionales corresponden con la presencia de los compañeros con cercanía social nula $\beta^{computer}$, baja $\beta^{stranger}$ y alta $\beta^{friend}$.
 
@@
 
-1. Hay mayor probabilidad de que se rompa la promesa a un compañero con cercanía nula (computadora) en comparación con los compañeros con cercanía social (desconocido y amigo).
+1. Hay mayor probabilidad de que se rompa la promesa a un compañero con cercanía nula (computadora) en comparación con el compañero de cercanía social baja (extraño).
 
-2. Hay mayor probabilidad de que se rompa la promesa a un compañero con cercanía social baja (desconocido) en comparación con el compañero de cercanía social alta (amigo).
+2. Hay mayor probabilidad de que se rompa la promesa a un compañero con cercanía social baja (extraño) en comparación con el compañero de cercanía social alta (amigo).
 
-La razón entre la probabilidad posterior de las hipótesis mencionadas y sus correspondientes hipótesis alternativas fue de 10.33 y 5.58 respectivamente para las hipótesis 1 y 2.
-Cabe mencionar que la hipótesis de que la cercanía social reduciría el engaño fue expresada _a priori_ como parte de un proyecto de investigación más amplio y se puede consultar aquí: https://osf.io/re7kp/.
+La razón entre la probabilidad posterior de las hipótesis mencionadas y sus correspondientes hipótesis alternativas fue de 7.47 y 8.64 respectivamente en favor de las hipótesis 1 y 2.
 
@@
 
-### Efectos de las promesas y la cercanía social en la decisión
+### Efectos de las promesas y la cercanía social en la cooperación
 
-Para evaluar el efecto de las condiciones experimentales en la decisión de pagar la mitad, se utilizaron todos los ensayos en los que los compañeros decidieron invertir.
-Nuevamente, se realizó un modelo bayesiano jerárquico, que asume que las promesas y los compañeros de juego tienen un efecto que varía para cada individuo, sin embargo, también asume que dichas variaciones pertenecen a distribuciones poblacionales comunes.
-El modelo estima que la probabilidad $\theta_i$ de que en cada ensayo se decida pagar la mitad está en función del efecto de la presencia de promesas $\beta^{promise}$, así como de los compañeros con cercanía social baja $\beta^{confederate}$ y alta $\beta^{friend}$.
+Para evaluar el efecto de las condiciones experimentales en la decisión de pagar la mitad, se utilizaron todos los ensayos en los que se programó que los compañeros invirtieran.
+Nuevamente, se realizó un modelo Bayesiano jerárquico, que asume que la fase de promesas y los compañeros de juego tienen un efecto que varía para cada individuo, sin embargo, también asume que dichas variaciones pertenecen a distribuciones poblacionales comunes.
+El modelo estima que la probabilidad $\theta_i$ de que en cada ensayo se decida pagar la mitad está en función del efecto de la presencia de promesas $\beta^{promise}$, así como de los compañeros con cercanía social baja $\beta^{stranger}$ y alta $\beta^{friend}$.
 
@@
 Como se puede observar, más del 95% de la densidad posterior de los coeficientes poblacionales está superior al 0, lo que indica fuerte evidencia del efecto de las condiciones experimentales en la decisión de pagar, de modo que la presencia de promesas y del confederado aumentan claramente la probabilidad de pagar, pero la presencia del amigo es la condición que más efecto tiene en esta conducta.
+Las distribuciones posteriores muestran claramente que la probabilidad de cooperación aumenta conforme lo hace también la cercanía social.
 
-Asimismo, la Figura 5 presenta la distribución posterior predictiva en contraste con la proporción de las decisiones a cada compañero, cada panel corresponde con uno de los primeros doce sujetos en la fase de promesas.
+Asimismo, la Figura 5 presenta la distribución posterior predictiva en contraste con la proporción de las decisiones a cada compañero durante la fase de promesas, cada panel corresponde con uno de los primeros doce sujetos.
 Las respuestas sobre la linea punteada indicarían que el sujeto pago la mitad de los ensayos en que ese compañero estuvo presente.
@@
 
-### Efectos de la cercanía social variantes por promesas
+### Efectos de la cercanía social en la cooperación variantes por promesas
 

### 2019-07-17 article_spanish.Rmd
Few changes in text

@@
 La distribución posterior predictiva simula observaciones del modelo y las compara con los datos reales, nos sirve para identificar si el modelo es suficientemente cercano al proceso que ha generado los datos [@Schad2019; @Lee2014].
-Se puede observar que existe gran correspondencia entre la respuesta de los sujetos y las predicciones del modelo, aún en los casos en los que el modelo se "equivoca" (por ejemplo el sujeto 1) la respuesta observada se sitúa en el margen de error de la predicción, lo que da credibilidad a las estimaciones.
+Se puede observar que existe gran correspondencia entre la respuesta de los sujetos y las predicciones del modelo, aún en los casos en los que el modelo se "equivoca" (por ejemplo el sujeto 1) la respuesta observada se sitúa en el rango de una desviación estándar de la predicción, lo que da credibilidad a las estimaciones.
 
@@
 En este modelo se asume que la cercanía social tiene un efecto que varía para cada nivel de promesa, lo que implica que hay niveles de promesa que son más sensibles que otros al efecto de los compañeros de juego sobre la decisión de pagar la mitad.
-Nuevamente se realizó un modelo bayesiano jerárquico para estimar el efecto de los compañeros de juego a nivel poblacional y las variaciones dependiendo de los niveles de promesa.
-La Tabla 1 resume las distribuciones posteriores de los coeficientes del modelo en escala logit, incluye los estimadores puntuales, sus errores estándar y los intervalos de credibilidad bayesianos del 95%.
+Nuevamente se realizó un modelo Bayesiano jerárquico para estimar el efecto de los compañeros de juego a nivel poblacional y las variaciones dependiendo de los niveles de promesa.
+La Tabla 1 resume las distribuciones posteriores de los coeficientes del modelo en escala logit, incluye los estimadores puntuales, sus errores estándar y los intervalos de credibilidad Bayesianos del 95%.
 Se puede observar una estimación similar a los modelos anteriores, con evidencia fuerte del efecto de la cercanía social sobre la decisión de pagar la mitad.
+Aunque el intervalo de credibilidad para el efecto del amigo incluye el 0, la razón de evidencia respecto a que dicho efecto es mayor que cero es de 15.81 con 94% de probabilidad posterior.
+
 Por otra parte, en la Figura 6 se muestra la distribución posterior predictiva, comparada con las tasas de pago de todos los individuos a los diferentes compañeros y su variación por el nivel de promesa.
@@
 De esta manera obtuvieron dos conjuntos de participantes que eran diferentes en sus tasas de pago, a pesar de que ambos hacían promesas muy altas, por tal motivo los autores denominaron al grupo que pagaba poco _deshonestos_ y al grupo que pagaba mucho _honestos_.
-En un ejercicio similar, en el presente estudio realizamos la técnica de agrupamiento jerárquico para obtener una solución de 2 grupos y encontramos dos conjuntos similares en $n$ que denominamos grupo "Low" y "High" (Low = 23, High = 19), con proporciones de pago bastante diferentes (Low = 58%, High = 84%), con una diferencia en un intervalo de confianza del 95% de 19% a 32% en favor del grupo High.
+En un ejercicio similar, en el presente estudio realizamos la técnica de agrupamiento jerárquico para obtener una solución de 2 grupos y encontramos dos conjuntos similares en $n$ que denominamos grupo "Low" y "High" (Low = 25, High = 20), con proporciones de pago bastante diferentes (Low = 58%, High = 83%), con una diferencia en un intervalo de confianza del 95% de 20% a 32% en favor del grupo High.
 
@@
 
-Con el objetivo de explorar si los grupos representan a poblaciones que no difieren en el nivel de compromiso expresado en las promesas, utilizamos un modelo bayesiano acumulativo, que asume que los niveles de promesas son una varable ordinal observada $Y$ que se origina de la categorización de una variable latente continua $\tilde{Y}$, para este caso, _el compromiso expresado de pagar la mitad_ [@Burkner2019].
+Con el objetivo de explorar si los grupos representan a poblaciones que no difieren en el nivel de compromiso expresado en las promesas, utilizamos un modelo Bayesiano acumulativo, que asume que los niveles de promesas son una varable ordinal observada $Y$ que se origina de la categorización de una variable latente continua $\tilde{Y}$, para este caso, _el compromiso expresado de pagar la mitad_ [@Burkner2019].
 El grado en que los sujetos del grupo High difieren del grupo Low, en desviaciones estándar normales ($z$-values), en la escala latente de $\tilde{Y}$, tiene un estimador puntual de 0.95, lo que implica que el grupo de High tiene 0.95 $z$-values mayor compromiso de pagar la mitad que el grupo Low.
 
-El intervalo de credibilidad bayesiano del 95% indica que el grupo High está entre 0.35 a 1.58 $z$-values de diferencia con respecto a Low.
+El intervalo de credibilidad bayesiano del 95% indica que el grupo High está entre 0.40 a 1.51 $z$-values de diferencia con respecto a Low.
 Por lo que podemos concluir con al menos 95% de probabilidad posterior que las personas que pertenecen al grupo High expresaron en sus promesas mayor compromiso de pagar la mitad de lo que hicieron los sujetos del grupo Low.

### 2019-07-17 article_spanish.Rmd
update

@@
 
-En la **fase de anticipación/asignación** se le indicó a los sujetos quién era su compañero de juego para ese ensayo (computadora, confederado o amigo) y se le dió el mensaje de que su compañero estaba tomando su decisión, posteriormente en la **fase de decisión** se le dió al participante la información sobre cuál había sido la decisión de su compañero (si invirtió sus 2 pesos o no), se le recordaba su nivel de promesas (si se trataba de ensayos con promesas) y, en el caso de que su compañero hubiera invertido, se le pedía que decidiera si pagaba de regreso o no.
+En la **fase de anticipación/asignación** se le indicó a los sujetos quién era su compañero de juego para ese ensayo (computadora, extraño o amigo) y se le dió el mensaje de que su compañero estaba tomando su decisión, posteriormente en la **fase de decisión** se le dió al participante la información sobre cuál había sido la decisión de su compañero (si invirtió sus 2 pesos o no), se le recordaba su nivel de promesas (si se trataba de ensayos con promesas) y, en el caso de que su compañero hubiera invertido, se le pedía que decidiera si pagaba de regreso o no.
 Finalmente, en la **fase de feedback** se mostraban los pagos para ese ensayo y se repetía la secuencia.
@@
 Cuando el sujeto concluía la tarea también se realizaba el _debriefing_, se le comentaba que las decisiones de sus compañeros habían sido programadas.
-Aunque ningún participante ejerció su derecho, se les indicó tanto a los sujetos como sus acompañantes que podrían retirar su participación y consentimiento informado si consideraban estar en desacuerdo por el _engaño_ cometido por el investigador.
+Aunque ningún participante ejerció su derecho, se les indicó tanto a los sujetos como sus acompañantes que podrían retirar su participación y consentimiento informado si consideraban estar en desacuerdo por el alguna de las manipulaciones realizadas por los investigadores.
 
@@
 En la Figura 2 se muestra la proporción de pagos dependiendo de los niveles de promesas y los compañeros de juego.
-Romper promesas, es decir, que el sujeto haya prometido siempre y posteriormente decida no pagar la mitad ocurrió solamente el 12.4% (19/153) de los ensayos, de los cuales, 8.50% (13/153) fueron ensayos con la computadora, 3.92%  (6/153) con el extraño y 0% (0/153) con el amigo.
+Romper promesas, es decir, que el sujeto haya prometido _siempre_ y posteriormente decida no pagar la mitad ocurrió solamente el 12.4% de ensayos (19 veces no pagaron la mitad de 153 que prometieron _siempre_), de los cuales, 8.50% (13/153) fueron ensayos con la computadora, 3.92%  (6/153) con el extraño y 0% (0/153) con el amigo.
 
@@
 Posteriormente, se utilizó inferencia Bayesiana para evaluar el efecto de los compañeros de juego en la decisión de romper la promesa a nivel individual y poblacional.
-Para tal propósito, se realizó un modelo Bayesiano jerárquico que asume que la incertidumbre en la estimación del efecto de los compañeros sobre la decisión de romper la promesa varía dependiendo de cada individuo, sin embargo, también asume que dichas variaciones pertenecen a distribuciones poblacionales comunes de el efecto de cada compañero sobre la decisión [@Gelman2006].
+Para tal propósito, se realizó un modelo Bayesiano jerárquico que asume que la incertidumbre en la estimación del efecto de los compañeros sobre la decisión de romper la promesa varía dependiendo de cada individuo, sin embargo, también asume que dichas variaciones pertenecen a distribuciones poblacionales comunes [@Gelman2006].
 
@@
 
-En el modelo anterior, la decisión de romper la promesa $y_i$ proviene de una distribución Bernoulli con probabilidad de pagar $\theta_i$, el objetivo del modelo jerárquico es predecir cada decisión a través de la combinación lineal de los efectos de cada compañero de juego, transformados por su función ligadora inversa $\mathrm{logit}$ [@Burkner2017].
+En el modelo anterior, la decisión de romper la promesa $y_i$ proviene de una distribución Bernoulli con probabilidad $\theta_i$, el objetivo del modelo jerárquico es predecir cada decisión a través de la combinación lineal de los efectos de cada compañero de juego, transformados por su función ligadora inversa $\mathrm{logit}$ [@Burkner2017].
 En este modelo, $\beta$ y $u$ son coeficientes a nivel poblacional y nivel individual respectivamente, mientras que $\mathbf{X}$, $\mathbf{Z}$ son sus correpondientes matrices del diseño.
@@
 
-1. Hay mayor probabilidad de que se rompa la promesa a un compañero con cercanía nula (computadora) en comparación con el compañero de cercanía social baja (extraño).
+- Hay mayor probabilidad de que se rompa la promesa a un compañero con cercanía nula (computadora) en comparación con el compañero de cercanía social baja (extraño).
 
-2. Hay mayor probabilidad de que se rompa la promesa a un compañero con cercanía social baja (extraño) en comparación con el compañero de cercanía social alta (amigo).
+- Hay mayor probabilidad de que se rompa la promesa a un compañero con cercanía social baja (extraño) en comparación con el compañero de cercanía social alta (amigo).
 
-La razón entre la probabilidad posterior de las hipótesis mencionadas y sus correspondientes hipótesis alternativas fue de 7.47 y 8.64 respectivamente en favor de las hipótesis 1 y 2.
+La razón entre la probabilidad posterior de las hipótesis mencionadas y sus correspondientes hipótesis alternativas fue de 7.47 y 8.64 respectivamente en favor de las hipótesis anteriores.
 
@@
 En la Figura 4 se presentan las distribuciones posteriores de los coeficientes $\beta$ en escala logit, la linea central representa la mediana de la distribución y el área sombreada corresponde con el intervalo de 50% de probabilidad posterior.
-Como se puede observar, más del 95% de la densidad posterior de los coeficientes poblacionales está superior al 0, lo que indica fuerte evidencia del efecto de las condiciones experimentales en la decisión de pagar, de modo que la presencia de promesas y del confederado aumentan claramente la probabilidad de pagar, pero la presencia del amigo es la condición que más efecto tiene en esta conducta.
+Como se puede observar, más del 95% de la densidad posterior de los coeficientes poblacionales está superior al 0, lo que indica fuerte evidencia del efecto de las condiciones experimentales en la decisión de pagar, de modo que la presencia de promesas y del extraño aumentan claramente la probabilidad de pagar, pero la presencia del amigo es la condición que más efecto tiene en esta conducta.
 Las distribuciones posteriores muestran claramente que la probabilidad de cooperación aumenta conforme lo hace también la cercanía social.
@@
 Por otra parte, en la Figura 6 se muestra la distribución posterior predictiva, comparada con las tasas de pago de todos los individuos a los diferentes compañeros y su variación por el nivel de promesa.
-A excepción de con la promesa _never_, se observa un efecto positivo monotónico de los compañeros de juego en todos los niveles de promesa, sin embargo se puede observar cómo el efecto de la cercanía social varía dependiendo de la fuerza de la promesa.
+A excepción de con la promesa _never_, se observa un efecto positivo monotónico de los compañeros de juego en todos los niveles de promesa, sin embargo se puede observar cómo el efecto de la cercanía social varía dependiendo de la fuerza de la promesa, principalmente para las decisiones hacia la computadora.
 
@@
 Según nuestros datos, no podríamos justificar la clasificación de nuestros grupos de acuerdo con su honestidad o deshonestidad, al menos no con la técnica empleada en Baumgartner (2009).
-Ya que las personas fueron bastante consistentes con cumplir lo que prometían pagar.
+Ya que las personas fueron bastante consistentes con cumplir lo que prometieron pagar.
 

### 2019-07-18 article_spanish.Rmd
Discussion

@@
 
+El objetivo del presente estudio fue evaluar el efecto de la cercanía social en la decisión de romper promesas.
+Nuestros resultados dan evidencia de que la cercanía social nula incrementa la probabilidad de romper la promesa y que ésta va disminuyendo monotónicamente conforme la cercanía social va aumentando hasta llegar a ser prácticamente cero.
+A nuestro conocimiento, se trata del primer estudio experimental que incorpora la cercanía social como predictor de la decisión de romper promesas con compañeros socialmente relevantes.
+Por ejemplo, en el estudio de Croson (1996) se evaluó la contribución en un juego de bienes públicos cuando un grupo de sujetos jugaban con los mismos individuos (_partners_) durante varios ensayos, en comparación con otro grupo que incluía sujetos diferentes durante cada ensayo (_strangers_) [@Croson1996].
+El estudio mencionado no da detalles respecto al reclutamiento de los participantes, por lo que podríamos asumir que aún en la condición de _partners_ se trata de individuos que no se conocen entre sí.
+
+En otro experimento se reporta un incremento de la cooperación en un juego de confianza en parejas cuando los individuos son cercanos socialmente [@Glaeser2000], en dicho estudio los sujetos se conocen entre sí y los investigadores midieron cuidadosamente varias variables respecto a su conexión social, sin embargo se permitió que algunos individuos que llegaban juntos realizaran la tarea entre ellos y otros fueron emparejados con un criterio poco claro.
+Lo anterior permite que la cercanía social entre las parejas sea heterogénea, permite que haya relaciones de tipo romántico y asume que dos individuos que llegan juntos se consideran cercanos entre sí.
+También, por tratarse de estudio de _one shot_, excluye la posibilidad de evaluar cómo un mismo sujeto varía su comportamiento en función de diferentes niveles de cercanía social.
+
 # Referencias

### 2019-07-18 article_spanish.Rmd
Discussion

@@
 El objetivo del presente estudio fue evaluar el efecto de la cercanía social en la decisión de romper promesas.
-Nuestros resultados dan evidencia de que la cercanía social nula incrementa la probabilidad de romper la promesa y que ésta va disminuyendo monotónicamente conforme la cercanía social va aumentando hasta llegar a ser prácticamente cero.
+Nuestros resultados dan evidencia de que la cercanía social nula incrementa la probabilidad de romper la promesa y que ésta va disminuyendo monotónicamente conforme la cercanía social va aumentando.
 A nuestro conocimiento, se trata del primer estudio experimental que incorpora la cercanía social como predictor de la decisión de romper promesas con compañeros socialmente relevantes.
-Por ejemplo, en el estudio de Croson (1996) se evaluó la contribución en un juego de bienes públicos cuando un grupo de sujetos jugaban con los mismos individuos (_partners_) durante varios ensayos, en comparación con otro grupo que incluía sujetos diferentes durante cada ensayo (_strangers_) [@Croson1996].
-El estudio mencionado no da detalles respecto al reclutamiento de los participantes, por lo que podríamos asumir que aún en la condición de _partners_ se trata de individuos que no se conocen entre sí.
+Por ejemplo, en un estudio se evaluó la contribución en un juego de bienes públicos durante varios ensayos en un grupo conformado por los mismos individuos (_partners_), en comparación con otro grupo de sujetos diferentes para cada ensayo (_strangers_) [@Croson1996].
+El estudio mencionado no da detalles respecto al reclutamiento de los participantes, por lo que podríamos asumir que aún en la condición de _partners_ se trata de individuos que no se conocen entre sí y no se consideran cercanos.
 
@@
 Lo anterior permite que la cercanía social entre las parejas sea heterogénea, permite que haya relaciones de tipo romántico y asume que dos individuos que llegan juntos se consideran cercanos entre sí.
-También, por tratarse de estudio de _one shot_, excluye la posibilidad de evaluar cómo un mismo sujeto varía su comportamiento en función de diferentes niveles de cercanía social.
+También, por tratarse de un estudio de _one shot_, excluye la posibilidad de evaluar cómo un mismo sujeto varía su comportamiento en función de diferentes niveles de cercanía social.
 

### 2019-07-19 article_spanish.Rmd
Discussion

--- 2019-07-17 article_spanish.Rmd
@@
 Romper promesas, es decir, que el sujeto haya prometido _siempre_ y posteriormente decida no pagar la mitad ocurrió solamente el 12.4% de ensayos (19 veces no pagaron la mitad de 153 que prometieron _siempre_), de los cuales, 8.50% (13/153) fueron ensayos con la computadora, 3.92%  (6/153) con el extraño y 0% (0/153) con el amigo.
+Es fundamental notar que romper la promesa no fue la decisión más frecuente, ya que aún cuando se trataba de la computadora, el 91.5% de los ensayos en que los sujetos prometieron _siempre_ y tuvieron este compañero, decidieron pagar la mitad.
 
@@
 La razón entre la probabilidad posterior de las hipótesis mencionadas y sus correspondientes hipótesis alternativas fue de 7.47 y 8.64 respectivamente en favor de las hipótesis anteriores.
+Como se observa en la Figura 5 en la estimación para $\beta^{computer}$, cuando no hay cercanía social tenemos el 95% de probabilidad posterior de que la proporción de rompimiento de promesas poblacional esté entre 4-38%, que si bien es una proporción pequeña, claramente excluye la probabilidad de que no se rompan promesas.
 
@@
 
+El objetivo del presente estudio fue evaluar el efecto de la cercanía social en el cumplimiento y rompimiento de promesas, así como en la cooperación en un juego de confianza.
+Nuestros resultados dan evidencia de que la cercanía social nula incrementa la probabilidad de romper la promesa y que ésta va disminuyendo monotónicamente conforme la cercanía social va aumentando.
+Asimismo, a medida que la cercanía social se incrementa, también lo hace la cooperación; la cercanía social _alta_ tiene un efecto en las decisiones que supera inclusive al que tienen todas las demás condiciones experimentales.
+Probablemente, el hallazgo más interesante fue que cuando los sujetos expresan alto compromiso de cooperar -a través de prometer que _siempre_ pagaran la mitad-, la probabilidad de que cumplan es también bastante alta, sin embargo, sí existe una proporción de transgresiones que según nuestras inferencias está entre 4 - 38% con el 95% de certeza.
+
+A nuestro conocimiento, se trata del primer estudio experimental que incorpora la cercanía social como predictor de la decisión de romper las promesas con compañeros socialmente relevantes.
+En los estudios anteriores los participantes permanecen anónimos durante el curso de las tareas [@Baumgartner2009], las mediciones para evaluar transgresiones son de autorreporte [@DePaulo1998; @DePaulo2004], no cuantifican directamente el rompimiento de las promesas [@Vanberg2008; @Charness2006], o  como discutiremos más adelante, sus medidas de cercanía social pueden ser heterogéneas [@Glaeser2000].
+
+Nuestro experimento es probablemente el primero en incluir un compañero sin cercanía social (_computadora_), nuestros datos dan evidencia de que el mero hecho de considerar que se juega con un humano disminuye la probabilidad de romper la promesa.
+Es aproximadamente 7.5 veces más probable romper la promesa a la computadora que al extraño, a pesar de que no se conoció a dicho compañero.
+En nuestro estudio, la cercanía social nula es importante porque permite explorar la motivación _intrínseca_ para cumplir las promesas, si los humanos mantienen su palabra porque es lo moralmente correcto, anticiparíamos que la probabilidad de romper la promesa fuera muy baja en los tres compañeros y, particularmente, que la inferencia respecto a la probabilidad de romper la promesa a la computadora incluyera el cero.
+
+La probabilidad de romper la promesa sin cercanía social, aunque es baja, es claramente mayor que cero, lo que proporciona evidencia que contradice -al menos en grado- la hipótesis de la motivación _intrínseca_.
+No podemos excluir la posibilidad que los sujetos cumplan las promesas principalmente motivados moralmente, porque aún tratándose de la computadora los sujetos cumplen en gran proporción, pero sí podemos excluir la posibilidad de que esa sea su única motivación.
+
+Por otra parte, la cercanía social alta nos permite explorar la motivación _instrumental_ para cumplir promesas.
+En nuestro estudio, es casi 9 veces más probable romper la promesa al extraño que al amigo; si los seres humanos mantienen su palabra para facilitar la cooperación en el futuro, anticiparíamos que ante un compañero de cercanía social alta -con el que tienen mucha posibilidad de cooperar, inclusive posterior al experimento- hubiera menos probabilidad de romper la promesa.
+De hecho, en nuestro estudio no se rompió la promesa a los amigos en ninguna ocasión, por lo que la inferencia en este caso resulta obvia.
+
+Nuestros hallazgos podrían explicarse por la norma social denominada _cooperación condicional_, que indica que la creencia de que otras personas cooperan en altos niveles induce también altos niveles de cooperación [@Fehr2018].
+Así, la falta de certeza respecto a las decisiones que tomaría la computadora, podría explicar la probabilidad de romper la promesa que existe hacia este compañero.
+De forma similar, la información con la que los sujetos cuentan respecto al comportamiento del amigo -inclusive antes del experimento-, puede explicar los altos niveles de cooperación y cumplimiento de promesas hacia este compañero.
+
+Respecto a la cooperación, no es la primera investigación en que se evalúa el efecto de la cercanía social, sin embargo, la naturaleza de la manipulación experimental ha sido diversa.
+Por ejemplo, en un estudio se evaluó la contribución en un juego de bienes públicos durante varios ensayos en un grupo conformado por los mismos individuos (_partners_), en comparación con otro grupo de sujetos diferentes para cada ensayo (_strangers_) [@Croson1996].
+Se suponía que en la condición de _partners_ la cooperación sería mayor por tratarse de un grupo estable en comparación con el grupo de _strangers_.
+El estudio mencionado no da detalles respecto al reclutamiento de los participantes, por lo que podríamos asumir que aún en la condición de _partners_ se trata de individuos que no se consideran cercanos socialmente.
+
+En otro experimento se reportó un incremento de la cooperación en un juego de confianza en parejas cuando los individuos son cercanos socialmente [@Glaeser2000], en dicho estudio los sujetos se conocen entre sí y los investigadores midieron cuidadosamente varias variables respecto a su conexión social, sin embargo se permitió que algunos individuos que llegaban juntos realizaran la tarea entre ellos y otros fueron emparejados con un criterio poco claro.
+Lo anterior permite que la cercanía social entre las parejas sea heterogénea, permite que haya relaciones de tipo romántico y asume que dos individuos que llegan juntos a clase se consideran cercanos entre sí.
+También, por tratarse de un estudio de _one-shot_, excluye la posibilidad de evaluar cómo un mismo sujeto varía su comportamiento en función de diferentes niveles de cercanía social.
+
+Para tratar de homogeneizar la cercanía social entre nuestros sujetos y sus acompañantes, los participantes realizaron la tarea con un amigo del mismo sexo considerado cercano por ellos mismos, en ningún caso se trató de un familiar y, aunque comprendemos que puede haber parejas del mismo sexo y que los sujetos pudieron haber ocultado su relación, se les enfatizó que para formar parte del estudio su acompañante no podría ser su pareja romántica y/o sexual.
+Si bien los resultados de los dos estudios mencionados están prácticamente en la misma dirección que los hallazgos de nuestro experimento, establecer la similitud en las magnitudes de los efectos no es posible por la diferencia en los diseños, las tareas evaluadas y los procedimientos estadísticos empleados.
+
 # Referencias

### 2019-07-22 article_spanish.Rmd
Updating discussion

@@
 
-En nuestro estudio, los sujetos realizan un juego de cooperación estándar en parejas con tres fases: _primero_, el fideicomisario realiza una promesa sobre pagar la mitad de sus ganancias independientemente de quién sea su inversor; _segundo_, el inversor recibe la promesa y decide si invierte su presupuesto inicial; _tercero_, en caso de que el inversor haya dado el presupuesto, el fideicomisario se enfrenta a la decisión de pagar o no la mitad de sus ganancias.
+En nuestro estudio, los sujetos realizan un juego de confianza estándar en parejas con tres fases: _primero_, el fideicomisario realiza una promesa sobre pagar la mitad de sus ganancias independientemente de quién sea su inversor; _segundo_, el inversor recibe la promesa y decide si invierte su presupuesto inicial; _tercero_, en caso de que el inversor haya dado el presupuesto, el fideicomisario se enfrenta a la decisión de pagar o no la mitad de sus ganancias.
 Con el propósito de evaluar el efecto de la cercanía social, nuestros sujetos participan en el papel de fideicomisario frente a tres compañeros con diferentes niveles de cercanía social (nula, baja y alta) en el rol del inversor: una _computadora_, un _extraño_ y un _amigo_.
@@
 Para tratar de homogeneizar la cercanía social entre nuestros sujetos y sus acompañantes, los participantes realizaron la tarea con un amigo del mismo sexo considerado cercano por ellos mismos, en ningún caso se trató de un familiar y, aunque comprendemos que puede haber parejas del mismo sexo y que los sujetos pudieron haber ocultado su relación, se les enfatizó que para formar parte del estudio su acompañante no podría ser su pareja romántica y/o sexual.
-Si bien los resultados de los dos estudios mencionados están prácticamente en la misma dirección que los hallazgos de nuestro experimento, establecer la similitud en las magnitudes de los efectos no es posible por la diferencia en los diseños, las tareas evaluadas y los procedimientos estadísticos empleados.
+Si bien los resultados de los dos estudios mencionados están prácticamente en la misma dirección que los hallazgos de nuestro experimento, establecer la similitud en las magnitudes de los efectos no es posible por la diferencia en los diseños, las tareas realizadas y los procedimientos estadísticos empleados.
+
+Otro aporte metodológico de nuestro estudio, es que se trata probablemente del primero en utilizar herramientas de inferencia Bayesiana: *modelos jerárquicos* y *modelos acumulativos*.
+Los *modelos jerárquicos* (o multinivel), nos permitieron modelar el efecto de las condiciones experimentales en la respuesta individual, estos modelos asumen que las observaciones de nivel inferior (e.g.
+las decisiones de cada individuo), están anidadas en unidades de nivel superior (e.g.
+los sujetos individuales), los diseños intrasujetos tradicionalmente se han analizado con AN(C)OVA de medidas repetidas, sin embargo, los *modelos jerárquicos* conceden las ventajas de lidiar naturalmente con datos desbalanceados, incluir predictores de naturaleza categórica y/o numérica, incorporar de manera explícita la variabilidad individual, entre otras [@Vuorre2018; @Gelman2006; @McElreath2018; @Burkner2017].
+
+En nuestro caso, como se mostró en la Figura 5, el *modelo jerárquico* nos permitió captar de manera muy precisa cómo afectaron las condiciones experimentales las decisiones de cada sujeto y las diferencias entre ellos.
+Por ejemplo, hay sujetos evidentemente _instrumentales_ como el número 8 o 12 que son muy sensibles a la identidad de sus inversores y modifican su cooperación en virtud de la cercanía social.
+Al mismo tiempo existen sujetos notablemente _intrínsecos_ como el 9 y el 10 que todo el tiempo cooperan independientemente de quiénes sean sus compañeros.
+El *modelo jerárquico* incorpora naturalmente esta información para la estimación de los efectos poblacionales, que de no considerarse daría lugar a imprecisiones en la inferencia.
 

### 2019-07-23 article_spanish.Rmd
Discussion

@@
 
-Otro aporte metodológico de nuestro estudio, es que se trata probablemente del primero en utilizar herramientas de inferencia Bayesiana: *modelos jerárquicos* y *modelos acumulativos*.
+Un aporte metodológico de nuestro estudio es que, en la literatura de promesas, se trata del primero en utilizar herramientas de inferencia Bayesiana: *modelos jerárquicos* y *modelos acumulativos*.
 Los *modelos jerárquicos* (o multinivel), nos permitieron modelar el efecto de las condiciones experimentales en la respuesta individual, estos modelos asumen que las observaciones de nivel inferior (e.g.
@@
 Al mismo tiempo existen sujetos notablemente _intrínsecos_ como el 9 y el 10 que todo el tiempo cooperan independientemente de quiénes sean sus compañeros.
-El *modelo jerárquico* incorpora naturalmente esta información para la estimación de los efectos poblacionales, que de no considerarse daría lugar a imprecisiones en la inferencia.
+El *modelo jerárquico* incluye naturalmente esta información para la estimación de los efectos poblacionales, que de no considerarse daría lugar a imprecisiones en la inferencia.
+
+Por otra parte, los *modelos acumulativos* nos permitieron modelar la fuerza del compromiso expresado a través de las promesas.
+Un problema muy frecuente que se ha señalado recientemente, es que analizar datos ordinales con métodos que asumen que las observaciones son _métricas_ puede llevar a graves errores de inferencia [@Liddell2018].
+Los *modelos acumulativos* asumen que las respuestas observadas provienen de la categorización de una variable latente continua [@Burkner2019], por lo que en nuestro estudio pudimos identificar que los grupos con distintas tasas de pago, que en otros artículos se han llamado de _deshonestos_ y _honestos_, difieren en el compromiso que expresan a través de sus promesas.
+Considerando que las herramientas para realizar los modelos acumulativos son relativamente recientes, sería valioso realizar la replicación de estudios publicados [por ejemplo, @Baumgartner2009; @Baumgartner2013] considerando las nuevas alternativas de inferencia.
+
+Aunque los *modelos jerárquicos* y *acumulativos* no son herramientas exclusivamente de la inferencia Bayesiana...
 

### 2019-07-24 article_spanish.Rmd
Update discussion

@@
 
-Aunque los *modelos jerárquicos* y *acumulativos* no son herramientas exclusivamente de la inferencia Bayesiana...
+Aunque los *modelos jerárquicos* y *acumulativos* no son herramientas exclusivamente de la inferencia Bayesiana, su aplicación desde dicha aproximación representa varias ventajas en comparación con la aproximación frecuentista.
+Problemas clásicos de la anterior como son: las múltiples comparaciones, la decisión de cúando detenerse en la recolección de sujetos (stopping rule), o el uso de comparaciones planeadas versus _post hoc_, no son factores que afecten el apoyo que brindan los datos a las hipótesis desde la aproximación Bayesiana [@Dienes2011].
+Cómo las inferencias y el contraste de hipótesis desde la aproximación que utilizamos, hacen uso de la probabilidad para expresar la plausibilidad de las teorías, en nuestro caso pudimos obtener razones de evidencia respecto a la medida en que nuestros datos apoyan nuestras hipótesis, independientemente de si se éstas fueron propuestas _a priori_ o _post hoc_.
 

### 2019-07-24 article_spanish.Rmd
Limitations

@@
 
+Una limitación del presente trabajo es el uso de recompensas hipóteticas en comparación con recompensas reales.
+Un estudio relativamente reciente sobre toma de decisiones, reportó que existe más aversión a la pérdida cuando los sujetos tienen recomensas monetarias reales en comparación con recompensas hipotéticas en una tarea de riesgo [@Xu2016].
+Sin embargo, existen otros trabajos que no reportan diferencias entre el uso de ambos tipos de recompensas en tareas de autocontrol, descuento temporal y descuento social [@Locey2011; @Johnson2006; @Rachlin2006].
+Asimismo, se puede argumentar que los resultados tienen congruencia teórica [@Fehr2018] y están en la misma dirección que otros trabajos que utilizan dinero real [@Croson1996; @Glaeser2000], por lo que no hay muchas razones para esperar que otro tipo de recompensas hubieran modificado nuestros resultados.
+
 # Referencias

### 2019-07-24 article_spanish.Rmd
Discussion

@@
 
+Otra posible limitación es el uso de ensayos múltiples con cada compañero de juego.
+Aunque la decisión de utilizar medidas repetidas durante nuestro diseño atiende más al propósito de reducir fuentes de error extrañas e incrementar la validez interna [@Maxwell2018], para tener más claridad respecto a la diferencia en las motivaciones _intrínseca_ e _instrumental_, los estudios podrían beneficiarse de sólo incluir un ensayo para cada compañero.
+Jugar un _one-shot_ con cada compañero
+evita la posibilidad de que los múltiples ensayos pudieran generar la creencia de que la computadora también puede variar su comportamiento de acuerdo las decisiones del _fideicomisario_.
+
+# Conclusiones
+
 # Referencias

### 2019-07-25 article_spanish.Rmd
New paragraph.

@@
 
+En resumen, los sujetos cumplen sus promesas por una mezcla entre la motivación _intrínseca_ e _instrumental_.
+Son predominantemente _nice guys_ porque mantienen su palabra inclusive ante inversores con nula cercanía social.
+Sin embargo, su integridad dista de ser perfecta, ya que existe una proporción pequeña, pero confiablemente mayor que cero, de traiciones cometidas hacia este socio.
+Tal parece ser, que si los sujetos no pueden asegurar que su inversor será un _potential cooperator_, la deshonestidad puede emerger en la forma de promesas rotas.
+
 # Referencias

### 2019-07-26 article_spanish.Rmd
Finished

@@
 ---
-title: "Nice guys or potential cooperators: an experimental and Bayesian account for two explanations"
+title: "Nice guys or potential cooperators when keeping promises: an experimental and Bayesian account for two explanations"
 author: "Said E. Jiménez"
@@
 
-Todos los sujetos realizaron una adaptación de la tarea de confianza y promesas presentada por Baumgartner (2009).
-La tarea se programó en PsychoPy2 versión 1.84.2 [@Peirce2019; @Peirce2008] y consiste en 24 ensayos entre dos jugadores: fideicomisario e inversor.
+Todos los sujetos realizaron una adaptación del juego de confianza y promesas con recompensas monetarias hipotéticas [@Baumgartner2009].
+La tarea se programó en PsychoPy2 versión 1.84.2 [@Peirce2019; @Peirce2008] y consistió en 24 ensayos entre dos jugadores: fideicomisario e inversor.
 El fideicomisario tiene originalmente 0 pesos mexicanos y el inversor tiene 2 pesos, al inversor se le presenta la oportunidad de dar su dinero al fideicomisario o conservarlo, si invierte su dinero se multiplica por 5 pesos, de modo que el fideicomisario tenga 10 pesos.
@@
 
-En resumen, los sujetos cumplen sus promesas por una mezcla entre la motivación _intrínseca_ e _instrumental_.
+Los sujetos cumplen sus promesas por una combinación de motivaciones entre la  _intrínseca_ y la _instrumental_.
 Son predominantemente _nice guys_ porque mantienen su palabra inclusive ante inversores con nula cercanía social.
@@
 Tal parece ser, que si los sujetos no pueden asegurar que su inversor será un _potential cooperator_, la deshonestidad puede emerger en la forma de promesas rotas.
+Las predicciones teóricas de la norma social _cooperación condicional_ enmarcan el hallazgo de que la cercanía social disminuya la probabilidad de romper la promesa y aumente la cooperación.
+De la misma forma que sugiere la correspondencia entre el compromiso expresado a través de las promesas y la conducta posterior.
 

### 2019-07-28 article_spanish.Rmd
IOS scale

@@
 Cada sujeto acudió con un amigo de su mismo sexo considerado cercano por él o ella, se les enfatizó que no tuvieran una relación romántica y/o familiar, para tratar de excluir el efecto en la cooperación por la relación consanguínea o por atracción sexual.
-En el laboratorio los sujetos y sus acompañantes firmaron un documento en el que consentían su participación, después eran entrenados en la tarea por dos de los investigadores, primero se les explicó verbalmente el juego, y posteriormente se les presentó la interfaz computarizada en un equipo portátil.
+Asimismo, para garantizar que los sujetos y sus acompañantes experimentaban un grado de cercanía social similar entre ellos, en el laboratorio ambos respondieron la escala de inclusión en el otro IOS [@Aron1997] sin que su compañero observara sus respuestas.
+La escala consiste en siete pares de circulos que varían en el grado de traslape entre ellos, el respondiente debe seleccionar el par de circulos que mejor representa la cercanía subjetiva respecto a su compañero.
 
+Los sujetos eran entrenados en la tarea por dos de los investigadores, primero se les explicó verbalmente el juego, y posteriormente se les presentó la interfaz computarizada en un equipo portátil.
 Se les indicó que tomarían sus decisiones con cuatro botones del teclado de la computadora, los cuales correspondían con los niveles de promesas y con sólo dos de estos para tomar su decisión de pagar o no la mitad.
@@
 Se utilizaron distribuciones iniciales vagamente informativas para los parámetros de interés en los modelos, lo que permite que los datos dominen la inferencia, asimismo asume lo menos posible respecto a la naturaleza del fenómeno, lo que podría ser adecuado para el estado de evidencia actual en el problema que estamos estudiando [@McElreath2018].
+
+### Cercanía social entre parejas
+
+Para evaluar la cercanía social, 30 (15 hombres) de nuestros sujetos y sus amigos respondieron la escala de inclusión en el otro IOS [@Aron1997; @Fareri2014; @Sip2015], que consisten en siete pares de circulos que varían en el grado de traslape y representan la cercanía social que percibe un individuo con respecto al otro.
+Un modelo Bayesiano jerárquico y acumulativo (Ver sección: Compromiso expresado en las promesas), apoya la hipótesis de que no existen diferencias entre la cercanía social subjetiva entre los sujetos y sus amigos, con una razón de evidencia posterior de 2.74 a su favor.
 
@@
 Para tratar de homogeneizar la cercanía social entre nuestros sujetos y sus acompañantes, los participantes realizaron la tarea con un amigo del mismo sexo considerado cercano por ellos mismos, en ningún caso se trató de un familiar y, aunque comprendemos que puede haber parejas del mismo sexo y que los sujetos pudieron haber ocultado su relación, se les enfatizó que para formar parte del estudio su acompañante no podría ser su pareja romántica y/o sexual.
+Además, el análisis Bayesiano de la escala IOS, mostró evidencia en favor de que el grado de cercanía social entre 30 de nuestros sujetos y sus amigos fue prácticamente el mismo.
 Si bien los resultados de los dos estudios mencionados están prácticamente en la misma dirección que los hallazgos de nuestro experimento, establecer la similitud en las magnitudes de los efectos no es posible por la diferencia en los diseños, las tareas realizadas y los procedimientos estadísticos empleados.

### 2019-07-28 ios_scale.R

@@ -1,0 +1,29 @@
+
+# IOS scale ---------------------------------------------------------------
+
+pacman::p_load(brms, tidyverse, readxl)
+
+
+# Data --------------------------------------------------------------------
+
+load("~/Google Drive/PromesaConducta_8to2/data/promesas_analisis/Analisis-Comportamiento/promesas_analisis/ios_modeling.RData")
+
+
+# Modeling ----------------------------------------------------------------
+
+fit <- brm(
+  response ~ partner + participant + (partner | id),
+  data = data,
+  family = cumulative("logit"),
+  prior = set_prior("normal(0, 1)"),
+  sample_prior = "yes",
+  cores = 4,
+  chains = 4,
+  control = list(adapt_delta = 0.9)
+)
+
+
+# Checking ----------------------------------------------------------------
+
+marginal_effects(fit, effects =  "participant", categorical = T)
+hypothesis(fit, "participantfriend = 0")

### 2019-07-28 article_english.Rmd
English manuscript

---
title: "Nice guys or potential cooperators when keeping promises: an experimental and Bayesian account for two explanations"
author: "Said Jiménez"
date: "July 2019"
output: 
  pdf_document:
    number_sections: true
fontsize: 12pt
bibliography: promises.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, fig.align='center', dev='png', dpi=400, out.width='80%')
load("~/Google Drive/PromesaConducta_8to2/data/promesas_analisis/Analisis-Comportamiento/promesas_analisis/data.RData")
pacman::p_load(tidyverse, kableExtra)

```

# Introduction

Human beings are social animals and we get advantages from being so. Historically, belonging to a social group has provided protection and guaranteed access to resources such as food, currently there has been evidence that belonging to a social circle has a positive effect on longevity, physical and mental health [@Tough2017; @Holt-Lunstad2018]. The interrelation between social closeness and cooperation is key to the formation of large groups of individuals without a genetic relationship, such groups form the basis of communities, societies, and nations, as well as probably constitute one of the most fundamental conditions for human survival [@Fehr2003; @Fehr2018].

An important requirement for cooperation between individuals is communication, a meta-analysis of 45 studies reported a large positive effect ($d =  1.01$) of communication in cooperation regardless of the communication medium [@Balliet2010]. In parallel, it is known that after communication sessions between completely unknown individuals there is an increase in subjective social closeness [@Aron1997]. Thus, the findings suggest a positive relationship between communication, cooperation, and social closeness.

One of the forms of communication that have received the most attention in psychological game theory is the promises, in an interaction between the sender and the recipient, it is believed that promises influence beliefs of the recipient, generating trust and cooperation [@Charness2006; @Vanberg2008]. However, there are situations where trust is betrayed, promises are broken or people deceive, for example, approximately 11% of people surveyed by the General Social Survey (GSS) in 2018 responded that they have had sex with someone different to their partner while they are married [@GSS2018]. Another example, according to the Washington Post, President Trump has said 10,796 false or misleading statements in 869 days in office [@Kessler2019].

In the laboratory, these transgressions to trust have been explicitly studied in experiments where subjects have incentives to lie or not keep their promises. However, the vast majority of these studies in economics, psychology and neurosciences have been conducted in people who do NOT know each other [to name a few, @Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a]. In social psychology some studies address deception in close interpersonal relationships, however, they use self-report measurements [@DePaulo1998; @DePaulo2004] or rather explore the development of deception detection skills in same-sex friends [@Anderson2002]. Despite the widespread presence of interactions between human beings belonging to the same group, it is not known how social closeness between subjects can affect keeping or breaking promises.

In this manuscript, we explore the effects of three partners with different levels of social closeness on keeping or breaking promises, as well as on cooperation in a trust game. The above, we analyze it in the light of the two main motivations that have been pointed out in the literature regarding keeping promises [@Baumgartner2009]:

1. The _instrumental_ suggests that promises are kept to make future cooperation easier.

2. The _intrinsic_ mentions that the promises are kept to do what is morally right.

In our study, subjects perform a standard trust game in pairs with three phases: _first_, the trustee makes a promise to pay half of his earnings regardless of who his investor is; _second_, the investor receives the promise and decides if he invests his initial budget; _third_, in case the investor has given the budget, the trustee faces the decision to pay or not to pay half of his earnings. To evaluate the effect of social closeness, our subjects participate in the role of trustee in front of three partners with different levels of social closeness (zero, low and high) in the role of the investor: a _computer_, a _stranger_, and a _friend_.

The manipulations mentioned allow us to evaluate several hypotheses, the first one was proposed a priori and is derived from a larger research project (you can check the pre-registration of the hypothesis here: https://osf.io/u97fd), while the following are exploratory:

1. Social closeness will reduce the decision of breaking the promise. According to the _instrumental_ motivation, we expect that subjects keep their promises with friends for the purpose of facilitating future cooperation, which can be extended even beyond the trials in the experiment. We also expect, although to a lesser extent, that the subjects keep promises to strangers, with the purpose of facilitating cooperation at least during the trials during the experiment. Finally, we anticipate that the participants break the promises to the computer because it is a partner without social closeness and they could not ensure cooperation in future trials. It should be noted that if the participants keep the promises to the computer, evidence would be given in favor of intrinsic motivation.

2. There will be an effect of social closeness on cooperation, regardless of promises. We expect that there is more probability of paying the _ friend_ than the _ stranger_ and more probability of paying the stranger than the _computer_. According to the _instrumental_ motivation, the cooperation will be greater for partners with whom the subject anticipates greater cooperation in the future (friend> stranger> computer).

3. Finally, we will obtain two subsamples according to the cooperation rate of the subjects as was done in another study [@Baumgartner2009]. However, what in the aforementioned study was classified as a group of _honest_ and _dishonest_, we will show that in our sample it is not supported because if the groups differ in their payment rate it will be due to the difference in their level of commitment expressed in the promises.

# Methods

## Subjects

We included 45 subjects (15 men), recruited from the National Autonomous University of Mexico, the age range from 19 to 33 years and their minimum educational level were bachelor's degrees. Subjects went to the study with a friend considered _close_ by themselves, who fulfilled the following characteristics: he was matched by sex, did not have a family bond and was not a person with a sentimental or sexual relationship. 30 subjects (15 men) performed the task within a Magnetic Resonance Imaging (MRI) scanner, however, their image data is not analyzed in the present work.

## Task

All subjects performed an adaptation of the trust game with promises, using hypothetical monetary rewards [@Baumgartner2009]. The task was programmed in PsychoPy2 version 1.84.2 [@Peirce2019; @Peirce2008] and consisted of 24 trials between two players: trustee and investor. The trustee originally has 0 Mexican pesos and the investor has 2 pesos, the investor is presented with the opportunity to give his money to the trustee or keep it. If he invests his money it is multiplied by 5 pesos, so that the trustee has 10 pesos. Finally, the trustee decides to pay half to the investor or keep the 10 pesos.

The structure described is repeated in 24 trials, however, in 4 of the trials the trustee can send a promise to the investor, the promises were that _always_, _mostly_, _sometimes_,  or _never_ would pay back. Each promise was valid for three trials so that 12 of the trials have the effect of the promise and the other 12 do not. It is worth mentioning that the promises are not made to a particular partner, but the subject expresses their level of commitment to pay back regardless of who their partners are in the next three trials in which the promise is valid.

The variation with respect to the original task is that in our experiment three partners were presented with three levels of social closeness in the role of the investor: *computer* (no closeness), *strange* (low closeness) and *friend* (high closeness), while the subject acts as the trustee. Each partner performs the role of investor in 8 of 24 total trials, however, both the promises and social closeness conditions were presented to the trustee in pseudorandom order.

Since our main interest was the trustee's behavior, investors' decisions were programmed _a priori_ to give their amount in 6 trials and in 2 did not. The covert story for all our subjects was that they would be playing in real-time with their friend, the stranger (was told he would be another same-sex unknown person) and the computer. A diagram of the chronology of the experimental task with the duration of each phase in seconds is shown in Figure 1, each box from left to right represents a screen that was shown to the subjects sequentially. Section A$_1$ corresponds to an example of trials without promises and section A$_2$ to trials with promises.

Fixation phase consisted only of a period in which the subject paid attention without performing any particular behavior, then, **promises phase** in part A$_1$ indicated to the subject that the following three trials they could decide without the effect of the promise, while in A$_2$  the subject was asked to decide between _always_, _mostly_, _sometimes_ or _never_ pay back. This was followed by another fixation period, subsequently, trails in both A$_1$ and A$_2$ continue in the same way.

In the **anticipation/assignment phase**, subjects were told who their partner was for that trial (computer, stranger or friend) and was given the message that their partner was making their decision. Later in the **decision phase**, the subject was informed if his partner invested his $2 or not, he was reminded of his promise level (if they were trails with promises) and, in case of his partner had invested, he was asked to decide whether to pay back or not. Finally, in **feedback phase** payments for that trial were shown and the sequence was repeated.

```{r figA, fig.cap='Trust game with promises'}

knitr::include_graphics("/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/task.png")

```

## Procedure

Subjects came with a same-sex friend considered close by him or her, it was emphasized that they must not have a romantic or family relationship with their friends, to try to exclude the effect on cooperation due to a consanguineous relationship or sexual attraction. Also, to ensure that the subjects and their companions had a similar degree of social closeness to each other, in the laboratory both responded to the "Inclusion of the Other in Self" IOS scale [@Aron1997] without observing their partner responses. The scale consists of seven pairs of circles that vary in the degree of overlap between them, the respondent must select the pair of circles that best represents the subjective closeness to his partner.

# Bibliography

### 2019-07-29 article_english.Rmd
translation

@@
 
+Subjects were trained in the task by two of the researchers, the game was first explained verbally, and then the computerized interface was presented to them on a portable computer.
+They were told that they would make their decisions with four buttons on the computer keyboard, which corresponded to the levels of promises and with only two of these to make their decision to pay back or not.
+Friends heard the explanation, they were told that they would make their decisions in a separate room on another computer.
+Subjects performed between 3 and 6 practice tests together with the researcher who exemplified the course of the game when the investor gave his budget.
+In the practice trials, all the phases indicated in Figure 1 were shown, however, the identity of the investors was replaced by question marks.
+
+When the subjects did not report doubts we proceeded to take them without their companions to another room where they would make their decisions on a laptop, or, with the Lumina Cedrus response system in the case that it was a subject to which we also performed MRI.
+The subjects began the task believing that they would really play with the three partners of different social closeness.
+In the other room, another of the researchers performed the _debriefing_ to the companion, they were told that the purpose of the research was to know if their mere presence had an effect on the subject's decisions, but that to simplify the analysis their responses were programmed _a priori_ so your participation ended there.
+
+When the subject finished the task, _debriefing_ was also carried out, he was told that the decisions of his partners had been programmed.
+Although no participant exercised their right, both subjects and their friends were told that they could withdraw their participation and informed consent if they considered disagreeing with any of the manipulations made by researchers.
+
+# Results
+
+## Descriptives
+
+We analyzed 810 decisions about paying back or not (18 per subject), as well as 180 promises (4 per subject), 69% of the decisions,  were pay back, while the proportion of the promises selected were 5.4%, 16.2% 43.8%, 40.2%, respectively for promises _never_, _sometimes_, _mostly_ and _always_.
+Figure 2 shows the payment proportion depending on the levels of promises and partners.
+
+Breaking promises, that is, that the subject had promised _always_ and subsequently decides not to pay back occurred only 12.4% of trials (19 times they did not pay back of 153 when promised _always_), of which, 8.50% (13/153) were trials with the computer, 3.92% (6/153) with the stranger and 0% (0/153) with the friend.
+It is essential to note that breaking the promise was not the most frequent decision, in 91.5% of trials when they promised _always_ and had the computer as a partner they decided to pay back.
+
+```{r fig2, fig.cap='Pay back proportion by partners and promises levels'}
+
+p2 + theme(text = element_text(size = 10),
+            axis.text.x = element_text(size = 8))
+
+```
+
+## Hierarchical Bayesian Modeling
+
+All models presented below were programmed in R via the **brms** package [@Burkner2017; @R2019], which performs the inference using sampling by Markov chain Monte Carlo through **Stan** [@Rstan2018].
+For each model, the posteriors distributions of all parameters were approximated with four chains of 2000 iterations each, the first 1000 iterations of each chain were discarded (burning period), for a total of 4000 post-burning samples.
+Models convergence was evaluated through visual inspection of the chains and calculation of the $\hat{R}$ statistic, which for all parameters was 1, which is interpreted as convergence.
+Vaguely informative prior distributions were used for the parameters of interest in the models, which allows the data to dominate the inference, also assumes as little as possible regarding the nature of the phenomenon, which could be adequate for the current state of evidence in the problem we are studying [@McElreath2018].
+
+### Social closeness between partners
+
+To assess social closeness, 30 (15 men) of our subjects and their friends responded to the IOS scale [@Aron1997; @Fareri2014; @Sip2015], which consist of seven pairs of circles that vary in the degree of overlap and represent the social closeness that an individual perceives with respect to the other.
+A Hierarchical and Cumulative Bayesian Model (See section: Commitment expressed in the promises), supports the hypothesis that there are no differences in subjective social closeness between subjects and their friends, with a posterior evidence ratio of 2.74 in its favor.
+
+### Effect of social closeness on breaking promises
+
+To evaluate the hypothesis that social closeness would reduce the behavior of breaking the promise, we filtered all trials in which subjects promised that they would _always_ pay back and then decided not to pay.
+Subsequently, Bayesian inference was used to assess the effect of partners on the decision to break the promise at the individual and population level.
+For this purpose, a Hierarchical Bayesian Model was carried out that assumes that the uncertainty in partners effect on the decision to break the promise varies depending on each individual, however, it also assumes that these variations belong to common population distributions [@Gelman2006].
+
+$$
+\begin{aligned}
+&y_i \sim \mathrm{Bernoulli}(\theta_i) \\
+&\mathrm{logit(\theta_i)} = \mathbf{X}\beta  +  \mathbf{Z}u
+\end{aligned}
+$$
+
+In the previous model, the decision to break the promise $y_i$ comes from a Bernoulli distribution with probability $\theta_i$, the goal of the Hierarchical Model is to predict each decision through the linear combination of the effects of each partner, transformed by its inverse link function $\mathrm{logit}$ [@Burkner2017].
+In this model, $\beta$ and $u$ are coefficients at the population level and individual level respectively, while $\mathbf{X}$, $\mathbf{Z}$ are their corresponding design matrices.
+In this case, the population coefficients correspond to the presence of partners with no social closeness $\beta^{computer}$, low $\beta^{stranger}$ and high $\beta^{friend}$.
+
+Figure 3 shows the posterior probability of breaking the promise depending on the partner, circles correspond to the medians of the distributions of the posterior estimates effects, the thick bar, and the thin bar correspond to the interval of 50% and 95% posterior probability.
+It is clear that the probability of breaking the promise decreases as social closeness increases, however, we calculate the reasons for evidence for the following hypotheses:
+
+- There is a greater probability to break the promise to the computer than the stranger.
+
+- There is more probability to break the promise to the stranger compared to a friend.
+
+The evidence ratio, which is the ratio between the posterior probability of the mentioned hypotheses and their corresponding alternative hypotheses was 7.47 and 8.64 respectively in favor of the previous hypotheses.
+As can be seen in Figure 5 in the estimate for $\beta^{computer}$, when there is no social closeness we have a 95% posterior probability that the parameter for promise-breaking is between 4-38%, although it is a small proportion, it clearly excludes the probability that promises are not broken.
+
+```{r fig3, fig.cap='Posterior probability of Promise Breaking'}
+p3
+
+```
+
+### Effects of promises and social closeness on cooperation
+
+To evaluate the effect of the experimental conditions on the decision to pay back, we used all trials were partners invest.
+Again, a Hierarchical Bayesian Model was fit, which assumes that the promises and partners have an effect that varies for each individual, however, it also assumes that these variations belong to common population distributions.
+The model estimates that the probability $\theta_i$ of the decision to pay back is based on the effect of the presence of promises $\beta^{promise}$, as well as partners with low $\beta^{stranger}$ and high $\beta^{friend}$ social closeness.
+
+Figure 4 shows the posterior distributions of the $\beta$ coefficients in the logit scale, the center line represents the median of the distribution and the shaded area corresponds to the interval of 50% posterior probability.
+As can be seen, more than 95% of the posterior density of the population coefficients is greater than 0, which indicates strong evidence of the effect of experimental conditions on the decision to pay back, so that the presence of promises and the stranger increase clearly the probability of paying, but the presence of the friend is the condition that has the greatest effect on this behavior.
+Posterior distributions clearly show that the probability of cooperation increases as social closeness does.
+
+Also, Figure 5 presents the posterior predictive distribution in contrast to the proportion of decisions to each partner during the promises phase, each panel corresponds to one of the first twelve subjects.
+The responses on the dotted line would indicate that the subject paid back random to that partner.
+Posterior predictive distribution simulates observations of the model and compares them with the actual data, it helps us to identify if the model is sufficiently close to the process that generated the data [@Schad2019; @Lee2014].
+It can be seen that there is a great correspondence between the subject's responses and predictions of the model, even in cases where the model is "wrong" (for example, subject 1), the observed response is in the range of a predicted standard deviation, which gives credibility to estimates.
+
+```{r fig4, fig.cap='Posterior estimates in logit scale'}
+
+p4
+
+```
+
+```{r fig5, fig.cap='Posterior predictive over pay back rate', out.width='100%', out.height='100%'}
+
+d_g9 %>% 
+    ggplot(aes(x = treatment, y = rate, col = case)) +
+    geom_hline(yintercept = 0.5, lty = 2, col = "gray") +
+    geom_line(aes(group = case), show.legend = F) +
+    geom_pointrange(aes(ymax = rate + pred_sd, ymin = rate - pred_sd),
+                    shape = 21, fill = "white", size = 0.4) +
+    scale_color_manual(values = c("#053778", "#A4CAE3")) +
+    facet_wrap(~id) +
+    my_theme +
+    scale_y_continuous(breaks = c(0, 0.5, 1.0)) +  
+    theme(axis.text.x = element_text(angle = 75, hjust = 1), 
+          legend.position = "top",
+          text = element_text(size = 10)) +
+    labs(x = NULL, y = "Rate", col = NULL)
+
+```
+
+### Effects of social closeness on cooperation varying by promises
+
+In this model, it is assumed that social closeness has an effect that varies for each level of promise, which implies that there are levels of promise that are more sensitive than others to the effect of the partners on the decision to pay back.
+Again, a Hierarchical Bayesian Model was made to estimate the effect of partners at the population level and the variations depending on the promise levels.
+Table 1 summarizes the subsequent distributions of the model coefficients in the logit scale, including point estimates, standard errors and Bayesian Credibility Intervals of 95%.
+An estimate similar to the previous models can be observed, with strong evidence of the effect of social closeness on the decision to pay back.
+Although the credibility range for the friend's effect includes 0, the evidence ratio that the effect is greater than zero is 15.81 with 94% of posterior probability.
+
+On the other hand, Figure 6 shows the subsequent predictive distribution, compared to the payment rates of all individuals to the different partners and their variation by the level of promise.
+With the exception of the promise _never_, a monotonic positive effect of partners is observed at all levels of promise, however, it can be observed how the effect of social closeness varies depending on the strength of the promise, mainly for the decisions towards the computer.
+
+```{r fig6, fig.cap='Posterior predictive over pay back rate, Social Closeness Varying effects by Promise levels'}
+
+p6 + 
+  scale_y_continuous(breaks = c(0, 0.5, 1.0)) +  
+  theme(axis.text.x = element_text(size = 7))
+
+```
+
+```{r tabla}
+
+tabla1 <- broom::tidy(fit) %>% 
+  slice(1:3)
+
+tabla1[, 1] <- c("Intercept", "Stranger", "Friend")
+
+kable(tabla1, 
+      digits = 3, 
+      booktabs = T,
+      col.names = c("Term", "Estimate", "Est.Error", "Lower", "Upper"),
+      caption = c("Posterior coefficients estimates")) %>%
+  add_header_above(c(" ", " " = 2, "95 % CI" = 2)) %>% 
+  kable_styling(latex_options = "hold_position")
+
+```
+
+### Commitment expressed in promises
+
+In the original study of promises, authors chose to divide their sample into two according to the hierarchical clustering technique with Ward's method  [@Baumgartner2009].
+In this way they obtained two sets of participants that were different in their payment rates, despite the fact that they both made very high promises, for this reason, the authors named the group that paid little _dishonest_ and the group that paid a lot _honest_.
+In a similar exercise, in the present study we performed the hierarchical grouping technique to obtain a solution of 2 groups and we found two similar sets in $n$ that we call the group "Low" and "High" (Low = 25, High = 20), with quite different payment ratios (Low = 58%, High = 83%), and a 95% confidence interval of 20% to 32% in the difference favor of the High group.
+
+Although it seems a similar result to that reported in that paper, we explore the pattern of promises of both groups to determine if it was possible to classify our subjects as _honest_ and _dishonest_.
+If we hypothesize that the commitment to pay would be reflected in the level of promises selected, a group of _dishonest_ people could generate in their partners the belief that they will pay by choosing a high level of promises (mostly or always) and, later, betraying that trust when deciding not to pay back.
+
+In order to explore whether the groups represent populations that do not differ in the level of commitment expressed in the promises, we use a Cumulative Bayesian Model, which assumes that the levels of promises are an observed ordinal variable $Y$ that originates from the categorization of a continuous latent variable $\tilde{Y}$, for this case, _the expressed commitment to pay back_ [@Burkner2019].
+The degree to which the subjects of the High group differ from the Low group, in normal standard deviations ($z$-values), on the latent scale of $\tilde{Y}$, has a point estimate of 0.95, which implies that the High group has 0.95 $z$-values greater commitment to pay back than the Low group.
+
+The 95% Bayesian Credibility Interval indicates that the High group is between 0.40 to 1.51 $z$-values of difference from Low.
+So we can conclude with at least a 95% probability that people belonging to the High group expressed in their promises a greater commitment to pay back than the subjects of the Low group.
+If we look at Figure 7, the probability of choosing the different levels of promises varies depending on the group, the one who had the highest percentage of decisions to pay back is more likely to choose _always_ (High group), while the group that had the lowest percentage of decisions to pay back are more likely to choose _mostly_ (Low group).
+
+According to our data, we could not justify the classification of our groups according to their honesty or dishonesty, at least not with the technique used in Baumgartner et al.
+(2009).
+Since people were quite consistent with keeping what they promised to pay.
+
+```{r fig7, fig.cap='Promise choices by group'}
+
+# Cumulative model
+p7
+
+```
+
+# Discussion
+
 # Bibliography

### 2019-07-29 article_english.Rmd
Translation

@@
 There will be an effect of social closeness on cooperation, regardless of promises.
-We expect that there is more probability of paying the _ friend_ than the _ stranger_ and more probability of paying the stranger than the _computer_.
-According to the _instrumental_ motivation, the cooperation will be greater for partners with whom the subject anticipates greater cooperation in the future (friend> stranger> computer).
+We expect that there is more probability of paying the _friend_ than the _stranger_ and more probability of paying the stranger than the _computer_.
+According to the _instrumental_ motivation, the cooperation will be greater for partners with whom the subject anticipates greater cooperation in the future (friend > stranger > computer).
 
@@
 
+## Cumulative Bayesian Modeling
+
 ### Commitment expressed in promises
@@
 
+The objective of this study was to evaluate the effect of social closeness on keeping and breaking promises, as well as on cooperation in a trust game.
+Our results give evidence that zero social closeness increases the probability of breaking the promise and it decreases monotonically as social closeness increases.
+Likewise, as social closeness increases, so does cooperation; _high_ social closeness has an effect on decisions that surpasses even those that all other experimental conditions.
+The most interesting finding was that when subjects express high commitment to cooperate (through choosing that they would _always_ pay back) probability that they comply is also quite high, however, there is a proportion of transgressions that according to our inferences are between 4 - 38% with 95% certainty.
+
+To our knowledge, this is the first experimental study that incorporates social closeness as a predictor of the decision to break promises with socially relevant partners.
+In previous studies, the participants remain anonymous during the course of the tasks [@Baumgartner2009], their measurements to evaluate transgressions are self-reported [@DePaulo1998; @DePaulo2004], they do not directly quantify the breaking of promises [@Vanberg2008; @Charness2006], or as we will discuss later, they use heterogeneous measures of social closeness [@Glaeser2000].
+
+Our experiment is probably the first to include a partner without social closeness (_computer_), our data give evidence that the mere fact of considering that you play with a human diminishes the probability of breaking the promise.
+It is approximately 7.5 times more likely to break the promise to the computer than to the stranger, even though that partner was not known.
+In our study, zero social closeness is important because it allows us to explore the _intrinsic_ motivation to keep the promises, if humans keep their word because it is morally correct, we would anticipate that probability of breaking the promise was very low in the three partners and, particularly, the inference regarding the probability of breaking the promise to the computer would include zero.
+
+The probability of breaking the promise without social closeness, although low, is clearly greater than zero, which provides evidence that contradicts, at least in degree, the hypothesis of _intrinsic_ motivation.
+We cannot exclude the possibility that the subjects keep promises mainly morally motivated, because even in the case of the computer, the subjects keep a large proportion, but we can exclude that this is their only motivation.
+
+On the other hand, high social closeness allows us to explore the _instrumental_ motivation to keep promises.
+In our study, it is almost 9 times more likely to break the promise to the stranger than to the friend; If human beings keep their word to facilitate cooperation in the future, we would anticipate that with a partner of high social closeness (with whom they are very likely to cooperate, even after the experiment) there would be less chance of breaking the promise.
+In fact, in our study, the promise to friends was not broken on any occasion, so the inference, in this case, is obvious.
+
+Our findings could be explained by the social norm called _conditional cooperation_, which indicates that the belief that other people cooperate at high levels also induces high levels of cooperation [@Fehr2018].
+Thus, the lack of certainty regarding the decisions that the computer would make could explain the probability of breaking the promise that exists towards this partner.
+Similarly, the information that the subjects have regarding the behavior of the friend -even before the experiment- can explain the high levels of cooperation and keeping of promises towards this partner.
+
+Regarding cooperation, it is not the first investigation in which the effect of social closeness is evaluated, however, the nature of experimental manipulation has been diverse.
+For example, in one study the contribution in a public goods game was evaluated during several trials in a group made up of the same individuals (_partners_), compared to another group of new different subjects for each trial (_strangers_) [@Croson1996].
+It was assumed that in the condition of _partners_ the cooperation would be greater because it is a stable group compared to the group of _strangers_.
+The mentioned study does not give details regarding the recruitment of participants, so we could assume that even in the condition of _partners_ these are individuals who do not consider themselves socially close.
+
+In another experiment, an increase in cooperation in a trust game in pairs was reported when individuals are socially close [@Glaeser2000], in this study, subjects know each other and the researchers carefully measured several variables regarding their social connection, however, some individuals who arrived together were allowed to perform the task between themselves and others were paired with unclear criteria.
+The above allows social closeness between partners to be heterogeneous, allows for romantic relationships and assumes that two individuals who come together to class are considered close to each other.
+Also, since it is a study of _one-shot_, it excludes the possibility of evaluating how the same subject varies his behavior based on different levels of social closeness.
+
+To try to homogenize social closeness between our subjects and their partners, participants performed the task with a same-sex match friend considered close by themselves, in none case was it a relative and, although we understand that there may be same-sex couples and that the subjects may have hidden their relationship, they were emphasized that to be part of the study their companion could not be a romantic or sexual partner.
+Besides, Bayesian analysis of the IOS scale showed evidence in favor that the degree of social closeness between 30 of our 45 subjects and their friends was practically the same.
+Although the results of the two studies mentioned are practically in the same direction as the findings of our experiment, establishing the similarity in effects magnitudes is not possible due to the design differences, the performed tasks, and the statistical procedures used.
+
+A methodological contribution of our study is that, in the literature of promises, it is the first to use Bayesian inference tools: *Hierarchical Models* and *Cumulative Models*.
+The former (aka multilevel models), allowed us to model the effect of the experimental conditions on the individual response, these models assume that lower level observations (e.g.
+decisions of each individual) are nested in higher level units (e.g.
+individual subjects).
+Within-subjects designs have traditionally been analyzed with repeated measures AN(C)OVA, however, *Hierarchical Models* grant the advantages of naturally dealing with unbalanced data, including categorical and/or numerical predictors, explicitly incorporate individual variability, among others [@Vuorre2018; @Gelman2006; @McElreath2018; @Burkner2017].
+
+In our case, as shown in Figure 5, the *Hierarchical Model* allowed us to capture very precisely how the experimental conditions affected the decisions of each subject and the differences between them.
+For example, there are obviously motivated _instrumental_ subjects such as number 8 or 12 who are very sensitive to the identity of their investors and modify their cooperation under social closeness.
+At the same time, there are notably _intrinsic_ subjects such as 9 and 10 who cooperate all the time regardless of who their partners are.
+The *Hierarchical Model* naturally includes this information for the estimation of population effects, which, if not considered, would lead to inaccurate inferences.
+
+On the other hand, the *Cumulative Models* allowed us to model the strength of the commitment expressed through promises.
+A very frequent problem that has been pointed out recently is that analyzing ordinal data with methods that assume that observations are _metric_ can lead to serious inference errors [@Liddell2018].
+The *Cumulative Models* assume that the observed responses come from the categorization of a continuous latent variable [@Burkner2019], so in our study, we could identify that the groups with different payment proportions, which in other articles have been called _dishonest_ and _honest_, differ in the commitment they express through their promises.
+Considering that the tools to perform the *Cumulative Models* are relatively recent, it would be valuable to replicate published studies [e.g., @Baumgartner2009; @Baumgartner2013] considering the new alternatives of inference.
+
+Although the *Hierarchical* and *Cumulative* models are not tools exclusively for Bayesian inference, their application from this approach represents several advantages compared to frequentist statistics.
+Classic problems of the previous one such as multiple comparisons, the decision of when to stop collecting subjects (stopping rule), or use of planned comparisons versus _post hoc_, are not factors that affect the support provided by the data to the hypothesis from the Bayesian approach [@Dienes2011].
+In Bayesian inference, hypothesis testing makes formal use of probability to express the plausibility of theories, in our case we were able to obtain evidence ratios regarding the extent to which our data support our hypotheses, regardless of whether these were proposed _a priori_ or _post hoc_.
+
+A limitation of this paper is the use of hypothetical rewards compared to real rewards.
+A relatively recent study on decision-making reported that there is more loss aversion when subjects have real monetary rewards compared to hypothetical in a risk task [@Xu2016].
+However, other works do not report differences between the use of both types of rewards in self-control, temporal and social discount tasks [@Locey2011; @Johnson2006; @Rachlin2006].
+Likewise, it can be argued that the results have theoretical congruence [@Fehr2018] and are in the same direction as other works that use real money [@Croson1996; @Glaeser2000], so there are not many reasons to expect that other types of rewards would modify our results.
+
+Another possible limitation is the use of multiple trials with each partner.
+Although the decision to use repeated measures during our design serves more the purpose of reducing contaminant sources and increasing internal validity [@Maxwell2018], to have more clarity regarding the difference in the _intrinsic_ and _instrumental_ motivations, the studies could benefit from only include one trial for each partner.
+Play a _one-shot_ with each partner avoids the possibility that multiple trials could generate the belief that the computer can also vary its behavior according to the decisions of the _trustee_.
+
+# Conclusions
+
+Subjects keep their promises by a combination between the _intrinsic_ and _instrumental_ motivations.
+They are predominantly _nice guys_ because they keep their word even with investors with no social closeness.
+However, its trustworthiness is far from perfect, since there is a small, but reliably greater than zero, proportion of betrayals committed towards this partner.
+It seems that if subjects cannot assure that their investor will be a _potential cooperator_, dishonesty may emerge in the form of broken promises.
+The theoretical predictions of the social norm _conditional cooperation_ frame the finding that social closeness decreases the probability of breaking the promise and increases cooperation.
+In the same way that suggests the correspondence between commitment expressed through promises and subsequent behavior.
+
 # Bibliography

### 2019-07-29 article_english.Rmd
Creating latex template

@@
     number_sections: true
+    keep_tex: true
 fontsize: 12pt
@@
 
-One of the forms of communication that have received the most attention in psychological game theory is the promises, in an interaction between the sender and the recipient, it is believed that promises influence beliefs of the recipient, generating trust and cooperation [@Charness2006; @Vanberg2008].
+One of the forms of communication that have received the most attention in psychological game theory is the promise, in an interaction between sender and recipient, it is believed that promises influence beliefs of the recipient, generating trust and cooperation [@Charness2006; @Vanberg2008].
 However, there are situations where trust is betrayed, promises are broken or people deceive, for example, approximately 11% of people surveyed by the General Social Survey (GSS) in 2018 responded that they have had sex with someone different to their partner while they are married [@GSS2018].
@@
 Finally, we will obtain two subsamples according to the cooperation rate of the subjects as was done in another study [@Baumgartner2009].
-However, what in the aforementioned study was classified as a group of _honest_ and _dishonest_, we will show that in our sample it is not supported because if the groups differ in their payment rate it will be due to the difference in their level of commitment expressed in the promises.
+However, what in the aforementioned study was classified as a group of _honest_ and _dishonest_, we will show that in our sample it is not supported because if the groups differ in their payment rate it will be due to the difference in their level of commitment expressed by promises.
 
@@
 Each promise was valid for three trials so that 12 of the trials have the effect of the promise and the other 12 do not.
-It is worth mentioning that the promises are not made to a particular partner, but the subject expresses their level of commitment to pay back regardless of who their partners are in the next three trials in which the promise is valid.
+It is worth mentioning that the promises are not made to a particular partner, but the subject expresses their commitment level to pay back regardless of who their partners are in the next three trials in which the promise is valid.
 
@@
 
-In the **anticipation/assignment phase**, subjects were told who their partner was for that trial (computer, stranger or friend) and was given the message that their partner was making their decision.
+In the **anticipation/assignation phase**, subjects were told who their partner was for that trial (computer, stranger or friend) and was given the message that their partner was making their decision.
 Later in the **decision phase**, the subject was informed if his partner invested his $2 or not, he was reminded of his promise level (if they were trails with promises) and, in case of his partner had invested, he was asked to decide whether to pay back or not.
@@
 
-We analyzed 810 decisions about paying back or not (18 per subject), as well as 180 promises (4 per subject), 69% of the decisions,  were pay back, while the proportion of the promises selected were 5.4%, 16.2% 43.8%, 40.2%, respectively for promises _never_, _sometimes_, _mostly_ and _always_.
+We analyzed 810 decisions about paying back or not (18 per subject), as well as 180 promises (4 per subject), 69% of the decisions,  were pay back, while the proportion of the promises selected were 5.4%, 16.2%, 43.8% and 40.2%, respectively for promises _never_, _sometimes_, _mostly_ and _always_.
 Figure 2 shows the payment proportion depending on the levels of promises and partners.
 
-Breaking promises, that is, that the subject had promised _always_ and subsequently decides not to pay back occurred only 12.4% of trials (19 times they did not pay back of 153 when promised _always_), of which, 8.50% (13/153) were trials with the computer, 3.92% (6/153) with the stranger and 0% (0/153) with the friend.
+Breaking promises, that is, subject had promised _always_ and subsequently decides not to pay back occurred only 12.4% of trials (19 times they did not pay back of 153 when promised _always_), of which, 8.50% (13/153) were trials with the computer, 3.92% (6/153) with the stranger and 0% (0/153) with the friend.
 It is essential to note that breaking the promise was not the most frequent decision, in 91.5% of trials when they promised _always_ and had the computer as a partner they decided to pay back.
@@
 
-Figure 3 shows the posterior probability of breaking the promise depending on the partner, circles correspond to the medians of the distributions of the posterior estimates effects, the thick bar, and the thin bar correspond to the interval of 50% and 95% posterior probability.
+Figure 3 shows the posterior probability of breaking the promise depending on the partner, circles correspond to the medians of the distributions of the posterior estimates effects, the thick bar, and the thin bar correspond to the interval of 50% and 95% posterior probability, respectively.
 It is clear that the probability of breaking the promise decreases as social closeness increases, however, we calculate the reasons for evidence for the following hypotheses:
@@
 
-On the other hand, Figure 6 shows the subsequent predictive distribution, compared to the payment rates of all individuals to the different partners and their variation by the level of promise.
+On the other hand, Figure 6 shows the posterior predictive distribution, compared to the payment rates of all individuals to the different partners and their variation by the level of promise.
 With the exception of the promise _never_, a monotonic positive effect of partners is observed at all levels of promise, however, it can be observed how the effect of social closeness varies depending on the strength of the promise, mainly for the decisions towards the computer.
@@
 
-Our experiment is probably the first to include a partner without social closeness (_computer_), our data give evidence that the mere fact of considering that you play with a human diminishes the probability of breaking the promise.
+Our experiment is probably the first to include a partner without social closeness (_computer_), our data give evidence that the mere fact of considering that subjects play with a human diminishes the probability of breaking the promise.
 It is approximately 7.5 times more likely to break the promise to the computer than to the stranger, even though that partner was not known.
@@
 On the other hand, high social closeness allows us to explore the _instrumental_ motivation to keep promises.
-In our study, it is almost 9 times more likely to break the promise to the stranger than to the friend; If human beings keep their word to facilitate cooperation in the future, we would anticipate that with a partner of high social closeness (with whom they are very likely to cooperate, even after the experiment) there would be less chance of breaking the promise.
+In our study, it is almost 9 times more likely to break the promise to the stranger than to the friend; if human beings keep their word to facilitate cooperation in the future, we would anticipate that with a partner of high social closeness (with whom they are very likely to cooperate, even after the experiment) there would be less chance of breaking the promise.
 In fact, in our study, the promise to friends was not broken on any occasion, so the inference, in this case, is obvious.
@@
 Thus, the lack of certainty regarding the decisions that the computer would make could explain the probability of breaking the promise that exists towards this partner.
-Similarly, the information that the subjects have regarding the behavior of the friend -even before the experiment- can explain the high levels of cooperation and keeping of promises towards this partner.
+Similarly, the information that the subjects have regarding friend's behavior -even before the experiment- can explain the high levels of cooperation and keeping of promises towards this partner.
 
@@
 To try to homogenize social closeness between our subjects and their partners, participants performed the task with a same-sex match friend considered close by themselves, in none case was it a relative and, although we understand that there may be same-sex couples and that the subjects may have hidden their relationship, they were emphasized that to be part of the study their companion could not be a romantic or sexual partner.
-Besides, Bayesian analysis of the IOS scale showed evidence in favor that the degree of social closeness between 30 of our 45 subjects and their friends was practically the same.
+Besides, Bayesian analysis of the IOS scale showed evidence in favor that the degree of social closeness between 30 of our 45 subjects and their friends was the same.
 Although the results of the two studies mentioned are practically in the same direction as the findings of our experiment, establishing the similarity in effects magnitudes is not possible due to the design differences, the performed tasks, and the statistical procedures used.
@@
 
-On the other hand, the *Cumulative Models* allowed us to model the strength of the commitment expressed through promises.
+On the other hand, the *Cumulative Model* allowed us to capture the strength of the commitment expressed through promises.
 A very frequent problem that has been pointed out recently is that analyzing ordinal data with methods that assume that observations are _metric_ can lead to serious inference errors [@Liddell2018].
@@
 Classic problems of the previous one such as multiple comparisons, the decision of when to stop collecting subjects (stopping rule), or use of planned comparisons versus _post hoc_, are not factors that affect the support provided by the data to the hypothesis from the Bayesian approach [@Dienes2011].
-In Bayesian inference, hypothesis testing makes formal use of probability to express the plausibility of theories, in our case we were able to obtain evidence ratios regarding the extent to which our data support our hypotheses, regardless of whether these were proposed _a priori_ or _post hoc_.
+In Bayesian inference, hypothesis testing makes formal use of probability to express the plausibility of theories, in our case we were able to obtain evidence ratios regarding the extent our data support hypotheses, regardless these were proposed _a priori_ or _post hoc_.
 
@@
 However, other works do not report differences between the use of both types of rewards in self-control, temporal and social discount tasks [@Locey2011; @Johnson2006; @Rachlin2006].
-Likewise, it can be argued that the results have theoretical congruence [@Fehr2018] and are in the same direction as other works that use real money [@Croson1996; @Glaeser2000], so there are not many reasons to expect that other types of rewards would modify our results.
+Likewise, it can be argued that our results have theoretical congruence [@Fehr2018] and are in the same direction as other works that use real money [@Croson1996; @Glaeser2000], so there are not many reasons to expect that other types of rewards would modify our results.
 

### 2019-07-29 article_english.tex
Creating latex template

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Nice guys or potential cooperators when keeping promises: an experimental and Bayesian account for two explanations},
            pdfauthor={Said Jiménez},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{Nice guys or potential cooperators when keeping promises: an
experimental and Bayesian account for two explanations}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Said Jiménez}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{July 2019}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Human beings are social animals and we get advantages from being so.
Historically, belonging to a social group has provided protection and
guaranteed access to resources such as food, currently there has been
evidence that belonging to a social circle has a positive effect on
longevity, physical and mental health (Holt-Lunstad, 2018; Tough,
Siegrist, \& Fekete, 2017). The interrelation between social closeness
and cooperation is key to the formation of large groups of individuals
without a genetic relationship, such groups form the basis of
communities, societies, and nations, as well as probably constitute one
of the most fundamental conditions for human survival (Fehr \&
Fischbacher, 2003; Fehr \& Schurtenberger, 2018).

An important requirement for cooperation between individuals is
communication, a meta-analysis of 45 studies reported a large positive
effect (\(d = 1.01\)) of communication in cooperation regardless of the
communication medium (Balliet, 2010). In parallel, it is known that
after communication sessions between completely unknown individuals
there is an increase in subjective social closeness (Aron, Melinat,
Aron, Vallone, \& Bator, 1997). Thus, the findings suggest a positive
relationship between communication, cooperation, and social closeness.

One of the forms of communication that have received the most attention
in psychological game theory is the promise, in an interaction between
sender and recipient, it is believed that promises influence beliefs of
the recipient, generating trust and cooperation (Charness \& Dufwenberg,
2006; Vanberg, 2008). However, there are situations where trust is
betrayed, promises are broken or people deceive, for example,
approximately 11\% of people surveyed by the General Social Survey (GSS)
in 2018 responded that they have had sex with someone different to their
partner while they are married (Smith, Davern, Freese, \& Hout, 2018).
Another example, according to the Washington Post, President Trump has
said 10,796 false or misleading statements in 869 days in office
(Kessler, Rizzo, \& Kelly, 2019).

In the laboratory, these transgressions to trust have been explicitly
studied in experiments where subjects have incentives to lie or not keep
their promises. However, the vast majority of these studies in
economics, psychology and neurosciences have been conducted in people
who do NOT know each other (to name a few, Gneezy, 2005; Baumgartner,
Fischbacher, Feierabend, Lutz, \& Fehr, 2009; Baumgartner, Gianotti, \&
Knoch, 2013; Charness \& Dufwenberg, 2006; Fischbacher \& Föllmi-Heusi,
2013; Gneezy, Rockenbach, \& Serra-Garcia, 2013; Mazar, Amir, \& Ariely,
2008). In social psychology some studies address deception in close
interpersonal relationships, however, they use self-report measurements
(DePaulo, Ansfield, Kirkendol, \& Boden, 2004; DePaulo \& Kashy, 1998)
or rather explore the development of deception detection skills in
same-sex friends (Anderson, DePaulo, \& Ansfield, 2002). Despite the
widespread presence of interactions between human beings belonging to
the same group, it is not known how social closeness between subjects
can affect keeping or breaking promises.

In this manuscript, we explore the effects of three partners with
different levels of social closeness on keeping or breaking promises, as
well as on cooperation in a trust game. The above, we analyze it in the
light of the two main motivations that have been pointed out in the
literature regarding keeping promises (Baumgartner et al., 2009):

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  The \emph{instrumental} suggests that promises are kept to make future
  cooperation easier.
\item
  The \emph{intrinsic} mentions that the promises are kept to do what is
  morally right.
\end{enumerate}

In our study, subjects perform a standard trust game in pairs with three
phases: \emph{first}, the trustee makes a promise to pay half of his
earnings regardless of who his investor is; \emph{second}, the investor
receives the promise and decides if he invests his initial budget;
\emph{third}, in case the investor has given the budget, the trustee
faces the decision to pay or not to pay half of his earnings. To
evaluate the effect of social closeness, our subjects participate in the
role of trustee in front of three partners with different levels of
social closeness (zero, low and high) in the role of the investor: a
\emph{computer}, a \emph{stranger}, and a \emph{friend}.

The manipulations mentioned allow us to evaluate several hypotheses, the
first one was proposed a priori and is derived from a larger research
project (you can check the pre-registration of the hypothesis here:
\url{https://osf.io/u97fd}), while the following are exploratory:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Social closeness will reduce the decision of breaking the promise.
  According to the \emph{instrumental} motivation, we expect that
  subjects keep their promises with friends for the purpose of
  facilitating future cooperation, which can be extended even beyond the
  trials in the experiment. We also expect, although to a lesser extent,
  that the subjects keep promises to strangers, with the purpose of
  facilitating cooperation at least during the trials during the
  experiment. Finally, we anticipate that the participants break the
  promises to the computer because it is a partner without social
  closeness and they could not ensure cooperation in future trials. It
  should be noted that if the participants keep the promises to the
  computer, evidence would be given in favor of intrinsic motivation.
\item
  There will be an effect of social closeness on cooperation, regardless
  of promises. We expect that there is more probability of paying the
  \emph{friend} than the \emph{stranger} and more probability of paying
  the stranger than the \emph{computer}. According to the
  \emph{instrumental} motivation, the cooperation will be greater for
  partners with whom the subject anticipates greater cooperation in the
  future (friend \textgreater{} stranger \textgreater{} computer).
\item
  Finally, we will obtain two subsamples according to the cooperation
  rate of the subjects as was done in another study (Baumgartner et al.,
  2009). However, what in the aforementioned study was classified as a
  group of \emph{honest} and \emph{dishonest}, we will show that in our
  sample it is not supported because if the groups differ in their
  payment rate it will be due to the difference in their level of
  commitment expressed by promises.
\end{enumerate}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{subjects}{%
\subsection{Subjects}\label{subjects}}

We included 45 subjects (15 men), recruited from the National Autonomous
University of Mexico, the age range from 19 to 33 years and their
minimum educational level were bachelor's degrees. Subjects went to the
study with a friend considered \emph{close} by themselves, who fulfilled
the following characteristics: he was matched by sex, did not have a
family bond and was not a person with a sentimental or sexual
relationship. 30 subjects (15 men) performed the task within a Magnetic
Resonance Imaging (MRI) scanner, however, their image data is not
analyzed in the present work.

\hypertarget{task}{%
\subsection{Task}\label{task}}

All subjects performed an adaptation of the trust game with promises,
using hypothetical monetary rewards (Baumgartner et al., 2009). The task
was programmed in PsychoPy2 version 1.84.2 (Peirce et al., 2019; Peirce,
2008) and consisted of 24 trials between two players: trustee and
investor. The trustee originally has 0 Mexican pesos and the investor
has 2 pesos, the investor is presented with the opportunity to give his
money to the trustee or keep it. If he invests his money it is
multiplied by 5 pesos, so that the trustee has 10 pesos. Finally, the
trustee decides to pay half to the investor or keep the 10 pesos.

The structure described is repeated in 24 trials, however, in 4 of the
trials the trustee can send a promise to the investor, the promises were
that \emph{always}, \emph{mostly}, \emph{sometimes}, or \emph{never}
would pay back. Each promise was valid for three trials so that 12 of
the trials have the effect of the promise and the other 12 do not. It is
worth mentioning that the promises are not made to a particular partner,
but the subject expresses their commitment level to pay back regardless
of who their partners are in the next three trials in which the promise
is valid.

The variation with respect to the original task is that in our
experiment three partners were presented with three levels of social
closeness in the role of the investor: \emph{computer} (no closeness),
\emph{strange} (low closeness) and \emph{friend} (high closeness), while
the subject acts as the trustee. Each partner performs the role of
investor in 8 of 24 total trials, however, both the promises and social
closeness conditions were presented to the trustee in pseudorandom
order.

Since our main interest was the trustee's behavior, investors' decisions
were programmed \emph{a priori} to give their amount in 6 trials and in
2 did not. The covert story for all our subjects was that they would be
playing in real-time with their friend, the stranger (was told he would
be another same-sex unknown person) and the computer. A diagram of the
chronology of the experimental task with the duration of each phase in
seconds is shown in Figure 1, each box from left to right represents a
screen that was shown to the subjects sequentially. Section A\(_1\)
corresponds to an example of trials without promises and section A\(_2\)
to trials with promises.

Fixation phase consisted only of a period in which the subject paid
attention without performing any particular behavior, then,
\textbf{promises phase} in part A\(_1\) indicated to the subject that
the following three trials they could decide without the effect of the
promise, while in A\(_2\) the subject was asked to decide between
\emph{always}, \emph{mostly}, \emph{sometimes} or \emph{never} pay back.
This was followed by another fixation period, subsequently, trails in
both A\(_1\) and A\(_2\) continue in the same way.

In the \textbf{anticipation/assignation phase}, subjects were told who
their partner was for that trial (computer, stranger or friend) and was
given the message that their partner was making their decision. Later in
the \textbf{decision phase}, the subject was informed if his partner
invested his \$2 or not, he was reminded of his promise level (if they
were trails with promises) and, in case of his partner had invested, he
was asked to decide whether to pay back or not. Finally, in
\textbf{feedback phase} payments for that trial were shown and the
sequence was repeated.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/task}

}

\caption{Trust game with promises}\label{fig:figA}
\end{figure}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

Subjects came with a same-sex friend considered close by him or her, it
was emphasized that they must not have a romantic or family relationship
with their friends, to try to exclude the effect on cooperation due to a
consanguineous relationship or sexual attraction. Also, to ensure that
the subjects and their companions had a similar degree of social
closeness to each other, in the laboratory both responded to the
``Inclusion of the Other in Self'' IOS scale (Aron et al., 1997) without
observing their partner responses. The scale consists of seven pairs of
circles that vary in the degree of overlap between them, the respondent
must select the pair of circles that best represents the subjective
closeness to his partner.

Subjects were trained in the task by two of the researchers, the game
was first explained verbally, and then the computerized interface was
presented to them on a portable computer. They were told that they would
make their decisions with four buttons on the computer keyboard, which
corresponded to the levels of promises and with only two of these to
make their decision to pay back or not. Friends heard the explanation,
they were told that they would make their decisions in a separate room
on another computer. Subjects performed between 3 and 6 practice tests
together with the researcher who exemplified the course of the game when
the investor gave his budget. In the practice trials, all the phases
indicated in Figure 1 were shown, however, the identity of the investors
was replaced by question marks.

When the subjects did not report doubts we proceeded to take them
without their companions to another room where they would make their
decisions on a laptop, or, with the Lumina Cedrus response system in the
case that it was a subject to which we also performed MRI. The subjects
began the task believing that they would really play with the three
partners of different social closeness. In the other room, another of
the researchers performed the \emph{debriefing} to the companion, they
were told that the purpose of the research was to know if their mere
presence had an effect on the subject's decisions, but that to simplify
the analysis their responses were programmed \emph{a priori} so your
participation ended there.

When the subject finished the task, \emph{debriefing} was also carried
out, he was told that the decisions of his partners had been programmed.
Although no participant exercised their right, both subjects and their
friends were told that they could withdraw their participation and
informed consent if they considered disagreeing with any of the
manipulations made by researchers.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{descriptives}{%
\subsection{Descriptives}\label{descriptives}}

We analyzed 810 decisions about paying back or not (18 per subject), as
well as 180 promises (4 per subject), 69\% of the decisions, were pay
back, while the proportion of the promises selected were 5.4\%, 16.2\%,
43.8\% and 40.2\%, respectively for promises \emph{never},
\emph{sometimes}, \emph{mostly} and \emph{always}. Figure 2 shows the
payment proportion depending on the levels of promises and partners.

Breaking promises, that is, subject had promised \emph{always} and
subsequently decides not to pay back occurred only 12.4\% of trials (19
times they did not pay back of 153 when promised \emph{always}), of
which, 8.50\% (13/153) were trials with the computer, 3.92\% (6/153)
with the stranger and 0\% (0/153) with the friend. It is essential to
note that breaking the promise was not the most frequent decision, in
91.5\% of trials when they promised \emph{always} and had the computer
as a partner they decided to pay back.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig2-1}

}

\caption{Pay back proportion by partners and promises levels}\label{fig:fig2}
\end{figure}

\hypertarget{hierarchical-bayesian-modeling}{%
\subsection{Hierarchical Bayesian
Modeling}\label{hierarchical-bayesian-modeling}}

All models presented below were programmed in R via the \textbf{brms}
package (Bürkner, 2017; R Core Team, 2019), which performs the inference
using sampling by Markov chain Monte Carlo through \textbf{Stan} (Stan
Development Team, 2018). For each model, the posteriors distributions of
all parameters were approximated with four chains of 2000 iterations
each, the first 1000 iterations of each chain were discarded (burning
period), for a total of 4000 post-burning samples. Models convergence
was evaluated through visual inspection of the chains and calculation of
the \(\hat{R}\) statistic, which for all parameters was 1, which is
interpreted as convergence. Vaguely informative prior distributions were
used for the parameters of interest in the models, which allows the data
to dominate the inference, also assumes as little as possible regarding
the nature of the phenomenon, which could be adequate for the current
state of evidence in the problem we are studying (McElreath, 2018).

\hypertarget{social-closeness-between-partners}{%
\subsubsection{Social closeness between
partners}\label{social-closeness-between-partners}}

To assess social closeness, 30 (15 men) of our subjects and their
friends responded to the IOS scale (Aron et al., 1997; Fareri \&
Delgado, 2014; Sip, Smith, Porcelli, Kar, \& Delgado, 2015), which
consist of seven pairs of circles that vary in the degree of overlap and
represent the social closeness that an individual perceives with respect
to the other. A Hierarchical and Cumulative Bayesian Model (See section:
Commitment expressed in the promises), supports the hypothesis that
there are no differences in subjective social closeness between subjects
and their friends, with a posterior evidence ratio of 2.74 in its favor.

\hypertarget{effect-of-social-closeness-on-breaking-promises}{%
\subsubsection{Effect of social closeness on breaking
promises}\label{effect-of-social-closeness-on-breaking-promises}}

To evaluate the hypothesis that social closeness would reduce the
behavior of breaking the promise, we filtered all trials in which
subjects promised that they would \emph{always} pay back and then
decided not to pay. Subsequently, Bayesian inference was used to assess
the effect of partners on the decision to break the promise at the
individual and population level. For this purpose, a Hierarchical
Bayesian Model was carried out that assumes that the uncertainty in
partners effect on the decision to break the promise varies depending on
each individual, however, it also assumes that these variations belong
to common population distributions (Gelman \& Hill, 2006).

\[
\begin{aligned}
&y_i \sim \mathrm{Bernoulli}(\theta_i) \\
&\mathrm{logit(\theta_i)} = \mathbf{X}\beta  +  \mathbf{Z}u
\end{aligned}
\]

In the previous model, the decision to break the promise \(y_i\) comes
from a Bernoulli distribution with probability \(\theta_i\), the goal of
the Hierarchical Model is to predict each decision through the linear
combination of the effects of each partner, transformed by its inverse
link function \(\mathrm{logit}\) (Bürkner, 2017). In this model,
\(\beta\) and \(u\) are coefficients at the population level and
individual level respectively, while \(\mathbf{X}\), \(\mathbf{Z}\) are
their corresponding design matrices. In this case, the population
coefficients correspond to the presence of partners with no social
closeness \(\beta^{computer}\), low \(\beta^{stranger}\) and high
\(\beta^{friend}\).

Figure 3 shows the posterior probability of breaking the promise
depending on the partner, circles correspond to the medians of the
distributions of the posterior estimates effects, the thick bar, and the
thin bar correspond to the interval of 50\% and 95\% posterior
probability, respectively. It is clear that the probability of breaking
the promise decreases as social closeness increases, however, we
calculate the reasons for evidence for the following hypotheses:

\begin{itemize}
\item
  There is a greater probability to break the promise to the computer
  than the stranger.
\item
  There is more probability to break the promise to the stranger
  compared to a friend.
\end{itemize}

The evidence ratio, which is the ratio between the posterior probability
of the mentioned hypotheses and their corresponding alternative
hypotheses was 7.47 and 8.64 respectively in favor of the previous
hypotheses. As can be seen in Figure 5 in the estimate for
\(\beta^{computer}\), when there is no social closeness we have a 95\%
posterior probability that the parameter for promise-breaking is between
4-38\%, although it is a small proportion, it clearly excludes the
probability that promises are not broken.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig3-1}

}

\caption{Posterior probability of Promise Breaking}\label{fig:fig3}
\end{figure}

\hypertarget{effects-of-promises-and-social-closeness-on-cooperation}{%
\subsubsection{Effects of promises and social closeness on
cooperation}\label{effects-of-promises-and-social-closeness-on-cooperation}}

To evaluate the effect of the experimental conditions on the decision to
pay back, we used all trials were partners invest. Again, a Hierarchical
Bayesian Model was fit, which assumes that the promises and partners
have an effect that varies for each individual, however, it also assumes
that these variations belong to common population distributions. The
model estimates that the probability \(\theta_i\) of the decision to pay
back is based on the effect of the presence of promises
\(\beta^{promise}\), as well as partners with low \(\beta^{stranger}\)
and high \(\beta^{friend}\) social closeness.

Figure 4 shows the posterior distributions of the \(\beta\) coefficients
in the logit scale, the center line represents the median of the
distribution and the shaded area corresponds to the interval of 50\%
posterior probability. As can be seen, more than 95\% of the posterior
density of the population coefficients is greater than 0, which
indicates strong evidence of the effect of experimental conditions on
the decision to pay back, so that the presence of promises and the
stranger increase clearly the probability of paying, but the presence of
the friend is the condition that has the greatest effect on this
behavior. Posterior distributions clearly show that the probability of
cooperation increases as social closeness does.

Also, Figure 5 presents the posterior predictive distribution in
contrast to the proportion of decisions to each partner during the
promises phase, each panel corresponds to one of the first twelve
subjects. The responses on the dotted line would indicate that the
subject paid back random to that partner. Posterior predictive
distribution simulates observations of the model and compares them with
the actual data, it helps us to identify if the model is sufficiently
close to the process that generated the data (Lee \& Wagenmakers, 2014;
Schad, Betancourt, \& Vasishth, 2019). It can be seen that there is a
great correspondence between the subject's responses and predictions of
the model, even in cases where the model is ``wrong'' (for example,
subject 1), the observed response is in the range of a predicted
standard deviation, which gives credibility to estimates.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig4-1}

}

\caption{Posterior estimates in logit scale}\label{fig:fig4}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{article_english_files/figure-latex/fig5-1}

}

\caption{Posterior predictive over pay back rate}\label{fig:fig5}
\end{figure}

\hypertarget{effects-of-social-closeness-on-cooperation-varying-by-promises}{%
\subsubsection{Effects of social closeness on cooperation varying by
promises}\label{effects-of-social-closeness-on-cooperation-varying-by-promises}}

In this model, it is assumed that social closeness has an effect that
varies for each level of promise, which implies that there are levels of
promise that are more sensitive than others to the effect of the
partners on the decision to pay back. Again, a Hierarchical Bayesian
Model was made to estimate the effect of partners at the population
level and the variations depending on the promise levels. Table 1
summarizes the subsequent distributions of the model coefficients in the
logit scale, including point estimates, standard errors and Bayesian
Credibility Intervals of 95\%. An estimate similar to the previous
models can be observed, with strong evidence of the effect of social
closeness on the decision to pay back. Although the credibility range
for the friend's effect includes 0, the evidence ratio that the effect
is greater than zero is 15.81 with 94\% of posterior probability.

On the other hand, Figure 6 shows the posterior predictive distribution,
compared to the payment rates of all individuals to the different
partners and their variation by the level of promise. With the exception
of the promise \emph{never}, a monotonic positive effect of partners is
observed at all levels of promise, however, it can be observed how the
effect of social closeness varies depending on the strength of the
promise, mainly for the decisions towards the computer.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig6-1}

}

\caption{Posterior predictive over pay back rate, Social Closeness Varying effects by Promise levels}\label{fig:fig6}
\end{figure}

\begin{table}[!h]

\caption{\label{tab:tabla}Posterior coefficients estimates}
\centering
\begin{tabular}{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{95 \% CI} \\
\cmidrule(l{3pt}r{3pt}){4-5}
Term & Estimate & Est.Error & Lower & Upper\\
\midrule
Intercept & -0.153 & 0.536 & -1.005 & 0.617\\
Stranger & 0.829 & 0.410 & 0.128 & 1.470\\
Friend & 2.084 & 1.248 & -0.151 & 3.975\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{cumulative-bayesian-modeling}{%
\subsection{Cumulative Bayesian
Modeling}\label{cumulative-bayesian-modeling}}

\hypertarget{commitment-expressed-in-promises}{%
\subsubsection{Commitment expressed in
promises}\label{commitment-expressed-in-promises}}

In the original study of promises, authors chose to divide their sample
into two according to the hierarchical clustering technique with Ward's
method (Baumgartner et al., 2009). In this way they obtained two sets of
participants that were different in their payment rates, despite the
fact that they both made very high promises, for this reason, the
authors named the group that paid little \emph{dishonest} and the group
that paid a lot \emph{honest}. In a similar exercise, in the present
study we performed the hierarchical grouping technique to obtain a
solution of 2 groups and we found two similar sets in \(n\) that we call
the group ``Low'' and ``High'' (Low = 25, High = 20), with quite
different payment ratios (Low = 58\%, High = 83\%), and a 95\%
confidence interval of 20\% to 32\% in the difference favor of the High
group.

Although it seems a similar result to that reported in that paper, we
explore the pattern of promises of both groups to determine if it was
possible to classify our subjects as \emph{honest} and \emph{dishonest}.
If we hypothesize that the commitment to pay would be reflected in the
level of promises selected, a group of \emph{dishonest} people could
generate in their partners the belief that they will pay by choosing a
high level of promises (mostly or always) and, later, betraying that
trust when deciding not to pay back.

In order to explore whether the groups represent populations that do not
differ in the level of commitment expressed in the promises, we use a
Cumulative Bayesian Model, which assumes that the levels of promises are
an observed ordinal variable \(Y\) that originates from the
categorization of a continuous latent variable \(\tilde{Y}\), for this
case, \emph{the expressed commitment to pay back} (Bürkner \& Vuorre,
2019). The degree to which the subjects of the High group differ from
the Low group, in normal standard deviations (\(z\)-values), on the
latent scale of \(\tilde{Y}\), has a point estimate of 0.95, which
implies that the High group has 0.95 \(z\)-values greater commitment to
pay back than the Low group.

The 95\% Bayesian Credibility Interval indicates that the High group is
between 0.40 to 1.51 \(z\)-values of difference from Low. So we can
conclude with at least a 95\% probability that people belonging to the
High group expressed in their promises a greater commitment to pay back
than the subjects of the Low group. If we look at Figure 7, the
probability of choosing the different levels of promises varies
depending on the group, the one who had the highest percentage of
decisions to pay back is more likely to choose \emph{always} (High
group), while the group that had the lowest percentage of decisions to
pay back are more likely to choose \emph{mostly} (Low group).

According to our data, we could not justify the classification of our
groups according to their honesty or dishonesty, at least not with the
technique used in Baumgartner et al. (2009). Since people were quite
consistent with keeping what they promised to pay.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig7-1}

}

\caption{Promise choices by group}\label{fig:fig7}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The objective of this study was to evaluate the effect of social
closeness on keeping and breaking promises, as well as on cooperation in
a trust game. Our results give evidence that zero social closeness
increases the probability of breaking the promise and it decreases
monotonically as social closeness increases. Likewise, as social
closeness increases, so does cooperation; \emph{high} social closeness
has an effect on decisions that surpasses even those that all other
experimental conditions. The most interesting finding was that when
subjects express high commitment to cooperate (through choosing that
they would \emph{always} pay back) probability that they comply is also
quite high, however, there is a proportion of transgressions that
according to our inferences are between 4 - 38\% with 95\% certainty.

To our knowledge, this is the first experimental study that incorporates
social closeness as a predictor of the decision to break promises with
socially relevant partners. In previous studies, the participants remain
anonymous during the course of the tasks (Baumgartner et al., 2009),
their measurements to evaluate transgressions are self-reported (DePaulo
et al., 2004; DePaulo \& Kashy, 1998), they do not directly quantify the
breaking of promises (Charness \& Dufwenberg, 2006; Vanberg, 2008), or
as we will discuss later, they use heterogeneous measures of social
closeness (Glaeser, Laibson, Sceinkman, \& Soutter, 2000).

Our experiment is probably the first to include a partner without social
closeness (\emph{computer}), our data give evidence that the mere fact
of considering that subjects play with a human diminishes the
probability of breaking the promise. It is approximately 7.5 times more
likely to break the promise to the computer than to the stranger, even
though that partner was not known. In our study, zero social closeness
is important because it allows us to explore the \emph{intrinsic}
motivation to keep the promises, if humans keep their word because it is
morally correct, we would anticipate that probability of breaking the
promise was very low in the three partners and, particularly, the
inference regarding the probability of breaking the promise to the
computer would include zero.

The probability of breaking the promise without social closeness,
although low, is clearly greater than zero, which provides evidence that
contradicts, at least in degree, the hypothesis of \emph{intrinsic}
motivation. We cannot exclude the possibility that the subjects keep
promises mainly morally motivated, because even in the case of the
computer, the subjects keep a large proportion, but we can exclude that
this is their only motivation.

On the other hand, high social closeness allows us to explore the
\emph{instrumental} motivation to keep promises. In our study, it is
almost 9 times more likely to break the promise to the stranger than to
the friend; if human beings keep their word to facilitate cooperation in
the future, we would anticipate that with a partner of high social
closeness (with whom they are very likely to cooperate, even after the
experiment) there would be less chance of breaking the promise. In fact,
in our study, the promise to friends was not broken on any occasion, so
the inference, in this case, is obvious.

Our findings could be explained by the social norm called
\emph{conditional cooperation}, which indicates that the belief that
other people cooperate at high levels also induces high levels of
cooperation (Fehr \& Schurtenberger, 2018). Thus, the lack of certainty
regarding the decisions that the computer would make could explain the
probability of breaking the promise that exists towards this partner.
Similarly, the information that the subjects have regarding friend's
behavior -even before the experiment- can explain the high levels of
cooperation and keeping of promises towards this partner.

Regarding cooperation, it is not the first investigation in which the
effect of social closeness is evaluated, however, the nature of
experimental manipulation has been diverse. For example, in one study
the contribution in a public goods game was evaluated during several
trials in a group made up of the same individuals (\emph{partners}),
compared to another group of new different subjects for each trial
(\emph{strangers}) (Croson, 1996). It was assumed that in the condition
of \emph{partners} the cooperation would be greater because it is a
stable group compared to the group of \emph{strangers}. The mentioned
study does not give details regarding the recruitment of participants,
so we could assume that even in the condition of \emph{partners} these
are individuals who do not consider themselves socially close.

In another experiment, an increase in cooperation in a trust game in
pairs was reported when individuals are socially close (Glaeser et al.,
2000), in this study, subjects know each other and the researchers
carefully measured several variables regarding their social connection,
however, some individuals who arrived together were allowed to perform
the task between themselves and others were paired with unclear
criteria. The above allows social closeness between partners to be
heterogeneous, allows for romantic relationships and assumes that two
individuals who come together to class are considered close to each
other. Also, since it is a study of \emph{one-shot}, it excludes the
possibility of evaluating how the same subject varies his behavior based
on different levels of social closeness.

To try to homogenize social closeness between our subjects and their
partners, participants performed the task with a same-sex match friend
considered close by themselves, in none case was it a relative and,
although we understand that there may be same-sex couples and that the
subjects may have hidden their relationship, they were emphasized that
to be part of the study their companion could not be a romantic or
sexual partner. Besides, Bayesian analysis of the IOS scale showed
evidence in favor that the degree of social closeness between 30 of our
45 subjects and their friends was the same. Although the results of the
two studies mentioned are practically in the same direction as the
findings of our experiment, establishing the similarity in effects
magnitudes is not possible due to the design differences, the performed
tasks, and the statistical procedures used.

A methodological contribution of our study is that, in the literature of
promises, it is the first to use Bayesian inference tools:
\emph{Hierarchical Models} and \emph{Cumulative Models}. The former (aka
multilevel models), allowed us to model the effect of the experimental
conditions on the individual response, these models assume that lower
level observations (e.g.~decisions of each individual) are nested in
higher level units (e.g.~individual subjects). Within-subjects designs
have traditionally been analyzed with repeated measures AN(C)OVA,
however, \emph{Hierarchical Models} grant the advantages of naturally
dealing with unbalanced data, including categorical and/or numerical
predictors, explicitly incorporate individual variability, among others
(Bürkner, 2017; Gelman \& Hill, 2006; McElreath, 2018; Vuorre \& Bolger,
2018).

In our case, as shown in Figure 5, the \emph{Hierarchical Model} allowed
us to capture very precisely how the experimental conditions affected
the decisions of each subject and the differences between them. For
example, there are obviously motivated \emph{instrumental} subjects such
as number 8 or 12 who are very sensitive to the identity of their
investors and modify their cooperation under social closeness. At the
same time, there are notably \emph{intrinsic} subjects such as 9 and 10
who cooperate all the time regardless of who their partners are. The
\emph{Hierarchical Model} naturally includes this information for the
estimation of population effects, which, if not considered, would lead
to inaccurate inferences.

On the other hand, the \emph{Cumulative Model} allowed us to capture the
strength of the commitment expressed through promises. A very frequent
problem that has been pointed out recently is that analyzing ordinal
data with methods that assume that observations are \emph{metric} can
lead to serious inference errors (Liddell \& Kruschke, 2018). The
\emph{Cumulative Models} assume that the observed responses come from
the categorization of a continuous latent variable (Bürkner \& Vuorre,
2019), so in our study, we could identify that the groups with different
payment proportions, which in other articles have been called
\emph{dishonest} and \emph{honest}, differ in the commitment they
express through their promises. Considering that the tools to perform
the \emph{Cumulative Models} are relatively recent, it would be valuable
to replicate published studies (e.g., Baumgartner et al., 2009, 2013)
considering the new alternatives of inference.

Although the \emph{Hierarchical} and \emph{Cumulative} models are not
tools exclusively for Bayesian inference, their application from this
approach represents several advantages compared to frequentist
statistics. Classic problems of the previous one such as multiple
comparisons, the decision of when to stop collecting subjects (stopping
rule), or use of planned comparisons versus \emph{post hoc}, are not
factors that affect the support provided by the data to the hypothesis
from the Bayesian approach (Dienes, 2011). In Bayesian inference,
hypothesis testing makes formal use of probability to express the
plausibility of theories, in our case we were able to obtain evidence
ratios regarding the extent our data support hypotheses, regardless
these were proposed \emph{a priori} or \emph{post hoc}.

A limitation of this paper is the use of hypothetical rewards compared
to real rewards. A relatively recent study on decision-making reported
that there is more loss aversion when subjects have real monetary
rewards compared to hypothetical in a risk task (Xu et al., 2016).
However, other works do not report differences between the use of both
types of rewards in self-control, temporal and social discount tasks
(Johnson \& Bickel, 2006; Locey, Jones, \& Rachlin, 2011; Rachlin \&
Jones, 2006). Likewise, it can be argued that our results have
theoretical congruence (Fehr \& Schurtenberger, 2018) and are in the
same direction as other works that use real money (Croson, 1996; Glaeser
et al., 2000), so there are not many reasons to expect that other types
of rewards would modify our results.

Another possible limitation is the use of multiple trials with each
partner. Although the decision to use repeated measures during our
design serves more the purpose of reducing contaminant sources and
increasing internal validity (Maxwell, Delaney, \& Ken, 2018), to have
more clarity regarding the difference in the \emph{intrinsic} and
\emph{instrumental} motivations, the studies could benefit from only
include one trial for each partner. Play a \emph{one-shot} with each
partner avoids the possibility that multiple trials could generate the
belief that the computer can also vary its behavior according to the
decisions of the \emph{trustee}.

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

Subjects keep their promises by a combination between the
\emph{intrinsic} and \emph{instrumental} motivations. They are
predominantly \emph{nice guys} because they keep their word even with
investors with no social closeness. However, its trustworthiness is far
from perfect, since there is a small, but reliably greater than zero,
proportion of betrayals committed towards this partner. It seems that if
subjects cannot assure that their investor will be a \emph{potential
cooperator}, dishonesty may emerge in the form of broken promises. The
theoretical predictions of the social norm \emph{conditional
cooperation} frame the finding that social closeness decreases the
probability of breaking the promise and increases cooperation. In the
same way that suggests the correspondence between commitment expressed
through promises and subsequent behavior.

\hypertarget{bibliography}{%
\section*{Bibliography}\label{bibliography}}
\addcontentsline{toc}{section}{Bibliography}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Anderson2002}{}%
Anderson, D. E., DePaulo, B. M., \& Ansfield, M. E. (2002). The
development of deception detection skill: A longitudinal study of
same-sex friends. \emph{Personality and Social Psychology Bulletin},
\emph{28}(4), 536--545. \url{https://doi.org/10.1177/0146167202287010}

\leavevmode\hypertarget{ref-Aron1997}{}%
Aron, A., Melinat, E., Aron, E. N., Vallone, R. D., \& Bator, R. J.
(1997). The experimental generation of interpersonal closeness: A
procedure and some preliminary findings. \emph{Personality and Social
Psychology Bulletin}, \emph{23}(4), 363--377.
\url{https://doi.org/10.1177/0146167297234003}

\leavevmode\hypertarget{ref-Balliet2010}{}%
Balliet, D. (2010). Communication and cooperation in social dilemmas: A
meta-analytic review. \emph{Journal of Conflict Resolution},
\emph{54}(1), 39--57. \url{https://doi.org/10.1177/0022002709352443}

\leavevmode\hypertarget{ref-Baumgartner2009}{}%
Baumgartner, T., Fischbacher, U., Feierabend, A., Lutz, K., \& Fehr, E.
(2009). The Neural Circuitry of a Broken Promise. \emph{Neuron},
\emph{64}(5), 756--770.
\url{https://doi.org/10.1016/j.neuron.2009.11.017}

\leavevmode\hypertarget{ref-Baumgartner2013}{}%
Baumgartner, T., Gianotti, L. R. R., \& Knoch, D. (2013). Who is honest
and why: Baseline activation in anterior insula predicts
inter-individual differences in deceptive behavior. \emph{Biological
Psychology}, \emph{94}(1), 192--197.
\url{https://doi.org/10.1016/j.biopsycho.2013.05.018}

\leavevmode\hypertarget{ref-Burkner2017}{}%
Bürkner, P.-C. (2017). brms : An R Package for Bayesian Multilevel
Models Using Stan. \emph{Journal of Statistical Software}, \emph{80}(1).
\url{https://doi.org/10.18637/jss.v080.i01}

\leavevmode\hypertarget{ref-Burkner2019}{}%
Bürkner, P.-C., \& Vuorre, M. (2019). Ordinal Regression Models in
Psychology: A Tutorial. \emph{Advances in Methods and Practices in
Psychological Science}, \emph{2}(1), 77--101.
\url{https://doi.org/10.1177/2515245918823199}

\leavevmode\hypertarget{ref-Charness2006}{}%
Charness, G., \& Dufwenberg, M. (2006). Promises and partnership.
\emph{Econometrica}, \emph{74}(6), 1579--1601.
\url{https://doi.org/10.1111/j.1468-0262.2006.00719.x}

\leavevmode\hypertarget{ref-Croson1996}{}%
Croson, R. T. (1996). Partners and strangers revisited. \emph{Economics
Letters}, \emph{53}(1), 25--32.
\url{https://doi.org/10.1016/S0165-1765(97)82136-2}

\leavevmode\hypertarget{ref-DePaulo2004}{}%
DePaulo, B. M., Ansfield, M. E., Kirkendol, S. E., \& Boden, J. M.
(2004). Serious Lies. \emph{Basic \& Applied Social Psychology},
\emph{26}(2/3), 147--167.
\url{https://doi.org/10.1207/s15324834basp2602\&3_4}

\leavevmode\hypertarget{ref-DePaulo1998}{}%
DePaulo, B. M., \& Kashy, D. A. (1998). Everyday Lies in Close and
Casual Relationships. \emph{Journal of Personality and Social
Psychology}, \emph{74}(1), 63--79.
\url{https://doi.org/10.1037/0022-3514.74.1.63}

\leavevmode\hypertarget{ref-Dienes2011}{}%
Dienes, Z. (2011). Bayesian versus orthodox statistics: Which side are
you on? \emph{Perspectives on Psychological Science}, \emph{6}(3),
274--290. \url{https://doi.org/10.1177/1745691611406920}

\leavevmode\hypertarget{ref-Fareri2014}{}%
Fareri, D. S., \& Delgado, M. R. (2014). Differential reward responses
during competition against in- and out-of-network others. \emph{Social
Cognitive and Affective Neuroscience}, \emph{9}(4), 412--420.
\url{https://doi.org/10.1093/scan/nst006}

\leavevmode\hypertarget{ref-Fehr2003}{}%
Fehr, E., \& Fischbacher, U. (2003). The nature of human altruism.
\emph{Nature}, \emph{425}(6960), 785--791.
\url{https://doi.org/10.1038/nature02043}

\leavevmode\hypertarget{ref-Fehr2018}{}%
Fehr, E., \& Schurtenberger, I. (2018). Normative foundations of human
cooperation review-article. \emph{Nature Human Behaviour}, \emph{2}(7),
458--468. \url{https://doi.org/10.1038/s41562-018-0385-5}

\leavevmode\hypertarget{ref-Fischbacher2013a}{}%
Fischbacher, U., \& Föllmi-Heusi, F. (2013). Lies in disguise-an
experimental study on cheating. \emph{Journal of the European Economic
Association}, \emph{11}(3), 525--547.
\url{https://doi.org/10.1111/jeea.12014}

\leavevmode\hypertarget{ref-Gelman2006}{}%
Gelman, A., \& Hill, J. (2006). \emph{Data analysis using regression and
multilevel/hierarchical models.} (p. 651).
\url{https://doi.org/10.2277/0521867061}

\leavevmode\hypertarget{ref-Glaeser2000}{}%
Glaeser, E., Laibson, D., Sceinkman, J., \& Soutter, C. (2000).
Measuring Trust. \emph{The Quartely Journal of Economics},
\emph{115}(3), 811--846.

\leavevmode\hypertarget{ref-Gneezy2005}{}%
Gneezy, U. (2005). Deception: The role of consequences. \emph{American
Economic Review}, \emph{95}(1), 384--394.
\url{https://doi.org/10.1257/0002828053828662}

\leavevmode\hypertarget{ref-Gneezy2013}{}%
Gneezy, U., Rockenbach, B., \& Serra-Garcia, M. (2013). Measuring lying
aversion. \emph{Journal of Economic Behavior and Organization},
\emph{93}, 293--300. \url{https://doi.org/10.1016/j.jebo.2013.03.025}

\leavevmode\hypertarget{ref-Holt-Lunstad2018}{}%
Holt-Lunstad, J. (2018). Why Social Relationships are Important for
Physical Health: A Systems Approach to Understanding and Modifying Risk
and Protection. \emph{Ssrn}, (October 2017), 1--22.
\url{https://doi.org/10.1146/annurev-psych-122216-011902}

\leavevmode\hypertarget{ref-Johnson2006}{}%
Johnson, M. W., \& Bickel, W. K. (2006). Within-subject comparison of
real and hypothetical money rewards in delay discounting. \emph{Journal
of the Experimental Analysis of Behavior}, \emph{77}(2), 129--146.
\url{https://doi.org/10.1901/jeab.2002.77-129}

\leavevmode\hypertarget{ref-Kessler2019}{}%
Kessler, G., Rizzo, S., \& Kelly, M. (2019). President Trump has made
more than 10,000 false or misleading claims. Retrieved from
\href{https://www.washingtonpost.com/politics/2019/06/10/president-trump-has-made-false-or-misleading-claims-over-days/?utm\%7B/_\%7Dterm=.8565a16aa5e8}{https://www.washingtonpost.com/politics/2019/06/10/president-trump-has-made-false-or-misleading-claims-over-days/?utm\{\textbackslash{}\_\}term=.8565a16aa5e8}

\leavevmode\hypertarget{ref-Lee2014}{}%
Lee, M. D., \& Wagenmakers, E.-J. (2014). \emph{Bayesian Cognitive
Modeling}. \url{https://doi.org/10.1017/cbo9781139087759}

\leavevmode\hypertarget{ref-Liddell2018}{}%
Liddell, T. M., \& Kruschke, J. K. (2018). Analyzing ordinal data with
metric models: What could possibly go wrong? \emph{Journal of
Experimental Social Psychology}, \emph{79}(November 2017), 328--348.
\url{https://doi.org/10.1016/j.jesp.2018.08.009}

\leavevmode\hypertarget{ref-Locey2011}{}%
Locey, M. L., Jones, B. A., \& Rachlin, H. (2011). Real and hypothetical
rewards in self-control and social discounting. \emph{Judgment and
Decision Making}, \emph{6}(6), 552--564.

\leavevmode\hypertarget{ref-Maxwell2018}{}%
Maxwell, S. E., Delaney, H. D., \& Ken, K. (2018). \emph{Designing
experiments and analyzing data: a model comparison perspective} (3rd
edition, pp. 611--612). New York: Routledge.

\leavevmode\hypertarget{ref-Mazar2008}{}%
Mazar, N., Amir, O., \& Ariely, D. (2008). The Dishonesty of Honest
People: A Theory of Self-Concept Maintenance. \emph{Journal of Marketing
Research}, \emph{45}(6), 633--644.
\url{https://doi.org/10.1509/jmkr.45.6.633}

\leavevmode\hypertarget{ref-McElreath2018}{}%
McElreath, R. (2018). \emph{Statistical rethinking: A bayesian course
with examples in R and stan}.
\url{https://doi.org/10.1201/9781315372495}

\leavevmode\hypertarget{ref-Peirce2019}{}%
Peirce, J., Gray, J. R., Simpson, S., MacAskill, M., Höchenberger, R.,
Sogo, H., \ldots{} Lindeløv, J. K. (2019). PsychoPy2: Experiments in
behavior made easy. \emph{Behavior Research Methods}, \emph{51}(1),
195--203. \url{https://doi.org/10.3758/s13428-018-01193-y}

\leavevmode\hypertarget{ref-Peirce2008}{}%
Peirce, J. W. (2008). Generating stimuli for neuroscience using
PsychoPy. \emph{Frontiers in Neuroinformatics}, \emph{2}.
\url{https://doi.org/10.3389/neuro.11.010.2008}

\leavevmode\hypertarget{ref-Rachlin2006}{}%
Rachlin, H., \& Jones, B. (2006). Social Discounting.
\emph{Psychological Science}, \emph{17}(4), 283--286.

\leavevmode\hypertarget{ref-R2019}{}%
R Core Team. (2019). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.
Retrieved from \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-Schad2019}{}%
Schad, D., Betancourt, M., \& Vasishth, S. (2019). Toward a principled
Bayesian workflow in cognitive science. Retrieved from
\url{osf.io/b2vx9}

\leavevmode\hypertarget{ref-Sip2015}{}%
Sip, K. E., Smith, D. V., Porcelli, A. J., Kar, K., \& Delgado, M. R.
(2015). Social closeness and feedback modulate susceptibility to the
framing effect. \emph{Social Neuroscience}, \emph{10}(1), 35--45.
\url{https://doi.org/10.1080/17470919.2014.944316}

\leavevmode\hypertarget{ref-GSS2018}{}%
Smith, T., Davern, M., Freese, J., \& Hout, M. (2018). GSS Data Explorer
\textbar{} NORC at the University of Chicago. Retrieved from
\url{https://gssdataexplorer.norc.org/variables/5067/vshow}

\leavevmode\hypertarget{ref-Rstan2018}{}%
Stan Development Team. (2018). RStan: The R interface to Stan. Retrieved
from \url{http://mc-stan.org/}

\leavevmode\hypertarget{ref-Tough2017}{}%
Tough, H., Siegrist, J., \& Fekete, C. (2017). Social relationships,
mental health and wellbeing in physical disability: A systematic review.
\emph{BMC Public Health}, \emph{17}(1), 1--18.
\url{https://doi.org/10.1186/s12889-017-4308-6}

\leavevmode\hypertarget{ref-Vanberg2008}{}%
Vanberg, C. (2008). Why Do People Keep Their Promises? An Experimental
Test of Two Explanations1. \emph{Econometrica}, \emph{76}(6),
1467--1480. \url{https://doi.org/10.3982/ECTA7673}

\leavevmode\hypertarget{ref-Vuorre2018}{}%
Vuorre, M., \& Bolger, N. (2018). Within-subject mediation analysis for
experimental data in cognitive psychology and neuroscience.
\emph{Behavior Research Methods}, \emph{50}(5), 2125--2143.
\url{https://doi.org/10.3758/s13428-017-0980-9}

\leavevmode\hypertarget{ref-Xu2016}{}%
Xu, S., Pan, Y., Wang, Y., Spaeth, A. M., Qu, Z., \& Rao, H. (2016).
Real and hypothetical monetary rewards modulate risk taking in the
brain. \emph{Scientific Reports}, \emph{6}.
\url{https://doi.org/10.1038/srep29520}

\end{document}

### 2019-07-29 article_english.Rmd
latex template
Translation

@@
 In the laboratory, these transgressions to trust have been explicitly studied in experiments where subjects have incentives to lie or not keep their promises.
-However, the vast majority of these studies in economics, psychology and neurosciences have been conducted in people who do NOT know each other [to name a few, @Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
+However, the vast majority of these studies in economics, psychology, and neurosciences have been conducted in people who do NOT know each other [to name a few, @Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
 In social psychology some studies address deception in close interpersonal relationships, however, they use self-report measurements [@DePaulo1998; @DePaulo2004] or rather explore the development of deception detection skills in same-sex friends [@Anderson2002].
@@
 In this manuscript, we explore the effects of three partners with different levels of social closeness on keeping or breaking promises, as well as on cooperation in a trust game.
-The above, we analyze it in the light of the two main motivations that have been pointed out in the literature regarding keeping promises [@Baumgartner2009]:
+The above, we analyze it in light of the two main motivations that have been pointed out in the literature regarding keeping promises [@Baumgartner2009]:
 
@@
 
-Subjects keep their promises by a combination between the _intrinsic_ and _instrumental_ motivations.
+Subjects keep their promises by a combination of _intrinsic_ and _instrumental_ motivations.
 They are predominantly _nice guys_ because they keep their word even with investors with no social closeness.

### 2019-07-29 article_english.tex
Translation

@@
 their promises. However, the vast majority of these studies in
-economics, psychology and neurosciences have been conducted in people
+economics, psychology, and neurosciences have been conducted in people
 who do NOT know each other (to name a few, Gneezy, 2005; Baumgartner,
@@
 different levels of social closeness on keeping or breaking promises, as
-well as on cooperation in a trust game. The above, we analyze it in the
+well as on cooperation in a trust game. The above, we analyze it in
 light of the two main motivations that have been pointed out in the
@@
 
-Subjects keep their promises by a combination between the
-\emph{intrinsic} and \emph{instrumental} motivations. They are
-predominantly \emph{nice guys} because they keep their word even with
-investors with no social closeness. However, its trustworthiness is far
-from perfect, since there is a small, but reliably greater than zero,
-proportion of betrayals committed towards this partner. It seems that if
-subjects cannot assure that their investor will be a \emph{potential
-cooperator}, dishonesty may emerge in the form of broken promises. The
-theoretical predictions of the social norm \emph{conditional
-cooperation} frame the finding that social closeness decreases the
-probability of breaking the promise and increases cooperation. In the
-same way that suggests the correspondence between commitment expressed
-through promises and subsequent behavior.
+Subjects keep their promises by a combination of \emph{intrinsic} and
+\emph{instrumental} motivations. They are predominantly \emph{nice guys}
+because they keep their word even with investors with no social
+closeness. However, its trustworthiness is far from perfect, since there
+is a small, but reliably greater than zero, proportion of betrayals
+committed towards this partner. It seems that if subjects cannot assure
+that their investor will be a \emph{potential cooperator}, dishonesty
+may emerge in the form of broken promises. The theoretical predictions
+of the social norm \emph{conditional cooperation} frame the finding that
+social closeness decreases the probability of breaking the promise and
+increases cooperation. In the same way that suggests the correspondence
+between commitment expressed through promises and subsequent behavior.
 

### 2019-08-08 article_english.Rmd
Updating manuscript.

@@
 ---
-title: "Nice guys or potential cooperators when keeping promises: an experimental and Bayesian account for two explanations"
+title: "Nice people or potential cooperators when keeping promises: an experimental and Bayesian account for two explanations"
 author: "Said Jiménez"
-date: "July 2019"
+date: "August 2019"
 output:  
@@
 
-Human beings are social animals and we get advantages from being so.
-Historically, belonging to a social group has provided protection and guaranteed access to resources such as food, currently there has been evidence that belonging to a social circle has a positive effect on longevity, physical and mental health [@Tough2017; @Holt-Lunstad2018].
-The interrelation between social closeness and cooperation is key to the formation of large groups of individuals without a genetic relationship, such groups form the basis of communities, societies, and nations, as well as probably constitute one of the most fundamental conditions for human survival [@Fehr2003; @Fehr2018].
+Human are social animals and we get survival advantages from being such.
+Historically, belonging to a social group has provided protection and guaranteed access to resources such as food, and currently, there has been evidence that belonging to a social group has a positive effect on longevity, physical and mental health [@Tough2017; @Holt-Lunstad2018].
+The relationship between social closeness and cooperation is key to the formation of large groups of individuals without a genetic relationship, and such groups form the basis of communities, societies, and nations, arguably constituting one of the most fundamental conditions for human survival [@Fehr2003; @Fehr2018].
+An important requirement for cooperation between individuals is communication.
+A meta-analysis of 45 studies reported a large positive effect ($d =  1.01$) of communication in cooperation regardless of the communication medium [@Balliet2010].
+In parallel, it is known that after communication sessions between completely unknown individuals there is an increase in subjective social closeness [@Aron1997].
+Thus, these findings suggest a positive relationship between communication, cooperation, and social closeness.
 
-An important requirement for cooperation between individuals is communication, a meta-analysis of 45 studies reported a large positive effect ($d =  1.01$) of communication in cooperation regardless of the communication medium [@Balliet2010].
-In parallel, it is known that after communication sessions between completely unknown individuals there is an increase in subjective social closeness [@Aron1997].
-Thus, the findings suggest a positive relationship between communication, cooperation, and social closeness.
+One of the forms of communication that have received the most attention in psychological game theory is "the promise".
+In an interaction between sender and recipient, it is believed that promises influence beliefs of the recipient, generating trust and cooperation [@Charness2006; @Vanberg2008].
+However, there are situations where trust is betrayed, promises are broken or people deceived.
+The General Social Survey (GSS) in 2018 showed that approximately 11% of people surveyed responded that they have had sex with someone different to their partner while they are married [@GSS2018].
+In economic and social terms, the United Nations Organization has stressed that deception (corruption) has a global cost of at least 5 percent of the annual gross domestic product (GDP), and it is a generator of conflict and instability in all nations [@UN2018].
 
-One of the forms of communication that have received the most attention in psychological game theory is the promise, in an interaction between sender and recipient, it is believed that promises influence beliefs of the recipient, generating trust and cooperation [@Charness2006; @Vanberg2008].
-However, there are situations where trust is betrayed, promises are broken or people deceive, for example, approximately 11% of people surveyed by the General Social Survey (GSS) in 2018 responded that they have had sex with someone different to their partner while they are married [@GSS2018].
-Another example, according to the Washington Post, President Trump has said 10,796 false or misleading statements in 869 days in office [@Kessler2019].
+Despite the widespread presence of interactions between human belonging to the same group, it is not known how social closeness between participants can affect keeping or breaking promises.
+This is important because it has been pointed out that lies and betrayals of trust occur daily in close relationships, such as friends, workmates, or classmates.
+And, their consequences can be serious such as loss of the relationship, work or damage to reputation [@DePaulo2004].
+In the laboratory, these transgressions to trust have been explicitly studied in experiments where subjects have incentives to lie or not keep their promises.
+However, the vast majority of these studies have been conducted in people who do NOT know each other [@Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
+Some studies address deception in close interpersonal relationships using self-report measurements, however, they have limitations due to social desirability bias [@DePaulo1998; @DePaulo2004] or rather explore the development of deception detection skills in same-sex friends [@Anderson2002].
 
-In the laboratory, these transgressions to trust have been explicitly studied in experiments where subjects have incentives to lie or not keep their promises.
-However, the vast majority of these studies in economics, psychology, and neurosciences have been conducted in people who do NOT know each other [to name a few, @Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
-In social psychology some studies address deception in close interpersonal relationships, however, they use self-report measurements [@DePaulo1998; @DePaulo2004] or rather explore the development of deception detection skills in same-sex friends [@Anderson2002].
-Despite the widespread presence of interactions between human beings belonging to the same group, it is not known how social closeness between subjects can affect keeping or breaking promises.
-
-In this manuscript, we explore the effects of three partners with different levels of social closeness on keeping or breaking promises, as well as on cooperation in a trust game.
-The above, we analyze it in light of the two main motivations that have been pointed out in the literature regarding keeping promises [@Baumgartner2009]:
+In this study, we wanted to understand the effects of three partners with different levels of social closeness on keeping or breaking promises, as well as on cooperation, using an experimental trust game.
+We analyzed it in light of the two main motivations that have been pointed out in the literature regarding keeping promises which are: instrumental and intrinsic [@Baumgartner2009]:
 
@@
 In our study, subjects perform a standard trust game in pairs with three phases: _first_, the trustee makes a promise to pay half of his earnings regardless of who his investor is; _second_, the investor receives the promise and decides if he invests his initial budget; _third_, in case the investor has given the budget, the trustee faces the decision to pay or not to pay half of his earnings.
-To evaluate the effect of social closeness, our subjects participate in the role of trustee in front of three partners with different levels of social closeness (zero, low and high) in the role of the investor: a _computer_, a _stranger_, and a _friend_.
-
-The manipulations mentioned allow us to evaluate several hypotheses, the first one was proposed a priori and is derived from a larger research project (you can check the pre-registration of the hypothesis here: https://osf.io/u97fd), while the following are exploratory:
+To evaluate the effect of social closeness, our subjects participate in the role of trustee in front of three partners with different levels of social closeness (null, low and high) in the role of the investor: a computer, a stranger, and a friend.
+The manipulations mentioned allow us to evaluate several hypotheses, the first one was proposed a priori and is derived from a larger research project (you can check the preregistration of the hypothesis here: https://osf.io/u97fd), while the following are exploratory:
 
@@
 Finally, we anticipate that the participants break the promises to the computer because it is a partner without social closeness and they could not ensure cooperation in future trials.
-It should be noted that if the participants keep the promises to the computer, evidence would be given in favor of intrinsic motivation.
+It should be noted that if the participants keep the promises to the computer, evidence would be given in favor of _intrinsic_ motivation.
 
@@
 There will be an effect of social closeness on cooperation, regardless of promises.
-We expect that there is more probability of paying the _friend_ than the _stranger_ and more probability of paying the stranger than the _computer_.
-According to the _instrumental_ motivation, the cooperation will be greater for partners with whom the subject anticipates greater cooperation in the future (friend > stranger > computer).
+We expect that there is more probability of paying the friend than the stranger and more probability of paying the stranger than the computer.
+According to the _instrumental motivation_, the cooperation will be greater for partners with whom the subject anticipates greater cooperation in the future (friend > stranger > computer).
 
@@
 Finally, we will obtain two subsamples according to the cooperation rate of the subjects as was done in another study [@Baumgartner2009].
-However, what in the aforementioned study was classified as a group of _honest_ and _dishonest_, we will show that in our sample it is not supported because if the groups differ in their payment rate it will be due to the difference in their level of commitment expressed by promises.
+However, what in the aforementioned study was classified as a group of "honest" and "dishonest", we will show that in our sample it is not supported because if the groups differ in their payment rate it will be due to the difference in their level of commitment expressed by promises.
 
@@
 
-We included 45 subjects (15 men), recruited from the National Autonomous University of Mexico, the age range from 19 to 33 years and their minimum educational level were bachelor's degrees.
-Subjects went to the study with a friend considered _close_ by themselves, who fulfilled the following characteristics: he was matched by sex, did not have a family bond and was not a person with a sentimental or sexual relationship.
-30 subjects (15 men) performed the task within a Magnetic Resonance Imaging (MRI) scanner, however, their image data is not analyzed in the present work.
+We recruited 45 subjects (15 male) from the National Autonomous University of Mexico, the age range from 19 to 33 years and their minimum educational level were bachelor.
+Subjects were asked to come to the study with a “close” friend, who fulfilled the following characteristics: 1) he/she was matched by sex, 2) did not have a family bond and 3) was not a person with a sentimental or sexual relationship.
+From this sample, 30 subjects (15 men) performed the task in a magnetic resonance imaging (MRI) scanner, however, their image data was not analyzed for the present work.
 
@@
 All subjects performed an adaptation of the trust game with promises, using hypothetical monetary rewards [@Baumgartner2009].
+The variation with respect to the original task is that in our experiment three partners were presented with three levels of social closeness in the role of the investor: computer (no closeness), strange (low closeness) and friend (high closeness), while the participant acted as the trustee.
 The task was programmed in PsychoPy2 version 1.84.2 [@Peirce2019; @Peirce2008] and consisted of 24 trials between two players: trustee and investor.
 The trustee originally has 0 Mexican pesos and the investor has 2 pesos, the investor is presented with the opportunity to give his money to the trustee or keep it.
-If he invests his money it is multiplied by 5 pesos, so that the trustee has 10 pesos.
+If investor gives his money, it is multiplied by 5 pesos, so that the trustee has 10 pesos.
 Finally, the trustee decides to pay half to the investor or keep the 10 pesos.
-
-The structure described is repeated in 24 trials, however, in 4 of the trials the trustee can send a promise to the investor, the promises were that _always_, _mostly_, _sometimes_,  or _never_ would pay back.
+The structure described is repeated in 24 trials, however, in 4 of the trials the trustee can send a promise to the investor, the promises were that always, mostly, sometimes, or never would pay back.
 Each promise was valid for three trials so that 12 of the trials have the effect of the promise and the other 12 do not.
-It is worth mentioning that the promises are not made to a particular partner, but the subject expresses their commitment level to pay back regardless of who their partners are in the next three trials in which the promise is valid.
-
-The variation with respect to the original task is that in our experiment three partners were presented with three levels of social closeness in the role of the investor: *computer* (no closeness), *strange* (low closeness) and *friend* (high closeness), while the subject acts as the trustee.
 Each partner performs the role of investor in 8 of 24 total trials, however, both the promises and social closeness conditions were presented to the trustee in pseudorandom order.
 
-Since our main interest was the trustee's behavior, investors' decisions were programmed _a priori_ to give their amount in 6 trials and in 2 did not.
-The covert story for all our subjects was that they would be playing in real-time with their friend, the stranger (was told he would be another same-sex unknown person) and the computer.
-A diagram of the chronology of the experimental task with the duration of each phase in seconds is shown in Figure 1, each box from left to right represents a screen that was shown to the subjects sequentially.
-Section A$_1$ corresponds to an example of trials without promises and section A$_2$ to trials with promises.
+Since our main interest was the trustee’s behavior, investors’ decisions were programmed _a priori_ to give their amount in 6 trials and in 2 did not randomly.
+The covert story for all our subjects was that they would be playing in real-time with their friend (whom they brought to the study), the stranger (was told he would be another same-sex unknown person) and the computer.
+After the study ended, the participants were debriefed about our own deception.
+A diagram of the chronology of the experimental task with the duration of each phase in seconds is shown in Figure 1.
 
-Fixation phase consisted only of a period in which the subject paid attention without performing any particular behavior, then, **promises phase** in part A$_1$ indicated to the subject that the following three trials they could decide without the effect of the promise, while in A$_2$  the subject was asked to decide between _always_, _mostly_, _sometimes_ or _never_ pay back.
-This was followed by another fixation period, subsequently, trails in both A$_1$ and A$_2$ continue in the same way.
-
-In the **anticipation/assignation phase**, subjects were told who their partner was for that trial (computer, stranger or friend) and was given the message that their partner was making their decision.
-Later in the **decision phase**, the subject was informed if his partner invested his $2 or not, he was reminded of his promise level (if they were trails with promises) and, in case of his partner had invested, he was asked to decide whether to pay back or not.
-Finally, in **feedback phase** payments for that trial were shown and the sequence was repeated.
-
-```{r figA, fig.cap='Trust game with promises'}
+```{r figA, fig.cap='Trust game with promises, each box from left to right represents a screen that was shown to the subjects sequentially.
+Section A1 corresponds to an example of trials without promises and section A2 to trials with promises.'}
 
@@
 
+Fixation phase consisted only of a period in which the subject paid attention without performing any particular behavior.
+Then, **promises phase** in part A1 indicated that in the following three trials they could decide without the effect of the promise.
+In A2, the subject was asked to decide between 1) always, 2) mostly, 3) sometimes or 4) never pay back.
+This pattern was repeated.
+In the **anticipation/assignation phase**, subjects were told who their partner was for that trial (computer, stranger or friend) and was given the message that their partner was making their decision.
+Later in the **decision phase**, the subject was informed if his partner invested his $2 or not, he was reminded of his promise level (if they were trails with promises) and, in case the partner had invested, he was asked to decide whether to pay back or not.
+Finally, payments for each trial were shown in the **feedback phase** and the sequence was repeated until the task finished.
+
 ## Procedure
 
-Subjects came with a same-sex friend considered close by him or her, it was emphasized that they must not have a romantic or family relationship with their friends, to try to exclude the effect on cooperation due to a consanguineous relationship or sexual attraction.
-Also, to ensure that the subjects and their companions had a similar degree of social closeness to each other, in the laboratory both responded to the "Inclusion of the Other in Self" IOS scale [@Aron1997] without observing their partner responses.
+Subjects came to the lab with a same-sex friend considered close by him or her.
+It was emphasized that they must not have a romantic or family relationship with their friends, to try to exclude the effect on cooperation due to a consanguineous relationship or sexual attraction.
+Also, to ensure that the subjects and their companions had a similar degree of social closeness to each other, both responded the "Inclusion of the Other in Self" IOS scale [@Aron1997] without observing their partner responses.
 The scale consists of seven pairs of circles that vary in the degree of overlap between them, the respondent must select the pair of circles that best represents the subjective closeness to his partner.
+Subjects were trained in the main task by two researchers, the game was first explained verbally, and then the computer interface was presented on a portable computer.
+They were told that they would make their decisions with four buttons on the computer keyboard, which corresponded to the levels of promises and with only two of these to make their decision to pay back or not.
+Friends heard the explanation, they were told that they would make their decisions in a separate room on another computer even though they were not.
+Subjects performed between 3 and 6 practice tests together with the researcher who exemplified the course of the game when the investor gave his budget.
+When the subjects were ready, we proceeded to take them without their companions to another room (or MRI scanner it that was the case) where they would perform the task.The subjects began the task believing that they would really play with the three partners of different social closeness.
+In the other room, we debriefed the companion about the deception.
+When the subject finished the task, they were debriefed.
+Although no participant exercised their right, both subjects and their friends were told that they could withdraw their participation and informed consent if they considered disagreeing with any of the manipulations made by the researchers.
 
-Subjects were trained in the task by two of the researchers, the game was first explained verbally, and then the computerized interface was presented to them on a portable computer.
-They were told that they would make their decisions with four buttons on the computer keyboard, which corresponded to the levels of promises and with only two of these to make their decision to pay back or not.
-Friends heard the explanation, they were told that they would make their decisions in a separate room on another computer.
-Subjects performed between 3 and 6 practice tests together with the researcher who exemplified the course of the game when the investor gave his budget.
-In the practice trials, all the phases indicated in Figure 1 were shown, however, the identity of the investors was replaced by question marks.
+## Bayesian Modeling
 
-When the subjects did not report doubts we proceeded to take them without their companions to another room where they would make their decisions on a laptop, or, with the Lumina Cedrus response system in the case that it was a subject to which we also performed MRI.
-The subjects began the task believing that they would really play with the three partners of different social closeness.
-In the other room, another of the researchers performed the _debriefing_ to the companion, they were told that the purpose of the research was to know if their mere presence had an effect on the subject's decisions, but that to simplify the analysis their responses were programmed _a priori_ so your participation ended there.
-
-When the subject finished the task, _debriefing_ was also carried out, he was told that the decisions of his partners had been programmed.
-Although no participant exercised their right, both subjects and their friends were told that they could withdraw their participation and informed consent if they considered disagreeing with any of the manipulations made by researchers.
+All models presented below were programmed in R via the **brms** package [@Burkner2017; @R2019], which performs the inference using sampling by Markov chain Monte Carlo through **Stan** [@Rstan2018].
+For each model, the posteriors distributions of all parameters were approximated with four chains of 2000 iterations each, the first 1000 iterations of each chain were discarded (burning period), for a total of 4000 post burning samples.
+Models convergence was evaluated through visual inspection of the chains and calculation of the $\hat{R}$ statistic, which for all parameters was 1, that can be interpreted as convergence.
+Vaguely informative prior distributions were used for the parameters of interest in the models, which allows the data to dominate the inference, also assumes as little as possible regarding the nature of the phenomenon, which could be adequate for the current state of evidence in the problem we are studying [@McElreath2018].
 
@@
 
-We analyzed 810 decisions about paying back or not (18 per subject), as well as 180 promises (4 per subject), 69% of the decisions,  were pay back, while the proportion of the promises selected were 5.4%, 16.2%, 43.8% and 40.2%, respectively for promises _never_, _sometimes_, _mostly_ and _always_.
+We analyzed 810 decisions about paying back or not (18 per subject), as well as 180 promises (4 per subject).
+69% of the decisions, were pay back, while the proportion of the promises selected were never = 5.4%, sometimes = 16.2%, mostly = 43.8% and always = 40.2%.
 Figure 2 shows the payment proportion depending on the levels of promises and partners.
-
-Breaking promises, that is, subject had promised _always_ and subsequently decides not to pay back occurred only 12.4% of trials (19 times they did not pay back of 153 when promised _always_), of which, 8.50% (13/153) were trials with the computer, 3.92% (6/153) with the stranger and 0% (0/153) with the friend.
-It is essential to note that breaking the promise was not the most frequent decision, in 91.5% of trials when they promised _always_ and had the computer as a partner they decided to pay back.
+Breaking promises, meaning the subject had promised always and subsequently decides not to pay back, occurred only in 12.4% of trials (19 times they did not pay back of 153 when promised always), of which, 8.50% (13/153) were trials with the computer, 3.92% (6/153) with the stranger and 0% (0/153) with the friend.
+It is essential to note that breaking the promise was not the most frequent decision, when they promised always and had the computer as a partner, they decided to pay back in 91.5% of trials.
 
@@
 
-## Hierarchical Bayesian Modeling
-
-All models presented below were programmed in R via the **brms** package [@Burkner2017; @R2019], which performs the inference using sampling by Markov chain Monte Carlo through **Stan** [@Rstan2018].
-For each model, the posteriors distributions of all parameters were approximated with four chains of 2000 iterations each, the first 1000 iterations of each chain were discarded (burning period), for a total of 4000 post-burning samples.
-Models convergence was evaluated through visual inspection of the chains and calculation of the $\hat{R}$ statistic, which for all parameters was 1, which is interpreted as convergence.
-Vaguely informative prior distributions were used for the parameters of interest in the models, which allows the data to dominate the inference, also assumes as little as possible regarding the nature of the phenomenon, which could be adequate for the current state of evidence in the problem we are studying [@McElreath2018].
-
 ### Social closeness between partners
 
-To assess social closeness, 30 (15 men) of our subjects and their friends responded to the IOS scale [@Aron1997; @Fareri2014; @Sip2015], which consist of seven pairs of circles that vary in the degree of overlap and represent the social closeness that an individual perceives with respect to the other.
+To assess social closeness, 30 (15 men) of our subjects and their friends responded to the IOS scale [@Aron1997; @Fareri2014; @Sip2015], which consists of seven pairs of circles that vary in the degree of overlap and represent the social closeness that an individual perceives with respect to the other.
 A Hierarchical and Cumulative Bayesian Model (See section: Commitment expressed in the promises), supports the hypothesis that there are no differences in subjective social closeness between subjects and their friends, with a posterior evidence ratio of 2.74 in its favor.
+
+## Hierarchical Bayesian Modeling
 
@@
 
-To evaluate the hypothesis that social closeness would reduce the behavior of breaking the promise, we filtered all trials in which subjects promised that they would _always_ pay back and then decided not to pay.
+To evaluate the hypothesis that social closeness would reduce the behavior of breaking the promise, we filtered all trials in which subjects promised that they would always pay back and then decided not to pay.
 Subsequently, Bayesian inference was used to assess the effect of partners on the decision to break the promise at the individual and population level.
@@
 The evidence ratio, which is the ratio between the posterior probability of the mentioned hypotheses and their corresponding alternative hypotheses was 7.47 and 8.64 respectively in favor of the previous hypotheses.
-As can be seen in Figure 5 in the estimate for $\beta^{computer}$, when there is no social closeness we have a 95% posterior probability that the parameter for promise-breaking is between 4-38%, although it is a small proportion, it clearly excludes the probability that promises are not broken.
+As seen in Figure 5 in the estimate for $\beta^{computer}$, no social closeness, we have a 95% posterior probability that the parameter for promise-breaking is between 4-38%, although it is a small proportion, it clearly excludes the probability that promises are not broken.
 
@@
 Figure 4 shows the posterior distributions of the $\beta$ coefficients in the logit scale, the center line represents the median of the distribution and the shaded area corresponds to the interval of 50% posterior probability.
-As can be seen, more than 95% of the posterior density of the population coefficients is greater than 0, which indicates strong evidence of the effect of experimental conditions on the decision to pay back, so that the presence of promises and the stranger increase clearly the probability of paying, but the presence of the friend is the condition that has the greatest effect on this behavior.
+As shown, more than 95% of the posterior density of the population coefficients is greater than 0, which shows strong evidence of the effect of experimental conditions on the decision to pay back, although the presence of promises and the stranger clearly increase the probability of paying, the presence of the friend is the condition that has the greatest effect on this behavior.
 Posterior distributions clearly show that the probability of cooperation increases as social closeness does.
-
-Also, Figure 5 presents the posterior predictive distribution in contrast to the proportion of decisions to each partner during the promises phase, each panel corresponds to one of the first twelve subjects.
-The responses on the dotted line would indicate that the subject paid back random to that partner.
-Posterior predictive distribution simulates observations of the model and compares them with the actual data, it helps us to identify if the model is sufficiently close to the process that generated the data [@Schad2019; @Lee2014].
-It can be seen that there is a great correspondence between the subject's responses and predictions of the model, even in cases where the model is "wrong" (for example, subject 1), the observed response is in the range of a predicted standard deviation, which gives credibility to estimates.
 
@@
 ```
+
+Figure 5 shows the posterior predictive distribution in contrast to the proportion of decisions to each partner during the promises phase, and each panel corresponds to one of the first twelve subjects.
+The responses on the dotted line would indicate that the subject paid back random to that partner.
+Posterior predictive distribution simulates observations of the model and compares them with the actual data, it helps us to identify if the model is sufficiently close to the process that generated the data [@Schad2019; @Lee2014].
+It can be seen that there is a great correspondence between the subject’s responses and predictions of the model.
+Even in cases where the model is "wrong" (for example, subject 1), the observed response is in the range of a predicted standard deviation, which gives credibility to estimates.
 
@@
 
-In this model, it is assumed that social closeness has an effect that varies for each level of promise, which implies that there are levels of promise that are more sensitive than others to the effect of the partners on the decision to pay back.
+In this model, it is assumed that social closeness has an effect that varies for each level of promise, which implies that there are levels of promise that are more sensitive than others to the effect of the partner’s on the decision to pay back.
 Again, a Hierarchical Bayesian Model was made to estimate the effect of partners at the population level and the variations depending on the promise levels.
@@
 An estimate similar to the previous models can be observed, with strong evidence of the effect of social closeness on the decision to pay back.
-Although the credibility range for the friend's effect includes 0, the evidence ratio that the effect is greater than zero is 15.81 with 94% of posterior probability.
-
-On the other hand, Figure 6 shows the posterior predictive distribution, compared to the payment rates of all individuals to the different partners and their variation by the level of promise.
-With the exception of the promise _never_, a monotonic positive effect of partners is observed at all levels of promise, however, it can be observed how the effect of social closeness varies depending on the strength of the promise, mainly for the decisions towards the computer.
+Although the credibility range for the friend’s effect includes 0, the evidence ratio that the effect is greater than zero is 15.81 with 94% of posterior probability.
 
@@
 ```
+
+On the other hand, Figure 6 shows the posterior predictive distribution, compared to the payment rates of all individuals to the different partners and their variation by the level of promise.
+With the exception of the promise never, a monotonic positive effect of partners is observed at all levels of promise.
+However, we also observe how the effect of social closeness varies depending on the strength of the promise, mainly for the decisions towards the computer.
 
@@
 
-In the original study of promises, authors chose to divide their sample into two according to the hierarchical clustering technique with Ward's method  [@Baumgartner2009].
-In this way they obtained two sets of participants that were different in their payment rates, despite the fact that they both made very high promises, for this reason, the authors named the group that paid little _dishonest_ and the group that paid a lot _honest_.
-In a similar exercise, in the present study we performed the hierarchical grouping technique to obtain a solution of 2 groups and we found two similar sets in $n$ that we call the group "Low" and "High" (Low = 25, High = 20), with quite different payment ratios (Low = 58%, High = 83%), and a 95% confidence interval of 20% to 32% in the difference favor of the High group.
+In the original study of promises, authors chose to divide their sample into two according to the hierarchical clustering technique with Ward’s method [@Baumgartner2009].
+In this way they obtained two sets of participants that were different in their payment rates, despite the fact that they both made very high promises.
+For this reason, the authors named the group that paid little as "dishonest" and the group that paid a lot as "honest".
+In a similar exercise, in the present study we performed the hierarchical grouping technique to obtain a solution for two groups and we found two similar sets in n that we call the group "Low" and "High" (Low = 25, High = 20), with quite different payment ratios (Low = 58%, High = 83%), and a 95% confidence interval of 20% to 32% in the difference favor of the High group.
 
-Although it seems a similar result to that reported in that paper, we explore the pattern of promises of both groups to determine if it was possible to classify our subjects as _honest_ and _dishonest_.
-If we hypothesize that the commitment to pay would be reflected in the level of promises selected, a group of _dishonest_ people could generate in their partners the belief that they will pay by choosing a high level of promises (mostly or always) and, later, betraying that trust when deciding not to pay back.
-
-In order to explore whether the groups represent populations that do not differ in the level of commitment expressed in the promises, we use a Cumulative Bayesian Model, which assumes that the levels of promises are an observed ordinal variable $Y$ that originates from the categorization of a continuous latent variable $\tilde{Y}$, for this case, _the expressed commitment to pay back_ [@Burkner2019].
-The degree to which the subjects of the High group differ from the Low group, in normal standard deviations ($z$-values), on the latent scale of $\tilde{Y}$, has a point estimate of 0.95, which implies that the High group has 0.95 $z$-values greater commitment to pay back than the Low group.
-
+Although it seems a similar result to that reported in that paper [@Baumgartner2009], we explore the pattern of promises of both groups to determine if it was possible to classify our subjects as honest and dishonest.
+If we hypothesize that the commitment to pay would be reflected in the level of promises selected, a group of dishonest people could generate in their partners the belief that they will pay by choosing a high level of promises (mostly or always) and, later, betraying that trust when deciding not to pay back.
+In order to explore whether the groups represent populations that do not differ in the level of commitment expressed in the promises, we use a Cumulative Bayesian Model, which assumes that the levels of promises are an observed ordinal variable  $Y$ that originates from the categorization of a continuous latent variable $\tilde{Y}$, for this case, the expressed commitment to pay back [@Burkner2019].
+The degree to which the subjects of the High group differ from the Low group, in normal standard deviations ($z$-values), on the latent scale of $\tilde{Y}$, has a point estimate of 0.95, which implies that the High group has 0.95 z-values greater commitment to pay back than the Low group.
 The 95% Bayesian Credibility Interval indicates that the High group is between 0.40 to 1.51 $z$-values of difference from Low.
 So we can conclude with at least a 95% probability that people belonging to the High group expressed in their promises a greater commitment to pay back than the subjects of the Low group.
-If we look at Figure 7, the probability of choosing the different levels of promises varies depending on the group, the one who had the highest percentage of decisions to pay back is more likely to choose _always_ (High group), while the group that had the lowest percentage of decisions to pay back are more likely to choose _mostly_ (Low group).
-
+If we look at Figure 7, the probability of choosing the different levels of promises varies depending on the group, the one who had the highest percentage of decisions to pay back is more likely to choose always (High group), while the group that had the lowest percentage of decisions to pay back are more likely to choose mostly (Low group).
 According to our data, we could not justify the classification of our groups according to their honesty or dishonesty, at least not with the technique used in Baumgartner et al.
@@
 
-The objective of this study was to evaluate the effect of social closeness on keeping and breaking promises, as well as on cooperation in a trust game.
+The goal of this study was to evaluate the effect of social closeness on keeping and breaking promises, as well as on cooperation in a trust game.
 Our results give evidence that zero social closeness increases the probability of breaking the promise and it decreases monotonically as social closeness increases.
-Likewise, as social closeness increases, so does cooperation; _high_ social closeness has an effect on decisions that surpasses even those that all other experimental conditions.
-The most interesting finding was that when subjects express high commitment to cooperate (through choosing that they would _always_ pay back) probability that they comply is also quite high, however, there is a proportion of transgressions that according to our inferences are between 4 - 38% with 95% certainty.
+Likewise, as social closeness increases, so does cooperation; high social closeness has an effect on decisions that surpasses even those that all other experimental conditions.
+The most interesting finding was that when subjects expressed high commitment to cooperate (through choosing that they would always pay back), the probability that they comply is also quite high.
+However, there is a small but consistent proportion of transgressions according to our inferences.
 
@@
 In previous studies, the participants remain anonymous during the course of the tasks [@Baumgartner2009], their measurements to evaluate transgressions are self-reported [@DePaulo1998; @DePaulo2004], they do not directly quantify the breaking of promises [@Vanberg2008; @Charness2006], or as we will discuss later, they use heterogeneous measures of social closeness [@Glaeser2000].
+Our experiment is the first one to include a partner without social closeness (computer).
+Our data suggest that the mere fact of considering that subjects play with a human diminishes the probability of breaking the promise.
+It is more likely to break the promise to the computer than to the stranger, even though that partner was not known.
+Also, null social closeness is important because it allows us to explore the intrinsic motivation to keep the promises.
+If humans keep their word because it is morally correct, we would anticipate that the probability of breaking a promise was very low in the three partners and, particularly, the inference regarding the probability of breaking the promise to the computer would include zero.
+However, we found that, although low, the probability was greater than zero, which provides evidence that seems to contradict, at least in degree, the hypothesis of intrinsic motivation.
+We cannot exclude the possibility that the subjects keep promises mainly due to moral motivation because, even in the case of the computer, the subjects kept a large proportion.
+We can, however, exclude that this is their only motivation.
 
-Our experiment is probably the first to include a partner without social closeness (_computer_), our data give evidence that the mere fact of considering that subjects play with a human diminishes the probability of breaking the promise.
-It is approximately 7.5 times more likely to break the promise to the computer than to the stranger, even though that partner was not known.
-In our study, zero social closeness is important because it allows us to explore the _intrinsic_ motivation to keep the promises, if humans keep their word because it is morally correct, we would anticipate that probability of breaking the promise was very low in the three partners and, particularly, the inference regarding the probability of breaking the promise to the computer would include zero.
+On the other hand, high social closeness allows us to explore the instrumental motivation to keep promises [@Baumgartner2009].
+In our study, it was more likely to break the promise to the stranger than to the friend.
+If humans keep their word to facilitate cooperation in the future, we would anticipate that with a partner of high social closeness (with whom they are very likely to cooperate, even after the experiment) there would be less of a chance to break the promise.
+In fact, the promise to friends was not broken on any occasion, hence the inference in this case, was met.
 
-The probability of breaking the promise without social closeness, although low, is clearly greater than zero, which provides evidence that contradicts, at least in degree, the hypothesis of _intrinsic_ motivation.
-We cannot exclude the possibility that the subjects keep promises mainly morally motivated, because even in the case of the computer, the subjects keep a large proportion, but we can exclude that this is their only motivation.
+The findings concerning motivations could be explained by the social norm called "conditional cooperation", which indicates that the belief that other people cooperate at high levels also induces high levels of cooperation [@Fehr2018].
+Thus, the lack of certainty regarding the decisions that the computer would make could explain the probability of breaking the promise that exists towards this partner.
+Similarly, the information that the subjects have regarding as their friend's behavior -even before the experiment- could explain the high levels of cooperation and keeping of promises towards this partner.
 
-On the other hand, high social closeness allows us to explore the _instrumental_ motivation to keep promises.
-In our study, it is almost 9 times more likely to break the promise to the stranger than to the friend; if human beings keep their word to facilitate cooperation in the future, we would anticipate that with a partner of high social closeness (with whom they are very likely to cooperate, even after the experiment) there would be less chance of breaking the promise.
-In fact, in our study, the promise to friends was not broken on any occasion, so the inference, in this case, is obvious.
+Cooperation has been studied with diverse experimental manipulations.
+In one study, the contribution in a public goods game was evaluated during several trials in a group made up of the same individuals (partners), and compared to another group of new different subjects for each trial (strangers) [@Croson1996].
+In the condition of partners the cooperation was greater because it is a stable group compared to the group of strangers.
+The mentioned study does not give details regarding the recruitment of participants, so we could assume that even in the condition of partners these are individuals who do not consider themselves socially close.
 
-Our findings could be explained by the social norm called _conditional cooperation_, which indicates that the belief that other people cooperate at high levels also induces high levels of cooperation [@Fehr2018].
-Thus, the lack of certainty regarding the decisions that the computer would make could explain the probability of breaking the promise that exists towards this partner.
-Similarly, the information that the subjects have regarding friend's behavior -even before the experiment- can explain the high levels of cooperation and keeping of promises towards this partner.
+Another study showed an increase in cooperation in a trust game when individuals were socially close [@Glaeser2000].
+In this study, subjects knew each other and the researchers carefully measured several variables regarding their social connection.However, some individuals who arrived together were allowed to perform the task between themselves and others were paired with unclear criteria.
+The above allows social closeness between partners to be heterogeneous, allows for romantic relationships and assumes that two individuals who come together to class are considered close to each other.
+Also, since it is a study of one-shot, it excludes the possibility of evaluating how the same subject varies his behavior based on different levels of social closeness.
 
-Regarding cooperation, it is not the first investigation in which the effect of social closeness is evaluated, however, the nature of experimental manipulation has been diverse.
-For example, in one study the contribution in a public goods game was evaluated during several trials in a group made up of the same individuals (_partners_), compared to another group of new different subjects for each trial (_strangers_) [@Croson1996].
-It was assumed that in the condition of _partners_ the cooperation would be greater because it is a stable group compared to the group of _strangers_.
-The mentioned study does not give details regarding the recruitment of participants, so we could assume that even in the condition of _partners_ these are individuals who do not consider themselves socially close.
+To try to homogenize social closeness between our subjects and their partners, they performed the task with a same-sex friend considered to be close, emphasizing their companion could not be a romantic or sexual partner.
+Bayesian analysis of the IOS scale showed evidence in favor that the degree of social closeness between 30 of our 45 subjects and their friends was the same.
+Results of the two mentioned studies also found that social closeness enhance cooperation [@Croson1996; @Glaeser2000], in the future would be valuable to homogenize both the performed tasks and the statistical procedure used, to establish similarity in effects magnitudes.
 
-In another experiment, an increase in cooperation in a trust game in pairs was reported when individuals are socially close [@Glaeser2000], in this study, subjects know each other and the researchers carefully measured several variables regarding their social connection, however, some individuals who arrived together were allowed to perform the task between themselves and others were paired with unclear criteria.
-The above allows social closeness between partners to be heterogeneous, allows for romantic relationships and assumes that two individuals who come together to class are considered close to each other.
-Also, since it is a study of _one-shot_, it excludes the possibility of evaluating how the same subject varies his behavior based on different levels of social closeness.
-
-To try to homogenize social closeness between our subjects and their partners, participants performed the task with a same-sex match friend considered close by themselves, in none case was it a relative and, although we understand that there may be same-sex couples and that the subjects may have hidden their relationship, they were emphasized that to be part of the study their companion could not be a romantic or sexual partner.
-Besides, Bayesian analysis of the IOS scale showed evidence in favor that the degree of social closeness between 30 of our 45 subjects and their friends was the same.
-Although the results of the two studies mentioned are practically in the same direction as the findings of our experiment, establishing the similarity in effects magnitudes is not possible due to the design differences, the performed tasks, and the statistical procedures used.
-
-A methodological contribution of our study is that, in the literature of promises, it is the first to use Bayesian inference tools: *Hierarchical Models* and *Cumulative Models*.
-The former (aka multilevel models), allowed us to model the effect of the experimental conditions on the individual response, these models assume that lower level observations (e.g.
+Our methodological contribution to the field is the use of Bayesian inference tools: Hierarchical Models and Cumulative Models.
+The Hierarchical Models, allowed us to model the effect of the experimental conditions on the individual response.
+These models assume that lower level observations (e.g.
 decisions of each individual) are nested in higher level units (e.g.
 individual subjects).
-Within-subjects designs have traditionally been analyzed with repeated measures AN(C)OVA, however, *Hierarchical Models* grant the advantages of naturally dealing with unbalanced data, including categorical and/or numerical predictors, explicitly incorporate individual variability, among others [@Vuorre2018; @Gelman2006; @McElreath2018; @Burkner2017].
+Within-subjects designs have traditionally been analyzed with repeated measures AN(C)OVA, however, Hierarchical Models grant the advantages of naturally dealing with unbalanced data, include categorical and/or numerical predictors, explicitly incorporate individual variability, among others [@Vuorre2018; @Gelman2006; @McElreath2018; @Burkner2017].
 
-In our case, as shown in Figure 5, the *Hierarchical Model* allowed us to capture very precisely how the experimental conditions affected the decisions of each subject and the differences between them.
-For example, there are obviously motivated _instrumental_ subjects such as number 8 or 12 who are very sensitive to the identity of their investors and modify their cooperation under social closeness.
-At the same time, there are notably _intrinsic_ subjects such as 9 and 10 who cooperate all the time regardless of who their partners are.
-The *Hierarchical Model* naturally includes this information for the estimation of population effects, which, if not considered, would lead to inaccurate inferences.
+In our case, the Hierarchical Model allowed us to capture how the experimental conditions affected the decisions of each subject and the differences between them.
+For example, there are obviously motivated instrumental subjects such as number 8 or 12 who are very sensitive to the identity of their investors and modify their cooperation under social closeness.
+At the same time, there were notably intrinsic subjects such as 9 and 10 who cooperate all the time regardless of who their partners are.
+The Hierarchical Model naturally includes this information for the estimation of population effects, which, if not considered, would lead to inaccurate inferences[@Burkner2017; @Gelman2006; @McElreath2018].
 
-On the other hand, the *Cumulative Model* allowed us to capture the strength of the commitment expressed through promises.
-A very frequent problem that has been pointed out recently is that analyzing ordinal data with methods that assume that observations are _metric_ can lead to serious inference errors [@Liddell2018].
-The *Cumulative Models* assume that the observed responses come from the categorization of a continuous latent variable [@Burkner2019], so in our study, we could identify that the groups with different payment proportions, which in other articles have been called _dishonest_ and _honest_, differ in the commitment they express through their promises.
-Considering that the tools to perform the *Cumulative Models* are relatively recent, it would be valuable to replicate published studies [e.g., @Baumgartner2009; @Baumgartner2013] considering the new alternatives of inference.
+On the other hand, the Cumulative Model allowed us to capture the strength of the commitment expressed through promises.
+A very frequent problem that has been pointed out recently is that analyzing ordinal data with methods that assume that observations are metric can lead to serious inference errors [@Liddell2018].
+The Cumulative Models assumes that the observed responses come from the categorization of a continuous latent variable [@Burkner2019].
+In our study, we could identify that groups with different payment proportions, which in other studies have been called "dishonest" and "honest"[@Baumgartner2009; @Baumgartner2013], differ in the commitment they express through their promises.
+Considering that the tools to perform the Cumulative Models are relatively recent, in future studies, it would be valuable to also use the new alternatives for inference.
 
-Although the *Hierarchical* and *Cumulative* models are not tools exclusively for Bayesian inference, their application from this approach represents several advantages compared to frequentist statistics.
-Classic problems of the previous one such as multiple comparisons, the decision of when to stop collecting subjects (stopping rule), or use of planned comparisons versus _post hoc_, are not factors that affect the support provided by the data to the hypothesis from the Bayesian approach [@Dienes2011].
-In Bayesian inference, hypothesis testing makes formal use of probability to express the plausibility of theories, in our case we were able to obtain evidence ratios regarding the extent our data support hypotheses, regardless these were proposed _a priori_ or _post hoc_.
+Although the Hierarchical and Cumulative models are not tools exclusively for Bayesian inference, their application from this approach represents several advantages compared to frequentist statistics.
+Classic problems such as multiple comparisons, the decision of when to stop collecting subjects (stopping rule), or use of planned comparisons versus post hoc, are not factors that affect the Bayesian approach [@Dienes2011].
+In Bayesian inference, hypothesis testing makes formal use of probability to express the plausibility of theories, and in our case, we were able to obtain evidence ratios regarding the extent of our data support hypotheses, regardless if these were proposed _a priori_ or _post hoc_.
+
+## Limitations
 
@@
 However, other works do not report differences between the use of both types of rewards in self-control, temporal and social discount tasks [@Locey2011; @Johnson2006; @Rachlin2006].
-Likewise, it can be argued that our results have theoretical congruence [@Fehr2018] and are in the same direction as other works that use real money [@Croson1996; @Glaeser2000], so there are not many reasons to expect that other types of rewards would modify our results.
-
+Likewise, it can be argued that our results have theoretical congruence [@Fehr2018] and are in the same direction as other works that use real money [@Croson1996; @Glaeser2000], thus, there are not many reasons to expect that other types of rewards would modify our results.
 Another possible limitation is the use of multiple trials with each partner.
-Although the decision to use repeated measures during our design serves more the purpose of reducing contaminant sources and increasing internal validity [@Maxwell2018], to have more clarity regarding the difference in the _intrinsic_ and _instrumental_ motivations, the studies could benefit from only include one trial for each partner.
-Play a _one-shot_ with each partner avoids the possibility that multiple trials could generate the belief that the computer can also vary its behavior according to the decisions of the _trustee_.
+Although the decision to use repeated measures during our design serves more the purpose of reducing contaminant sources and increasing internal validity [@Maxwell2018], to have more clarity regarding the difference in the intrinsic and instrumental motivations, the studies could benefit from only include one trial for each partner.
+Play a one-shot with each partner avoids the possibility that multiple trials could generate the belief that the computer can also vary its behavior according to the decisions of the trustee.
+Finally, subjects that performed the study inside the MRI scanner may differ in their responses than subjects outside of the scanner.
+However, our analysis did not show this explicitly.
 
@@
 
-Subjects keep their promises by a combination of _intrinsic_ and _instrumental_ motivations.
-They are predominantly _nice guys_ because they keep their word even with investors with no social closeness.
-However, its trustworthiness is far from perfect, since there is a small, but reliably greater than zero, proportion of betrayals committed towards this partner.
-It seems that if subjects cannot assure that their investor will be a _potential cooperator_, dishonesty may emerge in the form of broken promises.
-The theoretical predictions of the social norm _conditional cooperation_ frame the finding that social closeness decreases the probability of breaking the promise and increases cooperation.
-In the same way that suggests the correspondence between commitment expressed through promises and subsequent behavior.
+Subjects seem to keep their promises by a combination of _intrinsic_ and _instrumental_ motivations.
+They are predominantly "nice people" because they keep their word even with investors with no social closeness.
+However, their trustworthiness is far from perfect, since there is a small proportion of betrayals committed towards this partner.
+It seems that if subjects cannot be sure their investor will be a "potential cooperator", dishonesty may emerge in the form of broken promises.
+Framing the finding in terms of the theoretical predictions of the social norm "conditional cooperation", social closeness decreases the probability of breaking the promise and increases cooperation, and suggests the correspondence between commitment expressed through promises and subsequent behavior.
 

### 2019-08-08 article_english.tex
Updating manuscript.

--- 2019-07-29 article_english.tex
@@
 \hypersetup{unicode=true,
-            pdftitle={Nice guys or potential cooperators when keeping promises: an experimental and Bayesian account for two explanations},
+            pdftitle={Nice people or potential cooperators when keeping promises: an experimental and Bayesian account for two explanations},
             pdfauthor={Said Jiménez},
@@
 
-  \title{Nice guys or potential cooperators when keeping promises: an
+  \title{Nice people or potential cooperators when keeping promises: an
 experimental and Bayesian account for two explanations}
@@
   \postdate{\par}
-    \date{July 2019}
+    \date{August 2019}
 
@@
 
-Human beings are social animals and we get advantages from being so.
+Human are social animals and we get survival advantages from being such.
 Historically, belonging to a social group has provided protection and
-guaranteed access to resources such as food, currently there has been
-evidence that belonging to a social circle has a positive effect on
+guaranteed access to resources such as food, and currently, there has
+been evidence that belonging to a social group has a positive effect on
 longevity, physical and mental health (Holt-Lunstad, 2018; Tough,
-Siegrist, \& Fekete, 2017). The interrelation between social closeness
+Siegrist, \& Fekete, 2017). The relationship between social closeness
 and cooperation is key to the formation of large groups of individuals
-without a genetic relationship, such groups form the basis of
-communities, societies, and nations, as well as probably constitute one
-of the most fundamental conditions for human survival (Fehr \&
-Fischbacher, 2003; Fehr \& Schurtenberger, 2018).
-
-An important requirement for cooperation between individuals is
-communication, a meta-analysis of 45 studies reported a large positive
-effect (\(d = 1.01\)) of communication in cooperation regardless of the
-communication medium (Balliet, 2010). In parallel, it is known that
-after communication sessions between completely unknown individuals
-there is an increase in subjective social closeness (Aron, Melinat,
-Aron, Vallone, \& Bator, 1997). Thus, the findings suggest a positive
-relationship between communication, cooperation, and social closeness.
+without a genetic relationship, and such groups form the basis of
+communities, societies, and nations, arguably constituting one of the
+most fundamental conditions for human survival (Fehr \& Fischbacher,
+2003; Fehr \& Schurtenberger, 2018). An important requirement for
+cooperation between individuals is communication. A meta-analysis of 45
+studies reported a large positive effect (\(d = 1.01\)) of communication
+in cooperation regardless of the communication medium (Balliet, 2010).
+In parallel, it is known that after communication sessions between
+completely unknown individuals there is an increase in subjective social
+closeness (Aron, Melinat, Aron, Vallone, \& Bator, 1997). Thus, these
+findings suggest a positive relationship between communication,
+cooperation, and social closeness.
 
 One of the forms of communication that have received the most attention
-in psychological game theory is the promise, in an interaction between
-sender and recipient, it is believed that promises influence beliefs of
-the recipient, generating trust and cooperation (Charness \& Dufwenberg,
-2006; Vanberg, 2008). However, there are situations where trust is
-betrayed, promises are broken or people deceive, for example,
-approximately 11\% of people surveyed by the General Social Survey (GSS)
-in 2018 responded that they have had sex with someone different to their
-partner while they are married (Smith, Davern, Freese, \& Hout, 2018).
-Another example, according to the Washington Post, President Trump has
-said 10,796 false or misleading statements in 869 days in office
-(Kessler, Rizzo, \& Kelly, 2019).
-
-In the laboratory, these transgressions to trust have been explicitly
-studied in experiments where subjects have incentives to lie or not keep
-their promises. However, the vast majority of these studies in
-economics, psychology and neurosciences have been conducted in people
-who do NOT know each other (to name a few, Gneezy, 2005; Baumgartner,
+in psychological game theory is ``the promise''. In an interaction
+between sender and recipient, it is believed that promises influence
+beliefs of the recipient, generating trust and cooperation (Charness \&
+Dufwenberg, 2006; Vanberg, 2008). However, there are situations where
+trust is betrayed, promises are broken or people deceived. The General
+Social Survey (GSS) in 2018 showed that approximately 11\% of people
+surveyed responded that they have had sex with someone different to
+their partner while they are married (Smith, Davern, Freese, \& Hout,
+2018). In economic and social terms, the United Nations Organization has
+stressed that deception (corruption) has a global cost of at least 5
+percent of the annual gross domestic product (GDP), and it is a
+generator of conflict and instability in all nations (UN, 2018).
+
+Despite the widespread presence of interactions between human belonging
+to the same group, it is not known how social closeness between
+participants can affect keeping or breaking promises. This is important
+because it has been pointed out that lies and betrayals of trust occur
+daily in close relationships, such as friends, workmates, or classmates.
+And, their consequences can be serious such as loss of the relationship,
+work or damage to reputation (DePaulo, Ansfield, Kirkendol, \& Boden,
+2004). In the laboratory, these transgressions to trust have been
+explicitly studied in experiments where subjects have incentives to lie
+or not keep their promises. However, the vast majority of these studies
+have been conducted in people who do NOT know each other (Baumgartner,
 Fischbacher, Feierabend, Lutz, \& Fehr, 2009; Baumgartner, Gianotti, \&
 Knoch, 2013; Charness \& Dufwenberg, 2006; Fischbacher \& Föllmi-Heusi,
-2013; Gneezy, Rockenbach, \& Serra-Garcia, 2013; Mazar, Amir, \& Ariely,
-2008). In social psychology some studies address deception in close
-interpersonal relationships, however, they use self-report measurements
-(DePaulo, Ansfield, Kirkendol, \& Boden, 2004; DePaulo \& Kashy, 1998)
-or rather explore the development of deception detection skills in
-same-sex friends (Anderson, DePaulo, \& Ansfield, 2002). Despite the
-widespread presence of interactions between human beings belonging to
-the same group, it is not known how social closeness between subjects
-can affect keeping or breaking promises.
-
-In this manuscript, we explore the effects of three partners with
-different levels of social closeness on keeping or breaking promises, as
-well as on cooperation in a trust game. The above, we analyze it in the
-light of the two main motivations that have been pointed out in the
-literature regarding keeping promises (Baumgartner et al., 2009):
+2013; Gneezy, 2005; Gneezy, Rockenbach, \& Serra-Garcia, 2013; Mazar,
+Amir, \& Ariely, 2008). Some studies address deception in close
+interpersonal relationships using self-report measurements, however,
+they have limitations due to social desirability bias (DePaulo et al.,
+2004; DePaulo \& Kashy, 1998) or rather explore the development of
+deception detection skills in same-sex friends (Anderson, DePaulo, \&
+Ansfield, 2002).
+
+In this study, we wanted to understand the effects of three partners
+with different levels of social closeness on keeping or breaking
+promises, as well as on cooperation, using an experimental trust game.
+We analyzed it in light of the two main motivations that have been
+pointed out in the literature regarding keeping promises which are:
+instrumental and intrinsic (Baumgartner et al., 2009):
 
@@
 role of trustee in front of three partners with different levels of
-social closeness (zero, low and high) in the role of the investor: a
-\emph{computer}, a \emph{stranger}, and a \emph{friend}.
-
-The manipulations mentioned allow us to evaluate several hypotheses, the
-first one was proposed a priori and is derived from a larger research
-project (you can check the pre-registration of the hypothesis here:
-\url{https://osf.io/u97fd}), while the following are exploratory:
+social closeness (null, low and high) in the role of the investor: a
+computer, a stranger, and a friend. The manipulations mentioned allow us
+to evaluate several hypotheses, the first one was proposed a priori and
+is derived from a larger research project (you can check the
+preregistration of the hypothesis here: \url{https://osf.io/u97fd}),
+while the following are exploratory:
 
@@
   should be noted that if the participants keep the promises to the
-  computer, evidence would be given in favor of intrinsic motivation.
+  computer, evidence would be given in favor of \emph{intrinsic}
+  motivation.
 \item
@@
   of promises. We expect that there is more probability of paying the
-  \emph{friend} than the \emph{stranger} and more probability of paying
-  the stranger than the \emph{computer}. According to the
-  \emph{instrumental} motivation, the cooperation will be greater for
-  partners with whom the subject anticipates greater cooperation in the
-  future (friend \textgreater{} stranger \textgreater{} computer).
+  friend than the stranger and more probability of paying the stranger
+  than the computer. According to the \emph{instrumental motivation},
+  the cooperation will be greater for partners with whom the subject
+  anticipates greater cooperation in the future (friend \textgreater{}
+  stranger \textgreater{} computer).
 \item
@@
   2009). However, what in the aforementioned study was classified as a
-  group of \emph{honest} and \emph{dishonest}, we will show that in our
-  sample it is not supported because if the groups differ in their
-  payment rate it will be due to the difference in their level of
-  commitment expressed by promises.
+  group of ``honest'' and ``dishonest'', we will show that in our sample
+  it is not supported because if the groups differ in their payment rate
+  it will be due to the difference in their level of commitment
+  expressed by promises.
 \end{enumerate}
@@
 
-We included 45 subjects (15 men), recruited from the National Autonomous
+We recruited 45 subjects (15 male) from the National Autonomous
 University of Mexico, the age range from 19 to 33 years and their
-minimum educational level were bachelor's degrees. Subjects went to the
-study with a friend considered \emph{close} by themselves, who fulfilled
-the following characteristics: he was matched by sex, did not have a
-family bond and was not a person with a sentimental or sexual
-relationship. 30 subjects (15 men) performed the task within a Magnetic
-Resonance Imaging (MRI) scanner, however, their image data is not
-analyzed in the present work.
+minimum educational level were bachelor. Subjects were asked to come to
+the study with a ``close'' friend, who fulfilled the following
+characteristics: 1) he/she was matched by sex, 2) did not have a family
+bond and 3) was not a person with a sentimental or sexual relationship.
+From this sample, 30 subjects (15 men) performed the task in a magnetic
+resonance imaging (MRI) scanner, however, their image data was not
+analyzed for the present work.
 
@@
 All subjects performed an adaptation of the trust game with promises,
-using hypothetical monetary rewards (Baumgartner et al., 2009). The task
-was programmed in PsychoPy2 version 1.84.2 (Peirce et al., 2019; Peirce,
-2008) and consisted of 24 trials between two players: trustee and
-investor. The trustee originally has 0 Mexican pesos and the investor
-has 2 pesos, the investor is presented with the opportunity to give his
-money to the trustee or keep it. If he invests his money it is
-multiplied by 5 pesos, so that the trustee has 10 pesos. Finally, the
-trustee decides to pay half to the investor or keep the 10 pesos.
-
-The structure described is repeated in 24 trials, however, in 4 of the
-trials the trustee can send a promise to the investor, the promises were
-that \emph{always}, \emph{mostly}, \emph{sometimes}, or \emph{never}
-would pay back. Each promise was valid for three trials so that 12 of
-the trials have the effect of the promise and the other 12 do not. It is
-worth mentioning that the promises are not made to a particular partner,
-but the subject expresses their commitment level to pay back regardless
-of who their partners are in the next three trials in which the promise
-is valid.
-
-The variation with respect to the original task is that in our
-experiment three partners were presented with three levels of social
-closeness in the role of the investor: \emph{computer} (no closeness),
-\emph{strange} (low closeness) and \emph{friend} (high closeness), while
-the subject acts as the trustee. Each partner performs the role of
-investor in 8 of 24 total trials, however, both the promises and social
-closeness conditions were presented to the trustee in pseudorandom
-order.
+using hypothetical monetary rewards (Baumgartner et al., 2009). The
+variation with respect to the original task is that in our experiment
+three partners were presented with three levels of social closeness in
+the role of the investor: computer (no closeness), strange (low
+closeness) and friend (high closeness), while the participant acted as
+the trustee. The task was programmed in PsychoPy2 version 1.84.2 (Peirce
+et al., 2019; Peirce, 2008) and consisted of 24 trials between two
+players: trustee and investor. The trustee originally has 0 Mexican
+pesos and the investor has 2 pesos, the investor is presented with the
+opportunity to give his money to the trustee or keep it. If investor
+gives his money, it is multiplied by 5 pesos, so that the trustee has 10
+pesos. Finally, the trustee decides to pay half to the investor or keep
+the 10 pesos. The structure described is repeated in 24 trials, however,
+in 4 of the trials the trustee can send a promise to the investor, the
+promises were that always, mostly, sometimes, or never would pay back.
+Each promise was valid for three trials so that 12 of the trials have
+the effect of the promise and the other 12 do not. Each partner performs
+the role of investor in 8 of 24 total trials, however, both the promises
+and social closeness conditions were presented to the trustee in
+pseudorandom order.
 
@@
 were programmed \emph{a priori} to give their amount in 6 trials and in
-2 did not. The covert story for all our subjects was that they would be
-playing in real-time with their friend, the stranger (was told he would
-be another same-sex unknown person) and the computer. A diagram of the
-chronology of the experimental task with the duration of each phase in
-seconds is shown in Figure 1, each box from left to right represents a
-screen that was shown to the subjects sequentially. Section A\(_1\)
-corresponds to an example of trials without promises and section A\(_2\)
-to trials with promises.
+2 did not randomly. The covert story for all our subjects was that they
+would be playing in real-time with their friend (whom they brought to
+the study), the stranger (was told he would be another same-sex unknown
+person) and the computer. After the study ended, the participants were
+debriefed about our own deception. A diagram of the chronology of the
+experimental task with the duration of each phase in seconds is shown in
+Figure 1.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/task}
+
+}
+
+\caption{Trust game with promises, each box from left to right represents a screen that was shown to the subjects sequentially.
+Section A1 corresponds to an example of trials without promises and section A2 to trials with promises.}\label{fig:figA}
+\end{figure}
 
 Fixation phase consisted only of a period in which the subject paid
-attention without performing any particular behavior, then,
-\textbf{promises phase} in part A\(_1\) indicated to the subject that
-the following three trials they could decide without the effect of the
-promise, while in A\(_2\) the subject was asked to decide between
-\emph{always}, \emph{mostly}, \emph{sometimes} or \emph{never} pay back.
-This was followed by another fixation period, subsequently, trails in
-both A\(_1\) and A\(_2\) continue in the same way.
-
-In the \textbf{anticipation/assignation phase}, subjects were told who
-their partner was for that trial (computer, stranger or friend) and was
-given the message that their partner was making their decision. Later in
-the \textbf{decision phase}, the subject was informed if his partner
+attention without performing any particular behavior. Then,
+\textbf{promises phase} in part A1 indicated that in the following three
+trials they could decide without the effect of the promise. In A2, the
+subject was asked to decide between 1) always, 2) mostly, 3) sometimes
+or 4) never pay back. This pattern was repeated. In the
+\textbf{anticipation/assignation phase}, subjects were told who their
+partner was for that trial (computer, stranger or friend) and was given
+the message that their partner was making their decision. Later in the
+\textbf{decision phase}, the subject was informed if his partner
 invested his \$2 or not, he was reminded of his promise level (if they
-were trails with promises) and, in case of his partner had invested, he
-was asked to decide whether to pay back or not. Finally, in
-\textbf{feedback phase} payments for that trial were shown and the
-sequence was repeated.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/task}
-
-}
-
-\caption{Trust game with promises}\label{fig:figA}
-\end{figure}
+were trails with promises) and, in case the partner had invested, he was
+asked to decide whether to pay back or not. Finally, payments for each
+trial were shown in the \textbf{feedback phase} and the sequence was
+repeated until the task finished.
 
@@
 
-Subjects came with a same-sex friend considered close by him or her, it
-was emphasized that they must not have a romantic or family relationship
-with their friends, to try to exclude the effect on cooperation due to a
-consanguineous relationship or sexual attraction. Also, to ensure that
-the subjects and their companions had a similar degree of social
-closeness to each other, in the laboratory both responded to the
-``Inclusion of the Other in Self'' IOS scale (Aron et al., 1997) without
-observing their partner responses. The scale consists of seven pairs of
-circles that vary in the degree of overlap between them, the respondent
-must select the pair of circles that best represents the subjective
-closeness to his partner.
-
-Subjects were trained in the task by two of the researchers, the game
-was first explained verbally, and then the computerized interface was
-presented to them on a portable computer. They were told that they would
-make their decisions with four buttons on the computer keyboard, which
-corresponded to the levels of promises and with only two of these to
-make their decision to pay back or not. Friends heard the explanation,
-they were told that they would make their decisions in a separate room
-on another computer. Subjects performed between 3 and 6 practice tests
-together with the researcher who exemplified the course of the game when
-the investor gave his budget. In the practice trials, all the phases
-indicated in Figure 1 were shown, however, the identity of the investors
-was replaced by question marks.
-
-When the subjects did not report doubts we proceeded to take them
-without their companions to another room where they would make their
-decisions on a laptop, or, with the Lumina Cedrus response system in the
-case that it was a subject to which we also performed MRI. The subjects
-began the task believing that they would really play with the three
-partners of different social closeness. In the other room, another of
-the researchers performed the \emph{debriefing} to the companion, they
-were told that the purpose of the research was to know if their mere
-presence had an effect on the subject's decisions, but that to simplify
-the analysis their responses were programmed \emph{a priori} so your
-participation ended there.
-
-When the subject finished the task, \emph{debriefing} was also carried
-out, he was told that the decisions of his partners had been programmed.
+Subjects came to the lab with a same-sex friend considered close by him
+or her. It was emphasized that they must not have a romantic or family
+relationship with their friends, to try to exclude the effect on
+cooperation due to a consanguineous relationship or sexual attraction.
+Also, to ensure that the subjects and their companions had a similar
+degree of social closeness to each other, both responded the ``Inclusion
+of the Other in Self'' IOS scale (Aron et al., 1997) without observing
+their partner responses. The scale consists of seven pairs of circles
+that vary in the degree of overlap between them, the respondent must
+select the pair of circles that best represents the subjective closeness
+to his partner. Subjects were trained in the main task by two
+researchers, the game was first explained verbally, and then the
+computer interface was presented on a portable computer. They were told
+that they would make their decisions with four buttons on the computer
+keyboard, which corresponded to the levels of promises and with only two
+of these to make their decision to pay back or not. Friends heard the
+explanation, they were told that they would make their decisions in a
+separate room on another computer even though they were not. Subjects
+performed between 3 and 6 practice tests together with the researcher
+who exemplified the course of the game when the investor gave his
+budget. When the subjects were ready, we proceeded to take them without
+their companions to another room (or MRI scanner it that was the case)
+where they would perform the task.The subjects began the task believing
+that they would really play with the three partners of different social
+closeness. In the other room, we debriefed the companion about the
+deception. When the subject finished the task, they were debriefed.
 Although no participant exercised their right, both subjects and their
@@
 informed consent if they considered disagreeing with any of the
-manipulations made by researchers.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{descriptives}{%
-\subsection{Descriptives}\label{descriptives}}
-
-We analyzed 810 decisions about paying back or not (18 per subject), as
-well as 180 promises (4 per subject), 69\% of the decisions, were pay
-back, while the proportion of the promises selected were 5.4\%, 16.2\%,
-43.8\% and 40.2\%, respectively for promises \emph{never},
-\emph{sometimes}, \emph{mostly} and \emph{always}. Figure 2 shows the
-payment proportion depending on the levels of promises and partners.
-
-Breaking promises, that is, subject had promised \emph{always} and
-subsequently decides not to pay back occurred only 12.4\% of trials (19
-times they did not pay back of 153 when promised \emph{always}), of
-which, 8.50\% (13/153) were trials with the computer, 3.92\% (6/153)
-with the stranger and 0\% (0/153) with the friend. It is essential to
-note that breaking the promise was not the most frequent decision, in
-91.5\% of trials when they promised \emph{always} and had the computer
-as a partner they decided to pay back.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig2-1}
-
-}
-
-\caption{Pay back proportion by partners and promises levels}\label{fig:fig2}
-\end{figure}
-
-\hypertarget{hierarchical-bayesian-modeling}{%
-\subsection{Hierarchical Bayesian
-Modeling}\label{hierarchical-bayesian-modeling}}
+manipulations made by the researchers.
+
+\hypertarget{bayesian-modeling}{%
+\subsection{Bayesian Modeling}\label{bayesian-modeling}}
 
@@
 each, the first 1000 iterations of each chain were discarded (burning
-period), for a total of 4000 post-burning samples. Models convergence
+period), for a total of 4000 post burning samples. Models convergence
 was evaluated through visual inspection of the chains and calculation of
-the \(\hat{R}\) statistic, which for all parameters was 1, which is
+the \(\hat{R}\) statistic, which for all parameters was 1, that can be
 interpreted as convergence. Vaguely informative prior distributions were
@@
 
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{descriptives}{%
+\subsection{Descriptives}\label{descriptives}}
+
+We analyzed 810 decisions about paying back or not (18 per subject), as
+well as 180 promises (4 per subject). 69\% of the decisions, were pay
+back, while the proportion of the promises selected were never = 5.4\%,
+sometimes = 16.2\%, mostly = 43.8\% and always = 40.2\%. Figure 2 shows
+the payment proportion depending on the levels of promises and partners.
+Breaking promises, meaning the subject had promised always and
+subsequently decides not to pay back, occurred only in 12.4\% of trials
+(19 times they did not pay back of 153 when promised always), of which,
+8.50\% (13/153) were trials with the computer, 3.92\% (6/153) with the
+stranger and 0\% (0/153) with the friend. It is essential to note that
+breaking the promise was not the most frequent decision, when they
+promised always and had the computer as a partner, they decided to pay
+back in 91.5\% of trials.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig2-1}
+
+}
+
+\caption{Pay back proportion by partners and promises levels}\label{fig:fig2}
+\end{figure}
+
 \hypertarget{social-closeness-between-partners}{%
@@
 Delgado, 2014; Sip, Smith, Porcelli, Kar, \& Delgado, 2015), which
-consist of seven pairs of circles that vary in the degree of overlap and
-represent the social closeness that an individual perceives with respect
-to the other. A Hierarchical and Cumulative Bayesian Model (See section:
-Commitment expressed in the promises), supports the hypothesis that
-there are no differences in subjective social closeness between subjects
-and their friends, with a posterior evidence ratio of 2.74 in its favor.
+consists of seven pairs of circles that vary in the degree of overlap
+and represent the social closeness that an individual perceives with
+respect to the other. A Hierarchical and Cumulative Bayesian Model (See
+section: Commitment expressed in the promises), supports the hypothesis
+that there are no differences in subjective social closeness between
+subjects and their friends, with a posterior evidence ratio of 2.74 in
+its favor.
+
+\hypertarget{hierarchical-bayesian-modeling}{%
+\subsection{Hierarchical Bayesian
+Modeling}\label{hierarchical-bayesian-modeling}}
 
@@
 behavior of breaking the promise, we filtered all trials in which
-subjects promised that they would \emph{always} pay back and then
-decided not to pay. Subsequently, Bayesian inference was used to assess
-the effect of partners on the decision to break the promise at the
-individual and population level. For this purpose, a Hierarchical
-Bayesian Model was carried out that assumes that the uncertainty in
-partners effect on the decision to break the promise varies depending on
-each individual, however, it also assumes that these variations belong
-to common population distributions (Gelman \& Hill, 2006).
+subjects promised that they would always pay back and then decided not
+to pay. Subsequently, Bayesian inference was used to assess the effect
+of partners on the decision to break the promise at the individual and
+population level. For this purpose, a Hierarchical Bayesian Model was
+carried out that assumes that the uncertainty in partners effect on the
+decision to break the promise varies depending on each individual,
+however, it also assumes that these variations belong to common
+population distributions (Gelman \& Hill, 2006).
 
@@
 hypotheses was 7.47 and 8.64 respectively in favor of the previous
-hypotheses. As can be seen in Figure 5 in the estimate for
-\(\beta^{computer}\), when there is no social closeness we have a 95\%
-posterior probability that the parameter for promise-breaking is between
-4-38\%, although it is a small proportion, it clearly excludes the
-probability that promises are not broken.
+hypotheses. As seen in Figure 5 in the estimate for
+\(\beta^{computer}\), no social closeness, we have a 95\% posterior
+probability that the parameter for promise-breaking is between 4-38\%,
+although it is a small proportion, it clearly excludes the probability
+that promises are not broken.
 
@@
 distribution and the shaded area corresponds to the interval of 50\%
-posterior probability. As can be seen, more than 95\% of the posterior
-density of the population coefficients is greater than 0, which
-indicates strong evidence of the effect of experimental conditions on
-the decision to pay back, so that the presence of promises and the
-stranger increase clearly the probability of paying, but the presence of
-the friend is the condition that has the greatest effect on this
-behavior. Posterior distributions clearly show that the probability of
-cooperation increases as social closeness does.
-
-Also, Figure 5 presents the posterior predictive distribution in
-contrast to the proportion of decisions to each partner during the
-promises phase, each panel corresponds to one of the first twelve
-subjects. The responses on the dotted line would indicate that the
-subject paid back random to that partner. Posterior predictive
-distribution simulates observations of the model and compares them with
-the actual data, it helps us to identify if the model is sufficiently
-close to the process that generated the data (Lee \& Wagenmakers, 2014;
-Schad, Betancourt, \& Vasishth, 2019). It can be seen that there is a
-great correspondence between the subject's responses and predictions of
-the model, even in cases where the model is ``wrong'' (for example,
-subject 1), the observed response is in the range of a predicted
-standard deviation, which gives credibility to estimates.
+posterior probability. As shown, more than 95\% of the posterior density
+of the population coefficients is greater than 0, which shows strong
+evidence of the effect of experimental conditions on the decision to pay
+back, although the presence of promises and the stranger clearly
+increase the probability of paying, the presence of the friend is the
+condition that has the greatest effect on this behavior. Posterior
+distributions clearly show that the probability of cooperation increases
+as social closeness does.
 
@@
 \end{figure}
+
+Figure 5 shows the posterior predictive distribution in contrast to the
+proportion of decisions to each partner during the promises phase, and
+each panel corresponds to one of the first twelve subjects. The
+responses on the dotted line would indicate that the subject paid back
+random to that partner. Posterior predictive distribution simulates
+observations of the model and compares them with the actual data, it
+helps us to identify if the model is sufficiently close to the process
+that generated the data (Lee \& Wagenmakers, 2014; Schad, Betancourt, \&
+Vasishth, 2019). It can be seen that there is a great correspondence
+between the subject's responses and predictions of the model. Even in
+cases where the model is ``wrong'' (for example, subject 1), the
+observed response is in the range of a predicted standard deviation,
+which gives credibility to estimates.
 
@@
 promise that are more sensitive than others to the effect of the
-partners on the decision to pay back. Again, a Hierarchical Bayesian
+partner's on the decision to pay back. Again, a Hierarchical Bayesian
 Model was made to estimate the effect of partners at the population
@@
 
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig6-1}
+
+}
+
+\caption{Posterior predictive over pay back rate, Social Closeness Varying effects by Promise levels}\label{fig:fig6}
+\end{figure}
+
 On the other hand, Figure 6 shows the posterior predictive distribution,
@@
 partners and their variation by the level of promise. With the exception
-of the promise \emph{never}, a monotonic positive effect of partners is
-observed at all levels of promise, however, it can be observed how the
+of the promise never, a monotonic positive effect of partners is
+observed at all levels of promise. However, we also observe how the
 effect of social closeness varies depending on the strength of the
 promise, mainly for the decisions towards the computer.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig6-1}
-
-}
-
-\caption{Posterior predictive over pay back rate, Social Closeness Varying effects by Promise levels}\label{fig:fig6}
-\end{figure}
 
@@
 participants that were different in their payment rates, despite the
-fact that they both made very high promises, for this reason, the
-authors named the group that paid little \emph{dishonest} and the group
-that paid a lot \emph{honest}. In a similar exercise, in the present
+fact that they both made very high promises. For this reason, the
+authors named the group that paid little as ``dishonest'' and the group
+that paid a lot as ``honest''. In a similar exercise, in the present
 study we performed the hierarchical grouping technique to obtain a
-solution of 2 groups and we found two similar sets in \(n\) that we call
+solution for two groups and we found two similar sets in n that we call
 the group ``Low'' and ``High'' (Low = 25, High = 20), with quite
@@
 
-Although it seems a similar result to that reported in that paper, we
-explore the pattern of promises of both groups to determine if it was
-possible to classify our subjects as \emph{honest} and \emph{dishonest}.
-If we hypothesize that the commitment to pay would be reflected in the
-level of promises selected, a group of \emph{dishonest} people could
-generate in their partners the belief that they will pay by choosing a
-high level of promises (mostly or always) and, later, betraying that
-trust when deciding not to pay back.
-
-In order to explore whether the groups represent populations that do not
-differ in the level of commitment expressed in the promises, we use a
-Cumulative Bayesian Model, which assumes that the levels of promises are
-an observed ordinal variable \(Y\) that originates from the
-categorization of a continuous latent variable \(\tilde{Y}\), for this
-case, \emph{the expressed commitment to pay back} (Bürkner \& Vuorre,
-2019). The degree to which the subjects of the High group differ from
-the Low group, in normal standard deviations (\(z\)-values), on the
-latent scale of \(\tilde{Y}\), has a point estimate of 0.95, which
-implies that the High group has 0.95 \(z\)-values greater commitment to
-pay back than the Low group.
-
-The 95\% Bayesian Credibility Interval indicates that the High group is
-between 0.40 to 1.51 \(z\)-values of difference from Low. So we can
-conclude with at least a 95\% probability that people belonging to the
-High group expressed in their promises a greater commitment to pay back
-than the subjects of the Low group. If we look at Figure 7, the
-probability of choosing the different levels of promises varies
-depending on the group, the one who had the highest percentage of
-decisions to pay back is more likely to choose \emph{always} (High
-group), while the group that had the lowest percentage of decisions to
-pay back are more likely to choose \emph{mostly} (Low group).
-
-According to our data, we could not justify the classification of our
-groups according to their honesty or dishonesty, at least not with the
-technique used in Baumgartner et al. (2009). Since people were quite
-consistent with keeping what they promised to pay.
+Although it seems a similar result to that reported in that paper
+(Baumgartner et al., 2009), we explore the pattern of promises of both
+groups to determine if it was possible to classify our subjects as
+honest and dishonest. If we hypothesize that the commitment to pay would
+be reflected in the level of promises selected, a group of dishonest
+people could generate in their partners the belief that they will pay by
+choosing a high level of promises (mostly or always) and, later,
+betraying that trust when deciding not to pay back. In order to explore
+whether the groups represent populations that do not differ in the level
+of commitment expressed in the promises, we use a Cumulative Bayesian
+Model, which assumes that the levels of promises are an observed ordinal
+variable \(Y\) that originates from the categorization of a continuous
+latent variable \(\tilde{Y}\), for this case, the expressed commitment
+to pay back (Bürkner \& Vuorre, 2019). The degree to which the subjects
+of the High group differ from the Low group, in normal standard
+deviations (\(z\)-values), on the latent scale of \(\tilde{Y}\), has a
+point estimate of 0.95, which implies that the High group has 0.95
+z-values greater commitment to pay back than the Low group. The 95\%
+Bayesian Credibility Interval indicates that the High group is between
+0.40 to 1.51 \(z\)-values of difference from Low. So we can conclude
+with at least a 95\% probability that people belonging to the High group
+expressed in their promises a greater commitment to pay back than the
+subjects of the Low group. If we look at Figure 7, the probability of
+choosing the different levels of promises varies depending on the group,
+the one who had the highest percentage of decisions to pay back is more
+likely to choose always (High group), while the group that had the
+lowest percentage of decisions to pay back are more likely to choose
+mostly (Low group). According to our data, we could not justify the
+classification of our groups according to their honesty or dishonesty,
+at least not with the technique used in Baumgartner et al. (2009). Since
+people were quite consistent with keeping what they promised to pay.
 
@@
 
-The objective of this study was to evaluate the effect of social
-closeness on keeping and breaking promises, as well as on cooperation in
-a trust game. Our results give evidence that zero social closeness
-increases the probability of breaking the promise and it decreases
-monotonically as social closeness increases. Likewise, as social
-closeness increases, so does cooperation; \emph{high} social closeness
-has an effect on decisions that surpasses even those that all other
-experimental conditions. The most interesting finding was that when
-subjects express high commitment to cooperate (through choosing that
-they would \emph{always} pay back) probability that they comply is also
-quite high, however, there is a proportion of transgressions that
-according to our inferences are between 4 - 38\% with 95\% certainty.
+The goal of this study was to evaluate the effect of social closeness on
+keeping and breaking promises, as well as on cooperation in a trust
+game. Our results give evidence that zero social closeness increases the
+probability of breaking the promise and it decreases monotonically as
+social closeness increases. Likewise, as social closeness increases, so
+does cooperation; high social closeness has an effect on decisions that
+surpasses even those that all other experimental conditions. The most
+interesting finding was that when subjects expressed high commitment to
+cooperate (through choosing that they would always pay back), the
+probability that they comply is also quite high. However, there is a
+small but consistent proportion of transgressions according to our
+inferences.
 
@@
 as we will discuss later, they use heterogeneous measures of social
-closeness (Glaeser, Laibson, Sceinkman, \& Soutter, 2000).
-
-Our experiment is probably the first to include a partner without social
-closeness (\emph{computer}), our data give evidence that the mere fact
-of considering that subjects play with a human diminishes the
-probability of breaking the promise. It is approximately 7.5 times more
-likely to break the promise to the computer than to the stranger, even
-though that partner was not known. In our study, zero social closeness
-is important because it allows us to explore the \emph{intrinsic}
-motivation to keep the promises, if humans keep their word because it is
-morally correct, we would anticipate that probability of breaking the
-promise was very low in the three partners and, particularly, the
-inference regarding the probability of breaking the promise to the
-computer would include zero.
-
-The probability of breaking the promise without social closeness,
-although low, is clearly greater than zero, which provides evidence that
-contradicts, at least in degree, the hypothesis of \emph{intrinsic}
-motivation. We cannot exclude the possibility that the subjects keep
-promises mainly morally motivated, because even in the case of the
-computer, the subjects keep a large proportion, but we can exclude that
-this is their only motivation.
+closeness (Glaeser, Laibson, Sceinkman, \& Soutter, 2000). Our
+experiment is the first one to include a partner without social
+closeness (computer). Our data suggest that the mere fact of considering
+that subjects play with a human diminishes the probability of breaking
+the promise. It is more likely to break the promise to the computer than
+to the stranger, even though that partner was not known. Also, null
+social closeness is important because it allows us to explore the
+intrinsic motivation to keep the promises. If humans keep their word
+because it is morally correct, we would anticipate that the probability
+of breaking a promise was very low in the three partners and,
+particularly, the inference regarding the probability of breaking the
+promise to the computer would include zero. However, we found that,
+although low, the probability was greater than zero, which provides
+evidence that seems to contradict, at least in degree, the hypothesis of
+intrinsic motivation. We cannot exclude the possibility that the
+subjects keep promises mainly due to moral motivation because, even in
+the case of the computer, the subjects kept a large proportion. We can,
+however, exclude that this is their only motivation.
 
 On the other hand, high social closeness allows us to explore the
-\emph{instrumental} motivation to keep promises. In our study, it is
-almost 9 times more likely to break the promise to the stranger than to
-the friend; if human beings keep their word to facilitate cooperation in
+instrumental motivation to keep promises (Baumgartner et al., 2009). In
+our study, it was more likely to break the promise to the stranger than
+to the friend. If humans keep their word to facilitate cooperation in
 the future, we would anticipate that with a partner of high social
 closeness (with whom they are very likely to cooperate, even after the
-experiment) there would be less chance of breaking the promise. In fact,
-in our study, the promise to friends was not broken on any occasion, so
-the inference, in this case, is obvious.
-
-Our findings could be explained by the social norm called
-\emph{conditional cooperation}, which indicates that the belief that
-other people cooperate at high levels also induces high levels of
+experiment) there would be less of a chance to break the promise. In
+fact, the promise to friends was not broken on any occasion, hence the
+inference in this case, was met.
+
+The findings concerning motivations could be explained by the social
+norm called ``conditional cooperation'', which indicates that the belief
+that other people cooperate at high levels also induces high levels of
 cooperation (Fehr \& Schurtenberger, 2018). Thus, the lack of certainty
@@
 probability of breaking the promise that exists towards this partner.
-Similarly, the information that the subjects have regarding friend's
-behavior -even before the experiment- can explain the high levels of
-cooperation and keeping of promises towards this partner.
-
-Regarding cooperation, it is not the first investigation in which the
-effect of social closeness is evaluated, however, the nature of
-experimental manipulation has been diverse. For example, in one study
-the contribution in a public goods game was evaluated during several
-trials in a group made up of the same individuals (\emph{partners}),
-compared to another group of new different subjects for each trial
-(\emph{strangers}) (Croson, 1996). It was assumed that in the condition
-of \emph{partners} the cooperation would be greater because it is a
-stable group compared to the group of \emph{strangers}. The mentioned
-study does not give details regarding the recruitment of participants,
-so we could assume that even in the condition of \emph{partners} these
-are individuals who do not consider themselves socially close.
-
-In another experiment, an increase in cooperation in a trust game in
-pairs was reported when individuals are socially close (Glaeser et al.,
-2000), in this study, subjects know each other and the researchers
-carefully measured several variables regarding their social connection,
-however, some individuals who arrived together were allowed to perform
-the task between themselves and others were paired with unclear
-criteria. The above allows social closeness between partners to be
-heterogeneous, allows for romantic relationships and assumes that two
-individuals who come together to class are considered close to each
-other. Also, since it is a study of \emph{one-shot}, it excludes the
-possibility of evaluating how the same subject varies his behavior based
-on different levels of social closeness.
+Similarly, the information that the subjects have regarding as their
+friend's behavior -even before the experiment- could explain the high
+levels of cooperation and keeping of promises towards this partner.
+
+Cooperation has been studied with diverse experimental manipulations. In
+one study, the contribution in a public goods game was evaluated during
+several trials in a group made up of the same individuals (partners),
+and compared to another group of new different subjects for each trial
+(strangers) (Croson, 1996). In the condition of partners the cooperation
+was greater because it is a stable group compared to the group of
+strangers. The mentioned study does not give details regarding the
+recruitment of participants, so we could assume that even in the
+condition of partners these are individuals who do not consider
+themselves socially close.
+
+Another study showed an increase in cooperation in a trust game when
+individuals were socially close (Glaeser et al., 2000). In this study,
+subjects knew each other and the researchers carefully measured several
+variables regarding their social connection.However, some individuals
+who arrived together were allowed to perform the task between themselves
+and others were paired with unclear criteria. The above allows social
+closeness between partners to be heterogeneous, allows for romantic
+relationships and assumes that two individuals who come together to
+class are considered close to each other. Also, since it is a study of
+one-shot, it excludes the possibility of evaluating how the same subject
+varies his behavior based on different levels of social closeness.
 
 To try to homogenize social closeness between our subjects and their
-partners, participants performed the task with a same-sex match friend
-considered close by themselves, in none case was it a relative and,
-although we understand that there may be same-sex couples and that the
-subjects may have hidden their relationship, they were emphasized that
-to be part of the study their companion could not be a romantic or
-sexual partner. Besides, Bayesian analysis of the IOS scale showed
-evidence in favor that the degree of social closeness between 30 of our
-45 subjects and their friends was the same. Although the results of the
-two studies mentioned are practically in the same direction as the
-findings of our experiment, establishing the similarity in effects
-magnitudes is not possible due to the design differences, the performed
-tasks, and the statistical procedures used.
-
-A methodological contribution of our study is that, in the literature of
-promises, it is the first to use Bayesian inference tools:
-\emph{Hierarchical Models} and \emph{Cumulative Models}. The former (aka
-multilevel models), allowed us to model the effect of the experimental
-conditions on the individual response, these models assume that lower
+partners, they performed the task with a same-sex friend considered to
+be close, emphasizing their companion could not be a romantic or sexual
+partner. Bayesian analysis of the IOS scale showed evidence in favor
+that the degree of social closeness between 30 of our 45 subjects and
+their friends was the same. Results of the two mentioned studies also
+found that social closeness enhance cooperation (Croson, 1996; Glaeser
+et al., 2000), in the future would be valuable to homogenize both the
+performed tasks and the statistical procedure used, to establish
+similarity in effects magnitudes.
+
+Our methodological contribution to the field is the use of Bayesian
+inference tools: Hierarchical Models and Cumulative Models. The
+Hierarchical Models, allowed us to model the effect of the experimental
+conditions on the individual response. These models assume that lower
 level observations (e.g.~decisions of each individual) are nested in
@@
 have traditionally been analyzed with repeated measures AN(C)OVA,
-however, \emph{Hierarchical Models} grant the advantages of naturally
-dealing with unbalanced data, including categorical and/or numerical
-predictors, explicitly incorporate individual variability, among others
-(Bürkner, 2017; Gelman \& Hill, 2006; McElreath, 2018; Vuorre \& Bolger,
-2018).
-
-In our case, as shown in Figure 5, the \emph{Hierarchical Model} allowed
-us to capture very precisely how the experimental conditions affected
-the decisions of each subject and the differences between them. For
-example, there are obviously motivated \emph{instrumental} subjects such
-as number 8 or 12 who are very sensitive to the identity of their
-investors and modify their cooperation under social closeness. At the
-same time, there are notably \emph{intrinsic} subjects such as 9 and 10
-who cooperate all the time regardless of who their partners are. The
-\emph{Hierarchical Model} naturally includes this information for the
-estimation of population effects, which, if not considered, would lead
-to inaccurate inferences.
-
-On the other hand, the \emph{Cumulative Model} allowed us to capture the
+however, Hierarchical Models grant the advantages of naturally dealing
+with unbalanced data, include categorical and/or numerical predictors,
+explicitly incorporate individual variability, among others (Bürkner,
+2017; Gelman \& Hill, 2006; McElreath, 2018; Vuorre \& Bolger, 2018).
+
+In our case, the Hierarchical Model allowed us to capture how the
+experimental conditions affected the decisions of each subject and the
+differences between them. For example, there are obviously motivated
+instrumental subjects such as number 8 or 12 who are very sensitive to
+the identity of their investors and modify their cooperation under
+social closeness. At the same time, there were notably intrinsic
+subjects such as 9 and 10 who cooperate all the time regardless of who
+their partners are. The Hierarchical Model naturally includes this
+information for the estimation of population effects, which, if not
+considered, would lead to inaccurate inferences(Bürkner, 2017; Gelman \&
+Hill, 2006; McElreath, 2018).
+
+On the other hand, the Cumulative Model allowed us to capture the
 strength of the commitment expressed through promises. A very frequent
 problem that has been pointed out recently is that analyzing ordinal
-data with methods that assume that observations are \emph{metric} can
-lead to serious inference errors (Liddell \& Kruschke, 2018). The
-\emph{Cumulative Models} assume that the observed responses come from
-the categorization of a continuous latent variable (Bürkner \& Vuorre,
-2019), so in our study, we could identify that the groups with different
-payment proportions, which in other articles have been called
-\emph{dishonest} and \emph{honest}, differ in the commitment they
-express through their promises. Considering that the tools to perform
-the \emph{Cumulative Models} are relatively recent, it would be valuable
-to replicate published studies (e.g., Baumgartner et al., 2009, 2013)
-considering the new alternatives of inference.
-
-Although the \emph{Hierarchical} and \emph{Cumulative} models are not
-tools exclusively for Bayesian inference, their application from this
-approach represents several advantages compared to frequentist
-statistics. Classic problems of the previous one such as multiple
-comparisons, the decision of when to stop collecting subjects (stopping
-rule), or use of planned comparisons versus \emph{post hoc}, are not
-factors that affect the support provided by the data to the hypothesis
-from the Bayesian approach (Dienes, 2011). In Bayesian inference,
-hypothesis testing makes formal use of probability to express the
-plausibility of theories, in our case we were able to obtain evidence
-ratios regarding the extent our data support hypotheses, regardless
-these were proposed \emph{a priori} or \emph{post hoc}.
+data with methods that assume that observations are metric can lead to
+serious inference errors (Liddell \& Kruschke, 2018). The Cumulative
+Models assumes that the observed responses come from the categorization
+of a continuous latent variable (Bürkner \& Vuorre, 2019). In our study,
+we could identify that groups with different payment proportions, which
+in other studies have been called ``dishonest'' and
+``honest''(Baumgartner et al., 2009, 2013), differ in the commitment
+they express through their promises. Considering that the tools to
+perform the Cumulative Models are relatively recent, in future studies,
+it would be valuable to also use the new alternatives for inference.
+
+Although the Hierarchical and Cumulative models are not tools
+exclusively for Bayesian inference, their application from this approach
+represents several advantages compared to frequentist statistics.
+Classic problems such as multiple comparisons, the decision of when to
+stop collecting subjects (stopping rule), or use of planned comparisons
+versus post hoc, are not factors that affect the Bayesian approach
+(Dienes, 2011). In Bayesian inference, hypothesis testing makes formal
+use of probability to express the plausibility of theories, and in our
+case, we were able to obtain evidence ratios regarding the extent of our
+data support hypotheses, regardless if these were proposed \emph{a
+priori} or \emph{post hoc}.
+
+\hypertarget{limitations}{%
+\subsection{Limitations}\label{limitations}}
 
@@
 same direction as other works that use real money (Croson, 1996; Glaeser
-et al., 2000), so there are not many reasons to expect that other types
-of rewards would modify our results.
-
-Another possible limitation is the use of multiple trials with each
-partner. Although the decision to use repeated measures during our
-design serves more the purpose of reducing contaminant sources and
-increasing internal validity (Maxwell, Delaney, \& Ken, 2018), to have
-more clarity regarding the difference in the \emph{intrinsic} and
-\emph{instrumental} motivations, the studies could benefit from only
-include one trial for each partner. Play a \emph{one-shot} with each
+et al., 2000), thus, there are not many reasons to expect that other
+types of rewards would modify our results. Another possible limitation
+is the use of multiple trials with each partner. Although the decision
+to use repeated measures during our design serves more the purpose of
+reducing contaminant sources and increasing internal validity (Maxwell,
+Delaney, \& Ken, 2018), to have more clarity regarding the difference in
+the intrinsic and instrumental motivations, the studies could benefit
+from only include one trial for each partner. Play a one-shot with each
 partner avoids the possibility that multiple trials could generate the
 belief that the computer can also vary its behavior according to the
-decisions of the \emph{trustee}.
+decisions of the trustee. Finally, subjects that performed the study
+inside the MRI scanner may differ in their responses than subjects
+outside of the scanner. However, our analysis did not show this
+explicitly.
 
@@
 
-Subjects keep their promises by a combination between the
+Subjects seem to keep their promises by a combination of
 \emph{intrinsic} and \emph{instrumental} motivations. They are
-predominantly \emph{nice guys} because they keep their word even with
-investors with no social closeness. However, its trustworthiness is far
-from perfect, since there is a small, but reliably greater than zero,
-proportion of betrayals committed towards this partner. It seems that if
-subjects cannot assure that their investor will be a \emph{potential
-cooperator}, dishonesty may emerge in the form of broken promises. The
-theoretical predictions of the social norm \emph{conditional
-cooperation} frame the finding that social closeness decreases the
-probability of breaking the promise and increases cooperation. In the
-same way that suggests the correspondence between commitment expressed
-through promises and subsequent behavior.
+predominantly ``nice people'' because they keep their word even with
+investors with no social closeness. However, their trustworthiness is
+far from perfect, since there is a small proportion of betrayals
+committed towards this partner. It seems that if subjects cannot be sure
+their investor will be a ``potential cooperator'', dishonesty may emerge
+in the form of broken promises. Framing the finding in terms of the
+theoretical predictions of the social norm ``conditional cooperation'',
+social closeness decreases the probability of breaking the promise and
+increases cooperation, and suggests the correspondence between
+commitment expressed through promises and subsequent behavior.
 
@@
 
-\leavevmode\hypertarget{ref-Kessler2019}{}%
-Kessler, G., Rizzo, S., \& Kelly, M. (2019). President Trump has made
-more than 10,000 false or misleading claims. Retrieved from
-\href{https://www.washingtonpost.com/politics/2019/06/10/president-trump-has-made-false-or-misleading-claims-over-days/?utm\%7B/_\%7Dterm=.8565a16aa5e8}{https://www.washingtonpost.com/politics/2019/06/10/president-trump-has-made-false-or-misleading-claims-over-days/?utm\{\textbackslash{}\_\}term=.8565a16aa5e8}
-
 \leavevmode\hypertarget{ref-Lee2014}{}%
@@
 
+\leavevmode\hypertarget{ref-UN2018}{}%
+UN. (2018). Global Cost of Corruption at Least 5 Per Cent of World Gross
+Domestic Product, Secretary-General Tells Security Council, Citing World
+Economic Forum Data. Retrieved from
+\url{https://www.un.org/press/en/2018/sc13493.doc.htm}
+
 \leavevmode\hypertarget{ref-Vanberg2008}{}%

### 2019-08-09 behavioral-promises/behavioral-promises.Rmd
Using springer template

--- 2019-08-08 article_english.Rmd
@@
 ---
-title: "Nice people or potential cooperators when keeping promises: an experimental and Bayesian account for two explanations"
-author: "Said Jiménez"
-date: "August 2019"
-output:  
-  pdf_document:
-    number_sections: true
-    keep_tex: true
-fontsize: 12pt
-bibliography: promises.bib
-csl: apa.csl
+title: Nice people or potential cooperators when keeping promises
+subtitle: An experimental and Bayesian account for two explanations
+titlerunning: Nice people or potential cooperators
+authorrunning: S. Jiménez, et al.
+geometry: margin=1in
+thanks: 
+authors: 
+- name: Said Jiménez 
+  address: Department of Psychology, National University of México (UNAM)
+  email: said.ejp@gmail.com
+
+- name: Kamila E. Sip 
+  address: Institute for Neuroleadership
+  email: kami.sip@gmail.com
+
+- name: Roberto E. Mercadillo
+  address: Department of Biology, Universidad Autónoma Metropolitana (UAM)
+  email: emmanuele.mercadillo@gmail.com
+
+- name: Diego Angeles-Valdez
+  address: Institute of Neurobiology, UNAM
+  email: anglsd_20@hotmail.com
+
+- name: Jairo Muñoz-Delgado
+  address: Investigaciones en Neurociencias, INPRF
+  email: munozd460@gmail.com
+
+- name: Juan J. Sánchez-Sosa
+  address: Department of Psychology, National University of México (UNAM)
+  email: jujosaso@gmail.com
+
+- name: Eduardo A. Garza-Villarreal
+  address: Institute of Neurobiology, UNAM
+  email: egarza@gmail.com
+
+keywords:
+- Deception
+- Hierarchical Bayesian Models
+- Bayesian Cumulative Models
+- Social closeness
+- Promises
+
+#PACS: 
+#- PAC1
+#- superPAC
+
+#MSC:
+#- MSC code 1
+#- MSC code 2
+
+abstract: |
+  Promises increase cooperation between non-genetically related individuals, however, lies and betrayals occur daily in close social relationships.
+Despite this, the effect of social closeness on the decision to keep or break a promise has not been studied.
+We conducted an experiment in which subjects could freely decide if they broke or kept their promise to three partners with different levels of social closeness: null (computer), low (strange) and high (friend).
+If subjects keep their word with the computer, it provides evidence in favor of intrinsic motivation (comply to do the correct thing), otherwise extrinsic motivation would be supported (comply to facilitate future cooperation).
+Using Hierarchical Bayesian Modeling, we find that if social closeness increases, the probability of breaking promises decreases monotonically, the evidence ratio in favor to the hypothesis stranger < computer was 7.47, and friend < stranger was 8.64.
+Furthermore, using Bayesian Cumulative Modeling we find that subjects were very consistent between their promises and the subsequent decisions they make.
+Although is more probable that our subjects keep their promises to any of the three partners, there is a proportion of transgressions to the computer, whose inference excludes zero with a 95% posterior probability.
+Also, subjects never broke the promise to their friends.
+Our results indicate that subjects are predominantly "nice people" because they keep their promises even to partners without social closeness, however, if the subjects are not certain that their partner will also be a "potential cooperator", dishonesty emerges in the form of broken promises.
+
+bibliography: bibliography.bib
+header-includes:
+- \usepackage{booktabs}
+- \usepackage{longtable}
+- \usepackage{array}
+- \usepackage{multirow}
+- \usepackage{wrapfig}
+- \usepackage{float}
+- \usepackage{colortbl}
+- \usepackage{pdflscape}
+- \usepackage{tabu}
+- \usepackage{threeparttable}
+- \usepackage{threeparttablex}
+- \usepackage[normalem]{ulem}
+- \usepackage{makecell}
+- \usepackage{xcolor}
+output: rticles::springer_article
 ---
@@
 
-```{r fig5, fig.cap='Posterior predictive over pay back rate', out.width='100%', out.height='100%'}
+```{r fig5, fig.cap='Posterior predictive over pay back rate', out.width='100%', out.height='42%'}
 
@@
 
-kable(tabla1, 
+knitr::kable(tabla1, 
       digits = 3, 
@@
   add_header_above(c(" ", " " = 2, "95 % CI" = 2)) %>% 
-  kable_styling(latex_options = "hold_position")
+  kable_styling(position = "left")
 

### 2019-08-09 behavioral-promises/behavioral-promises.tex
Using springer template

--- 2019-08-08 article_english.tex
@@
-\documentclass[12pt,]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
+\AtBeginDocument{%
+  \paperwidth=\dimexpr
+    1in + \oddsidemargin
+    + \textwidth
+    % + \marginparsep + \marginparwidth
+    + 1in + \oddsidemargin
+  \relax
+  \paperheight=\dimexpr
+    1in + \topmargin
+    + \headheight + \headsep
+    + \textheight
+    % + \footskip
+    + 1in + \topmargin
+  \relax
+  \usepackage[pass]{geometry}\relax
+}
+
+% !TeX program = pdfLaTeX
+\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+\smartqed  % flush right qed marks, e.g. at end of proof
+%
+\usepackage{amsmath}
+\usepackage{graphicx}
 \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage[margin=1in]{geometry}
+
+\usepackage[hyphens]{url} % not crucial - just used below for the URL
 \usepackage{hyperref}
-\hypersetup{unicode=true,
-            pdftitle={Nice people or potential cooperators when keeping promises: an experimental and Bayesian account for two explanations},
-            pdfauthor={Said Jiménez},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\providecommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-
-  \title{Nice people or potential cooperators when keeping promises: an
-experimental and Bayesian account for two explanations}
-    \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-    \author{Said Jiménez}
-    \preauthor{\centering\large\emph}
-  \postauthor{\par}
-      \predate{\centering\large\emph}
-  \postdate{\par}
-    \date{August 2019}
+
+%
+% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
+%
+% insert here the call for the packages your document requires
+%\usepackage{latexsym}
+% etc.
+%
+% please place your own definitions here and don't use \def but
+% \newcommand{}{}
+%
+% Insert the name of "your journal" with
+% \journalname{myjournal}
+%
+
+%% load any required packages here
 
@@
 \begin{document}
+
+\title{Nice people or potential cooperators when keeping promises }
+ \subtitle{An experimental and Bayesian account for two explanations}
+
+    \titlerunning{Nice people or potential cooperators}
+
+\author{  Said Jiménez \and  Kamila E. Sip \and  Roberto E. Mercadillo \and  Diego Angeles-Valdez \and  Jairo Muñoz-Delgado \and  Juan J. Sánchez-Sosa \and  Eduardo A. Garza-Villarreal \and  }
+
+    \authorrunning{ S. Jiménez, et al. }
+
+\institute{
+        Said Jiménez \at
+     Department of Psychology, National University of México (UNAM) \\
+     \email{\href{mailto:said.ejp@gmail.com}{\nolinkurl{said.ejp@gmail.com}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
+        Kamila E. Sip \at
+     Institute for Neuroleadership \\
+     \email{\href{mailto:kami.sip@gmail.com}{\nolinkurl{kami.sip@gmail.com}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
+        Roberto E. Mercadillo \at
+     Department of Biology, Universidad Autónoma Metropolitana (UAM) \\
+     \email{\href{mailto:emmanuele.mercadillo@gmail.com}{\nolinkurl{emmanuele.mercadillo@gmail.com}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
+        Diego Angeles-Valdez \at
+     Institute of Neurobiology, UNAM \\
+     \email{\href{mailto:anglsd_20@hotmail.com}{\nolinkurl{anglsd\_20@hotmail.com}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
+        Jairo Muñoz-Delgado \at
+     Investigaciones en Neurociencias, INPRF \\
+     \email{\href{mailto:munozd460@gmail.com}{\nolinkurl{munozd460@gmail.com}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
+        Juan J. Sánchez-Sosa \at
+     Department of Psychology, National University of México (UNAM) \\
+     \email{\href{mailto:jujosaso@gmail.com}{\nolinkurl{jujosaso@gmail.com}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
+        Eduardo A. Garza-Villarreal \at
+     Institute of Neurobiology, UNAM \\
+     \email{\href{mailto:egarza@gmail.com}{\nolinkurl{egarza@gmail.com}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
+    }
+
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
+
 \maketitle
+
+\begin{abstract}
+Promises increase cooperation between non-genetically related
+individuals, however, lies and betrayals occur daily in close social
+relationships. Despite this, the effect of social closeness on the
+decision to keep or break a promise has not been studied. We conducted
+an experiment in which subjects could freely decide if they broke or
+kept their promise to three partners with different levels of social
+closeness: null (computer), low (strange) and high (friend). If subjects
+keep their word with the computer, it provides evidence in favor of
+intrinsic motivation (comply to do the correct thing), otherwise
+extrinsic motivation would be supported (comply to facilitate future
+cooperation). Using Hierarchical Bayesian Modeling, we find that if
+social closeness increases, the probability of breaking promises
+decreases monotonically, the evidence ratio in favor to the hypothesis
+stranger \textless{} computer was 7.47, and friend \textless{} stranger
+was 8.64. Furthermore, using Bayesian Cumulative Modeling we find that
+subjects were very consistent between their promises and the subsequent
+decisions they make. Although is more probable that our subjects keep
+their promises to any of the three partners, there is a proportion of
+transgressions to the computer, whose inference excludes zero with a
+95\% posterior probability. Also, subjects never broke the promise to
+their friends. Our results indicate that subjects are predominantly
+``nice people'' because they keep their promises even to partners
+without social closeness, however, if the subjects are not certain that
+their partner will also be a ``potential cooperator'', dishonesty
+emerges in the form of broken promises.
+\\
+\keywords{
+        Deception \and
+        Hierarchical Bayesian Models \and
+        Bayesian Cumulative Models \and
+        Social closeness \and
+        Promises \and
+    }
+
+\end{abstract}
+
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
 
@@
 been evidence that belonging to a social group has a positive effect on
-longevity, physical and mental health (Holt-Lunstad, 2018; Tough,
-Siegrist, \& Fekete, 2017). The relationship between social closeness
-and cooperation is key to the formation of large groups of individuals
+longevity, physical and mental health (Tough, Siegrist, and Fekete 2017;
+Holt-Lunstad 2018). The relationship between social closeness and
+cooperation is key to the formation of large groups of individuals
 without a genetic relationship, and such groups form the basis of
 communities, societies, and nations, arguably constituting one of the
-most fundamental conditions for human survival (Fehr \& Fischbacher,
-2003; Fehr \& Schurtenberger, 2018). An important requirement for
+most fundamental conditions for human survival (Fehr and Fischbacher
+2003; Fehr and Schurtenberger 2018). An important requirement for
 cooperation between individuals is communication. A meta-analysis of 45
 studies reported a large positive effect (\(d = 1.01\)) of communication
-in cooperation regardless of the communication medium (Balliet, 2010).
-In parallel, it is known that after communication sessions between
+in cooperation regardless of the communication medium (Balliet 2010). In
+parallel, it is known that after communication sessions between
 completely unknown individuals there is an increase in subjective social
-closeness (Aron, Melinat, Aron, Vallone, \& Bator, 1997). Thus, these
-findings suggest a positive relationship between communication,
-cooperation, and social closeness.
+closeness (Aron et al. 1997). Thus, these findings suggest a positive
+relationship between communication, cooperation, and social closeness.
 
@@
 between sender and recipient, it is believed that promises influence
-beliefs of the recipient, generating trust and cooperation (Charness \&
-Dufwenberg, 2006; Vanberg, 2008). However, there are situations where
+beliefs of the recipient, generating trust and cooperation (Charness and
+Dufwenberg 2006; Vanberg 2008). However, there are situations where
 trust is betrayed, promises are broken or people deceived. The General
@@
 surveyed responded that they have had sex with someone different to
-their partner while they are married (Smith, Davern, Freese, \& Hout,
-2018). In economic and social terms, the United Nations Organization has
-stressed that deception (corruption) has a global cost of at least 5
-percent of the annual gross domestic product (GDP), and it is a
-generator of conflict and instability in all nations (UN, 2018).
+their partner while they are married (Smith et al. 2018). In economic
+and social terms, the United Nations Organization has stressed that
+deception (corruption) has a global cost of at least 5 percent of the
+annual gross domestic product (GDP), and it is a generator of conflict
+and instability in all nations (UN 2018).
 
@@
 And, their consequences can be serious such as loss of the relationship,
-work or damage to reputation (DePaulo, Ansfield, Kirkendol, \& Boden,
-2004). In the laboratory, these transgressions to trust have been
-explicitly studied in experiments where subjects have incentives to lie
-or not keep their promises. However, the vast majority of these studies
-have been conducted in people who do NOT know each other (Baumgartner,
-Fischbacher, Feierabend, Lutz, \& Fehr, 2009; Baumgartner, Gianotti, \&
-Knoch, 2013; Charness \& Dufwenberg, 2006; Fischbacher \& Föllmi-Heusi,
-2013; Gneezy, 2005; Gneezy, Rockenbach, \& Serra-Garcia, 2013; Mazar,
-Amir, \& Ariely, 2008). Some studies address deception in close
-interpersonal relationships using self-report measurements, however,
-they have limitations due to social desirability bias (DePaulo et al.,
-2004; DePaulo \& Kashy, 1998) or rather explore the development of
-deception detection skills in same-sex friends (Anderson, DePaulo, \&
-Ansfield, 2002).
+work or damage to reputation (DePaulo et al. 2004). In the laboratory,
+these transgressions to trust have been explicitly studied in
+experiments where subjects have incentives to lie or not keep their
+promises. However, the vast majority of these studies have been
+conducted in people who do NOT know each other (Gneezy 2005; Gneezy,
+Rockenbach, and Serra-Garcia 2013; Baumgartner et al. 2009; Baumgartner,
+Gianotti, and Knoch 2013; Charness and Dufwenberg 2006; Mazar, Amir, and
+Ariely 2008; Fischbacher and Föllmi-Heusi 2013). Some studies address
+deception in close interpersonal relationships using self-report
+measurements, however, they have limitations due to social desirability
+bias (DePaulo and Kashy 1998; DePaulo et al. 2004) or rather explore the
+development of deception detection skills in same-sex friends (Anderson,
+DePaulo, and Ansfield 2002).
 
@@
 pointed out in the literature regarding keeping promises which are:
-instrumental and intrinsic (Baumgartner et al., 2009):
+instrumental and intrinsic (Baumgartner et al. 2009):
 
@@
   Finally, we will obtain two subsamples according to the cooperation
-  rate of the subjects as was done in another study (Baumgartner et al.,
+  rate of the subjects as was done in another study (Baumgartner et al.
   2009). However, what in the aforementioned study was classified as a
@@
 All subjects performed an adaptation of the trust game with promises,
-using hypothetical monetary rewards (Baumgartner et al., 2009). The
+using hypothetical monetary rewards (Baumgartner et al. 2009). The
 variation with respect to the original task is that in our experiment
@@
 the trustee. The task was programmed in PsychoPy2 version 1.84.2 (Peirce
-et al., 2019; Peirce, 2008) and consisted of 24 trials between two
+et al. 2019; Peirce 2008) and consisted of 24 trials between two
 players: trustee and investor. The trustee originally has 0 Mexican
@@
 degree of social closeness to each other, both responded the ``Inclusion
-of the Other in Self'' IOS scale (Aron et al., 1997) without observing
+of the Other in Self'' IOS scale (Aron et al. 1997) without observing
 their partner responses. The scale consists of seven pairs of circles
@@
 All models presented below were programmed in R via the \textbf{brms}
-package (Bürkner, 2017; R Core Team, 2019), which performs the inference
+package (Bürkner 2017; R Core Team 2019), which performs the inference
 using sampling by Markov chain Monte Carlo through \textbf{Stan} (Stan
-Development Team, 2018). For each model, the posteriors distributions of
+Development Team 2018). For each model, the posteriors distributions of
 all parameters were approximated with four chains of 2000 iterations
@@
 the nature of the phenomenon, which could be adequate for the current
-state of evidence in the problem we are studying (McElreath, 2018).
+state of evidence in the problem we are studying (McElreath 2018).
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig2-1}
+{\centering \includegraphics[width=0.8\linewidth]{behavioral-promises_files/figure-latex/fig2-1}
 
@@
 To assess social closeness, 30 (15 men) of our subjects and their
-friends responded to the IOS scale (Aron et al., 1997; Fareri \&
-Delgado, 2014; Sip, Smith, Porcelli, Kar, \& Delgado, 2015), which
-consists of seven pairs of circles that vary in the degree of overlap
-and represent the social closeness that an individual perceives with
-respect to the other. A Hierarchical and Cumulative Bayesian Model (See
-section: Commitment expressed in the promises), supports the hypothesis
-that there are no differences in subjective social closeness between
-subjects and their friends, with a posterior evidence ratio of 2.74 in
-its favor.
+friends responded to the IOS scale (Aron et al. 1997; Fareri and Delgado
+2014; Sip et al. 2015), which consists of seven pairs of circles that
+vary in the degree of overlap and represent the social closeness that an
+individual perceives with respect to the other. A Hierarchical and
+Cumulative Bayesian Model (See section: Commitment expressed in the
+promises), supports the hypothesis that there are no differences in
+subjective social closeness between subjects and their friends, with a
+posterior evidence ratio of 2.74 in its favor.
 
@@
 however, it also assumes that these variations belong to common
-population distributions (Gelman \& Hill, 2006).
+population distributions (Gelman and Hill 2006).
 
@@
 combination of the effects of each partner, transformed by its inverse
-link function \(\mathrm{logit}\) (Bürkner, 2017). In this model,
+link function \(\mathrm{logit}\) (Bürkner 2017). In this model,
 \(\beta\) and \(u\) are coefficients at the population level and
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig3-1}
+{\centering \includegraphics[width=0.8\linewidth]{behavioral-promises_files/figure-latex/fig3-1}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig4-1}
+{\centering \includegraphics[width=0.8\linewidth]{behavioral-promises_files/figure-latex/fig4-1}
 
@@
 helps us to identify if the model is sufficiently close to the process
-that generated the data (Lee \& Wagenmakers, 2014; Schad, Betancourt, \&
-Vasishth, 2019). It can be seen that there is a great correspondence
+that generated the data (Schad, Betancourt, and Vasishth 2019; Lee and
+Wagenmakers 2014). It can be seen that there is a great correspondence
 between the subject's responses and predictions of the model. Even in
@@
 
-{\centering \includegraphics[width=1\linewidth,height=1\textheight]{article_english_files/figure-latex/fig5-1}
+{\centering \includegraphics[width=1\linewidth,height=0.42\textheight]{behavioral-promises_files/figure-latex/fig5-1}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig6-1}
+{\centering \includegraphics[width=0.8\linewidth]{behavioral-promises_files/figure-latex/fig6-1}
 
@@
 
-\begin{table}[!h]
+\begin{table}[t]
 
 \caption{\label{tab:tabla}Posterior coefficients estimates}
-\centering
 \begin{tabular}{lrrrr}
@@
 into two according to the hierarchical clustering technique with Ward's
-method (Baumgartner et al., 2009). In this way they obtained two sets of
+method (Baumgartner et al. 2009). In this way they obtained two sets of
 participants that were different in their payment rates, despite the
@@
 Although it seems a similar result to that reported in that paper
-(Baumgartner et al., 2009), we explore the pattern of promises of both
+(Baumgartner et al. 2009), we explore the pattern of promises of both
 groups to determine if it was possible to classify our subjects as
@@
 latent variable \(\tilde{Y}\), for this case, the expressed commitment
-to pay back (Bürkner \& Vuorre, 2019). The degree to which the subjects
+to pay back (Bürkner and Vuorre 2019). The degree to which the subjects
 of the High group differ from the Low group, in normal standard
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{article_english_files/figure-latex/fig7-1}
+{\centering \includegraphics[width=0.8\linewidth]{behavioral-promises_files/figure-latex/fig7-1}
 
@@
 socially relevant partners. In previous studies, the participants remain
-anonymous during the course of the tasks (Baumgartner et al., 2009),
+anonymous during the course of the tasks (Baumgartner et al. 2009),
 their measurements to evaluate transgressions are self-reported (DePaulo
-et al., 2004; DePaulo \& Kashy, 1998), they do not directly quantify the
-breaking of promises (Charness \& Dufwenberg, 2006; Vanberg, 2008), or
-as we will discuss later, they use heterogeneous measures of social
-closeness (Glaeser, Laibson, Sceinkman, \& Soutter, 2000). Our
-experiment is the first one to include a partner without social
-closeness (computer). Our data suggest that the mere fact of considering
-that subjects play with a human diminishes the probability of breaking
-the promise. It is more likely to break the promise to the computer than
-to the stranger, even though that partner was not known. Also, null
-social closeness is important because it allows us to explore the
-intrinsic motivation to keep the promises. If humans keep their word
-because it is morally correct, we would anticipate that the probability
-of breaking a promise was very low in the three partners and,
-particularly, the inference regarding the probability of breaking the
-promise to the computer would include zero. However, we found that,
-although low, the probability was greater than zero, which provides
-evidence that seems to contradict, at least in degree, the hypothesis of
-intrinsic motivation. We cannot exclude the possibility that the
-subjects keep promises mainly due to moral motivation because, even in
-the case of the computer, the subjects kept a large proportion. We can,
-however, exclude that this is their only motivation.
+and Kashy 1998; DePaulo et al. 2004), they do not directly quantify the
+breaking of promises (Vanberg 2008; Charness and Dufwenberg 2006), or as
+we will discuss later, they use heterogeneous measures of social
+closeness (Glaeser et al. 2000). Our experiment is the first one to
+include a partner without social closeness (computer). Our data suggest
+that the mere fact of considering that subjects play with a human
+diminishes the probability of breaking the promise. It is more likely to
+break the promise to the computer than to the stranger, even though that
+partner was not known. Also, null social closeness is important because
+it allows us to explore the intrinsic motivation to keep the promises.
+If humans keep their word because it is morally correct, we would
+anticipate that the probability of breaking a promise was very low in
+the three partners and, particularly, the inference regarding the
+probability of breaking the promise to the computer would include zero.
+However, we found that, although low, the probability was greater than
+zero, which provides evidence that seems to contradict, at least in
+degree, the hypothesis of intrinsic motivation. We cannot exclude the
+possibility that the subjects keep promises mainly due to moral
+motivation because, even in the case of the computer, the subjects kept
+a large proportion. We can, however, exclude that this is their only
+motivation.
 
 On the other hand, high social closeness allows us to explore the
-instrumental motivation to keep promises (Baumgartner et al., 2009). In
+instrumental motivation to keep promises (Baumgartner et al. 2009). In
 our study, it was more likely to break the promise to the stranger than
@@
 that other people cooperate at high levels also induces high levels of
-cooperation (Fehr \& Schurtenberger, 2018). Thus, the lack of certainty
+cooperation (Fehr and Schurtenberger 2018). Thus, the lack of certainty
 regarding the decisions that the computer would make could explain the
@@
 and compared to another group of new different subjects for each trial
-(strangers) (Croson, 1996). In the condition of partners the cooperation
+(strangers) (Croson 1996). In the condition of partners the cooperation
 was greater because it is a stable group compared to the group of
@@
 Another study showed an increase in cooperation in a trust game when
-individuals were socially close (Glaeser et al., 2000). In this study,
+individuals were socially close (Glaeser et al. 2000). In this study,
 subjects knew each other and the researchers carefully measured several
@@
 their friends was the same. Results of the two mentioned studies also
-found that social closeness enhance cooperation (Croson, 1996; Glaeser
-et al., 2000), in the future would be valuable to homogenize both the
+found that social closeness enhance cooperation (Croson 1996; Glaeser et
+al. 2000), in the future would be valuable to homogenize both the
 performed tasks and the statistical procedure used, to establish
@@
 with unbalanced data, include categorical and/or numerical predictors,
-explicitly incorporate individual variability, among others (Bürkner,
-2017; Gelman \& Hill, 2006; McElreath, 2018; Vuorre \& Bolger, 2018).
+explicitly incorporate individual variability, among others (Vuorre and
+Bolger 2018; Gelman and Hill 2006; McElreath 2018; Bürkner 2017).
 
@@
 information for the estimation of population effects, which, if not
-considered, would lead to inaccurate inferences(Bürkner, 2017; Gelman \&
-Hill, 2006; McElreath, 2018).
+considered, would lead to inaccurate inferences(Bürkner 2017; Gelman and
+Hill 2006; McElreath 2018).
 
@@
 data with methods that assume that observations are metric can lead to
-serious inference errors (Liddell \& Kruschke, 2018). The Cumulative
+serious inference errors (Liddell and Kruschke 2018). The Cumulative
 Models assumes that the observed responses come from the categorization
-of a continuous latent variable (Bürkner \& Vuorre, 2019). In our study,
+of a continuous latent variable (Bürkner and Vuorre 2019). In our study,
 we could identify that groups with different payment proportions, which
 in other studies have been called ``dishonest'' and
-``honest''(Baumgartner et al., 2009, 2013), differ in the commitment
-they express through their promises. Considering that the tools to
-perform the Cumulative Models are relatively recent, in future studies,
-it would be valuable to also use the new alternatives for inference.
+``honest''(Baumgartner et al. 2009; Baumgartner, Gianotti, and Knoch
+2013), differ in the commitment they express through their promises.
+Considering that the tools to perform the Cumulative Models are
+relatively recent, in future studies, it would be valuable to also use
+the new alternatives for inference.
 
@@
 versus post hoc, are not factors that affect the Bayesian approach
-(Dienes, 2011). In Bayesian inference, hypothesis testing makes formal
+(Dienes 2011). In Bayesian inference, hypothesis testing makes formal
 use of probability to express the plausibility of theories, and in our
@@
 that there is more loss aversion when subjects have real monetary
-rewards compared to hypothetical in a risk task (Xu et al., 2016).
+rewards compared to hypothetical in a risk task (Xu et al. 2016).
 However, other works do not report differences between the use of both
 types of rewards in self-control, temporal and social discount tasks
-(Johnson \& Bickel, 2006; Locey, Jones, \& Rachlin, 2011; Rachlin \&
-Jones, 2006). Likewise, it can be argued that our results have
-theoretical congruence (Fehr \& Schurtenberger, 2018) and are in the
-same direction as other works that use real money (Croson, 1996; Glaeser
-et al., 2000), thus, there are not many reasons to expect that other
+(Locey, Jones, and Rachlin 2011; Johnson and Bickel 2006; Rachlin and
+Jones 2006). Likewise, it can be argued that our results have
+theoretical congruence (Fehr and Schurtenberger 2018) and are in the
+same direction as other works that use real money (Croson 1996; Glaeser
+et al. 2000), thus, there are not many reasons to expect that other
 types of rewards would modify our results. Another possible limitation
@@
 reducing contaminant sources and increasing internal validity (Maxwell,
-Delaney, \& Ken, 2018), to have more clarity regarding the difference in
+Delaney, and Ken 2018), to have more clarity regarding the difference in
 the intrinsic and instrumental motivations, the studies could benefit
@@
 \leavevmode\hypertarget{ref-Anderson2002}{}%
-Anderson, D. E., DePaulo, B. M., \& Ansfield, M. E. (2002). The
-development of deception detection skill: A longitudinal study of
-same-sex friends. \emph{Personality and Social Psychology Bulletin},
-\emph{28}(4), 536--545. \url{https://doi.org/10.1177/0146167202287010}
+Anderson, D. Eric, Bella M. DePaulo, and Matthew E. Ansfield. 2002.
+``The development of deception detection skill: A longitudinal study of
+same-sex friends.'' \emph{Personality and Social Psychology Bulletin} 28
+(4): 536--45. \url{https://doi.org/10.1177/0146167202287010}.
 
 \leavevmode\hypertarget{ref-Aron1997}{}%
-Aron, A., Melinat, E., Aron, E. N., Vallone, R. D., \& Bator, R. J.
-(1997). The experimental generation of interpersonal closeness: A
-procedure and some preliminary findings. \emph{Personality and Social
-Psychology Bulletin}, \emph{23}(4), 363--377.
-\url{https://doi.org/10.1177/0146167297234003}
+Aron, Arthur, Edward Melinat, Elaine N. Aron, Robert Darrin Vallone, and
+Renee J. Bator. 1997. ``The experimental generation of interpersonal
+closeness: A procedure and some preliminary findings.''
+\emph{Personality and Social Psychology Bulletin} 23 (4): 363--77.
+\url{https://doi.org/10.1177/0146167297234003}.
 
 \leavevmode\hypertarget{ref-Balliet2010}{}%
-Balliet, D. (2010). Communication and cooperation in social dilemmas: A
-meta-analytic review. \emph{Journal of Conflict Resolution},
-\emph{54}(1), 39--57. \url{https://doi.org/10.1177/0022002709352443}
+Balliet, Daniel. 2010. ``Communication and cooperation in social
+dilemmas: A meta-analytic review.'' \emph{Journal of Conflict
+Resolution} 54 (1): 39--57.
+\url{https://doi.org/10.1177/0022002709352443}.
 
 \leavevmode\hypertarget{ref-Baumgartner2009}{}%
-Baumgartner, T., Fischbacher, U., Feierabend, A., Lutz, K., \& Fehr, E.
-(2009). The Neural Circuitry of a Broken Promise. \emph{Neuron},
-\emph{64}(5), 756--770.
-\url{https://doi.org/10.1016/j.neuron.2009.11.017}
+Baumgartner, Thomas, Urs Fischbacher, Anja Feierabend, Kai Lutz, and
+Ernst Fehr. 2009. ``The Neural Circuitry of a Broken Promise.''
+\emph{Neuron} 64 (5). Elsevier Ltd: 756--70.
+\url{https://doi.org/10.1016/j.neuron.2009.11.017}.
 
 \leavevmode\hypertarget{ref-Baumgartner2013}{}%
-Baumgartner, T., Gianotti, L. R. R., \& Knoch, D. (2013). Who is honest
-and why: Baseline activation in anterior insula predicts
-inter-individual differences in deceptive behavior. \emph{Biological
-Psychology}, \emph{94}(1), 192--197.
-\url{https://doi.org/10.1016/j.biopsycho.2013.05.018}
+Baumgartner, Thomas, Lorena R R Gianotti, and Daria Knoch. 2013. ``Who
+is honest and why: Baseline activation in anterior insula predicts
+inter-individual differences in deceptive behavior.'' \emph{Biological
+Psychology} 94 (1). Elsevier B.V.: 192--97.
+\url{https://doi.org/10.1016/j.biopsycho.2013.05.018}.
 
 \leavevmode\hypertarget{ref-Burkner2017}{}%
-Bürkner, P.-C. (2017). brms : An R Package for Bayesian Multilevel
-Models Using Stan. \emph{Journal of Statistical Software}, \emph{80}(1).
-\url{https://doi.org/10.18637/jss.v080.i01}
+Bürkner, Paul-Christian. 2017. ``brms : An R Package for Bayesian
+Multilevel Models Using Stan.'' \emph{Journal of Statistical Software}
+80 (1). \url{https://doi.org/10.18637/jss.v080.i01}.
 
 \leavevmode\hypertarget{ref-Burkner2019}{}%
-Bürkner, P.-C., \& Vuorre, M. (2019). Ordinal Regression Models in
-Psychology: A Tutorial. \emph{Advances in Methods and Practices in
-Psychological Science}, \emph{2}(1), 77--101.
-\url{https://doi.org/10.1177/2515245918823199}
+Bürkner, Paul-Christian, and Matti Vuorre. 2019. ``Ordinal Regression
+Models in Psychology: A Tutorial.'' \emph{Advances in Methods and
+Practices in Psychological Science} 2 (1): 77--101.
+\url{https://doi.org/10.1177/2515245918823199}.
 
 \leavevmode\hypertarget{ref-Charness2006}{}%
-Charness, G., \& Dufwenberg, M. (2006). Promises and partnership.
-\emph{Econometrica}, \emph{74}(6), 1579--1601.
-\url{https://doi.org/10.1111/j.1468-0262.2006.00719.x}
+Charness, Gary, and Martin Dufwenberg. 2006. ``Promises and
+partnership.'' \emph{Econometrica} 74 (6): 1579--1601.
+\url{https://doi.org/10.1111/j.1468-0262.2006.00719.x}.
 
 \leavevmode\hypertarget{ref-Croson1996}{}%
-Croson, R. T. (1996). Partners and strangers revisited. \emph{Economics
-Letters}, \emph{53}(1), 25--32.
-\url{https://doi.org/10.1016/S0165-1765(97)82136-2}
+Croson, Rachel T.A. 1996. ``Partners and strangers revisited.''
+\emph{Economics Letters} 53 (1): 25--32.
+\url{https://doi.org/10.1016/S0165-1765(97)82136-2}.
 
 \leavevmode\hypertarget{ref-DePaulo2004}{}%
-DePaulo, B. M., Ansfield, M. E., Kirkendol, S. E., \& Boden, J. M.
-(2004). Serious Lies. \emph{Basic \& Applied Social Psychology},
-\emph{26}(2/3), 147--167.
-\url{https://doi.org/10.1207/s15324834basp2602\&3_4}
+DePaulo, Bella M, Matthew E Ansfield, Susan E Kirkendol, and Joseph M
+Boden. 2004. ``Serious Lies.'' \emph{Basic \& Applied Social Psychology}
+26 (2/3): 147--67. \url{https://doi.org/10.1207/s15324834basp2602\&3_4}.
 
 \leavevmode\hypertarget{ref-DePaulo1998}{}%
-DePaulo, B. M., \& Kashy, D. A. (1998). Everyday Lies in Close and
-Casual Relationships. \emph{Journal of Personality and Social
-Psychology}, \emph{74}(1), 63--79.
-\url{https://doi.org/10.1037/0022-3514.74.1.63}
+DePaulo, Bella M., and Deborah A. Kashy. 1998. ``Everyday Lies in Close
+and Casual Relationships.'' \emph{Journal of Personality and Social
+Psychology} 74 (1): 63--79.
+\url{https://doi.org/10.1037/0022-3514.74.1.63}.
 
 \leavevmode\hypertarget{ref-Dienes2011}{}%
-Dienes, Z. (2011). Bayesian versus orthodox statistics: Which side are
-you on? \emph{Perspectives on Psychological Science}, \emph{6}(3),
-274--290. \url{https://doi.org/10.1177/1745691611406920}
+Dienes, Zoltan. 2011. ``Bayesian versus orthodox statistics: Which side
+are you on?'' \emph{Perspectives on Psychological Science} 6 (3):
+274--90. \url{https://doi.org/10.1177/1745691611406920}.
 
 \leavevmode\hypertarget{ref-Fareri2014}{}%
-Fareri, D. S., \& Delgado, M. R. (2014). Differential reward responses
-during competition against in- and out-of-network others. \emph{Social
-Cognitive and Affective Neuroscience}, \emph{9}(4), 412--420.
-\url{https://doi.org/10.1093/scan/nst006}
+Fareri, Dominic S., and Mauricio R. Delgado. 2014. ``Differential reward
+responses during competition against in- and out-of-network others.''
+\emph{Social Cognitive and Affective Neuroscience} 9 (4): 412--20.
+\url{https://doi.org/10.1093/scan/nst006}.
 
 \leavevmode\hypertarget{ref-Fehr2003}{}%
-Fehr, E., \& Fischbacher, U. (2003). The nature of human altruism.
-\emph{Nature}, \emph{425}(6960), 785--791.
-\url{https://doi.org/10.1038/nature02043}
+Fehr, Ernst, and Urs Fischbacher. 2003. ``The nature of human
+altruism.'' \emph{Nature} 425 (6960). Nature Publishing Group: 785--91.
+\url{https://doi.org/10.1038/nature02043}.
 
 \leavevmode\hypertarget{ref-Fehr2018}{}%
-Fehr, E., \& Schurtenberger, I. (2018). Normative foundations of human
-cooperation review-article. \emph{Nature Human Behaviour}, \emph{2}(7),
-458--468. \url{https://doi.org/10.1038/s41562-018-0385-5}
+Fehr, Ernst, and Ivo Schurtenberger. 2018. ``Normative foundations of
+human cooperation review-article.'' \emph{Nature Human Behaviour} 2 (7).
+Springer US: 458--68. \url{https://doi.org/10.1038/s41562-018-0385-5}.
 
 \leavevmode\hypertarget{ref-Fischbacher2013a}{}%
-Fischbacher, U., \& Föllmi-Heusi, F. (2013). Lies in disguise-an
-experimental study on cheating. \emph{Journal of the European Economic
-Association}, \emph{11}(3), 525--547.
-\url{https://doi.org/10.1111/jeea.12014}
+Fischbacher, Urs, and Franziska Föllmi-Heusi. 2013. ``Lies in
+disguise-an experimental study on cheating.'' \emph{Journal of the
+European Economic Association} 11 (3): 525--47.
+\url{https://doi.org/10.1111/jeea.12014}.
 
 \leavevmode\hypertarget{ref-Gelman2006}{}%
-Gelman, A., \& Hill, J. (2006). \emph{Data analysis using regression and
-multilevel/hierarchical models.} (p. 651).
-\url{https://doi.org/10.2277/0521867061}
+Gelman, Andrew, and Jennifer Hill. 2006. \emph{Data analysis using
+regression and multilevel/hierarchical models.}
+\url{https://doi.org/10.2277/0521867061}.
 
 \leavevmode\hypertarget{ref-Glaeser2000}{}%
-Glaeser, E., Laibson, D., Sceinkman, J., \& Soutter, C. (2000).
-Measuring Trust. \emph{The Quartely Journal of Economics},
-\emph{115}(3), 811--846.
+Glaeser, Edward, David Laibson, Jose Sceinkman, and Christine Soutter.
+2000. ``Measuring Trust.'' \emph{The Quartely Journal of Economics} 115
+(3): 811--46.
 
 \leavevmode\hypertarget{ref-Gneezy2005}{}%
-Gneezy, U. (2005). Deception: The role of consequences. \emph{American
-Economic Review}, \emph{95}(1), 384--394.
-\url{https://doi.org/10.1257/0002828053828662}
+Gneezy, Uri. 2005. ``Deception: The role of consequences.''
+\emph{American Economic Review} 95 (1): 384--94.
+\url{https://doi.org/10.1257/0002828053828662}.
 
 \leavevmode\hypertarget{ref-Gneezy2013}{}%
-Gneezy, U., Rockenbach, B., \& Serra-Garcia, M. (2013). Measuring lying
-aversion. \emph{Journal of Economic Behavior and Organization},
-\emph{93}, 293--300. \url{https://doi.org/10.1016/j.jebo.2013.03.025}
+Gneezy, Uri, Bettina Rockenbach, and Marta Serra-Garcia. 2013.
+``Measuring lying aversion.'' \emph{Journal of Economic Behavior and
+Organization} 93. Elsevier B.V.: 293--300.
+\url{https://doi.org/10.1016/j.jebo.2013.03.025}.
 
 \leavevmode\hypertarget{ref-Holt-Lunstad2018}{}%
-Holt-Lunstad, J. (2018). Why Social Relationships are Important for
-Physical Health: A Systems Approach to Understanding and Modifying Risk
-and Protection. \emph{Ssrn}, (October 2017), 1--22.
-\url{https://doi.org/10.1146/annurev-psych-122216-011902}
+Holt-Lunstad, Julianne. 2018. ``Why Social Relationships are Important
+for Physical Health: A Systems Approach to Understanding and Modifying
+Risk and Protection.'' \emph{Ssrn}, no. October 2017: 1--22.
+\url{https://doi.org/10.1146/annurev-psych-122216-011902}.
 
 \leavevmode\hypertarget{ref-Johnson2006}{}%
-Johnson, M. W., \& Bickel, W. K. (2006). Within-subject comparison of
-real and hypothetical money rewards in delay discounting. \emph{Journal
-of the Experimental Analysis of Behavior}, \emph{77}(2), 129--146.
-\url{https://doi.org/10.1901/jeab.2002.77-129}
+Johnson, Matthew W, and Warren K Bickel. 2006. ``Within-subject
+comparison of real and hypothetical money rewards in delay
+discounting.'' \emph{Journal of the Experimental Analysis of Behavior}
+77 (2): 129--46. \url{https://doi.org/10.1901/jeab.2002.77-129}.
 
 \leavevmode\hypertarget{ref-Lee2014}{}%
-Lee, M. D., \& Wagenmakers, E.-J. (2014). \emph{Bayesian Cognitive
-Modeling}. \url{https://doi.org/10.1017/cbo9781139087759}
+Lee, Michael D., and Eric-Jan Wagenmakers. 2014. \emph{Bayesian
+Cognitive Modeling}. \url{https://doi.org/10.1017/cbo9781139087759}.
 
 \leavevmode\hypertarget{ref-Liddell2018}{}%
-Liddell, T. M., \& Kruschke, J. K. (2018). Analyzing ordinal data with
-metric models: What could possibly go wrong? \emph{Journal of
-Experimental Social Psychology}, \emph{79}(November 2017), 328--348.
-\url{https://doi.org/10.1016/j.jesp.2018.08.009}
+Liddell, Torrin M., and John K. Kruschke. 2018. ``Analyzing ordinal data
+with metric models: What could possibly go wrong?'' \emph{Journal of
+Experimental Social Psychology} 79 (November 2017). Elsevier: 328--48.
+\url{https://doi.org/10.1016/j.jesp.2018.08.009}.
 
 \leavevmode\hypertarget{ref-Locey2011}{}%
-Locey, M. L., Jones, B. A., \& Rachlin, H. (2011). Real and hypothetical
-rewards in self-control and social discounting. \emph{Judgment and
-Decision Making}, \emph{6}(6), 552--564.
+Locey, Matthew L, Bryan A Jones, and Howard Rachlin. 2011. ``Real and
+hypothetical rewards in self-control and social discounting.''
+\emph{Judgment and Decision Making} 6 (6): 552--64.
 
 \leavevmode\hypertarget{ref-Maxwell2018}{}%
-Maxwell, S. E., Delaney, H. D., \& Ken, K. (2018). \emph{Designing
-experiments and analyzing data: a model comparison perspective} (3rd
-edition, pp. 611--612). New York: Routledge.
+Maxwell, Scott E., Harold D. Delaney, and Kelley Ken. 2018.
+\emph{Designing experiments and analyzing data: a model comparison
+perspective}. 3rd edition. New York: Routledge.
 
 \leavevmode\hypertarget{ref-Mazar2008}{}%
-Mazar, N., Amir, O., \& Ariely, D. (2008). The Dishonesty of Honest
-People: A Theory of Self-Concept Maintenance. \emph{Journal of Marketing
-Research}, \emph{45}(6), 633--644.
-\url{https://doi.org/10.1509/jmkr.45.6.633}
+Mazar, Nina, On Amir, and Dan Ariely. 2008. ``The Dishonesty of Honest
+People: A Theory of Self-Concept Maintenance.'' \emph{Journal of
+Marketing Research} 45 (6): 633--44.
+\url{https://doi.org/10.1509/jmkr.45.6.633}.
 
 \leavevmode\hypertarget{ref-McElreath2018}{}%
-McElreath, R. (2018). \emph{Statistical rethinking: A bayesian course
-with examples in R and stan}.
-\url{https://doi.org/10.1201/9781315372495}
+McElreath, Richard. 2018. \emph{Statistical rethinking: A bayesian
+course with examples in R and stan}.
+\url{https://doi.org/10.1201/9781315372495}.
 
 \leavevmode\hypertarget{ref-Peirce2019}{}%
-Peirce, J., Gray, J. R., Simpson, S., MacAskill, M., Höchenberger, R.,
-Sogo, H., \ldots{} Lindeløv, J. K. (2019). PsychoPy2: Experiments in
-behavior made easy. \emph{Behavior Research Methods}, \emph{51}(1),
-195--203. \url{https://doi.org/10.3758/s13428-018-01193-y}
+Peirce, Jonathan, Jeremy R. Gray, Sol Simpson, Michael MacAskill,
+Richard Höchenberger, Hiroyuki Sogo, Erik Kastman, and Jonas Kristoffer
+Lindeløv. 2019. ``PsychoPy2: Experiments in behavior made easy.''
+\emph{Behavior Research Methods} 51 (1): 195--203.
+\url{https://doi.org/10.3758/s13428-018-01193-y}.
 
 \leavevmode\hypertarget{ref-Peirce2008}{}%
-Peirce, J. W. (2008). Generating stimuli for neuroscience using
-PsychoPy. \emph{Frontiers in Neuroinformatics}, \emph{2}.
-\url{https://doi.org/10.3389/neuro.11.010.2008}
+Peirce, Jonathan W. 2008. ``Generating stimuli for neuroscience using
+PsychoPy.'' \emph{Frontiers in Neuroinformatics} 2.
+\url{https://doi.org/10.3389/neuro.11.010.2008}.
 
 \leavevmode\hypertarget{ref-Rachlin2006}{}%
-Rachlin, H., \& Jones, B. (2006). Social Discounting.
-\emph{Psychological Science}, \emph{17}(4), 283--286.
+Rachlin, Howard, and Bryan Jones. 2006. ``Social Discounting.''
+\emph{Psychological Science} 17 (4): 283--86.
 
 \leavevmode\hypertarget{ref-R2019}{}%
-R Core Team. (2019). \emph{R: A language and environment for statistical
-computing}. Vienna, Austria: R Foundation for Statistical Computing.
-Retrieved from \url{https://www.R-project.org/}
+R Core Team. 2019. \emph{R: A Language and Environment for Statistical
+Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}.
 
 \leavevmode\hypertarget{ref-Schad2019}{}%
-Schad, D., Betancourt, M., \& Vasishth, S. (2019). Toward a principled
-Bayesian workflow in cognitive science. Retrieved from
-\url{osf.io/b2vx9}
+Schad, Daniel, Michael Betancourt, and Shravan Vasishth. 2019. ``Toward
+a principled Bayesian workflow in cognitive science.''
+\url{osf.io/b2vx9}.
 
 \leavevmode\hypertarget{ref-Sip2015}{}%
-Sip, K. E., Smith, D. V., Porcelli, A. J., Kar, K., \& Delgado, M. R.
-(2015). Social closeness and feedback modulate susceptibility to the
-framing effect. \emph{Social Neuroscience}, \emph{10}(1), 35--45.
-\url{https://doi.org/10.1080/17470919.2014.944316}
+Sip, Kamila E., David V. Smith, Anthony J. Porcelli, Kohitij Kar, and
+Mauricio R. Delgado. 2015. ``Social closeness and feedback modulate
+susceptibility to the framing effect.'' \emph{Social Neuroscience} 10
+(1): 35--45. \url{https://doi.org/10.1080/17470919.2014.944316}.
 
 \leavevmode\hypertarget{ref-GSS2018}{}%
-Smith, T., Davern, M., Freese, J., \& Hout, M. (2018). GSS Data Explorer
-\textbar{} NORC at the University of Chicago. Retrieved from
-\url{https://gssdataexplorer.norc.org/variables/5067/vshow}
+Smith, Tom, Michael Davern, Jeremy Freese, and Michael Hout. 2018. ``GSS
+Data Explorer \textbar{} NORC at the University of Chicago.''
+\url{https://gssdataexplorer.norc.org/variables/5067/vshow}.
 
 \leavevmode\hypertarget{ref-Rstan2018}{}%
-Stan Development Team. (2018). RStan: The R interface to Stan. Retrieved
-from \url{http://mc-stan.org/}
+Stan Development Team. 2018. ``RStan: The R Interface to Stan.''
+\url{http://mc-stan.org/}.
 
 \leavevmode\hypertarget{ref-Tough2017}{}%
-Tough, H., Siegrist, J., \& Fekete, C. (2017). Social relationships,
-mental health and wellbeing in physical disability: A systematic review.
-\emph{BMC Public Health}, \emph{17}(1), 1--18.
-\url{https://doi.org/10.1186/s12889-017-4308-6}
+Tough, Hannah, Johannes Siegrist, and Christine Fekete. 2017. ``Social
+relationships, mental health and wellbeing in physical disability: A
+systematic review.'' \emph{BMC Public Health} 17 (1). BMC Public Health:
+1--18. \url{https://doi.org/10.1186/s12889-017-4308-6}.
 
 \leavevmode\hypertarget{ref-UN2018}{}%
-UN. (2018). Global Cost of Corruption at Least 5 Per Cent of World Gross
+UN. 2018. ``Global Cost of Corruption at Least 5 Per Cent of World Gross
 Domestic Product, Secretary-General Tells Security Council, Citing World
-Economic Forum Data. Retrieved from
-\url{https://www.un.org/press/en/2018/sc13493.doc.htm}
+Economic Forum Data.''
+\url{https://www.un.org/press/en/2018/sc13493.doc.htm}.
 
 \leavevmode\hypertarget{ref-Vanberg2008}{}%
-Vanberg, C. (2008). Why Do People Keep Their Promises? An Experimental
-Test of Two Explanations1. \emph{Econometrica}, \emph{76}(6),
-1467--1480. \url{https://doi.org/10.3982/ECTA7673}
+Vanberg, Christoph. 2008. ``Why Do People Keep Their Promises? An
+Experimental Test of Two Explanations1.'' \emph{Econometrica} 76 (6):
+1467--80. \url{https://doi.org/10.3982/ECTA7673}.
 
 \leavevmode\hypertarget{ref-Vuorre2018}{}%
-Vuorre, M., \& Bolger, N. (2018). Within-subject mediation analysis for
-experimental data in cognitive psychology and neuroscience.
-\emph{Behavior Research Methods}, \emph{50}(5), 2125--2143.
-\url{https://doi.org/10.3758/s13428-017-0980-9}
+Vuorre, Matti, and Niall Bolger. 2018. ``Within-subject mediation
+analysis for experimental data in cognitive psychology and
+neuroscience.'' \emph{Behavior Research Methods} 50 (5): 2125--43.
+\url{https://doi.org/10.3758/s13428-017-0980-9}.
 
 \leavevmode\hypertarget{ref-Xu2016}{}%
-Xu, S., Pan, Y., Wang, Y., Spaeth, A. M., Qu, Z., \& Rao, H. (2016).
-Real and hypothetical monetary rewards modulate risk taking in the
-brain. \emph{Scientific Reports}, \emph{6}.
-\url{https://doi.org/10.1038/srep29520}
+Xu, Sihua, Yu Pan, You Wang, Andrea M Spaeth, Zhe Qu, and Hengyi Rao.
+2016. ``Real and hypothetical monetary rewards modulate risk taking in
+the brain.'' \emph{Scientific Reports} 6.
+\url{https://doi.org/10.1038/srep29520}.
+
+\bibliographystyle{spbasic}
+\bibliography{bibliography.bib}
 

### 2019-08-09 behavioral-promises/behavioral-promises.tex
Author correction
authors

@@
 
-\author{  Said Jiménez \and  Kamila E. Sip \and  Roberto E. Mercadillo \and  Diego Angeles-Valdez \and  Jairo Muñoz-Delgado \and  Juan J. Sánchez-Sosa \and  Eduardo A. Garza-Villarreal \and  }
+\author{  Said Jiménez  \and  Roberto E. Mercadillo \and  Diego Angeles-Valdez \and  Jairo Muñoz-Delgado \and  Juan J. Sánchez-Sosa \and  Eduardo A. Garza-Villarreal \and  }
 
@@
  %           \emph{Present address:} of F. Author  %  if needed
-    \and
-        Kamila E. Sip \at
-     Institute for Neuroleadership \\
-     \email{\href{mailto:kami.sip@gmail.com}{\nolinkurl{kami.sip@gmail.com}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-        Roberto E. Mercadillo \at
-     Department of Biology, Universidad Autónoma Metropolitana (UAM) \\
-     \email{\href{mailto:emmanuele.mercadillo@gmail.com}{\nolinkurl{emmanuele.mercadillo@gmail.com}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-        Diego Angeles-Valdez \at
-     Institute of Neurobiology, UNAM \\
-     \email{\href{mailto:anglsd_20@hotmail.com}{\nolinkurl{anglsd\_20@hotmail.com}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-        Jairo Muñoz-Delgado \at
-     Investigaciones en Neurociencias, INPRF \\
-     \email{\href{mailto:munozd460@gmail.com}{\nolinkurl{munozd460@gmail.com}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-        Juan J. Sánchez-Sosa \at
-     Department of Psychology, National University of México (UNAM) \\
-     \email{\href{mailto:jujosaso@gmail.com}{\nolinkurl{jujosaso@gmail.com}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-        Eduardo A. Garza-Villarreal \at
-     Institute of Neurobiology, UNAM \\
-     \email{\href{mailto:egarza@gmail.com}{\nolinkurl{egarza@gmail.com}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
     }

### 2019-08-14 behavioral-promises/behavioral-promises.Rmd
Update manuscript

@@
 abstract: |
-  Promises increase cooperation between non-genetically related individuals, however, lies and betrayals occur daily in close social relationships.
-Despite this, the effect of social closeness on the decision to keep or break a promise has not been studied.
-We conducted an experiment in which subjects could freely decide if they broke or kept their promise to three partners with different levels of social closeness: null (computer), low (strange) and high (friend).
-If subjects keep their word with the computer, it provides evidence in favor of intrinsic motivation (comply to do the correct thing), otherwise extrinsic motivation would be supported (comply to facilitate future cooperation).
-Using Hierarchical Bayesian Modeling, we find that if social closeness increases, the probability of breaking promises decreases monotonically, the evidence ratio in favor to the hypothesis stranger < computer was 7.47, and friend < stranger was 8.64.
-Furthermore, using Bayesian Cumulative Modeling we find that subjects were very consistent between their promises and the subsequent decisions they make.
-Although is more probable that our subjects keep their promises to any of the three partners, there is a proportion of transgressions to the computer, whose inference excludes zero with a 95% posterior probability.
-Also, subjects never broke the promise to their friends.
-Our results indicate that subjects are predominantly "nice people" because they keep their promises even to partners without social closeness, however, if the subjects are not certain that their partner will also be a "potential cooperator", dishonesty emerges in the form of broken promises.
+  Promises increase cooperation between non-genetically related individuals, whereas lies and betrayals occur daily even in close social relationships.
+Despite this, the effect of social closeness on the decision to keep or break a promise has not been thoroughly studied.
+We conducted an experiment in which subjects could freely decide if they broke or kept a promise to three partners with different levels of social closeness: null (computer), low (strange) and high (friend).
+If subjects kept their word with the computer, it provides evidence in favor of intrinsic motivation (comply to do the correct thing), while extrinsic motivation would be supported (comply to facilitate future cooperation).
+Using Hierarchical Bayesian Modeling, we found that as social closeness increases, the probability of breaking promises decreases monotonically.
+The evidence ratio in favor of the hypothesis stranger < computer was 7.47, and friend < stranger was 8.64.
+Furthermore, using Bayesian Cumulative Modeling we found that subjects were very consistent between their promises and their choices.
+Although it was more probable that our subjects kept their promises to any of the three partners, there was a proportion of transgressions to the computer, whose inference excludes zero with a 95% posterior probability.
+Also, our subjects never broke the promise to their friends.
+Our results suggest that subjects were predominantly "nice people" because they kept their promises even to partners without social closeness.
+However, if the subjects were not certain that their partner will also be a "potential cooperator", dishonesty emerged in the form of broken promises.
 
@@
 
-Human are social animals and we get survival advantages from being such.
-Historically, belonging to a social group has provided protection and guaranteed access to resources such as food, and currently, there has been evidence that belonging to a social group has a positive effect on longevity, physical and mental health [@Tough2017; @Holt-Lunstad2018].
-The relationship between social closeness and cooperation is key to the formation of large groups of individuals without a genetic relationship, and such groups form the basis of communities, societies, and nations, arguably constituting one of the most fundamental conditions for human survival [@Fehr2003; @Fehr2018].
-An important requirement for cooperation between individuals is communication.
-A meta-analysis of 45 studies reported a large positive effect ($d =  1.01$) of communication in cooperation regardless of the communication medium [@Balliet2010].
-In parallel, it is known that after communication sessions between completely unknown individuals there is an increase in subjective social closeness [@Aron1997].
-Thus, these findings suggest a positive relationship between communication, cooperation, and social closeness.
+Humans are social animals and we obtain survival advantages from proper socialization.
+Historically, belonging to a social group has provided protection and guaranteed access to resources such as food, and currently, there is evidence that belonging to a social group has a positive effect on longevity, physical and mental health [@Tough2017; @Holt-Lunstad2018].
+The interaction between social closeness and cooperation seems to be a key feature to the formation of large groups of individuals without a genetic relationship, and such groups form the basis of communities, societies, and nations, arguably constituting one of the most fundamental conditions for human survival [@Fehr2003; @Fehr2018].
+A recent meta-analysis showed that communication, regardless of the medium, is the most important element for cooperation between individuals [@Balliet2010].
+In parallel, there is evidence that following communication sessions between completely unknown individuals, there is an increase in subjective social closeness[@Aron1997].
+These findings suggest the importance of the relationship between communication, cooperation, and social closeness.
 
-One of the forms of communication that have received the most attention in psychological game theory is "the promise".
-In an interaction between sender and recipient, it is believed that promises influence beliefs of the recipient, generating trust and cooperation [@Charness2006; @Vanberg2008].
-However, there are situations where trust is betrayed, promises are broken or people deceived.
-The General Social Survey (GSS) in 2018 showed that approximately 11% of people surveyed responded that they have had sex with someone different to their partner while they are married [@GSS2018].
+One of the forms of communication that have received the most attention in psychological game theory is “the promise”.
+In an interaction between a sender and a recipient, it is believed that the sender's promises influence the recipient’s beliefs, influencing their ability to trust and cooperate [@Charness2006; @Vanberg2008].
+Commonly, however, there are situations where promises are broken, trust is betrayed and people are deceived.
+The General Social Survey (GSS) in 2018 showed that approximately 11% of people surveyed responded that they have had sexual intercourse with someone different to their partner while they were married  [@GSS2018].
 In economic and social terms, the United Nations Organization has stressed that deception (corruption) has a global cost of at least 5 percent of the annual gross domestic product (GDP), and it is a generator of conflict and instability in all nations  [@UN2018].
+Hence, breaking promises may greatly affect our own social groups and society itself.
 
 Despite the widespread presence of interactions between human belonging to the same group, it is not known how social closeness between participants can affect keeping or breaking promises.
-This is important because it has been pointed out that lies and betrayals of trust occur daily in close relationships, such as friends, workmates, or classmates.
-And, their consequences can be serious such as loss of the relationship, work or damage to reputation [@DePaulo2004].
-In the laboratory, these transgressions to trust have been explicitly studied in experiments where subjects have incentives to lie or not keep their promises.
-However, the vast majority of these studies have been conducted in people who do NOT know each other [@Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
-Some studies address deception in close interpersonal relationships using self-report measurements, however, they have limitations due to social desirability bias [@DePaulo1998; @DePaulo2004] or rather explore the development of deception detection skills in same-sex friends [@Anderson2002].
+This is important because it has been pointed out that lies and betrayals of trust occur daily even in close relationships such as friends, coworkers, or classmates, and their consequences can be serious, from loss of the relationship to work loss and damage to reputation [@DePaulo2004].
+The two main motivations that have been pointed out in the literature regarding keeping promises are: instrumental and intrinsic [@Baumgartner2009].
+The instrumental suggests that promises are kept to make future cooperation easier while the intrinsic suggests that the promises are kept to do what is "morally right".
+In the laboratory, the betrayals of trust have been explicitly studied in experiments where subjects have incentives to lie and break promises.
+However, the vast majority of studies have been conducted in people without any social closeness (strangers) [@Gneezy2005; @Gneezy2013; @Baumgartner2009; @Baumgartner2013; @Charness2006; @Mazar2008; @Fischbacher2013a].
+Some studies have addressed deception in close interpersonal relationships using self-report measurements or rather explore the development of deception detection skills in same-sex friends, with clear limitations due to the social desirability bias [@DePaulo1998; @DePaulo2004; @Anderson2002].
 
-In this study, we wanted to understand the effects of three partners with different levels of social closeness on keeping or breaking promises, as well as on cooperation, using an experimental trust game.
-We analyzed it in light of the two main motivations that have been pointed out in the literature regarding keeping promises which are: instrumental and intrinsic [@Baumgartner2009]:
-
-1. The _instrumental_ suggests that promises are kept to make future cooperation easier.
-
-2. The _intrinsic_ mentions that the promises are kept to do what is morally right.
-
-In our study, subjects perform a standard trust game in pairs with three phases: _first_, the trustee makes a promise to pay half of his earnings regardless of who his investor is; _second_, the investor receives the promise and decides if he invests his initial budget; _third_, in case the investor has given the budget, the trustee faces the decision to pay or not to pay half of his earnings.
-To evaluate the effect of social closeness, our subjects participate in the role of trustee in front of three partners with different levels of social closeness (null, low and high) in the role of the investor: a computer, a stranger, and a friend.
-The manipulations mentioned allow us to evaluate several hypotheses, the first one was proposed a priori and is derived from a larger research project (you can check the preregistration of the hypothesis here: https://osf.io/u97fd), while the following are exploratory:
+In this study, we wanted to understand the effects of social closeness on keeping or breaking promises and cooperation, by means of an experimental trust game with three partners with different levels of social closeness.
+For this, subjects performed a standard trust game in pairs with three phases: 1) the trustee makes a promise to pay half of his earnings regardless of who his/her investor; 2) the investor receives the promise and decides if he/she invests his/her initial budget; 3) in case the investor has given the budget, the trustee faces the decision to pay or not to pay half of his earnings (keep or break promise).
+To evaluate the effect of social closeness, our subjects participate in the role of trustee with three partners with different levels of social closeness (zero, low and high) in the role of the investor: a computer, a stranger, and a close friend.
+Our main pre-registered hypothesis was:
 
@@
 Social closeness will reduce the decision of breaking the promise.
-According to the _instrumental_ motivation, we expect that subjects keep their promises with friends for the purpose of facilitating future cooperation, which can be extended even beyond the trials in the experiment.
-We also expect, although to a lesser extent, that the subjects keep promises to strangers, with the purpose of facilitating cooperation at least during the trials during the experiment.
-Finally, we anticipate that the participants break the promises to the computer because it is a partner without social closeness and they could not ensure cooperation in future trials.
-It should be noted that if the participants keep the promises to the computer, evidence would be given in favor of _intrinsic_ motivation.
+According to the instrumental motivation, we expect that subjects keep their promises with friends for the purpose of facilitating future cooperation, which probably can be extended even beyond the trials in the experiment.
+We also expect, although to a lesser extent, that the subjects keep promises to strangers, with the purpose of facilitating cooperation during the experiment.
+Finally, we anticipate that the participants break the promises to the computer because it is a partner without any social closeness and they could not ensure cooperation in future trials.
+It should be noted that if the participants keep the promises to the computer, evidence would be given in favor of intrinsic motivation.
+
+Our secondary exploratory hypotheses were:
 
@@
 There will be an effect of social closeness on cooperation, regardless of promises.
-We expect that there is more probability of paying the friend than the stranger and more probability of paying the stranger than the computer.
-According to the _instrumental motivation_, the cooperation will be greater for partners with whom the subject anticipates greater cooperation in the future (friend > stranger > computer).
+According to the instrumental motivation, the payment will be greater for partners with whom the subject anticipates greater cooperation in the future (friend > stranger > computer).
 
-3.
-Finally, we will obtain two subsamples according to the cooperation rate of the subjects as was done in another study [@Baumgartner2009].
-However, what in the aforementioned study was classified as a group of "honest" and "dishonest", we will show that in our sample it is not supported because if the groups differ in their payment rate it will be due to the difference in their level of commitment expressed by promises.
+3. We hypothesize that the subjects will cooperate according to their degree of commitment expressed through promises.
 
@@
 
-We recruited 45 subjects (15 male) from the National Autonomous University of Mexico, the age range from 19 to 33 years and their minimum educational level were bachelor.
-Subjects were asked to come to the study with a “close” friend, who fulfilled the following characteristics: 1) he/she was matched by sex, 2) did not have a family bond and 3) was not a person with a sentimental or sexual relationship.
-From this sample, 30 subjects (15 men) performed the task in a magnetic resonance imaging (MRI) scanner, however, their image data was not analyzed for the present work.
+We recruited 45 subjects (15 male) from the National Autonomous University of Mexico, age range from 19 to 33 years, their minimum educational level were bachelor and right handed (for MRI).
+Subjects were asked to come to the study with a “close” friend, who fulfilled the following criteria: 1) he/she was matched by sex, 2) did not have a family bond and 3) was not a person with a sentimental or sexual relationship.
+From this sample (n = 45), 30 subjects (15 men) performed the task in a magnetic resonance imaging (MRI) scanner, however, their image data was not analyzed for the present work.
 
@@
 All subjects performed an adaptation of the trust game with promises, using hypothetical monetary rewards [@Baumgartner2009].
-The variation with respect to the original task is that in our experiment three partners were presented with three levels of social closeness in the role of the investor: computer (no closeness), strange (low closeness) and friend (high closeness), while the participant acted as the trustee.
+The variation with respect to the original task was that, in our experiment, three partners with three levels of social closeness were presented in the role of the investor: computer (no closeness), strange (low closeness) and friend (high closeness), while the participant acted as the trustee.
 The task was programmed in PsychoPy2 version 1.84.2 [@Peirce2019; @Peirce2008] and consisted of 24 trials between two players: trustee and investor.
-The trustee originally has 0 Mexican pesos and the investor has 2 pesos, the investor is presented with the opportunity to give his money to the trustee or keep it.
-If investor gives his money, it is multiplied by 5 pesos, so that the trustee has 10 pesos.
-Finally, the trustee decides to pay half to the investor or keep the 10 pesos.
-The structure described is repeated in 24 trials, however, in 4 of the trials the trustee can send a promise to the investor, the promises were that always, mostly, sometimes, or never would pay back.
-Each promise was valid for three trials so that 12 of the trials have the effect of the promise and the other 12 do not.
-Each partner performs the role of investor in 8 of 24 total trials, however, both the promises and social closeness conditions were presented to the trustee in pseudorandom order.
+The trustee originally had 0 Mexican pesos and the investor had 2 pesos, the investor was presented with the opportunity to give his/her money to the trustee or keep it.
+If the investor gave his/her money, it was multiplied by 5 pesos, so that the trustee had 10 pesos.
+Finally, the trustee had to decide if he/she wanted to pay half to the investor or keep the 10 pesos.
+The structure described was repeated in 24 trials, however, in 4 of the trials the trustee could send a promise to the investor, the promises were that he/she would: always, mostly, sometimes, or never pay back.
+Each promise was valid for three trials, so that 12 of the trials had the effect of the promise and the other 12 did not.
+Each partner performed the role of investor in 8 of 24 total trials, however, both the promises and social closeness conditions were presented to the trustee in pseudorandom order.
 
-Since our main interest was the trustee’s behavior, investors’ decisions were programmed _a priori_ to give their amount in 6 trials and in 2 did not randomly.
-The covert story for all our subjects was that they would be playing in real-time with their friend (whom they brought to the study), the stranger (was told he would be another same-sex unknown person) and the computer.
-After the study ended, the participants were debriefed about our own deception.
-A diagram of the chronology of the experimental task with the duration of each phase in seconds is shown in Figure 1.
+Since our main interest was the trustee’s behavior and to avoid unbalanced responses from investors, the investor was always the computer although the trustee was shown to have 3 types of investors, and the investors’ decisions were programmed _a priori_ to randomly give their amount in 6 trials and withhold the amount in 2 trials.
+The covert story for all our subjects was that they would be playing in real-time with their friend (whom they brought to the study), the stranger (was told it would be another same-sex unknown person) and the computer.
+After the study ended, the participants were debriefed about our deception.
+A diagram of the the experimental task is shown in Figure 1.
 
@@
 
-Fixation phase consisted only of a period in which the subject paid attention without performing any particular behavior.
-Then, **promises phase** in part A1 indicated that in the following three trials they could decide without the effect of the promise.
+Promise phase in part A1 indicated that in the following three trials they could decide without the effect of the promise.
 In A2, the subject was asked to decide between 1) always, 2) mostly, 3) sometimes or 4) never pay back.
 This pattern was repeated.
-In the **anticipation/assignation phase**, subjects were told who their partner was for that trial (computer, stranger or friend) and was given the message that their partner was making their decision.
-Later in the **decision phase**, the subject was informed if his partner invested his $2 or not, he was reminded of his promise level (if they were trails with promises) and, in case the partner had invested, he was asked to decide whether to pay back or not.
-Finally, payments for each trial were shown in the **feedback phase** and the sequence was repeated until the task finished.
+In the anticipation/assignation phase, subjects were told who their partner was for that trial (computer, stranger or friend) and was given the message that their partner was making their decision.
+Later in the decision phase, the subject was informed if his partner invested his $2 or not, he was reminded of his promise level (if they were trails with promises) and, in case the partner had invested, he was asked to decide whether to pay back or not.
+Finally, payments for each trial were shown in the feedback phase and the sequence was repeated until the task finished.
 
@@
 
-```{r fig2, fig.cap='Pay back proportion by partners and promises levels'}
+```{r fig2, fig.cap='Pay back proportion by partners and promises levels, the x-axis represents all decisions made to each partner, the different shades of blue shows the proportions in which the subjects paid back or not.
+The y-axis presents how these proportions vary according to the promises made.'}
 
@@
 
-```{r fig3, fig.cap='Posterior probability of Promise Breaking'}
+```{r fig3, fig.cap='Inference regarding the probability of breaking the promise depending on social closeness.
+The x-axis shows the posterior probability of breaking the promise, and the y-axis indicates the three partners.
+The dotted line shows the probability that breaking the promise would be zero.'}
+
 p3
@@
 
-```{r fig4, fig.cap='Posterior estimates in logit scale'}
+```{r fig4, fig.cap='Posterior estimates in logit scale.
+We show posteriors distributions of the hierarchical Bayesian model coefficients for the effect of experimental conditions on the decision to cooperate.
+The x-axis shows the magnitude of the logit scale coefficients, and the y-axis shows the experimental conditions associated with that effect.'}
 
@@
 
-```{r fig5, fig.cap='Posterior predictive over pay back rate', out.width='100%', out.height='42%'}
+```{r fig5, fig.cap='Posterior predictive over pay back rate.
+Correspondence between payment proportions and model predictions depending on the game partner for the first twelve subjects in the sample.
+The x-axis pointed the three playmates when the subjects had made a promise, while the y-axis indicates the proportion of decisions in which subjects payback.', out.width='100%', out.height='42%'}
 
@@
 
-```{r fig6, fig.cap='Posterior predictive over pay back rate, Social Closeness Varying effects by Promise levels'}
+```{r fig6, fig.cap='Posterior predictive over pay back rate, social closeness varying effects by promise levels.
+Correspondence between payment proportions and model predictions depending on the game partner at the group level.
+The x-axis pointed the three playmates when the subjects had made a promise, while the y-axis indicates the proportion of decisions in which subjects payback.'}
 
@@
 
-```{r fig7, fig.cap='Promise choices by group'}
+```{r fig7, fig.cap='Promise choices by group.
+We show posterior probability estimates regarding the level of promise depending on the group.
+The Low group (which paid 58/100 of the trials) is more likely to promise mostly, while the High group (which paid 83/100 of the trials) is more likely to promise always.'}
 
@@
 In previous studies, the participants remain anonymous during the course of the tasks [@Baumgartner2009], their measurements to evaluate transgressions are self-reported [@DePaulo1998; @DePaulo2004], they do not directly quantify the breaking of promises [@Vanberg2008; @Charness2006], or as we will discuss later, they use heterogeneous measures of social closeness [@Glaeser2000].
-Our experiment is the first one to include a partner without social closeness (computer).
-Our data suggest that the mere fact of considering that subjects play with a human diminishes the probability of breaking the promise.
+Our results suggest that the mere fact of considering that subjects play with a human diminishes the probability of breaking the promise.
 It is more likely to break the promise to the computer than to the stranger, even though that partner was not known.
-Also, null social closeness is important because it allows us to explore the intrinsic motivation to keep the promises.
+Also, zero social closeness is important to include because it allows us to explore the intrinsic motivation to keep the promises.
 If humans keep their word because it is morally correct, we would anticipate that the probability of breaking a promise was very low in the three partners and, particularly, the inference regarding the probability of breaking the promise to the computer would include zero.
-However, we found that, although low, the probability was greater than zero, which provides evidence that seems to contradict, at least in degree, the hypothesis of intrinsic motivation.
-We cannot exclude the possibility that the subjects keep promises mainly due to moral motivation because, even in the case of the computer, the subjects kept a large proportion.
-We can, however, exclude that this is their only motivation.
+However, we found that, although low, the probability was greater than zero, which provides evidence that seems to contradict, at least in some degree, the hypothesis of intrinsic motivation.
+This means that we cannot exclude the possibility that the subjects keep promises mainly due to moral motivation because, even in the case of the computer, the subjects kept a large proportion of promises.
+We can, however, exclude that this is their _only_ motivation.
 
-On the other hand, high social closeness allows us to explore the instrumental motivation to keep promises [@Baumgartner2009].
-In our study, it was more likely to break the promise to the stranger than to the friend.
-If humans keep their word to facilitate cooperation in the future, we would anticipate that with a partner of high social closeness (with whom they are very likely to cooperate, even after the experiment) there would be less of a chance to break the promise.
-In fact, the promise to friends was not broken on any occasion, hence the inference in this case, was met.
-
+High social closeness allows us to explore the instrumental motivation to keep promises [@Baumgartner2009].
+In our study, subjects were more likely to break the promise to the stranger than to the friend.
+If humans keep their word to facilitate cooperation in the future, we would anticipate that there would be less of a chance to break the promise with a partner of high social closeness (with whom they are very likely to cooperate, even after the experiment) and, in fact, the promise to friends was not broken on any occasion.
 The findings concerning motivations could be explained by the social norm called "conditional cooperation", which indicates that the belief that other people cooperate at high levels also induces high levels of cooperation [@Fehr2018].
-Thus, the lack of certainty regarding the decisions that the computer would make could explain the probability of breaking the promise that exists towards this partner.
-Similarly, the information that the subjects have regarding as their friend's behavior -even before the experiment- could explain the high levels of cooperation and keeping of promises towards this partner.
+Thus, the uncertainty regarding the computer’s decisions could explain the probability of breaking the promise.
+Similarly, the information that the subjects have regarding their friend’s behavior, even before the experiment, could explain the high levels of cooperation and keeping of promises towards the friend.
 
 Cooperation has been studied with diverse experimental manipulations.
-In one study, the contribution in a public goods game was evaluated during several trials in a group made up of the same individuals (partners), and compared to another group of new different subjects for each trial (strangers) [@Croson1996].
-In the condition of partners the cooperation was greater because it is a stable group compared to the group of strangers.
-The mentioned study does not give details regarding the recruitment of participants, so we could assume that even in the condition of partners these are individuals who do not consider themselves socially close.
-
+In one study, the contribution in a “public goods game” was evaluated during several trials in a group made up of the same individuals (partners), and compared to another group of new different subjects for each trial (strangers) [@Croson1996].
+In the condition of partners, the cooperation was greater because it was a stable group compared to the group of strangers.
+The mentioned study does not give details regarding the recruitment of participants, thus we could assume that even in the condition of partners these were individuals who did not consider themselves socially close.
 Another study showed an increase in cooperation in a trust game when individuals were socially close [@Glaeser2000].
-In this study, subjects knew each other and the researchers carefully measured several variables regarding their social connection.However, some individuals who arrived together were allowed to perform the task between themselves and others were paired with unclear criteria.
-The above allows social closeness between partners to be heterogeneous, allows for romantic relationships and assumes that two individuals who come together to class are considered close to each other.
-Also, since it is a study of one-shot, it excludes the possibility of evaluating how the same subject varies his behavior based on different levels of social closeness.
-
+In this study, subjects knew each other and the researchers carefully measured several variables regarding their social connection such as the number of friends in common and years of relationship.
+They found greater cooperation depending on the degree of social connection.
+However, the study did not control for social closeness as some individuals who arrived together were allowed to perform the task together whereas others were paired differently.
+This limitation allowed social closeness between partners to be heterogeneous, allowed for romantic relationships and assumed that two individuals who arrived together to class were considered close to each other.
 To try to homogenize social closeness between our subjects and their partners, they performed the task with a same-sex friend considered to be close, emphasizing their companion could not be a romantic or sexual partner.
 Bayesian analysis of the IOS scale showed evidence in favor that the degree of social closeness between 30 of our 45 subjects and their friends was the same.
-Results of the two mentioned studies also found that social closeness enhance cooperation [@Croson1996; @Glaeser2000], in the future would be valuable to homogenize both the performed tasks and the statistical procedure used, to establish similarity in effects magnitudes.
+Although results of the two mentioned studies also found that social closeness enhance cooperation [@Croson1996; @Glaeser2000], it would be valuable to homogenize both the performed tasks and the statistical procedure used to establish similarity in effects magnitudes.
 
@@
 Within-subjects designs have traditionally been analyzed with repeated measures AN(C)OVA, however, Hierarchical Models grant the advantages of naturally dealing with unbalanced data, include categorical and/or numerical predictors, explicitly incorporate individual variability, among others [@Vuorre2018; @Gelman2006; @McElreath2018; @Burkner2017].
-
 In our case, the Hierarchical Model allowed us to capture how the experimental conditions affected the decisions of each subject and the differences between them.
-For example, there are obviously motivated instrumental subjects such as number 8 or 12 who are very sensitive to the identity of their investors and modify their cooperation under social closeness.
+For example, there were obviously motivated instrumental subjects such as number 8 or 12 who are very sensitive to the identity of their investors and modify their cooperation under social closeness.
 At the same time, there were notably intrinsic subjects such as 9 and 10 who cooperate all the time regardless of who their partners are.
-The Hierarchical Model naturally includes this information for the estimation of population effects, which, if not considered, would lead to inaccurate inferences[@Burkner2017; @Gelman2006; @McElreath2018].
-
-On the other hand, the Cumulative Model allowed us to capture the strength of the commitment expressed through promises.
+The Hierarchical Model naturally includes this information for the estimation of population effects, which, if not considered, would lead to inaccurate inferences [@Burkner2017; @Gelman2006; @McElreath2018].
+The Cumulative Model allowed us to capture the strength of the commitment expressed through promises.
 A very frequent problem that has been pointed out recently is that analyzing ordinal data with methods that assume that observations are metric can lead to serious inference errors [@Liddell2018].
 The Cumulative Models assumes that the observed responses come from the categorization of a continuous latent variable [@Burkner2019].
-In our study, we could identify that groups with different payment proportions, which in other studies have been called "dishonest" and "honest"[@Baumgartner2009; @Baumgartner2013], differ in the commitment they express through their promises.
+In our study, we could identify that groups with different payment proportions, which in other studies have been called “dishonest” and “honest” [@Baumgartner2009; @Baumgartner2013], differ in the commitment they express through their promises.
 Considering that the tools to perform the Cumulative Models are relatively recent, in future studies, it would be valuable to also use the new alternatives for inference.
-
 Although the Hierarchical and Cumulative models are not tools exclusively for Bayesian inference, their application from this approach represents several advantages compared to frequentist statistics.
@@
 
-A limitation of this paper is the use of hypothetical rewards compared to real rewards.
+A limitation of our study was the use of hypothetical rewards compared to real rewards.
 A relatively recent study on decision-making reported that there is more loss aversion when subjects have real monetary rewards compared to hypothetical in a risk task [@Xu2016].
 However, other works do not report differences between the use of both types of rewards in self-control, temporal and social discount tasks [@Locey2011; @Johnson2006; @Rachlin2006].
-Likewise, it can be argued that our results have theoretical congruence [@Fehr2018] and are in the same direction as other works that use real money [@Croson1996; @Glaeser2000], thus, there are not many reasons to expect that other types of rewards would modify our results.
-Another possible limitation is the use of multiple trials with each partner.
-Although the decision to use repeated measures during our design serves more the purpose of reducing contaminant sources and increasing internal validity [@Maxwell2018], to have more clarity regarding the difference in the intrinsic and instrumental motivations, the studies could benefit from only include one trial for each partner.
+Likewise, it can be argued that our results have theoretical congruence  [@Fehr2018] and are in the same direction as other works that use real money [@Croson1996; @Glaeser2000].
+Thus, there are not many reasons to expect that other types of rewards would modify our results.
+Another possible limitation could be the use of multiple trials with each partner.
+Although the decision to use repeated measures during our design serves the purpose of reducing contaminant sources and increasing internal validity  [@Maxwell2018], the studies could benefit from only including one trial for each partner to have more clarity regarding the difference in the intrinsic and instrumental motivations.
 Play a one-shot with each partner avoids the possibility that multiple trials could generate the belief that the computer can also vary its behavior according to the decisions of the trustee.
-Finally, subjects that performed the study inside the MRI scanner may differ in their responses than subjects outside of the scanner.
-However, our analysis did not show this explicitly.
 
@@
 
-Subjects seem to keep their promises by a combination of _intrinsic_ and _instrumental_ motivations.
-They are predominantly "nice people" because they keep their word even with investors with no social closeness.
-However, their trustworthiness is far from perfect, since there is a small proportion of betrayals committed towards this partner.
-It seems that if subjects cannot be sure their investor will be a "potential cooperator", dishonesty may emerge in the form of broken promises.
-Framing the finding in terms of the theoretical predictions of the social norm "conditional cooperation", social closeness decreases the probability of breaking the promise and increases cooperation, and suggests the correspondence between commitment expressed through promises and subsequent behavior.
+Subjects in our study seemed to keep their promises by a combination of _intrinsic_ and _instrumental_ motivations.
+They can be regarded as predominantly "nice people" because they kept their word even with investors with no social closeness (computer).
+However, their trustworthiness was far from perfect, since there was a small proportion of betrayals committed towards the computer.
+If subjects could not be sure their investor would be a "potential cooperator", dishonesty may have emerged in the form of broken promises.
+Framing our findings in terms of the theoretical predictions of the social norm "conditional cooperation", social closeness decreases the probability of breaking the promise and increases cooperation, and suggests the correspondence between commitment expressed through promises and subsequent behavior.
 

### 2019-08-14 behavioral-promises/behavioral-promises.tex
Update manuscript

@@
-\AtBeginDocument{%
-  \paperwidth=\dimexpr
-    1in + \oddsidemargin
-    + \textwidth
-    % + \marginparsep + \marginparwidth
-    + 1in + \oddsidemargin
-  \relax
-  \paperheight=\dimexpr
-    1in + \topmargin
-    + \headheight + \headsep
-    + \textheight
-    % + \footskip
-    + 1in + \topmargin
-  \relax
-  \usepackage[pass]{geometry}\relax
-}
-
 % !TeX program = pdfLaTeX
@@
 
-\author{  Said Jiménez  \and  Roberto E. Mercadillo \and  Diego Angeles-Valdez \and  Jairo Muñoz-Delgado \and  Juan J. Sánchez-Sosa \and  Eduardo A. Garza-Villarreal \and  }
+\author{  Said Jiménez \and  Kamila E. Sip \and  Roberto E. Mercadillo \and  Diego Angeles-Valdez \and  Jairo Muñoz-Delgado \and  Juan J. Sánchez-Sosa \and  Eduardo A. Garza-Villarreal \and  }
 
@@
 %             \emph{Present address:} of F. Author  %  if needed
-    }
+    \and
+        Eduardo A. Garza-Villarreal \at
+     Institute of Neurobiology, UNAM \\
+     \email{\href{mailto:egarza@gmail.com}{\nolinkurl{egarza@gmail.com}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
 
@@
 Promises increase cooperation between non-genetically related
-individuals, however, lies and betrayals occur daily in close social
+individuals, whereas lies and betrayals occur daily even in close social
 relationships. Despite this, the effect of social closeness on the
-decision to keep or break a promise has not been studied. We conducted
-an experiment in which subjects could freely decide if they broke or
-kept their promise to three partners with different levels of social
-closeness: null (computer), low (strange) and high (friend). If subjects
-keep their word with the computer, it provides evidence in favor of
-intrinsic motivation (comply to do the correct thing), otherwise
+decision to keep or break a promise has not been thoroughly studied. We
+conducted an experiment in which subjects could freely decide if they
+broke or kept a promise to three partners with different levels of
+social closeness: null (computer), low (strange) and high (friend). If
+subjects kept their word with the computer, it provides evidence in
+favor of intrinsic motivation (comply to do the correct thing), while
 extrinsic motivation would be supported (comply to facilitate future
-cooperation). Using Hierarchical Bayesian Modeling, we find that if
+cooperation). Using Hierarchical Bayesian Modeling, we found that as
 social closeness increases, the probability of breaking promises
-decreases monotonically, the evidence ratio in favor to the hypothesis
+decreases monotonically. The evidence ratio in favor of the hypothesis
 stranger \textless{} computer was 7.47, and friend \textless{} stranger
-was 8.64. Furthermore, using Bayesian Cumulative Modeling we find that
-subjects were very consistent between their promises and the subsequent
-decisions they make. Although is more probable that our subjects keep
-their promises to any of the three partners, there is a proportion of
-transgressions to the computer, whose inference excludes zero with a
-95\% posterior probability. Also, subjects never broke the promise to
-their friends. Our results indicate that subjects are predominantly
-``nice people'' because they keep their promises even to partners
-without social closeness, however, if the subjects are not certain that
-their partner will also be a ``potential cooperator'', dishonesty
-emerges in the form of broken promises.
+was 8.64. Furthermore, using Bayesian Cumulative Modeling we found that
+subjects were very consistent between their promises and their choices.
+Although it was more probable that our subjects kept their promises to
+any of the three partners, there was a proportion of transgressions to
+the computer, whose inference excludes zero with a 95\% posterior
+probability. Also, our subjects never broke the promise to their
+friends. Our results suggest that subjects were predominantly ``nice
+people'' because they kept their promises even to partners without
+social closeness. However, if the subjects were not certain that their
+partner will also be a ``potential cooperator'', dishonesty emerged in
+the form of broken promises.
 \\
@@
 
-Human are social animals and we get survival advantages from being such.
-Historically, belonging to a social group has provided protection and
-guaranteed access to resources such as food, and currently, there has
-been evidence that belonging to a social group has a positive effect on
-longevity, physical and mental health (Tough, Siegrist, and Fekete 2017;
-Holt-Lunstad 2018). The relationship between social closeness and
-cooperation is key to the formation of large groups of individuals
-without a genetic relationship, and such groups form the basis of
-communities, societies, and nations, arguably constituting one of the
-most fundamental conditions for human survival (Fehr and Fischbacher
-2003; Fehr and Schurtenberger 2018). An important requirement for
-cooperation between individuals is communication. A meta-analysis of 45
-studies reported a large positive effect (\(d = 1.01\)) of communication
-in cooperation regardless of the communication medium (Balliet 2010). In
-parallel, it is known that after communication sessions between
-completely unknown individuals there is an increase in subjective social
-closeness (Aron et al. 1997). Thus, these findings suggest a positive
-relationship between communication, cooperation, and social closeness.
+Humans are social animals and we obtain survival advantages from proper
+socialization. Historically, belonging to a social group has provided
+protection and guaranteed access to resources such as food, and
+currently, there is evidence that belonging to a social group has a
+positive effect on longevity, physical and mental health (Tough,
+Siegrist, and Fekete 2017; Holt-Lunstad 2018). The interaction between
+social closeness and cooperation seems to be a key feature to the
+formation of large groups of individuals without a genetic relationship,
+and such groups form the basis of communities, societies, and nations,
+arguably constituting one of the most fundamental conditions for human
+survival (Fehr and Fischbacher 2003; Fehr and Schurtenberger 2018). A
+recent meta-analysis showed that communication, regardless of the
+medium, is the most important element for cooperation between
+individuals (Balliet 2010). In parallel, there is evidence that
+following communication sessions between completely unknown individuals,
+there is an increase in subjective social closeness(Aron et al. 1997).
+These findings suggest the importance of the relationship between
+communication, cooperation, and social closeness.
 
@@
 in psychological game theory is ``the promise''. In an interaction
-between sender and recipient, it is believed that promises influence
-beliefs of the recipient, generating trust and cooperation (Charness and
-Dufwenberg 2006; Vanberg 2008). However, there are situations where
-trust is betrayed, promises are broken or people deceived. The General
-Social Survey (GSS) in 2018 showed that approximately 11\% of people
-surveyed responded that they have had sex with someone different to
-their partner while they are married (Smith et al. 2018). In economic
-and social terms, the United Nations Organization has stressed that
-deception (corruption) has a global cost of at least 5 percent of the
-annual gross domestic product (GDP), and it is a generator of conflict
-and instability in all nations (UN 2018).
+between a sender and a recipient, it is believed that the sender's
+promises influence the recipient's beliefs, influencing their ability to
+trust and cooperate (Charness and Dufwenberg 2006; Vanberg 2008).
+Commonly, however, there are situations where promises are broken, trust
+is betrayed and people are deceived. The General Social Survey (GSS) in
+2018 showed that approximately 11\% of people surveyed responded that
+they have had sexual intercourse with someone different to their partner
+while they were married (Smith et al. 2018). In economic and social
+terms, the United Nations Organization has stressed that deception
+(corruption) has a global cost of at least 5 percent of the annual gross
+domestic product (GDP), and it is a generator of conflict and
+instability in all nations (UN 2018). Hence, breaking promises may
+greatly affect our own social groups and society itself.
 
@@
 because it has been pointed out that lies and betrayals of trust occur
-daily in close relationships, such as friends, workmates, or classmates.
-And, their consequences can be serious such as loss of the relationship,
-work or damage to reputation (DePaulo et al. 2004). In the laboratory,
-these transgressions to trust have been explicitly studied in
-experiments where subjects have incentives to lie or not keep their
-promises. However, the vast majority of these studies have been
-conducted in people who do NOT know each other (Gneezy 2005; Gneezy,
+daily even in close relationships such as friends, coworkers, or
+classmates, and their consequences can be serious, from loss of the
+relationship to work loss and damage to reputation (DePaulo et al.
+2004). The two main motivations that have been pointed out in the
+literature regarding keeping promises are: instrumental and intrinsic
+(Baumgartner et al. 2009). The instrumental suggests that promises are
+kept to make future cooperation easier while the intrinsic suggests that
+the promises are kept to do what is ``morally right''. In the
+laboratory, the betrayals of trust have been explicitly studied in
+experiments where subjects have incentives to lie and break promises.
+However, the vast majority of studies have been conducted in people
+without any social closeness (strangers) (Gneezy 2005; Gneezy,
 Rockenbach, and Serra-Garcia 2013; Baumgartner et al. 2009; Baumgartner,
 Gianotti, and Knoch 2013; Charness and Dufwenberg 2006; Mazar, Amir, and
-Ariely 2008; Fischbacher and Föllmi-Heusi 2013). Some studies address
-deception in close interpersonal relationships using self-report
-measurements, however, they have limitations due to social desirability
-bias (DePaulo and Kashy 1998; DePaulo et al. 2004) or rather explore the
-development of deception detection skills in same-sex friends (Anderson,
-DePaulo, and Ansfield 2002).
-
-In this study, we wanted to understand the effects of three partners
-with different levels of social closeness on keeping or breaking
-promises, as well as on cooperation, using an experimental trust game.
-We analyzed it in light of the two main motivations that have been
-pointed out in the literature regarding keeping promises which are:
-instrumental and intrinsic (Baumgartner et al. 2009):
+Ariely 2008; Fischbacher and Föllmi-Heusi 2013). Some studies have
+addressed deception in close interpersonal relationships using
+self-report measurements or rather explore the development of deception
+detection skills in same-sex friends, with clear limitations due to the
+social desirability bias (DePaulo and Kashy 1998; DePaulo et al. 2004;
+Anderson, DePaulo, and Ansfield 2002).
+
+In this study, we wanted to understand the effects of social closeness
+on keeping or breaking promises and cooperation, by means of an
+experimental trust game with three partners with different levels of
+social closeness. For this, subjects performed a standard trust game in
+pairs with three phases: 1) the trustee makes a promise to pay half of
+his earnings regardless of who his/her investor; 2) the investor
+receives the promise and decides if he/she invests his/her initial
+budget; 3) in case the investor has given the budget, the trustee faces
+the decision to pay or not to pay half of his earnings (keep or break
+promise). To evaluate the effect of social closeness, our subjects
+participate in the role of trustee with three partners with different
+levels of social closeness (zero, low and high) in the role of the
+investor: a computer, a stranger, and a close friend. Our main
+pre-registered hypothesis was:
 
@@
 \def\labelenumi{\arabic{enumi}.}
+\tightlist
 \item
-  The \emph{instrumental} suggests that promises are kept to make future
-  cooperation easier.
-\item
-  The \emph{intrinsic} mentions that the promises are kept to do what is
-  morally right.
+  Social closeness will reduce the decision of breaking the promise.
+  According to the instrumental motivation, we expect that subjects keep
+  their promises with friends for the purpose of facilitating future
+  cooperation, which probably can be extended even beyond the trials in
+  the experiment. We also expect, although to a lesser extent, that the
+  subjects keep promises to strangers, with the purpose of facilitating
+  cooperation during the experiment. Finally, we anticipate that the
+  participants break the promises to the computer because it is a
+  partner without any social closeness and they could not ensure
+  cooperation in future trials. It should be noted that if the
+  participants keep the promises to the computer, evidence would be
+  given in favor of intrinsic motivation.
 \end{enumerate}
 
-In our study, subjects perform a standard trust game in pairs with three
-phases: \emph{first}, the trustee makes a promise to pay half of his
-earnings regardless of who his investor is; \emph{second}, the investor
-receives the promise and decides if he invests his initial budget;
-\emph{third}, in case the investor has given the budget, the trustee
-faces the decision to pay or not to pay half of his earnings. To
-evaluate the effect of social closeness, our subjects participate in the
-role of trustee in front of three partners with different levels of
-social closeness (null, low and high) in the role of the investor: a
-computer, a stranger, and a friend. The manipulations mentioned allow us
-to evaluate several hypotheses, the first one was proposed a priori and
-is derived from a larger research project (you can check the
-preregistration of the hypothesis here: \url{https://osf.io/u97fd}),
-while the following are exploratory:
+Our secondary exploratory hypotheses were:
 
@@
 \def\labelenumi{\arabic{enumi}.}
-\item
-  Social closeness will reduce the decision of breaking the promise.
-  According to the \emph{instrumental} motivation, we expect that
-  subjects keep their promises with friends for the purpose of
-  facilitating future cooperation, which can be extended even beyond the
-  trials in the experiment. We also expect, although to a lesser extent,
-  that the subjects keep promises to strangers, with the purpose of
-  facilitating cooperation at least during the trials during the
-  experiment. Finally, we anticipate that the participants break the
-  promises to the computer because it is a partner without social
-  closeness and they could not ensure cooperation in future trials. It
-  should be noted that if the participants keep the promises to the
-  computer, evidence would be given in favor of \emph{intrinsic}
-  motivation.
+\setcounter{enumi}{1}
 \item
   There will be an effect of social closeness on cooperation, regardless
-  of promises. We expect that there is more probability of paying the
-  friend than the stranger and more probability of paying the stranger
-  than the computer. According to the \emph{instrumental motivation},
-  the cooperation will be greater for partners with whom the subject
-  anticipates greater cooperation in the future (friend \textgreater{}
-  stranger \textgreater{} computer).
+  of promises. According to the instrumental motivation, the payment
+  will be greater for partners with whom the subject anticipates greater
+  cooperation in the future (friend \textgreater{} stranger
+  \textgreater{} computer).
 \item
-  Finally, we will obtain two subsamples according to the cooperation
-  rate of the subjects as was done in another study (Baumgartner et al.
-  2009). However, what in the aforementioned study was classified as a
-  group of ``honest'' and ``dishonest'', we will show that in our sample
-  it is not supported because if the groups differ in their payment rate
-  it will be due to the difference in their level of commitment
-  expressed by promises.
+  We hypothesize that the subjects will cooperate according to their
+  degree of commitment expressed through promises.
 \end{enumerate}
@@
 We recruited 45 subjects (15 male) from the National Autonomous
-University of Mexico, the age range from 19 to 33 years and their
-minimum educational level were bachelor. Subjects were asked to come to
-the study with a ``close'' friend, who fulfilled the following
-characteristics: 1) he/she was matched by sex, 2) did not have a family
-bond and 3) was not a person with a sentimental or sexual relationship.
-From this sample, 30 subjects (15 men) performed the task in a magnetic
-resonance imaging (MRI) scanner, however, their image data was not
-analyzed for the present work.
+University of Mexico, age range from 19 to 33 years, their minimum
+educational level were bachelor and right handed (for MRI). Subjects
+were asked to come to the study with a ``close'' friend, who fulfilled
+the following criteria: 1) he/she was matched by sex, 2) did not have a
+family bond and 3) was not a person with a sentimental or sexual
+relationship. From this sample (n = 45), 30 subjects (15 men) performed
+the task in a magnetic resonance imaging (MRI) scanner, however, their
+image data was not analyzed for the present work.
 
@@
 using hypothetical monetary rewards (Baumgartner et al. 2009). The
-variation with respect to the original task is that in our experiment
-three partners were presented with three levels of social closeness in
+variation with respect to the original task was that, in our experiment,
+three partners with three levels of social closeness were presented in
 the role of the investor: computer (no closeness), strange (low
@@
 et al. 2019; Peirce 2008) and consisted of 24 trials between two
-players: trustee and investor. The trustee originally has 0 Mexican
-pesos and the investor has 2 pesos, the investor is presented with the
-opportunity to give his money to the trustee or keep it. If investor
-gives his money, it is multiplied by 5 pesos, so that the trustee has 10
-pesos. Finally, the trustee decides to pay half to the investor or keep
-the 10 pesos. The structure described is repeated in 24 trials, however,
-in 4 of the trials the trustee can send a promise to the investor, the
-promises were that always, mostly, sometimes, or never would pay back.
-Each promise was valid for three trials so that 12 of the trials have
-the effect of the promise and the other 12 do not. Each partner performs
-the role of investor in 8 of 24 total trials, however, both the promises
-and social closeness conditions were presented to the trustee in
-pseudorandom order.
-
-Since our main interest was the trustee's behavior, investors' decisions
-were programmed \emph{a priori} to give their amount in 6 trials and in
-2 did not randomly. The covert story for all our subjects was that they
-would be playing in real-time with their friend (whom they brought to
-the study), the stranger (was told he would be another same-sex unknown
-person) and the computer. After the study ended, the participants were
-debriefed about our own deception. A diagram of the chronology of the
-experimental task with the duration of each phase in seconds is shown in
-Figure 1.
+players: trustee and investor. The trustee originally had 0 Mexican
+pesos and the investor had 2 pesos, the investor was presented with the
+opportunity to give his/her money to the trustee or keep it. If the
+investor gave his/her money, it was multiplied by 5 pesos, so that the
+trustee had 10 pesos. Finally, the trustee had to decide if he/she
+wanted to pay half to the investor or keep the 10 pesos. The structure
+described was repeated in 24 trials, however, in 4 of the trials the
+trustee could send a promise to the investor, the promises were that
+he/she would: always, mostly, sometimes, or never pay back. Each promise
+was valid for three trials, so that 12 of the trials had the effect of
+the promise and the other 12 did not. Each partner performed the role of
+investor in 8 of 24 total trials, however, both the promises and social
+closeness conditions were presented to the trustee in pseudorandom
+order.
+
+Since our main interest was the trustee's behavior and to avoid
+unbalanced responses from investors, the investor was always the
+computer although the trustee was shown to have 3 types of investors,
+and the investors' decisions were programmed \emph{a priori} to randomly
+give their amount in 6 trials and withhold the amount in 2 trials. The
+covert story for all our subjects was that they would be playing in
+real-time with their friend (whom they brought to the study), the
+stranger (was told it would be another same-sex unknown person) and the
+computer. After the study ended, the participants were debriefed about
+our deception. A diagram of the the experimental task is shown in Figure
+1.
 
@@
 
-Fixation phase consisted only of a period in which the subject paid
-attention without performing any particular behavior. Then,
-\textbf{promises phase} in part A1 indicated that in the following three
-trials they could decide without the effect of the promise. In A2, the
-subject was asked to decide between 1) always, 2) mostly, 3) sometimes
-or 4) never pay back. This pattern was repeated. In the
-\textbf{anticipation/assignation phase}, subjects were told who their
-partner was for that trial (computer, stranger or friend) and was given
-the message that their partner was making their decision. Later in the
-\textbf{decision phase}, the subject was informed if his partner
-invested his \$2 or not, he was reminded of his promise level (if they
-were trails with promises) and, in case the partner had invested, he was
-asked to decide whether to pay back or not. Finally, payments for each
-trial were shown in the \textbf{feedback phase} and the sequence was
-repeated until the task finished.
+Promise phase in part A1 indicated that in the following three trials
+they could decide without the effect of the promise. In A2, the subject
+was asked to decide between 1) always, 2) mostly, 3) sometimes or 4)
+never pay back. This pattern was repeated. In the
+anticipation/assignation phase, subjects were told who their partner was
+for that trial (computer, stranger or friend) and was given the message
+that their partner was making their decision. Later in the decision
+phase, the subject was informed if his partner invested his \$2 or not,
+he was reminded of his promise level (if they were trails with promises)
+and, in case the partner had invested, he was asked to decide whether to
+pay back or not. Finally, payments for each trial were shown in the
+feedback phase and the sequence was repeated until the task finished.
 
@@
 
-\caption{Pay back proportion by partners and promises levels}\label{fig:fig2}
+\caption{Pay back proportion by partners and promises levels, the x-axis represents all decisions made to each partner, the different shades of blue shows the proportions in which the subjects paid back or not.
+The y-axis presents how these proportions vary according to the promises made.}\label{fig:fig2}
 \end{figure}
@@
 
-\caption{Posterior probability of Promise Breaking}\label{fig:fig3}
+\caption{Inference regarding the probability of breaking the promise depending on social closeness.
+The x-axis shows the posterior probability of breaking the promise, and the y-axis indicates the three partners.
+The dotted line shows the probability that breaking the promise would be zero.}\label{fig:fig3}
 \end{figure}
@@
 
-\caption{Posterior estimates in logit scale}\label{fig:fig4}
+\caption{Posterior estimates in logit scale.
+We show posteriors distributions of the hierarchical Bayesian model coefficients for the effect of experimental conditions on the decision to cooperate.
+The x-axis shows the magnitude of the logit scale coefficients, and the y-axis shows the experimental conditions associated with that effect.}\label{fig:fig4}
 \end{figure}
@@
 
-\caption{Posterior predictive over pay back rate}\label{fig:fig5}
+\caption{Posterior predictive over pay back rate.
+Correspondence between payment proportions and model predictions depending on the game partner for the first twelve subjects in the sample.
+The x-axis pointed the three playmates when the subjects had made a promise, while the y-axis indicates the proportion of decisions in which subjects payback.}\label{fig:fig5}
 \end{figure}
@@
 
-\caption{Posterior predictive over pay back rate, Social Closeness Varying effects by Promise levels}\label{fig:fig6}
+\caption{Posterior predictive over pay back rate, social closeness varying effects by promise levels.
+Correspondence between payment proportions and model predictions depending on the game partner at the group level.
+The x-axis pointed the three playmates when the subjects had made a promise, while the y-axis indicates the proportion of decisions in which subjects payback.}\label{fig:fig6}
 \end{figure}
@@
 
-\caption{Promise choices by group}\label{fig:fig7}
+\caption{Promise choices by group.
+We show posterior probability estimates regarding the level of promise depending on the group.
+The Low group (which paid 58/100 of the trials) is more likely to promise mostly, while the High group (which paid 83/100 of the trials) is more likely to promise always.}\label{fig:fig7}
 \end{figure}
@@
 we will discuss later, they use heterogeneous measures of social
-closeness (Glaeser et al. 2000). Our experiment is the first one to
-include a partner without social closeness (computer). Our data suggest
-that the mere fact of considering that subjects play with a human
-diminishes the probability of breaking the promise. It is more likely to
-break the promise to the computer than to the stranger, even though that
-partner was not known. Also, null social closeness is important because
-it allows us to explore the intrinsic motivation to keep the promises.
-If humans keep their word because it is morally correct, we would
-anticipate that the probability of breaking a promise was very low in
-the three partners and, particularly, the inference regarding the
+closeness (Glaeser et al. 2000). Our results suggest that the mere fact
+of considering that subjects play with a human diminishes the
+probability of breaking the promise. It is more likely to break the
+promise to the computer than to the stranger, even though that partner
+was not known. Also, zero social closeness is important to include
+because it allows us to explore the intrinsic motivation to keep the
+promises. If humans keep their word because it is morally correct, we
+would anticipate that the probability of breaking a promise was very low
+in the three partners and, particularly, the inference regarding the
 probability of breaking the promise to the computer would include zero.
 However, we found that, although low, the probability was greater than
-zero, which provides evidence that seems to contradict, at least in
-degree, the hypothesis of intrinsic motivation. We cannot exclude the
-possibility that the subjects keep promises mainly due to moral
-motivation because, even in the case of the computer, the subjects kept
-a large proportion. We can, however, exclude that this is their only
-motivation.
-
-On the other hand, high social closeness allows us to explore the
-instrumental motivation to keep promises (Baumgartner et al. 2009). In
-our study, it was more likely to break the promise to the stranger than
-to the friend. If humans keep their word to facilitate cooperation in
-the future, we would anticipate that with a partner of high social
-closeness (with whom they are very likely to cooperate, even after the
-experiment) there would be less of a chance to break the promise. In
-fact, the promise to friends was not broken on any occasion, hence the
-inference in this case, was met.
-
-The findings concerning motivations could be explained by the social
-norm called ``conditional cooperation'', which indicates that the belief
-that other people cooperate at high levels also induces high levels of
-cooperation (Fehr and Schurtenberger 2018). Thus, the lack of certainty
-regarding the decisions that the computer would make could explain the
-probability of breaking the promise that exists towards this partner.
-Similarly, the information that the subjects have regarding as their
-friend's behavior -even before the experiment- could explain the high
-levels of cooperation and keeping of promises towards this partner.
+zero, which provides evidence that seems to contradict, at least in some
+degree, the hypothesis of intrinsic motivation. This means that we
+cannot exclude the possibility that the subjects keep promises mainly
+due to moral motivation because, even in the case of the computer, the
+subjects kept a large proportion of promises. We can, however, exclude
+that this is their \emph{only} motivation.
+
+High social closeness allows us to explore the instrumental motivation
+to keep promises (Baumgartner et al. 2009). In our study, subjects were
+more likely to break the promise to the stranger than to the friend. If
+humans keep their word to facilitate cooperation in the future, we would
+anticipate that there would be less of a chance to break the promise
+with a partner of high social closeness (with whom they are very likely
+to cooperate, even after the experiment) and, in fact, the promise to
+friends was not broken on any occasion. The findings concerning
+motivations could be explained by the social norm called ``conditional
+cooperation'', which indicates that the belief that other people
+cooperate at high levels also induces high levels of cooperation (Fehr
+and Schurtenberger 2018). Thus, the uncertainty regarding the computer's
+decisions could explain the probability of breaking the promise.
+Similarly, the information that the subjects have regarding their
+friend's behavior, even before the experiment, could explain the high
+levels of cooperation and keeping of promises towards the friend.
 
 Cooperation has been studied with diverse experimental manipulations. In
-one study, the contribution in a public goods game was evaluated during
-several trials in a group made up of the same individuals (partners),
-and compared to another group of new different subjects for each trial
-(strangers) (Croson 1996). In the condition of partners the cooperation
-was greater because it is a stable group compared to the group of
-strangers. The mentioned study does not give details regarding the
-recruitment of participants, so we could assume that even in the
-condition of partners these are individuals who do not consider
-themselves socially close.
-
-Another study showed an increase in cooperation in a trust game when
-individuals were socially close (Glaeser et al. 2000). In this study,
-subjects knew each other and the researchers carefully measured several
-variables regarding their social connection.However, some individuals
-who arrived together were allowed to perform the task between themselves
-and others were paired with unclear criteria. The above allows social
-closeness between partners to be heterogeneous, allows for romantic
-relationships and assumes that two individuals who come together to
-class are considered close to each other. Also, since it is a study of
-one-shot, it excludes the possibility of evaluating how the same subject
-varies his behavior based on different levels of social closeness.
-
-To try to homogenize social closeness between our subjects and their
-partners, they performed the task with a same-sex friend considered to
-be close, emphasizing their companion could not be a romantic or sexual
-partner. Bayesian analysis of the IOS scale showed evidence in favor
-that the degree of social closeness between 30 of our 45 subjects and
-their friends was the same. Results of the two mentioned studies also
-found that social closeness enhance cooperation (Croson 1996; Glaeser et
-al. 2000), in the future would be valuable to homogenize both the
-performed tasks and the statistical procedure used, to establish
+one study, the contribution in a ``public goods game'' was evaluated
+during several trials in a group made up of the same individuals
+(partners), and compared to another group of new different subjects for
+each trial (strangers) (Croson 1996). In the condition of partners, the
+cooperation was greater because it was a stable group compared to the
+group of strangers. The mentioned study does not give details regarding
+the recruitment of participants, thus we could assume that even in the
+condition of partners these were individuals who did not consider
+themselves socially close. Another study showed an increase in
+cooperation in a trust game when individuals were socially close
+(Glaeser et al. 2000). In this study, subjects knew each other and the
+researchers carefully measured several variables regarding their social
+connection such as the number of friends in common and years of
+relationship. They found greater cooperation depending on the degree of
+social connection. However, the study did not control for social
+closeness as some individuals who arrived together were allowed to
+perform the task together whereas others were paired differently. This
+limitation allowed social closeness between partners to be
+heterogeneous, allowed for romantic relationships and assumed that two
+individuals who arrived together to class were considered close to each
+other. To try to homogenize social closeness between our subjects and
+their partners, they performed the task with a same-sex friend
+considered to be close, emphasizing their companion could not be a
+romantic or sexual partner. Bayesian analysis of the IOS scale showed
+evidence in favor that the degree of social closeness between 30 of our
+45 subjects and their friends was the same. Although results of the two
+mentioned studies also found that social closeness enhance cooperation
+(Croson 1996; Glaeser et al. 2000), it would be valuable to homogenize
+both the performed tasks and the statistical procedure used to establish
 similarity in effects magnitudes.
@@
 explicitly incorporate individual variability, among others (Vuorre and
-Bolger 2018; Gelman and Hill 2006; McElreath 2018; Bürkner 2017).
-
-In our case, the Hierarchical Model allowed us to capture how the
-experimental conditions affected the decisions of each subject and the
-differences between them. For example, there are obviously motivated
-instrumental subjects such as number 8 or 12 who are very sensitive to
-the identity of their investors and modify their cooperation under
-social closeness. At the same time, there were notably intrinsic
-subjects such as 9 and 10 who cooperate all the time regardless of who
-their partners are. The Hierarchical Model naturally includes this
-information for the estimation of population effects, which, if not
-considered, would lead to inaccurate inferences(Bürkner 2017; Gelman and
-Hill 2006; McElreath 2018).
-
-On the other hand, the Cumulative Model allowed us to capture the
-strength of the commitment expressed through promises. A very frequent
-problem that has been pointed out recently is that analyzing ordinal
-data with methods that assume that observations are metric can lead to
-serious inference errors (Liddell and Kruschke 2018). The Cumulative
-Models assumes that the observed responses come from the categorization
-of a continuous latent variable (Bürkner and Vuorre 2019). In our study,
-we could identify that groups with different payment proportions, which
-in other studies have been called ``dishonest'' and
-``honest''(Baumgartner et al. 2009; Baumgartner, Gianotti, and Knoch
-2013), differ in the commitment they express through their promises.
-Considering that the tools to perform the Cumulative Models are
-relatively recent, in future studies, it would be valuable to also use
-the new alternatives for inference.
-
-Although the Hierarchical and Cumulative models are not tools
+Bolger 2018; Gelman and Hill 2006; McElreath 2018; Bürkner 2017). In our
+case, the Hierarchical Model allowed us to capture how the experimental
+conditions affected the decisions of each subject and the differences
+between them. For example, there were obviously motivated instrumental
+subjects such as number 8 or 12 who are very sensitive to the identity
+of their investors and modify their cooperation under social closeness.
+At the same time, there were notably intrinsic subjects such as 9 and 10
+who cooperate all the time regardless of who their partners are. The
+Hierarchical Model naturally includes this information for the
+estimation of population effects, which, if not considered, would lead
+to inaccurate inferences (Bürkner 2017; Gelman and Hill 2006; McElreath
+2018). The Cumulative Model allowed us to capture the strength of the
+commitment expressed through promises. A very frequent problem that has
+been pointed out recently is that analyzing ordinal data with methods
+that assume that observations are metric can lead to serious inference
+errors (Liddell and Kruschke 2018). The Cumulative Models assumes that
+the observed responses come from the categorization of a continuous
+latent variable (Bürkner and Vuorre 2019). In our study, we could
+identify that groups with different payment proportions, which in other
+studies have been called ``dishonest'' and ``honest'' (Baumgartner et
+al. 2009; Baumgartner, Gianotti, and Knoch 2013), differ in the
+commitment they express through their promises. Considering that the
+tools to perform the Cumulative Models are relatively recent, in future
+studies, it would be valuable to also use the new alternatives for
+inference. Although the Hierarchical and Cumulative models are not tools
 exclusively for Bayesian inference, their application from this approach
@@
 
-A limitation of this paper is the use of hypothetical rewards compared
+A limitation of our study was the use of hypothetical rewards compared
 to real rewards. A relatively recent study on decision-making reported
@@
 same direction as other works that use real money (Croson 1996; Glaeser
-et al. 2000), thus, there are not many reasons to expect that other
+et al. 2000). Thus, there are not many reasons to expect that other
 types of rewards would modify our results. Another possible limitation
-is the use of multiple trials with each partner. Although the decision
-to use repeated measures during our design serves more the purpose of
-reducing contaminant sources and increasing internal validity (Maxwell,
-Delaney, and Ken 2018), to have more clarity regarding the difference in
-the intrinsic and instrumental motivations, the studies could benefit
-from only include one trial for each partner. Play a one-shot with each
-partner avoids the possibility that multiple trials could generate the
-belief that the computer can also vary its behavior according to the
-decisions of the trustee. Finally, subjects that performed the study
-inside the MRI scanner may differ in their responses than subjects
-outside of the scanner. However, our analysis did not show this
-explicitly.
+could be the use of multiple trials with each partner. Although the
+decision to use repeated measures during our design serves the purpose
+of reducing contaminant sources and increasing internal validity
+(Maxwell, Delaney, and Ken 2018), the studies could benefit from only
+including one trial for each partner to have more clarity regarding the
+difference in the intrinsic and instrumental motivations. Play a
+one-shot with each partner avoids the possibility that multiple trials
+could generate the belief that the computer can also vary its behavior
+according to the decisions of the trustee.
 
@@
 
-Subjects seem to keep their promises by a combination of
-\emph{intrinsic} and \emph{instrumental} motivations. They are
-predominantly ``nice people'' because they keep their word even with
-investors with no social closeness. However, their trustworthiness is
-far from perfect, since there is a small proportion of betrayals
-committed towards this partner. It seems that if subjects cannot be sure
-their investor will be a ``potential cooperator'', dishonesty may emerge
-in the form of broken promises. Framing the finding in terms of the
-theoretical predictions of the social norm ``conditional cooperation'',
-social closeness decreases the probability of breaking the promise and
-increases cooperation, and suggests the correspondence between
-commitment expressed through promises and subsequent behavior.
+Subjects in our study seemed to keep their promises by a combination of
+\emph{intrinsic} and \emph{instrumental} motivations. They can be
+regarded as predominantly ``nice people'' because they kept their word
+even with investors with no social closeness (computer). However, their
+trustworthiness was far from perfect, since there was a small proportion
+of betrayals committed towards the computer. If subjects could not be
+sure their investor would be a ``potential cooperator'', dishonesty may
+have emerged in the form of broken promises. Framing our findings in
+terms of the theoretical predictions of the social norm ``conditional
+cooperation'', social closeness decreases the probability of breaking
+the promise and increases cooperation, and suggests the correspondence
+between commitment expressed through promises and subsequent behavior.
 

### 2019-08-14 behavioral-promises/behavioral-promises.tex
Relax margin
.

@@
+\AtBeginDocument{%
+  \paperwidth=\dimexpr
+    1in + \oddsidemargin
+    + \textwidth
+    % + \marginparsep + \marginparwidth
+    + 1in + \oddsidemargin
+  \relax
+  \paperheight=\dimexpr
+    1in + \topmargin
+    + \headheight + \headsep
+    + \textheight
+    % + \footskip
+    + 1in + \topmargin
+  \relax
+  \usepackage[pass]{geometry}\relax
+}
+
 % !TeX program = pdfLaTeX
@@
      \email{\href{mailto:egarza@gmail.com}{\nolinkurl{egarza@gmail.com}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
+    }
 
@@
   participants keep the promises to the computer, evidence would be
-  given in favor of intrinsic motivation.
+  given in favor of intrinsic motivation (Pre-registered hypothesis is available
+here: \url{https://osf.io/53jqr}).
 \end{enumerate}
@@
 the \(\hat{R}\) statistic, which for all parameters was 1, that can be
-interpreted as convergence. Vaguely informative prior distributions were
-used for the parameters of interest in the models, which allows the data
-to dominate the inference, also assumes as little as possible regarding
-the nature of the phenomenon, which could be adequate for the current
-state of evidence in the problem we are studying (McElreath 2018).
+interpreted as convergence (All data and R scripts are available at 
+\url{https://github.com/saidejp/motivations-promises}. Vaguely informative 
+prior distributions were used for the parameters of interest in 
+the models, which allows the data to dominate the inference, also assumes as
+little as possible regarding the nature of the phenomenon, which could be 
+adequate for the current state of evidence in the problem 
+we are studying (McElreath 2018).
 
